### 2019-04-11 190410_Paper_ACPR/ver0.tex
advp a1: final

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
%\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}

\subsection{Motivation}
i. Pros of In-Air WIFI CSI signature system
1) Cheap: Use commercial device
2) Easy: No additional devices is needed
3) Secure: Hard to forgery
ii. Cons of In-Air WIFI CSI signature system
1) Setting direction problem
a) Different direction -> Different feature is needed
b) Hard to set exactly same direction as authentication before
Size of signature can varies

\subsection{Contribution}
- Overcome cons of WIFI signature system
- Robust to signal direction, size

\section{Related Works}
a. WIFI CSI
b. Siamese Networks

\subsection{WIFI CSI}
- An In-Air Signature Verification System Using Wi-Fi Signals 
\subsection{Siamese Networks}
i. Signature Verification using a "Siamese" Time Delay Neural Network
Siamese Neural Networks for One-Shot Image Recognition

\section{Proposed System}
\subsection{Data Acquisition and Preprocessing}
Gathering CSI signal, Make CSI Image
\subsection{Siamese Network For Verification}
i. Feature Extraction
- Symmetric CNN Architecture
® Symetric : Share Weights
◊ To extract the same characteristics from signals in different directions.
® CNN: Feature Extractor
◊ Automatically extract feature vector from CSI image
ii. Feature Matching
Use L1 distances of Feature vector of 2 input images

\section{Experiments}
\section{Conclusion}

\section{*** Template ***}
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2019-04-11 190401_AdvP_A1/vector/vector.h

@@ -91,7 +91,7 @@ typename vector_t<T>::iterator vector_t<T>::insert(const iterator &it, const T &
     /* Assignment */
     
     //get array index number of the iterator
-    int index = it.ptr - array;
+    size_t index = it.ptr - array;
     
     // Double up the array when full
     if(num_elements == array_size) {
@@ -111,7 +111,9 @@ typename vector_t<T>::iterator vector_t<T>::insert(const iterator &it, const T &
     // shift array elements
     for(size_t j=num_elements; j != index ; --j)
     {
+        // erase array elements in shifting position
         array[j].~T();
+        // shift array elements to right
         new(&array[j]) T(array[j-1]);
     }
     
@@ -119,7 +121,8 @@ typename vector_t<T>::iterator vector_t<T>::insert(const iterator &it, const T &
     new(&array[index]) T(t);
     // increment number of elements
     num_elements ++; 
-
+    // return iterator pointing to the inserted element
+    return iterator(&array[index]);
 }
 
 // Erase
@@ -127,37 +130,23 @@ template <typename T>
 typename vector_t<T>::iterator vector_t<T>::erase(const iterator &it) {
 
     /* Assignment */
-    /*
-    size_t i;
-    for(i=0; &array[i]<it.ptr;i++);
-    num_elements--;
-    //shift
-    for(size_t j=i;j<num_elements;j++){
-        array[j].~T();
-        new(&array)
-        ...
-    }
-    */
     
     //get array index number of the iterator
-    int index = it.ptr - array;
-    
+    int index = it.ptr - array;    
 
     // shift array elements
     for(size_t j=index; j != num_elements-1 ; ++j)
     {
+        // erase array elements in shifting position
         array[j].~T();
+        // shift array elements to left
         new(&array[j]) T(array[j+1]);
     }
     //delete last element
     pop_back();
     
-    // decrement number of elements
-    //num_elements --;
-
     //set pointer of the iterator to next of removed one
-    //it.ptr++; 
-    
+    return iterator(&array[index+1]);
 }
 
 // Reserve

### 2019-04-12 190412_AdvP_A2/dft_pthread/complex.cc
AdvP_A2

@@ -1,0 +1,57 @@
+#include <cmath>
+#include "complex.h"
+
+using namespace std;
+
+// Constructors
+complex_t::complex_t() :
+    re(0.0),
+    im(0.0) {
+}
+
+complex_t::complex_t(float m_re, float m_im) :
+    re(m_re),
+    im(m_im) {
+}
+
+// Copy constructor
+complex_t::complex_t(const complex_t &c) :
+    re(c.re),
+    im(c.im) {
+}
+
+// Destructor
+complex_t::~complex_t() {
+}
+
+// Operators
+complex_t complex_t::operator+(const complex_t &c) const {
+    return complex_t(re + c.re, im + c.im);
+}
+
+complex_t complex_t::operator-(const complex_t &c) const {
+    return complex_t(re - c.re, im - c.im);
+}
+
+complex_t complex_t::operator*(const complex_t &c) const {
+    return complex_t(re*c.re - im*c.im, re*c.im + im*c.re);
+}
+
+complex_t complex_t::operator/(const complex_t &c) const {
+    complex_t dividend = (*this) * c.conjugate();
+    complex_t divisor  = c.magnitude() * c.magnitude();
+    return complex_t(dividend.re / divisor.re, dividend.im / divisor.re);
+}
+
+complex_t complex_t::magnitude() const {
+    return complex_t(sqrt(re * re + im * im), 0.0);
+}
+
+complex_t complex_t::conjugate() const {
+    return complex_t(re, -im);
+}
+
+void complex_t::print() const {
+    cout << "(" << re << ", " << im << ")";
+}
+

### 2019-04-12 190412_AdvP_A2/dft_pthread/dft.cc

@@ -1,0 +1,64 @@
+#include <assert.h>
+#include <cmath>
+#include <cstdlib>
+#include <cstring>
+#include <pthread.h>
+#include "dft.h"
+
+using namespace std;
+
+// Custom thread exit function.
+void thread_exit() {
+    // Use pthread mutex and condition variables to exit the child function,
+    // and signal the parent thread that this thread is done.
+    /* Assignment */
+}
+
+// Custom thread join function.
+void thread_join() {
+    // Use pthread mutex and condition variables to wait until all children
+    // threads complete their executions.
+    /* Assignment */
+}
+
+// Perform 1-D DFT.
+void dft1d(complex_t *h, const unsigned N) {
+    // Use Cooley-Tuckey algorithm to perform row-wise 1-D DFT.
+    // Step 1: The elements of row input, h, have to be first hashed in the
+    //         bit-reversed order.
+    // Step 2: Follow Danielson-Lanczos Lemma to perform the DFT.
+    /* Assignment */
+}
+
+// 1-D DFT Thread function
+void* dft_thread(void *arg) {
+    // This thread function calls dft1d() function above for data rows.
+    // Each thread performs 1-D DFT for height/num_threads number of rows.
+    /* Assignment */
+
+    return 0;
+}
+
+// Perform 2-D DFT.
+void dft2d() {
+    // Perform 2-D DFT with the data.
+    // Step 1: Pre-calculate weight values to avoid the repeated calculations
+    //         of the weight. Apparently, the pre-calculation is traded width
+    //         extra memory usage.
+    // Step 2: Initialize pthread-related variables, e.g., mutex and cond
+    //         variables, as well as other necessary parameters.
+    // Step 3: Create threads to run dft_thread() for row-wise DFTs.
+    // Step 4: Call thread_join() to wait for all threads to complete.
+    //         Do not use pthread_join().
+    // Step 5: Transpose the data matrix so that column-wise DFT can be
+    //         performed by the same row-wise DFT function.
+    // Step 6: Create threads to run dft_thread() for row-wise DFTs.
+    //         It is actually column-wise DFT after transpose.
+    // Step 7: Call thread_join() to wait for all threads to complete.
+    //         Do not use pthread_join().
+    // Step 8: Transpose the data matrix back to the original orientation.
+    // Step 9: Destroy pthread-related variables.
+    // Step 10: Deallocated heap memory blocks if any.
+    /* Assignment */
+}
+

### 2019-04-12 190412_AdvP_A2/dft_pthread/dft.h

@@ -1,0 +1,20 @@
+#ifndef __DFT_H__
+#define __DFT_H__
+
+#include "complex.h"
+#include "file_handler.h"
+
+// Perform 2-D DFT.
+void dft2d();
+
+// File handler
+extern file_handler_t file_handler;
+// Number of threads
+extern unsigned num_threads;
+// Data to perform DFT.
+extern complex_t *data;
+// Data dimension
+extern unsigned width, height;
+
+#endif
+

### 2019-04-12 190412_AdvP_A2/dft_pthread/file_handler.h

@@ -1,0 +1,19 @@
+#ifndef __FILE_HANDLER_H__
+#define __FILE_HANDLER_H__
+
+#include <cstring>
+#include "complex.h"
+
+class file_handler_t {
+public:
+    file_handler_t();                               // Constructor
+    ~file_handler_t();                              // Destructor
+
+    void read_data(const std::string m_file_name,   // Read data from a file
+                   complex_t *&m_data, unsigned &m_width, unsigned &m_height);
+    void save_data(const std::string m_file_name,   // Save data to a file
+                   complex_t *m_data, unsigned m_width, unsigned m_height);
+};
+
+#endif
+

### 2019-04-12 190412_AdvP_A2/dft_pthread/main.cc

@@ -1,0 +1,50 @@
+#include <cstdlib>
+#include <stdio.h>
+#include "complex.h"
+#include "dft.h"
+#include "file_handler.h"
+
+using namespace std;
+
+file_handler_t file_handler;        // File handler
+unsigned num_threads = 0;           // Number of threads
+complex_t *data = 0;                // Data to perform DFT
+unsigned width = 0, height = 0;     // Data dimension
+
+int main(int argc, char **argv) {
+    // Print usage message.
+    if(argc != 2) {
+        cerr << "Usage: " << argv[0] << " [num_threads]" << endl;
+        exit(1);
+    }
+
+    // Get number of threads.
+    num_threads = unsigned(atoi(argv[1]));
+
+    unsigned val = num_threads;
+    // Max num_threads is 1024.
+    if(val > 1024) {
+        cerr << "Error: too many threads" << endl;
+        exit(1);
+    }
+    // Check if num_threads is power of two.
+    while(!(val%2)) { val = val >> 1; }
+    if(val != 1) {
+        cerr << "Error: num_threads must be a power of two." << endl;
+        exit(1);
+    }
+
+    // Load input data file a file.
+    file_handler.read_data("input.txt", data, width, height);
+
+    // Perform 2-D DFT.
+    dft2d();
+
+    // Save the result to a file.
+    file_handler.save_data("output-2d.txt", data, width, height);
+
+    // Deallocate data.
+    delete [] data;
+
+    return 0;
+}

### 2019-04-17 190410_Paper_ACPR/paper_v0.tex
latex: setting

--- 2019-04-11 190410_Paper_ACPR/ver0.tex
@@
 %
-%\usepackage{graphicx}
+\usepackage{graphicx}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal\thanks{Supported by organization x.}}
+\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal}
 %
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Young Woong KWON\inst{1} \and
+JooYoung KIM\inst{1} \and
+Kar-Ann TOH\inst{1}}
 %
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+\institute{Yonsei University \and
 \email{lncs@springer.com}\\
@@
 \subsection{Data Acquisition and Preprocessing}
-Gathering CSI signal, Make CSI Image
+In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
+An overview of the proposed scheme is shown in Fig.1.
+\begin{figure}
+\includegraphics[width=\textwidth]{methods1.eps}
+\caption{...} \label{method1}
+\end{figure}
+
+ Two preprocessed signals enter the Siamese network and the network 
+extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
+ The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
+the network is learned by the back-propagation.
+
+The main purpose of this system is to receive two csi signals as input, to determine if the two signals are the same signature.
+Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
+
+In order to be used as an input to a siamese network, the data must be pre-processed.
+
+First, the signal have to converted to non-complex form.
+Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase[ref] we used absolute of signal only.
+
+Second, all inputs must be arranged of same size.
+Since all signals have different length, the gradient operation with respect to the time instance is adopted to measure the short time energy. 
+Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
+And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data.
+
 \subsection{Siamese Network For Verification}
-i. Feature Extraction
-- Symmetric CNN Architecture
-® Symetric : Share Weights
-◊ To extract the same characteristics from signals in different directions.
-® CNN: Feature Extractor
-◊ Automatically extract feature vector from CSI image
-ii. Feature Matching
-Use L1 distances of Feature vector of 2 input images
+The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output.
+
+Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
+To classify regardless of the direction of the signal, the model shall be capable of extracting features unrelated to the direction.
+\subsection{Feature Extraction}
+When two processed signals come as the input, they are put to 2 symmetric CNN network.
+
+Purpose of CNN is to extract features from signal.
+By sharing their feature map, this CNN networks is trainin to learn characteristics regardless of the direction only.
+
+To perform the feature extraction, we firstly need to have a convolutional neural networks  to serve as the feature extractor
+Based on the ConvNet structure [17] the feature extractor of the proposed pretraining model consists of i convolution layers and activation functions followed by i max-pooling layers.
+Each convolution layer has f∗ filters to be trained, where ∗ = 1, ..., i.
+In a similar manner, j fully connected layers constitute the classifier of pretraining model where each layer has g•,(•=1,...,j) neurons to be trained.
+
+\subsection{Feature Matching}
+Output of the CNN are feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
+In the proposed system, this Euclidean distance is utilized to match between two feature vectors.
+
+\subsection{Loss and Backpropagation}
+ We impose a regularized cross-entropy objective on our binary classifier.
+This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
+ We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2.
+Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
+\begin{figure}
+\includegraphics[width=\textwidth]{network1.eps}
+\caption{...} \label{network1}
+\end{figure}
 

### 2019-04-17 190412_AdvP_A2/dft_pthread/dft.cc

@@ -60,5 +60,21 @@ void dft2d() {
     // Step 9: Destroy pthread-related variables.
     // Step 10: Deallocated heap memory blocks if any.
     /* Assignment */
+
+    // Step1: Pre-Calc
+    cout << "Step1" << endl;
+    // Allocate data.
+    unsigned N = 1024;
+    complex_t *w_data[N];
+    // Pre-Calc Weights.
+    for(unsigned r = 0; r < N; r++) {      // Rows
+        complex_t *w_val = new complex_t(cos(2*M_PI/N), -1 * sin(2*M_PI/N));
+        new (&w_data[r]) complex_t &w_val; 
+    }
+    //cout << "wdata[0].re:"<< &w_data[0].re << endl;
+    //cout << "wdata[0].im:"<< &w_data[0].im << endl;
+    //cout << "wdata[N-1].re:"<< &w_data[N-1].re << endl;
+    //cout << "wdata[N-1].im:"<< &w_data[N-1].im << endl;
+    
 }
 

### 2019-04-17 190410_Paper_ACPR/paper_v0.tex
paper:methods

@@
 - An In-Air Signature Verification System Using Wi-Fi Signals
-\subsection{Siamese Networks}
-i. Signature Verification using a "Siamese" Time Delay Neural Network
-Siamese Neural Networks for One-Shot Image Recognition
 
@@
 And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data. 
+% Methods
 
 \subsection{Siamese Network For Verification}
+Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem (Bromley et al., 1993)
+Siamese neural networks employ a unique structure to naturally rank similarity between inputs.[1] 
+It can discriminate between the class-identity of image pairs[1]
+The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.[1]
+
 The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output.
@@
 
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{mybibliography}
+%
+\begin{thebibliography}{8}
+\bibitem{ref_article1}
+Koch, Gregory, Richard Zemel, and Ruslan Salakhutdinov.
+ "Siamese neural networks for one-shot image recognition." 
+ ICML deep learning workshop. Vol. 2. 2015.
+
+\end{thebibliography}
+\end{document}
+
+%% Template End
 \section{*** Template ***}

### 2019-04-27 190412_AdvP_A2/dft_pthread/dft.cc
AdvP_A2: making pthread

@@ -29,6 +29,7 @@ void dft1d(complex_t *h, complex_t *w, const unsigned N) {
     //         bit-reversed order.
     // Step 2: Follow Danielson-Lanczos Lemma to perform the DFT.
     /* Assignment */
+
     //block
     for(int r = 0; r < int(1024*1024/N) ; r++)
     {
@@ -36,13 +37,6 @@ void dft1d(complex_t *h, complex_t *w, const unsigned N) {
         //calc
         for(int k=0; k < int(N/2); k++)
         {
-            //dft_calc2(&h[n_start+k],&h[n_start+k + int(N/2)],w[k*int(1024/2)]);
-            //complex_t h1 = h[n_start+k];
-            //complex_t h2 = h[n_start+k + int(N/2)];
-            //complex_t w_val = w[k*int(1024/2)];
-            
-            //complex_t h1_new = h[n_start+k] + w[k*int(1024/2)] * h[n_start+k + int(N/2)];
-            //complex_t h2_new = h[n_start+k] - w[k*int(1024/2)] * h[n_start+k + int(N/2)];
             complex_t h1_new, h2_new, wval;
 
             int w_num = k*int(1024/N);
@@ -51,13 +45,9 @@ void dft1d(complex_t *h, complex_t *w, const unsigned N) {
 
             h1_new = h[n_start+k] + wval * h[n_start+k + int(N/2)];
             h2_new = h[n_start+k] - wval * h[n_start+k + int(N/2)];
-            
-            //h1_new = new complex_t *(h[n_start+k] + w[k*int(1024/2)] * h[n_start+k + int(N/2)]);
-            //h2_new = new complex_t *(h[n_start+k] - w[k*int(1024/2)] * h[n_start+k + int(N/2)])
 
             h[n_start+k] = h1_new;
             h[n_start+k + int(N/2)] = h2_new;
-
         }
     }
 
@@ -69,11 +59,27 @@ void* dft_thread(void *arg) {
     // Each thread performs 1-D DFT for height/num_threads number of rows.
     /* Assignment */
 
-    // beginning of critical section
-    // pthread_mutex_lock(&lock);
-    // use condition var to wait turn
-    
+    //cast and dereference the input argument.
+    unsigned tid = * (unsigned*) arg;
 
+    //beginning of the critical section
+    pthread_mutex_lock(&lock);
+    //use condition variable to wait for thread's turn.
+    while(tid > turn)
+    {
[…]

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
AdvP_a2: making thrad

@@ -6,48 +6,60 @@
 #include "dft.h"
 
 using namespace std;
+        
+
+unsigned sum = 0;
+unsigned turn  = 0;
+pthread_mutex_t lock;
+pthread_cond_t cond;
+//make w array
+complex_t *w_arr = (complex_t*)malloc(width * sizeof(complex_t));
 
 // Custom thread exit function.
-void thread_exit() {
+
+//void thread_exit() {
     // Use pthread mutex and condition variables to exit the child function,
     // and signal the parent thread that this thread is done.
     /* Assignment */
-}
+//}
 
 // Custom thread join function.
-void thread_join() {
+//void thread_join() {
     // Use pthread mutex and condition variables to wait until all children
     // threads complete their executions.
     /* Assignment */
-}
+//}
+
 
 
 // Perform 1-D DFT.
-void dft1d(complex_t *h, complex_t *w, const unsigned N) {
+void dft1d(complex_t *h, const unsigned N) {
     // Use Cooley-Tuckey algorithm to perform row-wise 1-D DFT.
     // Step 1: The elements of row input, h, have to be first hashed in the
     //         bit-reversed order.
     // Step 2: Follow Danielson-Lanczos Lemma to perform the DFT.
     /* Assignment */
+    
 
+    // Step 2
     //block
-    for(int r = 0; r < int(1024*1024/N) ; r++)
+    for(int r = 0; r < int(width*(height/num_threads)/N) ; r++)
     {
-        int n_start = N*r;
+        //int n_start = 1024*1024*(tid/num_threads)*(r/N);
         //calc
         for(int k=0; k < int(N/2); k++)
         {
             complex_t h1_new, h2_new, wval;
 
             int w_num = k*int(1024/N);
-            if(w_num > 512) wval = complex_t(-1.0,0.0) * w[w_num-512];
-            else wval = w[w_num];
+            if(w_num >= 512) wval =  complex_t(-1.0,0.0) * w_arr[w_num-512];
+            else wval = w_arr[w_num];
 
-            h1_new = h[n_start+k] + wval * h[n_start+k + int(N/2)];
-            h2_new = h[n_start+k] - wval * h[n_start+k + int(N/2)];
+            h1_new = h[r*N+k] + wval * h[r*N+k + int(N/2)];
+            h2_new = h[r*N+k] - wval * h[r*N+k + int(N/2)];
 
-            h[n_start+k] = h1_new;
-            h[n_start+k + int(N/2)] = h2_new;
[…]

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
AdvP_a2: thread test

@@ -40,7 +40,7 @@ void dft1d(complex_t *h, const unsigned N) {
     // Step 2: Follow Danielson-Lanczos Lemma to perform the DFT.
     /* Assignment */
     
-
+    printf("h[5]: %f\n",h[5].re);
     // Step 2
     //block
     for(int r = 0; r < int(width*(height/num_threads)/N) ; r++)
@@ -58,8 +58,15 @@ void dft1d(complex_t *h, const unsigned N) {
             h1_new = h[r*N+k] + wval * h[r*N+k + int(N/2)];
             h2_new = h[r*N+k] - wval * h[r*N+k + int(N/2)];
 
-            h[r*N+k] = h1_new;
-            h[r*N+k + int(N/2)] = h2_new;
+//            h[r*N+k] = h1_new;
+//            h[r*N+k + int(N/2)] = h2_new;
+
+            h[r*N+k].~complex_t();
+            new (&h[r*N+k]) complex_t(h1_new);
+            h[r*N+k + int(N/2)].~complex_t();
+            new (&h[r*N+k + int(N/2)]) complex_t(h2_new);
+
+
         }
     }
 
@@ -89,6 +96,9 @@ void* dft_thread(void *arg) {
     //dft calc
 
     int n_start = width*(height/num_threads)*tid;
+            
+    printf("tid: %d\n",tid);
+    printf("n_st: %d\n",n_start);
     for(int p=1; p<=10; p++)
     {
         dft1d(&data[n_start],pow(2,p));
@@ -143,7 +153,7 @@ void dft2d() {
     complex_t *old_data = data;
     data = new complex_t[width * height];
     
-    for(unsigned row=0; row<height/num_threads; row++) // Do it for every row
+    for(unsigned row=0; row<height; row++) // Do it for every row
     {
         for(unsigned r=0; r<width; r++) // do it for every value
         {

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
AdvP_a2: thread test1

@@ -41,6 +41,7 @@ void dft1d(complex_t *h, const unsigned N) {
     /* Assignment */
     
     printf("h[5]: %f\n",h[5].re);
+    printf("N: %d\n",N);
     // Step 2
     //block
     for(int r = 0; r < int(width*(height/num_threads)/N) ; r++)

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
AdvP a2: done join

@@ -7,28 +7,46 @@
 
 using namespace std;
         
-
-unsigned sum = 0;
 unsigned turn  = 0;
+unsigned running = 0;
 pthread_mutex_t lock;
 pthread_cond_t cond;
+pthread_mutex_t lock_join;
+pthread_cond_t cond_join;
+
 //make w array
 complex_t *w_arr = (complex_t*)malloc(width * sizeof(complex_t));
 
-// Custom thread exit function.
-
-//void thread_exit() {
+void thread_exit() {
     // Use pthread mutex and condition variables to exit the child function,
     // and signal the parent thread that this thread is done.
     /* Assignment */
-//}
+    
+    pthread_mutex_lock(&lock_join); //beginning of the critical section
+    running = 0; // condition variable to check whether this thread is running
+    pthread_cond_broadcast(&cond_join); //signal the parent thread that this thread is done
+    pthread_mutex_unlock(&lock_join); //ending of the critical section
+
+}
 
 // Custom thread join function.
-//void thread_join() {
+void thread_join() {
     // Use pthread mutex and condition variables to wait until all children
     // threads complete their executions.
     /* Assignment */
-//}
+    //beginning of the critical section
+    //pthread_mutex_lock(&lock);
+    //printf("thread join\n");
+
+    //beginning of the critical section
+    pthread_mutex_lock(&lock_join);
+    //use condition variable to wait for thread's turn.
+    while(running == 1)
+    {
+        pthread_cond_wait(&cond_join, &lock_join);
+    }    
+    pthread_mutex_unlock(&lock_join);
+}
 
 
 
@@ -40,8 +58,8 @@ void dft1d(complex_t *h, const unsigned N) {
     // Step 2: Follow Danielson-Lanczos Lemma to perform the DFT.
     /* Assignment */
     
-    printf("h[5]: %f\n",h[5].re);
-    printf("N: %d\n",N);
+    //printf("h[5]: %f\n",h[5].re);
+    //printf("N: %d\n",N);
     // Step 2
     //block
     for(int r = 0; r < int(width*(height/num_threads)/N) ; r++)
@@ -85,6 +103,7 @@ void* dft_thread(void *arg) {
 
     //beginning of the critical section
     pthread_mutex_lock(&lock);
+    running=1;
     //use condition variable to wait for thread's turn.
     while(tid > turn)
     {
@@ -98,8 +117,8 @@ void* dft_thread(void *arg) {
 
[…]

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
AdvP_a2: ver1

@@ -60,32 +60,66 @@ void dft1d(complex_t *h, const unsigned N) {
     
     //printf("h[5]: %f\n",h[5].re);
     //printf("N: %d\n",N);
+
+    // Step 1
+    //cout << "DFT:Step1: Shuffle inputs to binary order" << endl;
+    //make new data array
+    complex_t *dft_data;
+    dft_data = new complex_t[width * height/num_threads];
+    
+    for(unsigned row=0; row<height/num_threads; row++) // Do it for every row
+    {
+        for(unsigned r=0; r<width; r++) // do it for every value
+        {
+            //calc shuffle order
+            int quo_2 = r;
+            int rem_2 = 0;
+            int new_ind = 0;
+            for(int k = int(log2(width))-1; k>=0 ; k--)
+            {
+                rem_2 = quo_2 % 2;
+                quo_2 = int(quo_2 / 2);
+                new_ind += pow(2,k) * rem_2;
+            }
+            //put reordered data to array
+            new (&dft_data[height*row + new_ind]) complex_t(h[height*row + r]);
+            //dft_data[height*row + new_ind] = h[height*row + r];
+            //old_data[height*row + r].~complex_t();
+        }
+    }
+
     // Step 2
     //block
-    for(int r = 0; r < int(width*(height/num_threads)/N) ; r++)
+    for(int p=1; p<=int(log2(N)); p++)
     {
-        //int n_start = 1024*1024*(tid/num_threads)*(r/N);
-        //calc
-        for(int k=0; k < int(N/2); k++)
-        {
-            complex_t h1_new, h2_new, wval;
+        int size = pow(2,p);
+            for(int r = 0; r < int(width*(height/num_threads)/size) ; r++)
+            {
+            //int n_start = 1024*1024*(tid/num_threads)*(r/N);
+            //calc
+            for(int k=0; k < int(size/2); k++)
+            {
+                complex_t h1_new, h2_new, wval;
 
-            int w_num = k*int(1024/N);
-            if(w_num >= 512) wval =  complex_t(-1.0,0.0) * w_arr[w_num-512];
-            else wval = w_arr[w_num];
+                int w_num = k*int(1024/size);
+                if(w_num >= 512) wval =  complex_t(-1.0,0.0) * w_arr[w_num-512];
+                else wval = w_arr[w_num];
 
[…]

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
advp_a2: debug linux

@@ -4,7 +4,7 @@
 #include <cstring>
 #include <pthread.h>
 #include "dft.h"
-
+#include <stdio.h>
 using namespace std;
         
 unsigned turn  = 0;
@@ -260,12 +260,12 @@ void dft2d() {
     }
     
     // deallocate pthreads.
-    //delete [] threads;
-    //delete [] tid;
+    delete [] threads;
+    delete [] tid;
 
     // destroy mutex lock
-    //assert(!pthread_mutex_destroy(&lock));
-    //assert(!pthread_cond_destroy(&cond));
+    assert(!pthread_mutex_destroy(&lock));
+    assert(!pthread_cond_destroy(&cond));
     
     cout << "Step 5: Transpose the data matrix so that column-wise DFT can be performed" << endl;
     

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: fix join

@@ -8,7 +8,7 @@
 using namespace std;
         
 unsigned turn  = 0;
-unsigned running = 0;
+unsigned running = 1;
 pthread_mutex_t lock;
 pthread_cond_t cond;
 pthread_mutex_t lock_join;
@@ -43,8 +43,10 @@ void thread_join() {
     //use condition variable to wait for thread's turn.
     while(running == 1)
     {
+        printf("run 1\n");
         pthread_cond_wait(&cond_join, &lock_join);
     }    
+    printf("run 0\n");
     pthread_mutex_unlock(&lock_join);
 }
 
@@ -166,13 +168,13 @@ void* dft_thread(void *arg) {
 
     //printf() is in the critical section only for demonstration purpose.
     printf("thread %d:\n",tid);
-    thread_exit();
+
 
     //wake up all other threads to check if they are the next one to go.
     pthread_cond_broadcast(&cond);
     pthread_mutex_unlock(&lock);
     
-    
+    thread_exit();
     return 0;
     
 }
@@ -258,7 +260,7 @@ void dft2d() {
         thread_join();
         printf("thread %u done\n",t);
     }
-    
+    /*
     // deallocate pthreads.
     delete [] threads;
     delete [] tid;
@@ -266,7 +268,7 @@ void dft2d() {
     // destroy mutex lock
     assert(!pthread_mutex_destroy(&lock));
     assert(!pthread_cond_destroy(&cond));
-    
+    */
     cout << "Step 5: Transpose the data matrix so that column-wise DFT can be performed" << endl;
     
     //transpose array

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: ver2

@@ -8,15 +8,17 @@
 using namespace std;
         
 unsigned turn  = 0;
-unsigned running = 1;
+unsigned running = 0;
 pthread_mutex_t lock;
 pthread_cond_t cond;
 pthread_mutex_t lock_join;
 pthread_cond_t cond_join;
 
 //make w array
-complex_t *w_arr = (complex_t*)malloc(width * sizeof(complex_t));
+complex_t *w_arr = (complex_t*)malloc(511 * sizeof(complex_t));
 
+
+            
 void thread_exit() {
     // Use pthread mutex and condition variables to exit the child function,
     // and signal the parent thread that this thread is done.
@@ -43,10 +45,8 @@ void thread_join() {
     //use condition variable to wait for thread's turn.
     while(running == 1)
     {
-        printf("run 1\n");
         pthread_cond_wait(&cond_join, &lock_join);
     }    
-    printf("run 0\n");
     pthread_mutex_unlock(&lock_join);
 }
 
@@ -89,7 +89,7 @@ void dft1d(complex_t *h, const unsigned N) {
             //old_data[height*row + r].~complex_t();
         }
     }
-
+    
     // Step 2
     //block
     for(int p=1; p<=int(log2(N)); p++)
@@ -114,17 +114,17 @@ void dft1d(complex_t *h, const unsigned N) {
                 dft_data[r*size+k + int(size/2)] = h2_new;
                 h[r*size+k] = h1_new;
                 h[r*size+k + int(size/2)] = h2_new;
-/*
-                h[r*N+k].~complex_t();
-                new (&h[r*N+k]) complex_t(h1_new);
-                h[r*N+k + int(N/2)].~complex_t();
-                new (&h[r*N+k + int(N/2)]) complex_t(h2_new);
-*/
+
+                //h[r*N+k].~complex_t();
+                //new (&h[r*N+k]) complex_t(h1_new);
+                //h[r*N+k + int(N/2)].~complex_t();
+                //new (&h[r*N+k + int(N/2)]) complex_t(h2_new);
+
 
             }
         }
     }
-
+   
 }
 
 // 1-D DFT Thread function
@@ -202,40 +202,15 @@ void dft2d() {
     /* Assignment */
 
     cout << "Step1-1: Pre-Calc Weight" << endl;
-
     
-    for(unsigned r = 0; r < width/2-1; r++) //Loop for N/2-1 times
+    for(unsigned r = 0; r < unsigned(width/2-1); r++) //Loop for N/2-1 times
     {
[…]

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: v2_1

@@ -15,7 +15,7 @@ pthread_mutex_t lock_join;
 pthread_cond_t cond_join;
 
 //make w array
-complex_t *w_arr = (complex_t*)malloc(511 * sizeof(complex_t));
+complex_t *w_arr = (complex_t*)malloc(512 * sizeof(complex_t));
 
 
             

### 2019-04-28 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: working join

@@ -146,22 +146,11 @@ void* dft_thread(void *arg) {
         pthread_cond_wait(&cond, &lock);
     }    
 
-    //accumulate thread ID values
-    //sum += tid;
 
     //dft calc
-
     int n_start = width*(height/num_threads)*tid;
-            
-    //printf("tid: %d\n",tid);
-    //printf("n_st: %d\n",n_start);
-    /*
-    for(int p=1; p<=10; p++)
-    {
-        dft1d(&data[n_start],pow(2,p));
-    }
-    */
     dft1d(&data[n_start],width);
+
     //update the turn
     turn++;
     
@@ -169,12 +158,12 @@ void* dft_thread(void *arg) {
     //printf() is in the critical section only for demonstration purpose.
     printf("thread %d:\n",tid);
 
-
+    thread_exit();
     //wake up all other threads to check if they are the next one to go.
     pthread_cond_broadcast(&cond);
     pthread_mutex_unlock(&lock);
     
-    thread_exit();
+    
     return 0;
     
 }

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: making join

@@ -38,16 +38,19 @@ void thread_join() {
     /* Assignment */
     //beginning of the critical section
     //pthread_mutex_lock(&lock);
-    //printf("thread join\n");
+    printf("thread join\n");
 
     //beginning of the critical section
-    pthread_mutex_lock(&lock_join);
+    //pthread_mutex_lock(&lock_join);
+    printf("thread join lock: changing condition\n");
+    //pthread_mutex_unlock(&lock_join);
     //use condition variable to wait for thread's turn.
     while(running == 1)
     {
+        printf("thread join waiting\n");
         pthread_cond_wait(&cond_join, &lock_join);
     }    
-    pthread_mutex_unlock(&lock_join);
+    
 }
 
 
@@ -139,14 +142,14 @@ void* dft_thread(void *arg) {
 
     //beginning of the critical section
     pthread_mutex_lock(&lock);
-    running=1;
+    
     //use condition variable to wait for thread's turn.
     while(tid > turn)
     {
         pthread_cond_wait(&cond, &lock);
     }    
 
-
+    running=1;
     //dft calc
     int n_start = width*(height/num_threads)*tid;
     dft1d(&data[n_start],width);
@@ -158,12 +161,12 @@ void* dft_thread(void *arg) {
     //printf() is in the critical section only for demonstration purpose.
     printf("thread %d:\n",tid);
 
-    thread_exit();
+    
     //wake up all other threads to check if they are the next one to go.
     pthread_cond_broadcast(&cond);
     pthread_mutex_unlock(&lock);
     
-    
+    thread_exit();
     return 0;
     
 }

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: making join

@@ -8,7 +8,7 @@
 using namespace std;
         
 unsigned turn  = 0;
-unsigned running = 0;
+unsigned running = 1;
 pthread_mutex_t lock;
 pthread_cond_t cond;
 pthread_mutex_t lock_join;
@@ -24,10 +24,10 @@ void thread_exit() {
     // and signal the parent thread that this thread is done.
     /* Assignment */
     
-    pthread_mutex_lock(&lock_join); //beginning of the critical section
+    pthread_mutex_lock(&lock); //beginning of the critical section
     running = 0; // condition variable to check whether this thread is running
     pthread_cond_broadcast(&cond_join); //signal the parent thread that this thread is done
-    pthread_mutex_unlock(&lock_join); //ending of the critical section
+    pthread_mutex_unlock(&lock); //ending of the critical section
 
 }
 
@@ -39,17 +39,21 @@ void thread_join() {
     //beginning of the critical section
     //pthread_mutex_lock(&lock);
     printf("thread join\n");
-
+    //running=1;
     //beginning of the critical section
     //pthread_mutex_lock(&lock_join);
-    printf("thread join lock: changing condition\n");
     //pthread_mutex_unlock(&lock_join);
     //use condition variable to wait for thread's turn.
+    pthread_mutex_lock(&lock_join);
+
     while(running == 1)
     {
         printf("thread join waiting\n");
         pthread_cond_wait(&cond_join, &lock_join);
-    }    
+    }
+    printf("thread join waking\n");
+    pthread_mutex_unlock(&lock_join);
+    thread_exit();
     
 }
 
@@ -142,14 +146,18 @@ void* dft_thread(void *arg) {
 
     //beginning of the critical section
     pthread_mutex_lock(&lock);
-    
     //use condition variable to wait for thread's turn.
     while(tid > turn)
     {
         pthread_cond_wait(&cond, &lock);
-    }    
-
+        //pthread_cond_wait(&cond_join, &lock_join);
+    }
     running=1;
+    
+    //while(running==0)
+    //{
+    //    pthread_cond_wait(&cond_join, &lock_join);
+    //}    
     //dft calc
     int n_start = width*(height/num_threads)*tid;
     dft1d(&data[n_start],width);

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: v3 working

@@ -7,6 +7,7 @@
 #include <stdio.h>
 using namespace std;
         
+// conditional variables
 unsigned turn  = 0;
 unsigned running = 1;
 pthread_mutex_t lock;
@@ -14,11 +15,9 @@ pthread_cond_t cond;
 pthread_mutex_t lock_join;
 pthread_cond_t cond_join;
 
-//make w array
+//make global w array
 complex_t *w_arr = (complex_t*)malloc(512 * sizeof(complex_t));
 
-
-            
 void thread_exit() {
     // Use pthread mutex and condition variables to exit the child function,
     // and signal the parent thread that this thread is done.
@@ -36,28 +35,21 @@ void thread_join() {
     // Use pthread mutex and condition variables to wait until all children
     // threads complete their executions.
     /* Assignment */
+
     //beginning of the critical section
-    //pthread_mutex_lock(&lock);
-    printf("thread join\n");
-    //running=1;
-    //beginning of the critical section
-    //pthread_mutex_lock(&lock_join);
-    //pthread_mutex_unlock(&lock_join);
-    //use condition variable to wait for thread's turn.
     pthread_mutex_lock(&lock_join);
 
+    // if thread is already running, wait for it.
     while(running == 1)
     {
-        printf("thread join waiting\n");
         pthread_cond_wait(&cond_join, &lock_join);
     }
-    printf("thread join waking\n");
+
+    //ending of critical section
     pthread_mutex_unlock(&lock_join);
+    //broadcast other thread to run
     thread_exit();
-    
 }
-
-
 
 // Perform 1-D DFT.
 void dft1d(complex_t *h, const unsigned N) {
@@ -67,71 +59,63 @@ void dft1d(complex_t *h, const unsigned N) {
     // Step 2: Follow Danielson-Lanczos Lemma to perform the DFT.
     /* Assignment */
     
-    //printf("h[5]: %f\n",h[5].re);
-    //printf("N: %d\n",N);
-
     // Step 1
     //cout << "DFT:Step1: Shuffle inputs to binary order" << endl;
     //make new data array
     complex_t *dft_data;
     dft_data = new complex_t[width * height/num_threads];
     
-    for(unsigned row=0; row<height/num_threads; row++) // Do it for every row
+    for(unsigned c=0; c<height/num_threads; c++) // Do it for every row
     {
         for(unsigned r=0; r<width; r++) // do it for every value
         {
-            //calc shuffle order
-            int quo_2 = r;
[…]

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: working v3

@@ -205,7 +205,9 @@ void dft2d() {
         thread_join();
         printf("thread %u done\n",t);
     }
-
+    // deallocate pthreads.
+    delete [] threads;
+    delete [] tid;
     cout << "Step 5: Transpose the data matrix so that column-wise DFT can be performed" << endl;
     // make copy of old array
     complex_t *old_data1 = data;
@@ -272,6 +274,7 @@ void dft2d() {
     assert(!pthread_cond_destroy(&cond_join));
     
     // Step 10: Deallocated heap memory blocks if any.
+    //delete w values
     free(w_arr);
 
 }

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: join fixing

@@ -23,10 +23,10 @@ void thread_exit() {
     // and signal the parent thread that this thread is done.
     /* Assignment */
     
-    pthread_mutex_lock(&lock); //beginning of the critical section
+    pthread_mutex_lock(&lock_join); //beginning of the critical section
     running = 0; // condition variable to check whether this thread is running
     pthread_cond_broadcast(&cond_join); //signal the parent thread that this thread is done
-    pthread_mutex_unlock(&lock); //ending of the critical section
+    pthread_mutex_unlock(&lock_join); //ending of the critical section
 
 }
 
@@ -44,11 +44,11 @@ void thread_join() {
     {
         pthread_cond_wait(&cond_join, &lock_join);
     }
-
     //ending of critical section
     pthread_mutex_unlock(&lock_join);
     //broadcast other thread to run
     thread_exit();
+    
 }
 
 // Perform 1-D DFT.
@@ -129,14 +129,17 @@ void* dft_thread(void *arg) {
     unsigned tid = * (unsigned*) arg;
 
     //beginning of the critical section
+    
     pthread_mutex_lock(&lock);
+    
     //use condition variable to wait for thread's turn.
     while(tid > turn)
     {
         pthread_cond_wait(&cond, &lock);
     }
-    
-    running=1; //notice join that this thread is running
+
+    pthread_mutex_lock(&lock_join);
+    //running=1; //notice join that this thread is running
     
     int n_start = width*(height/num_threads)*tid; //starting position of this data block
     dft1d(&data[n_start],width); // calculate DFT
@@ -149,7 +152,9 @@ void* dft_thread(void *arg) {
     
     //wake up all other threads to check if they are the next one to go.
     pthread_cond_broadcast(&cond);
+    pthread_mutex_unlock(&lock_join); 
     pthread_mutex_unlock(&lock);
+       
     
     thread_exit(); // inform join that this thread is finished
     return 0;    

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: ver 4

@@ -9,7 +9,7 @@ using namespace std;
         
 // conditional variables
 unsigned turn  = 0;
-unsigned running = 1;
+unsigned running = 0;
 pthread_mutex_t lock;
 pthread_cond_t cond;
 pthread_mutex_t lock_join;
@@ -46,8 +46,6 @@ void thread_join() {
     }
     //ending of critical section
     pthread_mutex_unlock(&lock_join);
-    //broadcast other thread to run
-    thread_exit();
     
 }
 
@@ -139,7 +137,7 @@ void* dft_thread(void *arg) {
     }
 
     pthread_mutex_lock(&lock_join);
-    //running=1; //notice join that this thread is running
+    running=1; //notice join that this thread is running
     
     int n_start = width*(height/num_threads)*tid; //starting position of this data block
     dft1d(&data[n_start],width); // calculate DFT
@@ -155,8 +153,7 @@ void* dft_thread(void *arg) {
     pthread_mutex_unlock(&lock_join); 
     pthread_mutex_unlock(&lock);
        
-    
-    thread_exit(); // inform join that this thread is finished
+    if(tid==num_threads-1) thread_exit(); // inform join that this thread is finished
     return 0;    
 }
 

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: join fix

@@ -149,8 +149,8 @@ void* dft_thread(void *arg) {
     printf("thread %d:\n",tid);
     
     //wake up all other threads to check if they are the next one to go.
-    pthread_cond_broadcast(&cond);
     pthread_mutex_unlock(&lock_join); 
+    pthread_cond_broadcast(&cond);
     pthread_mutex_unlock(&lock);
        
     if(tid==num_threads-1) thread_exit(); // inform join that this thread is finished

### 2019-04-29 190412_AdvP_A2/dft_pthread/dft.cc
advp a2: v5 running

@@ -9,7 +9,8 @@ using namespace std;
         
 // conditional variables
 unsigned turn  = 0;
-unsigned running = 0;
+unsigned running = 1;
+unsigned exit_var = 0;
 pthread_mutex_t lock;
 pthread_cond_t cond;
 pthread_mutex_t lock_join;
@@ -22,12 +23,16 @@ void thread_exit() {
     // Use pthread mutex and condition variables to exit the child function,
     // and signal the parent thread that this thread is done.
     /* Assignment */
-    
+
     pthread_mutex_lock(&lock_join); //beginning of the critical section
     running = 0; // condition variable to check whether this thread is running
     pthread_cond_broadcast(&cond_join); //signal the parent thread that this thread is done
+    while(exit_var == 0) // wait for response of join function
+    {
+        pthread_cond_wait(&cond_join, &lock_join);
+    }
+    exit_var = 0; // lock condition variable
     pthread_mutex_unlock(&lock_join); //ending of the critical section
-
 }
 
 // Custom thread join function.
@@ -38,15 +43,16 @@ void thread_join() {
 
     //beginning of the critical section
     pthread_mutex_lock(&lock_join);
-
     // if thread is already running, wait for it.
     while(running == 1)
     {
         pthread_cond_wait(&cond_join, &lock_join);
     }
-    //ending of critical section
-    pthread_mutex_unlock(&lock_join);
-    
+  
+    exit_var = 1;
+    running = 1;
+    pthread_cond_broadcast(&cond_join); // broadcast for thread function to exit
+    pthread_mutex_unlock(&lock_join);  //ending of critical section
 }
 
 // Perform 1-D DFT.
@@ -126,8 +132,6 @@ void* dft_thread(void *arg) {
     //cast and dereference the input argument.
     unsigned tid = * (unsigned*) arg;
 
-    //beginning of the critical section
-    
     pthread_mutex_lock(&lock);
     
     //use condition variable to wait for thread's turn.
@@ -135,25 +139,18 @@ void* dft_thread(void *arg) {
     {
         pthread_cond_wait(&cond, &lock);
     }
-
-    pthread_mutex_lock(&lock_join);
-    running=1; //notice join that this thread is running
+    //printf() is in the critical section only for demonstration.
+    printf("thread %d:\n",tid);
     
     int n_start = width*(height/num_threads)*tid; //starting position of this data block
[…]

### 2019-04-29 190410_Paper_ACPR/paper_v0.tex
Paper_acpr : methods

@@
 \section{Proposed System}
-\subsection{Data Acquisition and Preprocessing}
+
 In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
 An overview of the proposed scheme is shown in Fig.1.
+The main purpose of this system is to receive two csi signals as input, to determine if the two signals are the same signature.
+Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
+% Figure 1
 \begin{figure}
@@
 
- Two preprocessed signals enter the Siamese network and the network 
-extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
- The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
-the network is learned by the back-propagation.
-
-The main purpose of this system is to receive two csi signals as input, to determine if the two signals are the same signature.
-Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
-
+\subsection{Data Acquisition and Preprocessing}
 In order to be used as an input to a siamese network, the data must be pre-processed.
@@
 And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data.
+
 % Methods
@@
 \subsection{Siamese Network For Verification}
+
+% From Ref1 start
 Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem (Bromley et al., 1993)
 Siamese neural networks employ a unique structure to naturally rank similarity between inputs.[1] 
-It can discriminate between the class-identity of image pairs[1]
+It can discriminate between the class-identity of image pairs
 The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.[1]
+% From Ref1 End
+
+Two preprocessed signals enter the Siamese network and the network 
+extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
+ The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
+the network is learned by the back-propagation.
 
@@
 To classify regardless of the direction of the signal, the model shall be capable of extracting features unrelated to the direction.
+
+% Section: Feature Extraction
 \subsection{Feature Extraction}
@@
 
+% CNN: purpose
 Purpose of CNN is to extract features from signal.
@@
 
+% how to extract feature using CNN
 To perform the feature extraction, we firstly need to have a convolutional neural networks  to serve as the feature extractor
@@
 In a similar manner, j fully connected layers constitute the classifier of pretraining model where each layer has g•,(•=1,...,j) neurons to be trained.
+
+%Symmetric Architecture
+
+Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures.
+some may be heavily influenced by the direction in which the signature was entered.
+We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
+
+To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
+It was also designed to have the same weight on the symmetrical CNN network as on a symmetrical CNN network. % weight sharing
+
+%Symetric : Share Weights
+% To extract the same characteristics from signals in different directions.
+% CNN: Feature Extractor
+%Automatically extract feature vector from CSI image
 

### 2019-05-02 190410_Paper_ACPR/paper_v0.tex
paper:acpr_method v1

@@
 
+%system overview
 In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
 An overview of the proposed scheme is shown in Fig.1.
-The main purpose of this system is to receive two csi signals as input, to determine if the two signals are the same signature.
+% main purpose
+The main purpose of this system is to receive two csi signals as input, to 
+determine if the two signals are the same signature.
 Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
@@
 
-\subsection{Data Acquisition and Preprocessing}
-In order to be used as an input to a siamese network, the data must be pre-processed.
+\subsection{Data Preprocessing}
+% preprocessing
+In order to be used as an input to a siamese network, the signal must be pre-processed.
 
-First, the signal have to converted to non-complex form.
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase[ref] we used absolute of signal only.
+First, the signal have to be converted to non-complex form.
+Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase[ref]. so we used absolute of signal only.
 
+% From HC's Papaer
 Second, all inputs must be arranged of same size.
@@
 And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data. 
+% HC's end
 
@@
 
+% Introduce Siamese Net
 % From Ref1 start
 Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem (Bromley et al., 1993)
-Siamese neural networks employ a unique structure to naturally rank similarity between inputs.[1] 
+Siamese neural networks employ a unique structure to naturally rank similarity between inputs.
 It can discriminate between the class-identity of image pairs
@@
 
-Two preprocessed signals enter the Siamese network and the network 
-extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
+% Functions of Siamese in our system
+The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output. 
 The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
@@
 
-The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output.
+Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
 
@@
 % Section: Feature Extraction
-\subsection{Feature Extraction}
+\subsubsection{Feature Extraction}
 When two processed signals come as the input, they are put to 2 symmetric CNN network.
@@
 %Symmetric Architecture
-
 Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures.
@@
 To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
-It was also designed to have the same weight on the symmetrical CNN network as on a symmetrical CNN network. % weight sharing
+It was also designed to have the same weight on the symmetrical CNN network as on a symmetrical CNN network.
+
+% tied weights
 
@@
 
-\subsection{Feature Matching}
+\subsubsection{Feature Matching}
+
+% Use L1 distances of Feature vector of 2 input images
+% From HC's In-Air paper below:
+Let $\mathbf{m}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{n}\in{\mathrm{R}}^{d\times1}$ be feature vectors extracted from two samples.
+The L-1 distance between the two features can be calculated as  follows:
+Where $\mathbf{p}$ denotes the L-1 distance. In the Siamese networks, this L-1 distance is utilized to match between two feature vectors.
+
+% From HC's End
+% From Oneshot paper below
+\begin{equation}
+    \mathbf{p} = 
+    \sigma(\sum_j\alpha_{j}\mid
+    \mathbf{m}_{1,L-1}^{(j)} - 
+    \mathbf{n}_{1,L-1}^{(j)}\mid)  
+\end{equation}
+where σ is the sigmoidal
+activation function.
+This final layer induces a metric on the learned feature space of the (L − 1)th hidden layer and scores the similarity between the two feature vec- tors.
+The αj are additional parameters that are learned by the model during training, weighting the importance of the component-wise distance.
+This defines a final Lth fully-connected layer for the network which joins the two siamese twins.
+% From oneshot end
+
 Output of the CNN are feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
@@
 
-\subsection{Loss and Backpropagation}
+\subsubsection{Loss and Backpropagation}
  We impose a regularized cross-entropy objective on our binary classifier.

### 2019-05-03 190501_DBS_A1/lbp.py
DBS_A1: LBP

@@ -1,0 +1,48 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+import skimage.data as data
+import skimage.feature as feature
+import skimage.transform as transform
+
+# for truncated img files
+from PIL import ImageFile
+ImageFile.LOAD_TRUNCATED_IMAGES = True
+
+#image path
+path_img = 'D:\\Data\\AnimalsOnTheWeb_v1\\'
+
+#df to aggregate results
+lbp_df = pd.DataFrame()
+
+list_folder = os.listdir(path_img)
+list_folder = [f for f in list_folder if not 'other' in f]
+
+for foldername in list_folder:
+    print(foldername)
+    list_files = os.listdir(path_img+foldername+'\\')
+    list_files = [f for f in list_files if 'pic' in f]
+
+    for filename in list_files:
+        try:
+            img_arr = data.load(path_img + foldername+'\\'+filename,as_grey=True)
+        
+            lbp = feature.local_binary_pattern(img_arr, 8, 2, "uniform") #image, P, R, method
+            brickCount = 10#int(lbp.max() + 1)
+            lbp_hist, _ = np.histogram(lbp, normed = True, bins = brickCount, range = (0, brickCount))
+        except:
+            lbp_hist = np.array([0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0,0.0])
+
+        # Result
+        lbp_ser = pd.Series([foldername,filename,\
+                lbp_hist[0],lbp_hist[1],lbp_hist[2],lbp_hist[3],lbp_hist[4],\
+                lbp_hist[5],lbp_hist[6],lbp_hist[7],lbp_hist[8],lbp_hist[9]],\
+                index=['Animal','File','LBP0','LBP1','LBP2','LBP3','LBP4',\
+                        'LBP5','LBP6','LBP7','LBP8','LBP9'])
+        # Aggregate result
+        lbp_df.append(lbp_ser,ignore_index=True)
+
+
+lbp_df.to_csv('Res_LBP.csv')

### 2019-05-09 190410_Paper_ACPR/paper_v0.tex
Paper_ACPR: related1

@@
 \subsection{WIFI CSI}
+- An In-Air Signature Verification System Using Wi-Fi Signals
+
+% Meaning of CSI
+%[From Halperin paper]
+CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
+It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
+The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
+%[From Halperin End]
+
+% Structure of CSI
+%[From HC's ELM paper]
+In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
+$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
+The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
+The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
+\begin{equation}
+    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
+\end{equation}
+where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
+%[From HC's ELM end]
+
+\subsection{Siamese Networks}
 - An In-Air Signature Verification System Using Wi-Fi Signals
@@
 \begin{thebibliography}{8}
+% Deep Learning Siamese Paper
 \bibitem{ref_article1}
@@
  ICML deep learning workshop. Vol. 2. 2015.
+% HC's Conference Paper
+ \bibitem{ref_article2}
+Moon, Han-Cheol, et al. "An In-Air Signature Verification System Using Wi-Fi Signals." Proceedings of the 2017 4th International Conference on Biomedical and Bioinformatics Engineering. ACM, 2017.
+% JS's Conf Paper
+\bibitem{ref_article3}
+JS's Conf Paper
+% Halperin CSI tool paper
+\bibitem{ref_article4}
+Halperin, Daniel, et al. "Tool release: Gathering 802.11 n traces with channel state information." ACM SIGCOMM Computer Communication Review 41.1 (2011): 53-53.
 

### 2019-05-09 190509_AdvP_A3/dft_mpi/complex.h

@@ -1,0 +1,28 @@
+#ifndef __COMPLEX_H__
+#define __COMPLEX_H__
+
+#include <iostream>
+#include <cstring>
+
+class complex_t {
+public:
+    complex_t();                            // Constructor
+    complex_t(float m_re, float m_im);      // Real and imaginary
+    complex_t(const complex_t &c);          // Copy constructor
+    ~complex_t();                           // Destructor
+
+    // Operators
+    complex_t operator+(const complex_t &c) const;
+    complex_t operator-(const complex_t &c) const;
+    complex_t operator*(const complex_t &c) const;
+    complex_t operator/(const complex_t &c) const;
+    complex_t magnitude() const;            // Magnitude of complex number
+    complex_t conjugate() const;            // Conjugate of complex number
+    void print() const;                     // Print the complex number.
+
+    float re;                               // Real part of complex number
+    float im;                               // Imaginary part of complex number
+};
+
+#endif
+

### 2019-05-09 190509_AdvP_A3/dft_mpi/dft.cc

@@ -1,0 +1,50 @@
+#include <cmath>
+#include <cstdlib>
+#include <cstring>
+#include <mpi.h>
+#include "dft.h"
+
+using namespace std;
+
+// Custom MPI_Allgather function with complex_t data type
+void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
+                   complex_t *m_recv_buffer, int m_recv_count,
+                   MPI_Comm m_comm) {
+    // Use a group of non-blocking receive (i.e., MPI_Irecv) and blocking
+    // send (i.e., MPI_Send) along with MPI_Wait() to implement the custom
+    // MPI_Allgather function. Do not use collective communication functions
+    // such as MPI_Allgather(), MPI_Gather, MPI_Scatter, or MPI_Broadcast.
+    /* Assignment */
+
+    // byte 단위로 보내고 계산해야 함
+    
+}
+
+// Transpose a matrix.
+void transpose_matrix(complex_t *h, const unsigned m_width, const unsigned m_height) {
+    // Transpose the matrix h that has the dimension of m_width * m_height.
+}
+
+// Perform 1-D DFT.
+void dft1d(complex_t *h, const unsigned N) {
+    // This function implements 1-D DFT for the array h of length N.
+    // You may reuse the Cooley-Tuckey algorithm that you wrote for the
+    // previous pthread assignment, or you may directly calculate the DFT
+    // equation shown in the lecture note.
+    /* Assignment */
+}
+
+// Perform 2-D DFT.
+void dft2d() {
+    // This function performs 2-D DFT with the data.
+    // Step 1: Calculate 1-D DFT for the given rows per process.
+    // Step 2: Use the custom mpi_allgather() as a barrier to gather the
+    //         1-D DFT result.
+    // Step 3: Transpose the matrix.
+    // Step 4: Calculate 1-D DFT again, which is technically column-wise DFT.
+    // Step 5: Use again the custom mpi_allgather() to gather the 2-D DFT
+    //         results calculated in the previous step.
+    // Step 6: Transpose the matrix back to the original orientation.
+    /* Assignment */
+}
+

### 2019-05-09 190509_AdvP_A3/dft_mpi/dft.h

@@ -1,0 +1,22 @@
+#ifndef __DFT_H__
+#define __DFT_H__
+
+#include "complex.h"
+#include "file_handler.h"
+
+// Perform 2-D DFT.
+void dft2d();
+
+// File handler
+extern file_handler_t file_handler;
+// Number of ranks
+extern int num_ranks;
+// Rank ID
+extern int rank_id;
+// Data to perform DFT.
+extern complex_t *data;
+// Data dimension
+extern unsigned width, height;
+
+#endif
+

### 2019-05-09 190509_AdvP_A3/dft_mpi/file_handler.cc

@@ -1,0 +1,69 @@
+#include <cstdlib>
+#include <fstream>
+#include <stdint.h>
+#include "file_handler.h"
+
+using namespace std;
+
+// Constructor
+file_handler_t::file_handler_t() {
+}
+
+// Destructor
+file_handler_t::~file_handler_t() {
+}
+
+// Read data from a file.
+void file_handler_t::read_data(const string m_file_name, complex_t *&m_data,
+                               unsigned &m_width, unsigned &m_height) {
+    // Open the file.
+    fstream file_stream;
+    file_stream.open(m_file_name.c_str(), fstream::in|fstream::binary);
+    if(!file_stream.is_open()) {
+        cerr << "Error: failed to open " << m_file_name << endl;
+        exit(1);
+    }
+
+    // Read the dimension information.
+    file_stream >> m_width >> m_height;
+
+    // Allocate data.
+    m_data = new complex_t[m_width * m_height];
+
+    // Load the data.
+    for(unsigned r = 0; r < m_height; r++) {      // Rows
+        for(unsigned c = 0; c < m_width; c++) {   // Columns
+            file_stream >> m_data[r * m_width + c].re;
+        }
+    }
+
+    // Close the file. 
+    file_stream.close();
+}
+
+// Save data to a file.
+void file_handler_t::save_data(const string m_file_name, complex_t *m_data,
+                               unsigned m_width, unsigned m_height) {
+    // Open the file.
+    fstream file_stream;
+    file_stream.open(m_file_name.c_str(), fstream::out|fstream::binary);
+    if(!file_stream.is_open()) {
+        cerr << "Error: failed to open " << m_file_name << endl;
+        exit(1);
+    }
+
+    // Store the dimension information.
+    file_stream << m_width << " " << m_height << endl;
+
+    // Store the magnitude data.
+    for(unsigned r = 0; r < m_height; r++) {      // Rows
+        for(unsigned c = 0; c < m_width; c++) {   // Columns
+            file_stream << m_data[r * m_width + c].magnitude().re << " ";
+        }
+        file_stream << endl;
+    }
+
+    // Close the file.
+    file_stream.close();
+}
+

### 2019-05-09 190509_AdvP_A3/dft_mpi/main.cc

@@ -1,0 +1,60 @@
+#include <cstdlib>
+#include <iostream>
+#include <mpi.h>
+#include "complex.h"
+#include "dft.h"
+#include "file_handler.h"
+
+using namespace std;
+
+file_handler_t file_handler;        // File handler
+int num_ranks = 0;                  // Number of ranks
+int rank_id = 0;                    // Rank ID
+complex_t *data = 0;                // Data to perform DFT
+unsigned width = 0, height = 0;     // Data dimension
+
+int main(int argc, char **argv) {
+    // Initialize MPI.
+    MPI_Init(&argc, &argv);
+
+    // Get the communicator size and rank information.
+    MPI_Comm_size(MPI_COMM_WORLD, &num_ranks);
+    MPI_Comm_rank(MPI_COMM_WORLD, &rank_id);
+
+    // Print usage message.
+    if(argc != 1) {
+        if(rank_id == 0) { cerr << "Usage: mpirun -np [num_ranks] " << argv[0] << endl; }
+        MPI_Finalize(); return 0;
+    }
+
+    int val = num_ranks;
+    // Max num_ranks is 1024.
+    if(val > 1024) {
+        if(rank_id == 0) { cerr << "Error: too many ranks" << endl; }
+        MPI_Finalize(); return 0;
+    }
+    // Check if num_threads is power of two.
+    while(!(val%2)) { val = val >> 1; }
+    if(val != 1) {
+        if(rank_id == 0) { cerr << "Error: num_threads must be a power of two." << endl; }
+        MPI_Finalize(); return 0;
+    }
+
+    // Load input data file.
+    file_handler.read_data("input.txt", data, width, height);
+
+    // Perform 2-D DFT.
+    dft2d();
+
+    // Save the result to a file.
+    if(rank_id == 0) { file_handler.save_data("output-2d.txt", data, width, height); }
+
+    // Deallocate data.
+    delete [] data;
+
+    // Finalize MPI.
+    MPI_Finalize();
+
+    return 0;
+}
+

### 2019-05-12 190410_Paper_ACPR/paper_v0.tex
paper_acpr: method v1

@@
 %
-\author{Young Woong KWON\inst{1} \and
+\author{YoungWoong KWON\inst{1} \and
 JooYoung KIM\inst{1} \and
@@
 \section{Related Works}
-a. WIFI CSI
-b. Siamese Networks
 
@@
 \subsection{Siamese Networks}
-- An In-Air Signature Verification System Using Wi-Fi Signals
+Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem.\cite{koch2015siamese}
 
@@
 
+\subsection{System Overview}
+
 %system overview
+
 In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
-An overview of the proposed scheme is shown in Fig.1.
-% main purpose
-The main purpose of this system is to receive two csi signals as input, to 
-determine if the two signals are the same signature.
-Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
+An overview of the proposed system is shown in Fig.1.
 % Figure 1
@@
     \includegraphics[width=\textwidth]{methods1.eps}
-\caption{...} \label{method1}
+    \caption{Overview of the proposed system} \label{method1}
 \end{figure}
 
+% purpose of the system
+This system receives two Wi-Fi CSI signals as input.
+The main purpose of the system is to verify if two input signals are of the same signature.
+
+% main purpose1: interpreting CSI 
+Our system must have the ability to distinguish signatures by reading Wi-Fi CSI signals.
+% verification model
+The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.\cite{koch2015siamese}
+
+% main purpose2: direction free
+Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
+
+Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
+To classify regardless of the direction of the signal, we focused on the model shall be capable of extracting features unrelated to the direction.
+
+%% Pre-processing
 \subsection{Data Preprocessing}
-% preprocessing
+
 In order to be used as an input to a siamese network, the signal must be pre-processed.
 
+% used only abs value
 First, the signal have to be converted to non-complex form.
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase[ref]. so we used absolute of signal only.
+Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.
 
+% preprocessing
 % From HC's Papaer
@@
 Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
-And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data. 
+And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}
 % HC's end
@@
 
+% Functions of Siamese in our system
 % Introduce Siamese Net
-% From Ref1 start
-Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem (Bromley et al., 1993)
-Siamese neural networks employ a unique structure to naturally rank similarity between inputs.
-It can discriminate between the class-identity of image pairs
-The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.[1]
-% From Ref1 End
 
-% Functions of Siamese in our system
-The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output. 
-The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
-the network is learned by the back-propagation.
+Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
+\cite{koch2015siamese}
 
 Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
-
-Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
-To classify regardless of the direction of the signal, the model shall be capable of extracting features unrelated to the direction.
+The model outputs the probability that the two signals are of the same class.
+%it is learned by the back-propagation.
+This network consists of feature extraction and feature matching part.
 
@@
 \subsubsection{Feature Extraction}
-When two processed signals come as the input, they are put to 2 symmetric CNN network.
+
+% structure of siamese network
+To perform the feature extraction, we firstly need to have a convolutional neural networks to serve as the feature extractor
+Based on the ConvNet structure. \cite{lecun1998gradient}
+
+% structure of siamese network
+When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
+%Symmetric Architecture
+Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures.
+some may be heavily influenced by the direction in which the signature was entered.Structure of the network is shown in Fig.2.
+% Figure 2
+\begin{figure}
+    \includegraphics[width=\textwidth]{network1.eps}
+    \caption{Structure of Siamese network} \label{network1}
+\end{figure}
+% weight tying
+We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
+To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
+It was also designed to have the same weight on the symmetrical CNN network.
+
+% sister networks
+This feature extractor is composed of two sister network, which are identical ConvNets with the exact same weights
 
 % CNN: purpose
-Purpose of CNN is to extract features from signal.
-By sharing their feature map, this CNN networks is trainin to learn characteristics regardless of the direction only.
+Purpose of ConvNet in our model is to extract a feature vector from CSI signal. 
+%Local Connectivity – image is locally correlated.
+Because each CSI signal has a locally related characteristic, the convolution filters apply local connectivity between inputs.
+and it helps to extract the feature vector.
+and by weight of feature output is shared through all feature map.
+%Weight Sharing – overcome enormous weights problem
+so it helps to reduce number of weights and can be appliable to CSI signal, which is relatively large size.
 
-% how to extract feature using CNN
-To perform the feature extraction, we firstly need to have a convolutional neural networks  to serve as the feature extractor
-Based on the ConvNet structure [17] the feature extractor of the proposed pretraining model consists of i convolution layers and activation functions followed by i max-pooling layers.
-Each convolution layer has f∗ filters to be trained, where ∗ = 1, ..., i.
-In a similar manner, j fully connected layers constitute the classifier of pretraining model where each layer has g•,(•=1,...,j) neurons to be trained.
+% parameters of convnet
+this ConvNets are consists of a number of consecutive convolution layers with active functions, and a pooling layer in the end.
+the Convolution Layer has n convolution filters in it.
 
-%Symmetric Architecture
-Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures.
-some may be heavily influenced by the direction in which the signature was entered.
-We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
+% functions of convnet
+Their weights are tied to extract the same characteristics from signals in different directions.
+By sharing their feature map, this ConvNet is train to learn characteristics regardless of the direction.
 
-To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
-It was also designed to have the same weight on the symmetrical CNN network as on a symmetrical CNN network.
-
-% tied weights
-
-%Symetric : Share Weights
-% To extract the same characteristics from signals in different directions.
-% CNN: Feature Extractor
-%Automatically extract feature vector from CSI image
+% outputs feature vector
+Through a convolution filter, each CSI signal is transformed to a feature vector. this entire process is jointly optimized by backpropagation.
 
@@
 
+\section{Experiments}
+
 \subsubsection{Loss and Backpropagation}
@@
 Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
-\begin{figure}
-\includegraphics[width=\textwidth]{network1.eps}
-\caption{...} \label{network1}
-\end{figure}
 
-\section{Experiments}
 \section{Conclusion}
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
+%\bibliographystyle{splncs04}
+%\bibliography{mybibliography}
 %
-\begin{thebibliography}{8}
-% Deep Learning Siamese Paper
-\bibitem{ref_article1}
-Koch, Gregory, Richard Zemel, and Ruslan Salakhutdinov.
- "Siamese neural networks for one-shot image recognition." 
- ICML deep learning workshop. Vol. 2. 2015.
-% HC's Conference Paper
- \bibitem{ref_article2}
-Moon, Han-Cheol, et al. "An In-Air Signature Verification System Using Wi-Fi Signals." Proceedings of the 2017 4th International Conference on Biomedical and Bioinformatics Engineering. ACM, 2017.
-% JS's Conf Paper
-\bibitem{ref_article3}
-JS's Conf Paper
-% Halperin CSI tool paper
-\bibitem{ref_article4}
-Halperin, Daniel, et al. "Tool release: Gathering 802.11 n traces with channel state information." ACM SIGCOMM Computer Communication Review 41.1 (2011): 53-53.
 
-\end{thebibliography}
+%\begin{thebibliography}{8}
+
+\bibliographystyle{splncs04}
+\bibliography{bib_acpr}
+
+%\end{thebibliography}
+
 \end{document}

### 2019-05-12 190509_AdvP_A3/dft_mpi/dft.cc

@@ -23,6 +23,24 @@ void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
 // Transpose a matrix.
 void transpose_matrix(complex_t *h, const unsigned m_width, const unsigned m_height) {
     // Transpose the matrix h that has the dimension of m_width * m_height.
+    
+    // make copy of old array
+    complex_t *old_data1 = h;
+    // make new data array
+    h = new complex_t[width * height];
+    
+    // Copy elements from the transposed value from old array
+    for(unsigned i=0; i<height; i++)
+    {
+        for(unsigned j=0; j<width; j++)
+        {
+            //transpose
+            new (&h[i*height+j]) complex_t(old_data1[i+j*width]);
+            old_data1[i+j*width].~complex_t();
+        }
+    }
+    // Deallocate the old array.
+    delete[] old_data1;
 }
 
 // Perform 1-D DFT.

### 2019-05-12 190509_AdvP_A3/dft_mpi/dft.cc
advp_a3: making 1d

@@ -6,6 +6,10 @@
 
 using namespace std;
 
+//make global w array
+complex_t *w_arr = (complex_t*)malloc(512 * sizeof(complex_t));
+
+
 // Custom MPI_Allgather function with complex_t data type
 void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
                    complex_t *m_recv_buffer, int m_recv_count,
@@ -17,6 +21,10 @@ void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
     /* Assignment */
 
     // byte 단위로 보내고 계산해야 함
+    //MPI_Request mpi_recv_request;
+
+    //int size = sizeof(data) / num_ranks;
+    //MPI_Allgather(&rank_id,size,MPI_FLOAT,m_recv_buffer,size,MPI_FLOAT,MPI_COMM_WORLD);
     
 }
 
@@ -50,6 +58,65 @@ void dft1d(complex_t *h, const unsigned N) {
     // previous pthread assignment, or you may directly calculate the DFT
     // equation shown in the lecture note.
     /* Assignment */
+
+    // Step 1
+    //cout << "DFT:Step1: Shuffle inputs to binary order" << endl;
+    //make new data array
+    complex_t *dft_data;
+    dft_data = new complex_t[width * height/num_ranks];
+    
+    for(unsigned c=0; c<height/num_ranks; c++) // Do it for every row
+    {
+        for(unsigned r=0; r<width; r++) // do it for every value
+        {
+            // initialize variables
+            int quo_2 = r; 
+            int rem_2 = 0;
+            int new_ind = 0;
+            //calc binary shuffle order by dividing 2
+            for(int k = int(log2(width))-1; k>=0 ; k--)
+            {
+                rem_2 = quo_2 % 2;
+                quo_2 = int(quo_2 / 2);
+                new_ind += pow(2,k) * rem_2; //order number in decimal value
+            }
+            //put reordered data to array
+            new (&dft_data[height*c + new_ind]) complex_t(h[height*c + r]);
+        }
+    }
+    
+    // Step 2
+    //cout << "DFT:Step2: Perform DFT" << endl;
+    // iterate power of 2
+    for(int p=1; p<=int(log2(N)); p++)
+    {
+        int size = pow(2,p);
+        // do it for every row
+        for(int r = 0; r < int(width*(height/num_ranks)/size) ; r++)
[…]

### 2019-05-13 190410_Paper_ACPR/paper_v0.tex
paper_acpr: rel works

@@
 \subsection{Siamese Networks}
-Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem.\cite{koch2015siamese}
+
+% description of siamese net
+In \cite{bromley1994signature}, LeCun et al. Introduced Siamese nets as parts of their handwritten signature verification system. 
+A siamese neural network consists of twin networks which accept distinct inputs but are joined by an energy function at the top.\cite{koch2015siamese}
+% differences in feature extractor
+They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector.
+Apart from this work based on ConvNet as feature extractor and L1 distance as feature matcher.
+In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
+% advantages of using Convnet filter
+Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
+The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.
 
@@
 % used only abs value
-First, the signal have to be converted to non-complex form.
+First, the signal has to be converted to non-complex form.
 Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.
@@
 % From HC's Papaer
-Second, all inputs must be arranged of same size.
-Since all signals have different length, the gradient operation with respect to the time instance is adopted to measure the short time energy. 
+Second, all inputs must be arranged of the same size.
+Since all signals have different length, the gradient operation with respect to the time instance is adapted to measure the short time energy. 
 Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
-And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}
-% HC's end
+And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}% HC's end
 
@@
 % structure of siamese network
-To perform the feature extraction, we firstly need to have a convolutional neural networks to serve as the feature extractor
-Based on the ConvNet structure. \cite{lecun1998gradient}
+To perform the feature extraction, we first need to have convolutional neural networks to serve as the feature extractor
+Based on the ConvNet structure.\cite{lecun1998gradient}
 
@@
 %Symmetric Architecture
-Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures.
-some may be heavily influenced by the direction in which the signature was entered.Structure of the network is shown in Fig.2.
+Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that help to classify signatures.
+some may be heavily influenced by the direction in which the signature was entered.
+Structure of the network is shown in Fig.2.
 % Figure 2
@@
 % CNN: purpose
-Purpose of ConvNet in our model is to extract a feature vector from CSI signal. 
-%Local Connectivity – image is locally correlated.
-Because each CSI signal has a locally related characteristic, the convolution filters apply local connectivity between inputs.
-and it helps to extract the feature vector.
-and by weight of feature output is shared through all feature map.
-%Weight Sharing – overcome enormous weights problem
-so it helps to reduce number of weights and can be appliable to CSI signal, which is relatively large size.
+Purpose of ConvNet in our model is to extract a feature vector from the CSI signal.
 
@@
 Their weights are tied to extract the same characteristics from signals in different directions.
-By sharing their feature map, this ConvNet is train to learn characteristics regardless of the direction.
+By sharing their feature map, this ConvNet is trained to learn characteristics regardless of the direction.
 
 % outputs feature vector
-Through a convolution filter, each CSI signal is transformed to a feature vector. this entire process is jointly optimized by backpropagation.
+Through a convolution filter, each CSI signal is transformed into a feature vector. this entire process is jointly optimized by backpropagation.
 
@@
 activation function.
-This final layer induces a metric on the learned feature space of the (L − 1)th hidden layer and scores the similarity between the two feature vec- tors.
+This final layer induces a metric on the learned feature space of the (L − 1)th hidden layer and scores the similarity between the two feature vectors.
 The αj are additional parameters that are learned by the model during training, weighting the importance of the component-wise distance.
-This defines a final Lth fully-connected layer for the network which joins the two siamese twins.
+This defines a final Lth fully-connected layer for the network which joins the two Siamese twins.
 % From oneshot end
 
-Output of the CNN are feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
+The output of the CNN is feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
 In the proposed system, this Euclidean distance is utilized to match between two feature vectors.

### 2019-05-14 190509_AdvP_A3/dft_mpi/dft.cc
advp_a3: minor change

@@ -30,12 +30,9 @@ void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
 
 // Transpose a matrix.
 void transpose_matrix(complex_t *h, const unsigned m_width, const unsigned m_height) {
-    // Transpose the matrix h that has the dimension of m_width * m_height.
     
-    // make copy of old array
-    complex_t *old_data1 = h;
     // make new data array
-    h = new complex_t[width * height];
+    data = new complex_t[width * height];
     
     // Copy elements from the transposed value from old array
     for(unsigned i=0; i<height; i++)
@@ -43,12 +40,9 @@ void transpose_matrix(complex_t *h, const unsigned m_width, const unsigned m_hei
         for(unsigned j=0; j<width; j++)
         {
             //transpose
-            new (&h[i*height+j]) complex_t(old_data1[i+j*width]);
-            old_data1[i+j*width].~complex_t();
+            new (&data[i*height+j]) complex_t(h[i+j*width]);
         }
     }
-    // Deallocate the old array.
-    delete[] old_data1;
 }
 
 // Perform 1-D DFT.
@@ -143,36 +137,45 @@ void dft2d() {
     cout << "Temp: Number of ranks = " << num_ranks
     << ", rank ID = " << rank_id << endl;
 
-    // temp
-    //unsigned buffer_size = num_ranks;
-    //int recv_buffer[buffer_size];
-
-    //MPI_Allgather(&data[0].re,1,MPI_FLOAT,recv_buffer,1,MPI_FLOAT,
-    //MPI_COMM_WORLD);
-
     unsigned buffer_size = width*height;
     complex_t *recv_buffer = (complex_t*)malloc(buffer_size * sizeof(complex_t));
-    //recv_buffer = new complex_t[buffer_size];
     
     printf("rank %d:\n",rank_id);
     
     int n_start = width*(height/num_ranks)*rank_id; //starting position of this data block
 
-    //data_mpi = data[n_start];
     dft1d(&data[n_start],width); // calculate DFT
 
     // the message is gathered across all process
-    //mpi_allgather(&rank_id,buffer_size,recv_buffer,buffer_size,MPI_COMM_WORLD);
-    //MPI_Allgather(&rank_id,1,MPI_INT,recv_buffer,1,MPI_INT,MPI_COMM_WOR LD);
[…]

### 2019-05-15 190410_Paper_ACPR/paper_v0.tex
advp_a3: making join

@@
 
+% Network Learning
 \subsubsection{Loss and Backpropagation}
@@
 \end{document}
-
-%% Template End
-\section{*** Template ***}
-\section{First Section}
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
-
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
-\end{document}

### 2019-05-15 190509_AdvP_A3/dft_mpi/dft.cc

@@ -20,12 +20,35 @@ void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
     // such as MPI_Allgather(), MPI_Gather, MPI_Scatter, or MPI_Broadcast.
     /* Assignment */
 
-    // byte 단위로 보내고 계산해야 함
-    //MPI_Request mpi_recv_request;
-
-    //int size = sizeof(data) / num_ranks;
-    //MPI_Allgather(&rank_id,size,MPI_FLOAT,m_recv_buffer,size,MPI_FLOAT,MPI_COMM_WORLD);
+    //MPI_Allgather(&data[n_start],width*(height/num_ranks)*sizeof(complex_t),MPI_BYTE,
+    //recv_buffer,width*(height/num_ranks)*sizeof(complex_t),MPI_BYTE,MPI_COMM_WORLD);
     
+    //int n_start = width*(height/num_ranks)*rank_id; //starting position of this data block
+    complex_t *temp_recv_buffer = (complex_t*)malloc(m_recv_count * sizeof(complex_t));
+
+    MPI_Request mpi_recv_request;
+    // receive a message from the previous process
+    MPI_Irecv(temp_recv_buffer,m_recv_count,MPI_BYTE,MPI_ANY_SOURCE,
+    rank_id, MPI_COMM_WORLD, &mpi_recv_request);
+    // send the message to the next process
+    MPI_Send(m_send_buffer,m_send_count,MPI_BYTE,
+            (rank_id+1)%num_ranks,(rank_id+1)%num_ranks, MPI_COMM_WORLD);
+    // receive a message from the last process
+    MPI_Status mpi_status;
+    MPI_Wait(&mpi_recv_request, &mpi_status);
+    
+    int temp_start = m_recv_count*mpi_status.MPI_SOURCE; //starting position of this data block
+    /*
+    for(int i = 0; i < m_recv_count; i++) {
+        m_recv_buffer[temp_start+i].~complex_t();
+        new (&m_recv_buffer[temp_start+i]) complex_t(temp_recv_buffer[i]);   
+        temp_recv_buffer[i].~complex_t();
+    }
+    */
+
+    cout << "MPI Rank " << rank_id << " start from "<< temp_start << " received a message from rank "
+    << mpi_status.MPI_SOURCE << ": " << temp_recv_buffer[0].re << endl;
+
 }
 
 // Transpose a matrix.
@@ -147,8 +170,14 @@ void dft2d() {
     dft1d(&data[n_start],width); // calculate DFT
 
[…]

### 2019-05-16 190410_Paper_ACPR/paper_v1.tex
paper_acpr: v2 upload

--- 2019-05-15 190410_Paper_ACPR/paper_v0.tex
@@
 \subsection{Contribution}
-- Overcome cons of WIFI signature system
+- Overcome cons of WIFI signature systems
 - Robust to signal direction, size
@@
 
-\subsection{WIFI CSI}
-- An In-Air Signature Verification System Using Wi-Fi Signals
-
-% Meaning of CSI
-%[From Halperin paper]
-CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
-It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
-The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
-%[From Halperin End]
-
-% Structure of CSI
-%[From HC's ELM paper]
-In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
-$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
-The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
-The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
-\begin{equation}
-    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
-\end{equation}
-where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
-%[From HC's ELM end]
+\subsection{ConvNets}
+% description of convnet
+Convolutional Neural Networks is a specal case of MLP and it has unified feature extractor and classifier in one network.
+It has been widely applied to visual objects such as image or video or 2D array input.
+Several factors make ConvNets attractive in image related tasks.
+Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.
+Weight sharing helps to reduce the number of weights in feature maps.
+Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
+%
 
@@
 They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector.
-Apart from this work based on ConvNet as feature extractor and L1 distance as feature matcher.
-In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
-% advantages of using Convnet filter
-Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
-The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.
 
@@
 \section{Experiments}
+% Dataset
+\subsubsection{Dataset}
+ To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
+ % description
+ we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
+
+% network shape
+
+% network parameters
 
@@
 \end{document}
+
+% old parts
+
+% Meaning of CSI
+%[From Halperin paper]
+CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
+It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
+The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
+%[From Halperin End]
+
+% Structure of CSI
+%[From HC's ELM paper]
+In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
+$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
+The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
+The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
+\begin{equation}
+    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
+\end{equation}
+where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
+%[From HC's ELM end]
+
+% description of siamese
+In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
+% advantages of using Convnet filter
+Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
+The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.

### 2019-05-17 190410_Paper_ACPR/paper_v1.tex
Advp_a3: done_v1

@@
 % description of convnet
-Convolutional Neural Networks is a specal case of MLP and it has unified feature extractor and classifier in one network.
-It has been widely applied to visual objects such as image or video or 2D array input.
+Convolutional Neural Networks is a specal case of Multi Layer Perceptron and it has unified feature extractor and classifier in one network.
+It has been widely applied to visual objects such as image, video or 2D array input.
 Several factors make ConvNets attractive in image related tasks.
-Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.
-Weight sharing helps to reduce the number of weights in feature maps.
+Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.Weight sharing helps to reduce the number of weights in feature maps.
 Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
@@
 
-In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
+In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature which utilizes the Siamese network learning.
+\iffalse
 An overview of the proposed system is shown in Fig.1.
@@
 \end{figure}
+\fi
+Essentially, we train the verification model to identify the input pairs according to the probability on whether they belong to the same class or different classes.\cite{koch2015siamese} Subsequently, the
 
-% purpose of the system
-This system receives two Wi-Fi CSI signals as input.
-The main purpose of the system is to verify if two input signals are of the same signature.
-
-% main purpose1: interpreting CSI 
-Our system must have the ability to distinguish signatures by reading Wi-Fi CSI signals.
-% verification model
-The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.\cite{koch2015siamese}
-
+\iffalse
 % main purpose2: direction free
 Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
+\fi
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{network1.eps}
-    \caption{Structure of Siamese network} \label{network1}
+    \includegraphics[width=\textwidth]{network2.eps}
+    \caption{Structure of Siamese network} \label{network2}
 \end{figure}

### 2019-05-17 190509_AdvP_A3/dft_mpi/dft.cc

@@ -23,21 +23,42 @@ void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
     //MPI_Allgather(&data[n_start],width*(height/num_ranks)*sizeof(complex_t),MPI_BYTE,
     //recv_buffer,width*(height/num_ranks)*sizeof(complex_t),MPI_BYTE,MPI_COMM_WORLD);
     
-    //int n_start = width*(height/num_ranks)*rank_id; //starting position of this data block
-    complex_t *temp_recv_buffer = (complex_t*)malloc(m_recv_count * sizeof(complex_t));
+    int n_start = width*(height/num_ranks) * rank_id; //starting position of this data block
+    //complex_t *temp_recv_buffer = (complex_t*)malloc(m_recv_count * sizeof(complex_t));
+
+    // copy recv buffer to data
+    for(int i = 0; i < int(m_send_count/sizeof(complex_t)); i++) {
+        m_recv_buffer[n_start+i].~complex_t();
+        new (&m_recv_buffer[n_start+i]) complex_t(m_send_buffer[i]);   
+    }
 
     MPI_Request mpi_recv_request;
-    // receive a message from the previous process
-    MPI_Irecv(temp_recv_buffer,m_recv_count,MPI_BYTE,MPI_ANY_SOURCE,
-    rank_id, MPI_COMM_WORLD, &mpi_recv_request);
-    // send the message to the next process
-    MPI_Send(m_send_buffer,m_send_count,MPI_BYTE,
-            (rank_id+1)%num_ranks,(rank_id+1)%num_ranks, MPI_COMM_WORLD);
-    // receive a message from the last process
-    MPI_Status mpi_status;
-    MPI_Wait(&mpi_recv_request, &mpi_status);
+    for(int r = 0; r < num_ranks; r++) 
+    {
+        if(r!=rank_id)
+        {
+            // receive a message from the previous process
+            MPI_Irecv(&m_recv_buffer[width*(height/num_ranks)*r],m_recv_count,MPI_BYTE,MPI_ANY_SOURCE,
+            r, MPI_COMM_WORLD, &mpi_recv_request);
+            // send the message to the next process
+            MPI_Send(m_send_buffer,m_send_count,MPI_BYTE,
+            r,rank_id, MPI_COMM_WORLD);
+        }
+        
+    }
     
-    int temp_start = m_recv_count*mpi_status.MPI_SOURCE; //starting position of this data block
+    for(int k = 0; k < num_ranks-1 ; k++)
[…]

### 2019-05-18 190509_AdvP_A3/dft_mpi/dft.cc
AdvP_a3: markdown

@@ -9,7 +9,6 @@ using namespace std;
 //make global w array
 complex_t *w_arr = (complex_t*)malloc(512 * sizeof(complex_t));
 
-
 // Custom MPI_Allgather function with complex_t data type
 void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
                    complex_t *m_recv_buffer, int m_recv_count,
@@ -20,52 +19,38 @@ void mpi_allgather(complex_t *m_send_buffer, int m_send_count,
     // such as MPI_Allgather(), MPI_Gather, MPI_Scatter, or MPI_Broadcast.
     /* Assignment */
 
-    //MPI_Allgather(&data[n_start],width*(height/num_ranks)*sizeof(complex_t),MPI_BYTE,
-    //recv_buffer,width*(height/num_ranks)*sizeof(complex_t),MPI_BYTE,MPI_COMM_WORLD);
-    
-    int n_start = width*(height/num_ranks) * rank_id; //starting position of this data block
-    //complex_t *temp_recv_buffer = (complex_t*)malloc(m_recv_count * sizeof(complex_t));
+    //starting position of send data
+    int n_start = width*(height/num_ranks) * rank_id; 
 
-    // copy recv buffer to data
+    // copy values in its send buffer to receive buffer
     for(int i = 0; i < int(m_send_count/sizeof(complex_t)); i++) {
-        m_recv_buffer[n_start+i].~complex_t();
-        new (&m_recv_buffer[n_start+i]) complex_t(m_send_buffer[i]);   
+        m_recv_buffer[n_start+i].~complex_t(); // delete previous value of receive buffer
+        new (&m_recv_buffer[n_start+i]) complex_t(m_send_buffer[i]); // copy send buffer value to receive buffer
     }
 
-    MPI_Request mpi_recv_request;
-    for(int r = 0; r < num_ranks; r++) 
+    // send messages to other buffer
+    MPI_Request mpi_recv_request; // requese receive
+    for(int r = 0; r < num_ranks; r++) // send to other ranks
     {
-        if(r!=rank_id)
+        if(r!=rank_id) // dont send itself
         {
             // receive a message from the previous process
             MPI_Irecv(&m_recv_buffer[width*(height/num_ranks)*r],m_recv_count,MPI_BYTE,MPI_ANY_SOURCE,
             r, MPI_COMM_WORLD, &mpi_recv_request);
-            // send the message to the next process
+            // send the message to other buffer
[…]

### 2019-05-19 190410_Paper_ACPR/paper_v1.tex
paper_acpr: rev0517

@@
 \author{YoungWoong KWON\inst{1} \and
-JooYoung KIM\inst{1} \and
-Kar-Ann TOH\inst{1}}
+Jooyoung Kim\inst{1} \and
+Kar-Ann Toh\inst{1}}
 %
-\authorrunning{F. Author et al.}
+\authorrunning{Y. Kwon et al.}
 % First names are abbreviated in the running head.
@@
 \subsection{Contribution}
-- Overcome cons of WIFI signature systems
+- Overcome cons of WIFI signature system
 - Robust to signal direction, size
@@
 
-\subsection{System Overview}
-
 %system overview
@@
 In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature which utilizes the Siamese network learning.
-\iffalse
+
 An overview of the proposed system is shown in Fig.1.
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{methods1.eps}
-    \caption{Overview of the proposed system} \label{method1}
+    \includegraphics[width=\textwidth]{network2.eps}
+    \caption{Structure of Siamese network} \label{network2}
 \end{figure}
-\fi
+
 Essentially, we train the verification model to identify the input pairs according to the probability on whether they belong to the same class or different classes.\cite{koch2015siamese} Subsequently, the
@@
 % Methods 
-
-\subsection{Siamese Network For Verification}
-
-% Functions of Siamese in our system
-% Introduce Siamese Net
-
-Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
-\cite{koch2015siamese}
-
-Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
-The model outputs the probability that the two signals are of the same class.
-%it is learned by the back-propagation.
-This network consists of feature extraction and feature matching part.
-
 % Section: Feature Extraction
-\subsubsection{Feature Extraction}
+\subsubsection{Convolutional Neural Network for Feature Extraction}
 
@@
 % Figure 2
-\begin{figure}
-    \includegraphics[width=\textwidth]{network2.eps}
-    \caption{Structure of Siamese network} \label{network2}
-\end{figure}
+
 % weight tying
@@
 Through a convolution filter, each CSI signal is transformed into a feature vector. this entire process is jointly optimized by backpropagation.
+
+\subsection{Siamese Network For.}
+
+% Functions of Siamese in our system
+% Introduce Siamese Net
+
+Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
+\cite{koch2015siamese}
+
+Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
+The model outputs the probability that the two signals are of the same class.
+%it is learned by the back-propagation.
+This network consists of feature extraction and feature matching part.
 
@@
 \section{Experiments}
-% Dataset
-\subsubsection{Dataset}
- To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
- % description
- we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
 
-% network shape
-
-% network parameters
-
-% Network Learning
 \subsubsection{Loss and Backpropagation}
@@
 
+\end{document}
+
+%% Template End
+\section{*** Template ***}
+\section{First Section}
+\subsection{A Subsection Sample}
+Please note that the first paragraph of a section or subsection is
+not indented. The first paragraph that follows a table, figure,
+equation etc. does not need an indent, either.
+
+Subsequent paragraphs, however, are indented.
+
+\subsubsection{Sample Heading (Third Level)} Only two levels of
+headings should be numbered. Lower level headings remain unnumbered;
+they are formatted as run-in headings.
+
+\paragraph{Sample Heading (Fourth Level)}
+The contribution should contain no more than four levels of
+headings. Table~\ref{tab1} gives a summary of all heading levels.
+
+\begin{table}
+\caption{Table captions should be placed above the
+tables.}\label{tab1}
+\begin{tabular}{|l|l|l|}
+\hline
+Heading level &  Example & Font size and style\\
+\hline
+Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
+1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
+2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
+3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
+4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
+\hline
+\end{tabular}
+\end{table}
+
+\noindent Displayed equations are centered and set on a separate
+line.
+\begin{equation}
+x + y = z
+\end{equation}
+Please try to avoid rasterized images for line-art diagrams and
+schemas. Whenever possible, use vector graphics instead (see
+Fig.~\ref{fig1}).
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig1.eps}
+\caption{A figure caption is always placed below the illustration.
+Please note that short captions are centered, while long ones are
+justified by the macro package automatically.} \label{fig1}
+\end{figure}
+
+\begin{theorem}
+This is a sample theorem. The run-in heading is set in bold, while
+the following text appears in italics. Definitions, lemmas,
+propositions, and corollaries are styled the same way.
+\end{theorem}
+%
+% the environments 'definition', 'lemma', 'proposition', 'corollary',
+% 'remark', and 'example' are defined in the LLNCS documentclass as well.
+%
+\begin{proof}
+Proofs, examples, and remarks have the initial word in italics,
+while the following text appears in normal font.
+\end{proof}
+For citations of references, we prefer the use of square brackets
+and consecutive numbers. Citations using labels or the author/year
+convention are also acceptable. The following bibliography provides
+a sample reference list with entries for journal
+articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
+book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
+and a homepage~\cite{ref_url1}. Multiple citations are grouped
+\cite{ref_article1,ref_lncs1,ref_book1},
+\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{mybibliography}
+%
+\begin{thebibliography}{8}
+\bibitem{ref_article1}
+Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
+
+\bibitem{ref_lncs1}
+Author, F., Author, S.: Title of a proceedings paper. In: Editor,
+F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
+Springer, Heidelberg (2016). \doi{10.10007/1234567890}
+
+\bibitem{ref_book1}
+Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
+Location (1999)
+
+\bibitem{ref_proc1}
+Author, A.-B.: Contribution title. In: 9th International Proceedings
+on Proceedings, pp. 1--2. Publisher, Location (2010)
+
+\bibitem{ref_url1}
+LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
+Oct 2017
+\end{thebibliography}
 \end{document}

### 2019-05-20 190410_Paper_ACPR/paper_v1.tex
paper_acpr: update method

@@
 
-% description of siamese net
+% history of siamese net
 In \cite{bromley1994signature}, LeCun et al. Introduced Siamese nets as parts of their handwritten signature verification system. 
 A siamese neural network consists of twin networks which accept distinct inputs but are joined by an energy function at the top.\cite{koch2015siamese}
+
+% description of siamese net
+% from https://becominghuman.ai/siamese-networks-algorithm-applications-and-pytorch-implementation-4ffa3304c18
+
+It is important that not only the architecture of the subnetworks is identical, but the weights have to be shared among them as well for the network to be called “siamese”.
+Usually, siamese networks perform binary classification at the output, classifying if the inputs are of the same class or not
+
+% end site
+
 % differences in feature extractor
@@
 
+% another research which used Siamese Nets
+In a recent related study, pedestrian tracking \cite{Leal-Taixe_2016_CVPR_Workshops}, object cosegmedtation \cite{mukherjee2018object} showed that Siamese Networks can be used for image classification tasks and \cite{maheshwary2018matching} captures semantics from job resumes.
+
 \section{Proposed System}
 
-%system overview
+In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
+An overview of the proposed system utilizing the Siamese network learning is shown in Fig.1.
+Essentially, the Wi-Fi signature signals are preprocessed to create the input data for our Siamese network.
+Subsequently, the Siamese network using ConvNet structure is trained to measure the similarity between two inputs.
+The resultant similarity score is utilized to verify whether the input signals are belong to the same identity regardless of the capturing directions.
+The following subsections detail the
+data preprocessing and the Siamese network model.
 
-In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature which utilizes the Siamese network learning.
-
-An overview of the proposed system is shown in Fig.1.
 % Figure 1
 \begin{figure}
-    \includegraphics[width=\textwidth]{network2.eps}
-    \caption{Structure of Siamese network} \label{network2}
+    \includegraphics[width=\textwidth]{network3.eps}
+    \caption{Structure of Siamese network} \label{fig1}
 \end{figure}
 
-Essentially, we train the verification model to identify the input pairs according to the probability on whether they belong to the same class or different classes.\cite{koch2015siamese} Subsequently, the
-
-\iffalse
-% main purpose2: direction free
-Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
-\fi
-
-Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
-To classify regardless of the direction of the signal, we focused on the model shall be capable of extracting features unrelated to the direction.
-
-%% Pre-processing
 \subsection{Data Preprocessing}
 
-In order to be used as an input to a siamese network, the signal must be pre-processed.
-
-% used only abs value
-First, the signal has to be converted to non-complex form.
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.
-
-% preprocessing
-% From HC's Papaer
-Second, all inputs must be arranged of the same size.
-Since all signals have different length, the gradient operation with respect to the time instance is adapted to measure the short time energy. 
-Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
-And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}% HC's end
+Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy.
+Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.
+Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
+As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the Siamese network.
 
@@
 % Section: Feature Extraction
-\subsubsection{Convolutional Neural Network for Feature Extraction}
+\subsection{Siamese Networks for Identity Verification}
 
-% structure of siamese network
-To perform the feature extraction, we first need to have convolutional neural networks to serve as the feature extractor
-Based on the ConvNet structure.\cite{lecun1998gradient}
+To design the Siamese networks, we firstly need to select the feature extracting networks which convert the input data into a vector.
+In this work, we utilize the ConvNet structure \cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
 
-% structure of siamese network
-When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
-%Symmetric Architecture
-Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that help to classify signatures.
-some may be heavily influenced by the direction in which the signature was entered.
-Structure of the network is shown in Fig.2.
-% Figure 2
+Our ConvNet structure (See Fig~\ref{fig1} (b)) for the Siamese network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
+The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
+The Rectiﬁed Linear (ReLU) function as an activation function and the max-pooling layers are applied between each convolutional layers.
+The features from the last convolutional layer are directly flattened into a single vector without activation function and the Max-pooling layer followed by the fully-connected layer.
+Since the Siamese networks utilize two ConvNet structures which ties the weights each other, noting here that two structures described in Fig~\ref{fig1} (b) are actually the same model.
 
-% weight tying
-We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
-To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
-It was also designed to have the same weight on the symmetrical CNN network.
+The Siamese networks employ a learning process based on the similarity between two inputs~\cite{koch2015siamese}.
+In our Siamese networks, we utilize the $L_1$ distance to calculate the similarity score.
+Let $\mathbf{m}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{n}\in{\mathrm{R}}^{d\times1}$ be two feature vectors extracted from the ConvNet structure.
+Then the $L_1$ distance $d$ between the two features can be calculated as follows:
+\begin{equation}
+d = \sigma {\left\| {{\mathbf{m}} - {\mathbf{n}}} \right\|_1}  ,
+\end{equation}
+where $\sigma$ is the sigmoidal activation function.
 
-% sister networks
-This feature extractor is composed of two sister network, which are identical ConvNets with the exact same weights
+% Loss function and training
+The label $\mathnormal{y}$ for input $()\mathnormal{x}_{1},\mathnormal{x}_{2})$ becomes 1 when $()\mathnormal{x}_{1},\mathnormal{x}_{2})$ is in the same class and 0 otherwise.
+When the size of each minibatch is set to $\mathnormal{M}$, the label for the i-th batch is $\mathbf{y}_{i}(\mathnormal{x}_{1}^{(i)},\mathnormal{x}_{2}^{(i)})$.
 
-% CNN: purpose
-Purpose of ConvNet in our model is to extract a feature vector from the CSI signal.
+% optimization
+The loss function of our model is given by the following binary cross entropy and passed into standard backpropagation algorithm to calcuate weights.
 
-% parameters of convnet
-this ConvNets are consists of a number of consecutive convolution layers with active functions, and a pooling layer in the end.
-the Convolution Layer has n convolution filters in it.
+\begin{equation}
+    \mathnormal{BCE} = 
+    \mathbf{y}_{i}(\mathnormal{x}_{1}^{(i)},\mathnormal{x}_{2}^{(i)})
+    \log(\mathbf{d}(\mathnormal{x}_{1}^{(i)},\mathnormal{x}_{2}^{(i)}))+
+    (1-\mathbf{y}_{i}(\mathnormal{x}_{1}^{(i)},\mathnormal{x}_{2}^{(i)}))
+    \log(1-\mathbf{d}(\mathnormal{x}_{1}^{(i)},\mathnormal{x}_{2}^{(i)}))
+\end{equation}
 
-% functions of convnet
-Their weights are tied to extract the same characteristics from signals in different directions.
-By sharing their feature map, this ConvNet is trained to learn characteristics regardless of the direction.
-
-% outputs feature vector
-Through a convolution filter, each CSI signal is transformed into a feature vector. this entire process is jointly optimized by backpropagation.
-
-\subsection{Siamese Network For.}
-
-% Functions of Siamese in our system
-% Introduce Siamese Net
-
-Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
-\cite{koch2015siamese}
-
-Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
-The model outputs the probability that the two signals are of the same class.
-%it is learned by the back-propagation.
-This network consists of feature extraction and feature matching part.
-
-\subsubsection{Feature Matching}
-
-% Use L1 distances of Feature vector of 2 input images
-% From HC's In-Air paper below:
-Let $\mathbf{m}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{n}\in{\mathrm{R}}^{d\times1}$ be feature vectors extracted from two samples.
-The L-1 distance between the two features can be calculated as  follows:
-Where $\mathbf{p}$ denotes the L-1 distance. In the Siamese networks, this L-1 distance is utilized to match between two feature vectors.
-
-% From HC's End
-% From Oneshot paper below
-\begin{equation}
-    \mathbf{p} = 
-    \sigma(\sum_j\alpha_{j}\mid
-    \mathbf{m}_{1,L-1}^{(j)} - 
-    \mathbf{n}_{1,L-1}^{(j)}\mid)  
-\end{equation}
-where σ is the sigmoidal
-activation function.
-This final layer induces a metric on the learned feature space of the (L − 1)th hidden layer and scores the similarity between the two feature vectors.
-The αj are additional parameters that are learned by the model during training, weighting the importance of the component-wise distance.
-This defines a final Lth fully-connected layer for the network which joins the two Siamese twins.
-% From oneshot end
-
-The output of the CNN is feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
-In the proposed system, this Euclidean distance is utilized to match between two feature vectors.
+% weight initialization
+We initialized the weights of each layer to normal distribution with zero-mean and a standard deviation of 0.01.
+Biases are initialized to mean 0.5 and standard deviation 0.01, as presented in the paper\cite{koch2015siamese}.
 
 \section{Experiments}
-
-\subsubsection{Loss and Backpropagation}
- We impose a regularized cross-entropy objective on our binary classifier.
-This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
- We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2.
-Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
 

### 2019-05-23 190522_Wisig_KAR/mnist_cnn.py
wisig_kar: mnist cnn

@@ -1,0 +1,53 @@
+# keras version
+
+import keras
+keras.__version__
+
+
+#convnet filters
+from keras import layers
+from keras import models
+
+model = models.Sequential()
+model.add(layers.Conv2D(32, (3, 3), activation='relu', input_shape=(28, 28, 1)))
+model.add(layers.MaxPooling2D((2, 2)))
+model.add(layers.Conv2D(64, (3, 3), activation='relu'))
+model.add(layers.MaxPooling2D((2, 2)))
+model.add(layers.Conv2D(64, (3, 3), activation='relu'))
+
+model.summary()
+
+# add FC
+model.add(layers.Flatten())
+model.add(layers.Dense(64, activation='relu'))
+model.add(layers.Dense(10, activation='softmax'))
+
+model.summary()
+
+# import mnist data
+
+from keras.datasets import mnist
+from keras.utils import to_categorical
+
+(train_images, train_labels), (test_images, test_labels) = mnist.load_data()
+
+train_images = train_images.reshape((60000, 28, 28, 1))
+train_images = train_images.astype('float32') / 255
+
+test_images = test_images.reshape((10000, 28, 28, 1))
+test_images = test_images.astype('float32') / 255
+
+train_labels = to_categorical(train_labels)
+test_labels = to_categorical(test_labels)
+
+# training
+model.compile(optimizer='rmsprop',
+              loss='categorical_crossentropy',
+              metrics=['accuracy'])
+model.fit(train_images, train_labels, epochs=5, batch_size=64)
+
+# testing
+test_loss, test_acc = model.evaluate(test_images, test_labels)
+
+print(test_acc)
+

### 2019-07-04 190522_Wisig_KAR/siam_utils.py
wisig_siamkar: working

@@ -10,7 +10,8 @@ from sklearn.utils import shuffle
 from scipy.optimize import brentq
 from scipy.interpolate import interp1d
 from sklearn.metrics import roc_curve
-
+from datetime import datetime 
+import socket
 
 # function to return key for any value 
 def get_key(val,my_dict): 
@@ -21,7 +22,7 @@ def get_key(val,my_dict):
     return "key doesn't exist"
 
 
-def ReadData(PATH,n_splits):
+def ReadData(PATH,n_splits,rseed):
     print("loading data from {}".format(PATH))
     list_csi = []
     list_lab = []
@@ -57,7 +58,7 @@ def ReadData(PATH,n_splits):
     arr_csi = np.array(list_csi).swapaxes(0,1).reshape([50*len(file_list),10,500,30,6])
     arr_lab = np.array(list_lab).swapaxes(0,1).reshape([50*len(file_list),10])
 
-    skf = StratifiedKFold(n_splits,random_state=10)
+    skf = StratifiedKFold(n_splits,random_state=rseed)
     data_list = []
 
     arr_csi1 = arr_csi.reshape([-1,500,30,6])
@@ -87,12 +88,13 @@ def ReadData(PATH,n_splits):
         data_list.append([X,c,Xval,cval,Y,Yval])
     
     return(data_list)
-
-def eer_graphs(dist_truth,dist_score,pos_label):
+    
+def eer_graphs(dist_truth,dist_score,pos_label,save_path):
     fpr, tpr, thresholds = roc_curve(dist_truth, dist_score,pos_label=pos_label)
     eer = brentq(lambda x : 1. - x - interp1d(fpr, tpr)(x), 0., 1.)
 
     # ROC
+    fig = plt.figure()
     plt.plot(fpr, tpr, '.-')#, label=self.model_name)
     plt.plot([0, 1], [0, 1], 'k--', label="random guess")
 
@@ -100,7 +102,10 @@ def eer_graphs(dist_truth,dist_score,pos_label):
     plt.ylabel('True Positive Rate (Recall)')
     plt.title('Receiver Operating Characteristic curve')
     plt.legend()
+    fig.savefig(save_path + '_roc.png')
     plt.show()
+    #fig.savefig(res_path + 'fig_loss_' + timenow + '_' + str(splits) + '.png')
+    plt.close(fig)
 
     # EER
[…]

### 2019-07-04 190522_Wisig_KAR/siamkar_v1.py

@@ -8,47 +8,85 @@ from keras.losses import binary_crossentropy
 from siam_utils import get_key
 import numpy.random as rng
 import numpy as np
+from keras.utils.multi_gpu_utils import multi_gpu_model
+import socket
+
+host = socket.gethostname()
+
 
 def triplet_loss(y_true, y_pred):
     fc_size = 1024
-    alpha = 0.01
+    alpha = 0.05
     a_pred = y_pred[:, 0:fc_size]
     p_pred = y_pred[:, fc_size:2*fc_size]
     n_pred = y_pred[:, 2*fc_size:3*fc_size]
     pos_dist = tf.reduce_sum(tf.square(tf.subtract(a_pred, p_pred)), axis=-1)
     neg_dist = tf.reduce_sum(tf.square(tf.subtract(a_pred, n_pred)), axis=-1)
     basic_loss = tf.add(tf.subtract(pos_dist, neg_dist), alpha)
-    loss = tf.reduce_sum(tf.maximum(basic_loss, 0.0))
+    loss = tf.reduce_mean(tf.maximum(basic_loss, 0.0),0)
+    #basic_loss = tf.add(tf.subtract(pos_dist, neg_dist), fc_size)
+    #loss = tf.reduce_sum(basic_loss)
+    
     return loss
-
-# Network
+def W_init(shape,name=None):
+    """Initialize weights as in paper"""
+    values = rng.normal(loc=0,scale=1e-2,size=shape)
+    return K.variable(values,name=name)
+#//TODO: figure out how to initialize layer biases in keras.
+def b_init(shape,name=None):
+    """Initialize bias as in paper"""
+    values=rng.normal(loc=0.5,scale=1e-2,size=shape)
+    return K.variable(values,name=name)
+# Network: Siamese with Triplet loss
 input_shape = (500, 30, 6)
 ank_input = Input(input_shape)
 pos_input = Input(input_shape)
 neg_input = Input(input_shape)
 #build convnet to use in each siamese 'leg'
+'''
+convnet = Sequential()
+convnet.add(Conv2D(64,(3,3),activation='relu',input_shape=input_shape,padding='same',
+                   kernel_initializer=W_init,kernel_regularizer=l2(2e-4)))
+convnet.add(MaxPooling2D())
+convnet.add(Conv2D(128,(3,3),activation='relu',padding='same',
[…]

### 2019-07-04 190522_Wisig_KAR/wisig_siamese.py

@@ -5,8 +5,8 @@ import numpy.random as rng
 from keras.utils import to_categorical
 
 from siam_utils import *
-from siamkar_v1 import *
-from karnet_v1 import KARnet
+from siamkar_v1 import Siamese_Loader,siamese_net
+#from karnet_v1 import KARnet
 
 np.random.seed(8)
 %matplotlib inline
@@ -30,7 +30,7 @@ list_losstr = []
 list_losste = []
 for splits in range(len(data_skf)):
     data_list = data_skf[splits]
-    
+    '''
     # Train KARnet
     kar_x = np.squeeze(data_list[0]).reshape([-1,500*30*6])
     kar_labels = [get_key(i,data_list[1]) for i in range(len(kar_x))]
@@ -45,13 +45,11 @@ for splits in range(len(data_skf)):
     t1 = time.time()
     kar.train()
     print("KAR Training time : "+ str(time.time()-t1))
-    
+    '''
 
     #Instantiate the class
-    # Triplet 
-    loader = SiamKar_Loader(data_list,kar,dist_rate)
-    # Siamese
-    #loader = Siamese_Loader(data_list)
+    #loader = SiamKar_Loader(data_list,kar,dist_rate)
+    loader = Siamese_Loader(data_list)
 
     #Training loop
     print("!")
@@ -60,40 +58,40 @@ for splits in range(len(data_skf)):
     t1 = time.time()
     
     for i in range(0, n_iter):
-        #loss=loader.train(siamtri_net,n_epoch,batch_size,True)
+        #loss=loader.train(siamese_net,n_epoch,batch_size,True)
         (inputs,targets)=loader.get_batch(batch_size,s='train')
-        loss=siamtri_net.train_on_batch(inputs,targets)
+        loss=siamese_net.train_on_batch(inputs,targets)
         #print(loss)
         list_losstr.append([splits,loss])
 
         if i % loss_every == 0:
             (x_te,y_te)=loader.get_batch(n_val,s='val')
-            loss_te = siamtri_net.test_on_batch(x_te, y_te, sample_weight=None)
+            loss_te = siamese_net.test_on_batch(x_te, y_te, sample_weight=None)
             list_losste.append([splits,loss_te])
             print("iteration {}, training loss: {:.5f}, validation loss: {:.5f}".format(i,loss,loss_te))
             
[…]

### 2019-07-04 190522_Wisig_KAR/wisig_siamkar_v1.py

@@ -1,0 +1,180 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy.random as rng
+from keras.utils import to_categorical
+from siam_utils import *
+#from siamkar_v1 import *
+#from karnet_v1 import KARnet
+from datetime import datetime 
+import socket
+
+%matplotlib inline
+
+# Select Model Type
+model_type = 0 # SiamKar:0, SiamTri:1, Siamese:2
+alpha=0.05
+desc = 'def_siamese'
+
+if model_type==0:
+    from siamkar_v1 import SiamKar_Loader,siamtri_net
+    from karnet_v1 import KARnet
+elif(model_type==1):
+    from siamkar_v1 import SiamTri_Loader,siamtri_net
+elif(model_type==2):
+    from siamkar_v1 import Siamese_Loader,siamese_net
+
+## Data
+#PATH = "/home/herokwon/mount_data/Data/Wi-Fi_HC/180_100/"
+PATH = "D:\\Data\\WIFI\\Wi-Fi_HC\\180_100\\"
+# save path
+res_path = 'D:\\Git\\MILab\\190522_Wisig_KAR\\res\\'
+now = datetime.now()
+timenow = str(now).replace(' ','_').replace(':','_')
+col_df = (['timenow','host','model_type','rseed',
+'splits','n_val','dist_rate','batch_size','n_iter','alpha','lr','eer','trn_time','desc'])
+res_df = pd.read_csv(res_path + 'res_df.csv')
+
+#Read Data
+rseed=20
+np.random.seed(rseed)
+n_splits = 5
+data_skf = ReadData(PATH,n_splits,rseed=rseed)
+loss_every = 100
+n_val = 10
+dist_rate= 0.3
+batch_size = 32
+n_iter = 1500
+lr = 0.00001
+
+res_eer = pd.DataFrame()
+
+list_losstr = []
+list_losste = []
+for splits in range(len(data_skf)):
+    data_list = data_skf[splits]
+    
+    if model_type==0:
+        # Train KARnet
+        kar_x = np.squeeze(data_list[0]).reshape([-1,500*30*6])
+        kar_labels = [get_key(i,data_list[1]) for i in range(len(kar_x))]
+        kar_y = to_categorical(kar_labels)
+
+        kar_xval = np.squeeze(data_list[2]).reshape([-1,500*30*6])
[…]

### 2019-07-05 190410_Paper_ACPR/paper_tcnn_kar.tex
paper_acpr_v2: start method

--- 2019-05-17 190410_Paper_ACPR/paper_v1.tex
@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{amsmath}
 
@@
 %
-\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal}
+\title{Deep triplet network adopting the kernel and the range space learning for Wi-Fi signature verification}
 %
@@
 
-\subsection{ConvNets}
-% description of convnet
-Convolutional Neural Networks is a specal case of Multi Layer Perceptron and it has unified feature extractor and classifier in one network.
-It has been widely applied to visual objects such as image, video or 2D array input.
-Several factors make ConvNets attractive in image related tasks.
-Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.Weight sharing helps to reduce the number of weights in feature maps.
-Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
-%
+\subsection{WIFI CSI}
+- An In-Air Signature Verification System Using Wi-Fi Signals
 
-\subsection{Siamese Networks}
+% Meaning of CSI
+%[From Halperin paper]
+CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
+It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
+The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
+%[From Halperin End]
+
+% Structure of CSI
+%[From HC's ELM paper]
+In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
+$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
+The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
+The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
+\begin{equation}
+    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
+\end{equation}
+where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
+%[From HC's ELM end]
+
+\subsection{ConvNet with triplet loss}
 
@@
 They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector.
+Apart from this work based on ConvNet as feature extractor and L1 distance as feature matcher.
+In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
+% advantages of using Convnet filter
+Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
+The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.
 
@@
 
-\subsection{System Overview}
+In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
+An overview of the proposed system utilizing the ConvNet with triplet loss is shown in Fig.1.
+Essentially, the Wi-Fi signature signals are preprocessed to create the input data for our network.
+Subsequently, the ConvNet structure is trained to minimize distance from anchor to positive input while maximize distance from anchor to negative inputs.
+The following subsections detail the data preprocessing and the proposed method.
 
-%system overview
-
-In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature which utilizes the Siamese network learning.
-\iffalse
-An overview of the proposed system is shown in Fig.1.
 % Figure 1
 \begin{figure}
-    \includegraphics[width=\textwidth]{methods1.eps}
-    \caption{Overview of the proposed system} \label{method1}
+    \includegraphics[width=\textwidth]{fig1_network_structure.pdf}
+    \caption{Structure of the network} \label{fig1}
 \end{figure}
-\fi
-Essentially, we train the verification model to identify the input pairs according to the probability on whether they belong to the same class or different classes.\cite{koch2015siamese} Subsequently, the
 
-\iffalse
-% main purpose2: direction free
-Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
-\fi
-
-Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
-To classify regardless of the direction of the signal, we focused on the model shall be capable of extracting features unrelated to the direction.
-
-%% Pre-processing
 \subsection{Data Preprocessing}
 
-In order to be used as an input to a siamese network, the signal must be pre-processed.
-
-% used only abs value
-First, the signal has to be converted to non-complex form.
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.
-
-% preprocessing
-% From HC's Papaer
-Second, all inputs must be arranged of the same size.
-Since all signals have different length, the gradient operation with respect to the time instance is adapted to measure the short time energy. 
-Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
-And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}% HC's end
+Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy.
+Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.
+Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
+As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
 
 % Methods 
+% Section: Feature Extraction
+\subsection{ConvNets with triplet loss}
 
-\subsection{Siamese Network For Verification}
+To design the proposed networks, we firstly need to select the feature extracting networks which convert the input data into a vector.
+In this work, we utilize the ConvNet structure \cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
 
-% Functions of Siamese in our system
-% Introduce Siamese Net
+Our ConvNet structure (See Fig~\ref{fig1} (b)) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
+The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
+The Rectiﬁed Linear (ReLU) function as an activation function and the max-pooling layers are applied between each convolutional layers.
+The features from the last convolutional layer are directly flattened into a single vector without activation function and the Max-pooling layer followed by the fully-connected layer.
+%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
 
-Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
-\cite{koch2015siamese}
+In our proposed networks, we utilize the $L_2$ distance to calculate the triplet loss.
+For the $i_{th}$ signal as anchor input $\mathbf{I}_{i,anc}$, positive input $\mathbf{I}_{i,pos}$ is belong to the same class for anchor input while negative input $\mathbf{I}_{i,neg}$ is from another class.
+Let $\mathbf{x}_{i,anc}\in{\mathrm{R}}^{d\times1}$, $\mathbf{x}_{i,pos}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{x}_{i,neg}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
+Then the loss for the triplet inputs can be calculated as follows:
+\begin{equation}
+loss = \sum_i^N { \left[ {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,pos}}} \right\|_2^2} -
+{\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,neg}}} \right\|_2^2}  + \alpha \right]_+},
+\end{equation} 
+where $\alpha$ is the margin to make distance between positive and negative pairs, N is size of the mini-batch.
 
-Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
-The model outputs the probability that the two signals are of the same class.
-%it is learned by the back-propagation.
-This network consists of feature extraction and feature matching part.
+% KAR learning
+\subsection{Triplet selection by the kernel and the range space learning}
 
-% Section: Feature Extraction
-\subsubsection{Feature Extraction}
+% importance of selecting hard pos/neg
+in \cite{schroff2015facenet}, when training triplet loss networks, it is important to take hard positive and hard negative sample for faster convergence of the loss function.
 
-% structure of siamese network
-To perform the feature extraction, we first need to have convolutional neural networks to serve as the feature extractor
-Based on the ConvNet structure.\cite{lecun1998gradient}
+% methods of KAR learning
+since we don't know which is the hard sample before training entire network, we make multilayer feedforward neural network instead to select the hard positive and the hard negative.
+we adopted gradient-free learning to train this network. by the kernel and the range (KAR) space projection learning \cite{toh2018learning,toh2018gradient}.
 
-% structure of siamese network
-When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
-%Symmetric Architecture
-Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that help to classify signatures.
-some may be heavily influenced by the direction in which the signature was entered.
-Structure of the network is shown in Fig.2.
-% Figure 2
-\begin{figure}
-    \includegraphics[width=\textwidth]{network2.eps}
-    \caption{Structure of Siamese network} \label{network2}
-\end{figure}
-% weight tying
-We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
-To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
-It was also designed to have the same weight on the symmetrical CNN network.
+% training KARnet
+first, let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$.
 
-% sister networks
-This feature extractor is composed of two sister network, which are identical ConvNets with the exact same weights
+set multilayer neural network structure 
+\begin{equation}
+\mathbf{Y} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
+\end{equation}
 
-% CNN: purpose
-Purpose of ConvNet in our model is to extract a feature vector from the CSI signal.
+where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,
+$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathrm{R}}^{m \times 1}$
+and $\sigma(.)$ is activation function.
 
-% parameters of convnet
-this ConvNets are consists of a number of consecutive convolution layers with active functions, and a pooling layer in the end.
-the Convolution Layer has n convolution filters in it.
+the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ can be separated into weights and bias term,
+$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
+$\begin{bmatrix}
+\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
+\end{bmatrix}
+\dots
+\begin{bmatrix}
+\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
+\end{bmatrix}$
 
-% functions of convnet
-Their weights are tied to extract the same characteristics from signals in different directions.
-By sharing their feature map, this ConvNet is trained to learn characteristics regardless of the direction.
+after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we can get $\mathbf{W}_{1}$. the equation can be solved as follows:
 
-% outputs feature vector
-Through a convolution filter, each CSI signal is transformed into a feature vector. this entire process is jointly optimized by backpropagation.
+\begin{equation}
+\left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
+\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
+\end{equation}
 
-\subsubsection{Feature Matching}
+%\begin{equation}
+\begin{multline*}
+\Rightarrow
+\biggl[\sigma^{-1}\biggl(
+\dots
+\biggl[\sigma^{-1}\biggl(
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+\biggr)\\
+- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+\dots\biggr) 
+- \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
+= \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
+\end{multline*}
+%\end{equation}
 
-% Use L1 distances of Feature vector of 2 input images
-% From HC's In-Air paper below:
-Let $\mathbf{m}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{n}\in{\mathrm{R}}^{d\times1}$ be feature vectors extracted from two samples.
-The L-1 distance between the two features can be calculated as  follows:
-Where $\mathbf{p}$ denotes the L-1 distance. In the Siamese networks, this L-1 distance is utilized to match between two feature vectors.
+\begin{multline*}
+\Rightarrow
+\mathbf{X}^{\dagger}\sigma^{-1}\biggl(
+\biggl[\sigma^{-1}\biggl(
+\dots
+\biggl[\sigma^{-1}\biggl(
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+\biggr)\\
+- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+\dots\biggr)
+- \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
+= \mathbf{W}_{1}
+\end{multline*}
 
-% From HC's End
-% From Oneshot paper below
+after getting $\mathbf{W}_{1}$, $\mathbf{W}_{2}$ can also be optimized
+
+\begin{multline*}
+\Rightarrow
+\left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
+\biggl(\dots
+\biggl[\sigma^{-1}\biggl(
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+\biggr)
+- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+\dots\biggr)\\ 
+= \mathbf{W}_{2}
+\end{multline*}
+
+Repeat this process recursively until all weight maxtrix values are obtained.
+finally, $\mathbf{W}_{i}$ can be obtained as follows:
+
 \begin{equation}
-    \mathbf{p} = 
-    \sigma(\sum_j\alpha_{j}\mid
-    \mathbf{m}_{1,L-1}^{(j)} - 
-    \mathbf{n}_{1,L-1}^{(j)}\mid)  
+    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right),
 \end{equation}
-where σ is the sigmoidal
-activation function.
-This final layer induces a metric on the learned feature space of the (L − 1)th hidden layer and scores the similarity between the two feature vectors.
-The αj are additional parameters that are learned by the model during training, weighting the importance of the component-wise distance.
-This defines a final Lth fully-connected layer for the network which joins the two Siamese twins.
-% From oneshot end
-
-The output of the CNN is feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
-In the proposed system, this Euclidean distance is utilized to match between two feature vectors.
 
@@
 \end{document}
-
-% old parts
-
-% Meaning of CSI
-%[From Halperin paper]
-CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
-It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
-The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
-%[From Halperin End]
-
-% Structure of CSI
-%[From HC's ELM paper]
-In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
-$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
-The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
-The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
-\begin{equation}
-    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
-\end{equation}
-where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
-%[From HC's ELM end]
-
-% description of siamese
-In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
-% advantages of using Convnet filter
-Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
-The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.

### 2019-07-08 190410_Paper_ACPR/paper_tcnn_kar.tex
paper_acpr: methods

@@
 
-\subsection{ConvNet with triplet loss}
+\subsection{the kernel and the range space learning}
 
-% description of siamese net
-In \cite{bromley1994signature}, LeCun et al. Introduced Siamese nets as parts of their handwritten signature verification system. 
-A siamese neural network consists of twin networks which accept distinct inputs but are joined by an energy function at the top.\cite{koch2015siamese}
-% differences in feature extractor
-They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector.
-Apart from this work based on ConvNet as feature extractor and L1 distance as feature matcher.
-In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
-% advantages of using Convnet filter
-Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
-The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.
+Multilayer feedforward neural networks has been widely used to feature extractor and classifier.
+For traning the feedforward multilayer networks, non-gradient learning method by using linear matrix equation has invented recently. \cite{wang2018review}
 
+This model avoids the problems of the deep learning model such as vanishing gradient and local minima.
+And except for the number of layers and neurons used in the network, there are few parameters for the network configuration.
+
+More recently, a new learning framework has been developed to train the weights of the deep networks by a series of kernel and range space manipulations \cite{toh2018gradient,toh2018learning}.
+This method allows to quickly learn the weights of the deep network with little  system resources.
+we adopted this method to mining negative samples for the anker signal.
+
+%% Methods
 \section{Proposed System}
@@
 In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
-An overview of the proposed system utilizing the ConvNet with triplet loss is shown in Fig.1.
+An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) is shown in Fig.1.
 Essentially, the Wi-Fi signature signals are preprocessed to create the input data for our network.
-Subsequently, the ConvNet structure is trained to minimize distance from anchor to positive input while maximize distance from anchor to negative inputs.
-The following subsections detail the data preprocessing and the proposed method.
+Subsequently, the training dataset is moved to KAR space learning.
+it mines the hard positve and negative samples for given anchor signal from training dataset whtout using gradient.
+ConvNet structure extract feature vectors from given triplet using convnet filters.
+ConvNet training is achived by triplet loss, which is L2 distance of given feature vectors of the triplet. 
+The following subsections detail the proposed method.
 
@@
 
-\subsection{Data Preprocessing}
+% Methods: Triplet loss
+\subsection{Triplet loss}
 
-Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy.
-Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.
-Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
-As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
+Our proposed networks utilizes the $L_2$ distance to calculate the triplet loss.
+For the $i_{th}$ signal as anchor input $\mathbf{I}_{i,anc}$, positive input $\mathbf{I}_{i,pos}$ is belong to the same class for anchor input while negative input $\mathbf{I}_{i,neg}$ is from another class.
+Let $\mathbf{x}_{i,anc}\in{\mathrm{R}}^{d\times1}$, $\mathbf{x}_{i,pos}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{x}_{i,neg}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
+Then the loss for the triplet inputs can be calculated as follows:
+\begin{equation}
+loss = \sum_i^N { \left[ {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,pos}}} \right\|_2^2} -
+{\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,neg}}} \right\|_2^2}  + \alpha \right]_+},
+\end{equation} 
+where $\alpha$ is the margin to make distance between positive and negative pairs, N is size of the mini-batch.
++ sign means greater between zero or calculated loss.
 
-% Methods 
-% Section: Feature Extraction
-\subsection{ConvNets with triplet loss}
+% Methods: KAR learning
+
+\subsection{Triplet mining by the kernel and the range space learning}
+
+% importance of selecting hard pos/neg
+in \cite{schroff2015facenet}, when training triplet loss networks, it is important to take hard positive and hard negative sample for faster convergence of the loss function.
+
+% methods of KAR learning
+since we don't know which is the hard sample before training entire network, we make multilayer feedforward neural network to select the hard positive and the hard negative.
+we adopted gradient-free, the kernel and the range (KAR) space projection learning to train multilayer feedforward neural network. \cite{toh2018learning,toh2018gradient}.
+
+% training KARnet
+first, multilayer neural network structure is shown below:
+
+\begin{equation}
+\mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
+\end{equation}
+
+let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathrm{R}}^{m \times n}$ is network outputs.
+
+network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$ instead of $\mathbf{G}$.
+
+the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ can be separated into weights and bias term,
+$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
+$\begin{bmatrix}
+\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
+\end{bmatrix}
+\dots
+\begin{bmatrix}
+\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
+\end{bmatrix}$.
+
+where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,
+$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathrm{R}}^{m \times 1}$
+and $\sigma(.)$ is activation function.
+
+after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we can get $\mathbf{W}_{1}$. the equation can be solved as follows:
+
+\begin{equation}
+\left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
+\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
+\end{equation}
+
+%\begin{multline*}
+\begin{equation}
+\begin{aligned}
+\Rightarrow
+\biggl[\sigma^{-1}\biggl(
+\dots
+\biggl[\sigma^{-1}\biggl(
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+\biggr)
+- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+\dots\biggr)\\
+- \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
+= \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
+%\end{multline*}
+\end{aligned}
+\end{equation}
+
+%\begin{multline*}
+\begin{equation}
+\begin{aligned}
+\Rightarrow
+\mathbf{X}^{\dagger}\sigma^{-1}\biggl(
+\biggl[\sigma^{-1}\biggl(
+\dots
+\biggl[\sigma^{-1}\biggl(
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+\biggr)
+- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+\dots\biggr)\\
+- \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
+= \mathbf{W}_{1}
+\end{aligned}
+\end{equation}
+%\end{multline*}
+
+after getting $\mathbf{W}_{1}$, $\mathbf{W}_{2}$ can also be optimized
+
+\begin{equation}
+\begin{aligned}
+%\begin{multline*}
+\Rightarrow
+\left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
+\biggl(\dots
+\biggl[\sigma^{-1}\biggl(
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+\biggr)
+- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+\dots\biggr)\\
+= \mathbf{W}_{2}
+%\end{multline*}
+\end{aligned}
+\end{equation}
+
+Repeat this process recursively until all weight maxtrix values are obtained.
+finally, $\mathbf{W}_{i}$ can be obtained as follows:
+
+\begin{equation}
+    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right),
+\end{equation}
+
+when anker signal is set, negative samples can be mined if the distance of network output $\mathbf{G}$ is above the threshold.
+
+% Methods: ConvNets
+\subsection{ConvNet Structures}
 
@@
 
-In our proposed networks, we utilize the $L_2$ distance to calculate the triplet loss.
-For the $i_{th}$ signal as anchor input $\mathbf{I}_{i,anc}$, positive input $\mathbf{I}_{i,pos}$ is belong to the same class for anchor input while negative input $\mathbf{I}_{i,neg}$ is from another class.
-Let $\mathbf{x}_{i,anc}\in{\mathrm{R}}^{d\times1}$, $\mathbf{x}_{i,pos}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{x}_{i,neg}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
-Then the loss for the triplet inputs can be calculated as follows:
-\begin{equation}
-loss = \sum_i^N { \left[ {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,pos}}} \right\|_2^2} -
-{\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,neg}}} \right\|_2^2}  + \alpha \right]_+},
-\end{equation} 
-where $\alpha$ is the margin to make distance between positive and negative pairs, N is size of the mini-batch.
+\section{Experiments}
 
-% KAR learning
-\subsection{Triplet selection by the kernel and the range space learning}
-
-% importance of selecting hard pos/neg
-in \cite{schroff2015facenet}, when training triplet loss networks, it is important to take hard positive and hard negative sample for faster convergence of the loss function.
-
-% methods of KAR learning
-since we don't know which is the hard sample before training entire network, we make multilayer feedforward neural network instead to select the hard positive and the hard negative.
-we adopted gradient-free learning to train this network. by the kernel and the range (KAR) space projection learning \cite{toh2018learning,toh2018gradient}.
-
-% training KARnet
-first, let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$.
-
-set multilayer neural network structure 
-\begin{equation}
-\mathbf{Y} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
-\end{equation}
-
-where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,
-$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathrm{R}}^{m \times 1}$
-and $\sigma(.)$ is activation function.
-
-the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ can be separated into weights and bias term,
-$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
-$\begin{bmatrix}
-\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
-\end{bmatrix}
-\dots
-\begin{bmatrix}
-\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
-\end{bmatrix}$
-
-after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we can get $\mathbf{W}_{1}$. the equation can be solved as follows:
-
-\begin{equation}
-\left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
-\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
-\end{equation}
-
-%\begin{equation}
-\begin{multline*}
-\Rightarrow
-\biggl[\sigma^{-1}\biggl(
-\dots
-\biggl[\sigma^{-1}\biggl(
-    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
-\biggr)\\
-- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
-\dots\biggr) 
-- \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
-= \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
-\end{multline*}
-%\end{equation}
-
-\begin{multline*}
-\Rightarrow
-\mathbf{X}^{\dagger}\sigma^{-1}\biggl(
-\biggl[\sigma^{-1}\biggl(
-\dots
-\biggl[\sigma^{-1}\biggl(
-    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
-\biggr)\\
-- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
-\dots\biggr)
-- \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
-= \mathbf{W}_{1}
-\end{multline*}
-
-after getting $\mathbf{W}_{1}$, $\mathbf{W}_{2}$ can also be optimized
-
-\begin{multline*}
-\Rightarrow
-\left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
-\biggl(\dots
-\biggl[\sigma^{-1}\biggl(
-    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
-\biggr)
-- \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
-\dots\biggr)\\ 
-= \mathbf{W}_{2}
-\end{multline*}
-
-Repeat this process recursively until all weight maxtrix values are obtained.
-finally, $\mathbf{W}_{i}$ can be obtained as follows:
-
-\begin{equation}
-    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right),
-\end{equation}
-
-\section{Experiments}
 % Dataset
@@
  To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
+ % pre-processing
+ Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy.
+Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.
+Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
+As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
  % description
@@
 % Network Learning
-\subsubsection{Loss and Backpropagation}
- We impose a regularized cross-entropy objective on our binary classifier.
+\subsubsection{ConvNet structure}
+ We impose a triplet loss objective on our classifier.
 This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.

### 2019-07-09 190410_Paper_ACPR/paper_tcnn_kar.tex
paper_acpr: methods

@@
 \author{YoungWoong KWON\inst{1} \and
-JooYoung KIM\inst{1} \and
-Kar-Ann TOH\inst{1}}
+Jooyoung Kim \inst{1} \and
+Kar-Ann Toh\inst{1}}
 %
@@
 This model avoids the problems of the deep learning model such as vanishing gradient and local minima.
-And except for the number of layers and neurons used in the network, there are few parameters for the network configuration.
+And except for the number of layers and number of neurons in the network, no more parameters are needed for the network configuration.
 
-More recently, a new learning framework has been developed to train the weights of the deep networks by a series of kernel and range space manipulations \cite{toh2018gradient,toh2018learning}.
+More recently, a new learning framework has been developed to train the weights of the deep networks by a series of kernel and range space projection method \cite{toh2018learning,toh2018gradient}.
 This method allows to quickly learn the weights of the deep network with little system resources.
-we adopted this method to mining negative samples for the anker signal.
+we adopted this method to mining negative samples for the training dataset.
 
@@
 In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
-An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) is shown in Fig.1.
+An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.
 Essentially, the Wi-Fi signature signals are preprocessed to create the input data for our network.
 Subsequently, the training dataset is moved to KAR space learning.
-it mines the hard positve and negative samples for given anchor signal from training dataset whtout using gradient.
-ConvNet structure extract feature vectors from given triplet using convnet filters.
-ConvNet training is achived by triplet loss, which is L2 distance of given feature vectors of the triplet. 
+KAR space learning generates triplet data by mining the hard positve and hard negative samples for given anchor signal.
+generated triplet data flows into ConvNet structure. ConvNet extracts feature vectors by using filters.
+ConvNet training is achived by triplet loss, which is formulated by the L-2 distance of feature vectors for the triplet. 
 The following subsections detail the proposed method.
@@
 
-Our proposed networks utilizes the $L_2$ distance to calculate the triplet loss.
-For the $i_{th}$ signal as anchor input $\mathbf{I}_{i,anc}$, positive input $\mathbf{I}_{i,pos}$ is belong to the same class for anchor input while negative input $\mathbf{I}_{i,neg}$ is from another class.
+Our proposed networks utilizes the L-2 distance to calculate the triplet loss for given triplet input.
+For the $i_{th}$ anchor input signal $\mathbf{I}_{i,anc}$, triplet input can be generated by grouping positive input signal $\mathbf{I}_{i,pos}$ and negative input signal $\mathbf{I}_{i,neg}$.
+positive input is drawn from the same identity for anchor signal and negative input is chosen from another identity for the anchor.
+Generated triplet $\left\{\mathbf{I}_{i,anc},\mathbf{I}_{i,pos},\mathbf{I}_{i,neg}\right\}$ is the input to the ConvNet structure.
 Let $\mathbf{x}_{i,anc}\in{\mathrm{R}}^{d\times1}$, $\mathbf{x}_{i,pos}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{x}_{i,neg}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
-Then the loss for the triplet inputs can be calculated as follows:
+The triplet loss for the inputs can be calculated as follows:
 \begin{equation}
@@
 \end{equation} 
-where $\alpha$ is the margin to make distance between positive and negative pairs, N is size of the mini-batch.
-+ sign means greater between zero or calculated loss.
+where $\alpha$ is the margin between distances from anchor to positive and anchor to negative, N is size of the mini-batch. (+) means greater number between zero or calculated loss.
 
@@
 % importance of selecting hard pos/neg
-in \cite{schroff2015facenet}, when training triplet loss networks, it is important to take hard positive and hard negative sample for faster convergence of the loss function.
+Regarding to \cite{schroff2015facenet}, it is important to take hard positive and hard negative sample for faster convergence of the loss when training triplet networks.
+hard positive sample means distance between feature vectors from positive signal to anchor signal is the greatest, while hard negative sample means distance between feature vectors from negative signal to anchor signal is the smallest.
 
 % methods of KAR learning
-since we don't know which is the hard sample before training entire network, we make multilayer feedforward neural network to select the hard positive and the hard negative.
-we adopted gradient-free, the kernel and the range (KAR) space projection learning to train multilayer feedforward neural network. \cite{toh2018learning,toh2018gradient}.
+since we don't know which is the hard sample before training the network, we train multilayer feedforward neural network to mine the hard positive and the hard negative from traning dataset.
+For training multilayer neural network, we adopted gradient-free the kernel and the range (KAR) space projection learning. \cite{toh2018learning,toh2018gradient}.
 
-% training KARnet
-first, multilayer neural network structure is shown below:
+% Karnet structure and mining samples.
+Let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathrm{R}}^{m \times n}$ is network outputs.
+Multilayer neural network structure is shown below:
 
@@
 
-let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathrm{R}}^{m \times n}$ is network outputs.
+$\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
+\in{\mathrm{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
 
-network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$ instead of $\mathbf{G}$.
+when all weights have been learned, for given anker signal, hard negative samples can be mined among the distance of network output of desired signal $\mathbf{G}$ is below the threshold.
 
-the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ can be separated into weights and bias term,
+% training KARnet
+Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
+After that, we have the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ to train. the weight matrix can be separated into weights and bias term as
 $\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
@@
 
-where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,
-$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathrm{R}}^{m \times 1}$
-and $\sigma(.)$ is activation function.
-
-after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we can get $\mathbf{W}_{1}$. the equation can be solved as follows:
+after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we get $\mathbf{W}_{1}$. it is solved as follows:
 
@@
         = \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
-%\end{multline*}
     \end{aligned}
 \end{equation}
+%\end{multline*}
 
@@
 
+%\begin{multline*}
 \begin{equation}
     \begin{aligned}
-%\begin{multline*}
         \Rightarrow
@@
         = \mathbf{W}_{2}
-%\end{multline*}
     \end{aligned}
 \end{equation}
+%\end{multline*}
 
@@
 
-when anker signal is set, negative samples can be mined if the distance of network output $\mathbf{G}$ is above the threshold.
-
 % Methods: ConvNets
@@
 
-To design the proposed networks, we firstly need to select the feature extracting networks which convert the input data into a vector.
+To design the proposed networks, we firstly need to select the feature extracting networks which convert the triplet data into a feature vector.
 In this work, we utilize the ConvNet structure \cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
@@
 The Rectiﬁed Linear (ReLU) function as an activation function and the max-pooling layers are applied between each convolutional layers.
-The features from the last convolutional layer are directly flattened into a single vector without activation function and the Max-pooling layer followed by the fully-connected layer.
+The features from the last convolutional layer are directly flattened into a single vector.
+we used sigmoid activation at ConvNet output and L-2 normalize output vectors to prevent negative distance when calculating triplet loss.
+
 %Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
@@
  We impose a triplet loss objective on our classifier.
-This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
- We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2.
-Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
+This objective is combined with standard backpropagation algorithm.
+ We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 0.01.
+Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 0.01.
+ all layers are L-2 regularized using parameters of 0.0002. for output layer, regularization is 0.001
+
+ For KARnet trainied multilayer neural networks, we set 2 layer and number of neurons are [1024,128]. initialized as uniform distribution over [0, 1).
+ activation and inverse activation functions are [arctan, tan].
 

### 2019-07-10 190410_Paper_ACPR/paper_tcnn_kar.tex
paper_acpr: rel works

@@
 \subsection{Motivation}
-i. Pros of In-Air WIFI CSI signature system
-1) Cheap: Use commercial device
-2) Easy: No additional devices is needed
-3) Secure: Hard to forgery
-ii. Cons of In-Air WIFI CSI signature system
-1) Setting direction problem
-a) Different direction -> Different feature is needed
-b) Hard to set exactly same direction as authentication before
-Size of signature can varies
 
 \subsection{Contribution}
-- Overcome cons of WIFI signature system
-- Robust to signal direction, size
 
@@
 
-\subsection{WIFI CSI}
-- An In-Air Signature Verification System Using Wi-Fi Signals
+\subsection{ConvNets with triplet input}
+ConvNets with triplet input is widely used in face recognition \cite{schroff2015facenet} and person re-id \cite{cheng2016person,chen2017beyond}.
+The distinction between classes may be ambiguous in the above tasks. This is because the targets may be looking in different directions or taking different positions.
+Triplet ConvNets works by extract feature vectors which expand margins between same class and different class,so it has good ability to distinguish between classes.
 
-% Meaning of CSI
-%[From Halperin paper]
-CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
-It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
-The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
-%[From Halperin End]
+but loss function depends on the distance between each triplet samples, loss can be down to 0, when negative class distance is much more greater than positive distance.
+also, outliers affects a lot to training.
+so it is important to optimize the training process when traning triplet ConvNets.
 
-% Structure of CSI
-%[From HC's ELM paper]
-In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
-$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
-The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
-The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
-\begin{equation}
-    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
-\end{equation}
-where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
-%[From HC's ELM end]
+There are many ways to optimize training. in \cite{schroff2015facenet}, they selects appropriate samples from large mini-batch before each traning iteration.
+in \cite{cheng2016person}, they adopt second margin to triplet loss and expand intra-class distance.
+in \cite{chen2017beyond}, they made quadruplet loss, which makes the distance between the same classes, 
+regardless of class, is less than the distance between the different classes.
+
+in this paper, we adopt the kernel and the range space learning to select good samples for training triplet ConvNets.
+it has advantage for reducing computing resources, speed up training, and optimize training.
 
@@
 The triplet loss for the inputs can be calculated as follows:
+
 \begin{equation}
@@
 \end{equation}
+
 where $\alpha$ is the margin between distances from anchor to positive and anchor to negative, N is size of the mini-batch. (+) means greater number between zero or calculated loss.

### 2019-07-11 190410_Paper_ACPR/paper_tcnn_kar.tex
paper_acpr: method_update_fig

@@
 \subsection{ConvNets with triplet input}
+
 ConvNets with triplet input is widely used in face recognition \cite{schroff2015facenet} and person re-id \cite{cheng2016person,chen2017beyond}.
 The distinction between classes may be ambiguous in the above tasks. This is because the targets may be looking in different directions or taking different positions.
-Triplet ConvNets works by extract feature vectors which expand margins between same class and different class,so it has good ability to distinguish between classes.
+Triplet ConvNets works by extract feature vectors which expand margins between same class and different class, so it has good ability to distinguish between classes.
 
-but loss function depends on the distance between each triplet samples, loss can be down to 0, when negative class distance is much more greater than positive distance.
+Loss function depends on the distance between each triplet samples, loss can be down to 0, when negative class distance is much more greater than positive distance.
 also, outliers affects a lot to training.
@@
 
-in this paper, we adopt the kernel and the range space learning to select good samples for training triplet ConvNets.
-it has advantage for reducing computing resources, speed up training, and optimize training.
+in this paper, we adopt multilayer feedforward networks, trained by the kernel and the range space learning to select good samples for training triplet ConvNets.
+it has advantage for reducing computing resources, speed up and optimize training.
 
@@
 
+% Methods: System overview(Fig.1)
 In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
 An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.
-Essentially, the Wi-Fi signature signals are preprocessed to create the input data for our network.
-Subsequently, the training dataset is moved to KAR space learning.
-KAR space learning generates triplet data by mining the hard positve and hard negative samples for given anchor signal.
-generated triplet data flows into ConvNet structure. ConvNet extracts feature vectors by using filters.
-ConvNet training is achived by triplet loss, which is formulated by the L-2 distance of feature vectors for the triplet. 
+
+Essentially, the Wi-Fi signature signals are separated to create the training and validation data.
+Subsequently, KAR space projection learning generates triplet data by mining the hard positve and hard negative samples for given anchor signal from training dataset.
+
+For training ConvNet structure, generated triplet data flows into ConvNet structure. ConvNet extracts feature vectors from given triplet.
+ConvNet training is achived by triplet loss, which is formulated by the L-2 distance metrics of feature vectors.
+ConvNet network is trained by backpropagation.
 The following subsections detail the proposed method.
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{fig1_network_structure.pdf}
+    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v1}
     \caption{Structure of the network} \label{fig1}
@@
 
-Our proposed networks utilizes the L-2 distance to calculate the triplet loss for given triplet input.
-For the $i_{th}$ anchor input signal $\mathbf{I}_{i,anc}$, triplet input can be generated by grouping positive input signal $\mathbf{I}_{i,pos}$ and negative input signal $\mathbf{I}_{i,neg}$.
-positive input is drawn from the same identity for anchor signal and negative input is chosen from another identity for the anchor.
-Generated triplet $\left\{\mathbf{I}_{i,anc},\mathbf{I}_{i,pos},\mathbf{I}_{i,neg}\right\}$ is the input to the ConvNet structure.
-Let $\mathbf{x}_{i,anc}\in{\mathrm{R}}^{d\times1}$, $\mathbf{x}_{i,pos}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{x}_{i,neg}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
+Triplet loss is used to train ConvNet to extract feature vector better from triplet input.
+For the $i_{th}$ anchor input signal $\mathbf{X}_{anc,i}$, triplet input is generated by grouping positive input signal $\mathbf{X}_{pos,i}$, which drawn from the same identity for anchor and negative input signal $\mathbf{X}_{neg,i}$, chosen from another identity for the anchor.
+Generated triplet input $\left\{\mathbf{X}_{anc,i},\mathbf{X}_{pos,i},\mathbf{X}_{neg,i}\right\}$ is fed into the ConvNet structure one by one and makes anchor, positive and negative feature vectors.
+
+Let $\mathbf{v}_{anc,i}\in{\mathrm{R}}^{d\times1}$, $\mathbf{v}_{pos,i}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{v}_{neg,i}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
+
+triplet loss is calculated by comparing positive distance(L-2 distance from anchor to positive feature vector)and negative distance(L-2 distance from anchor to negative feature vector).
+ConvNet is trained to maximize gap between positive distance to negative distance more than margin $\alpha$.
+
 The triplet loss for the inputs can be calculated as follows:
@@
 \begin{equation}
-    loss = \sum_i^N { \left[ {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,pos}}} \right\|_2^2} -
-    {\left\| {{\mathbf{x}_{i,anc}} - {\mathbf{x}_{i,neg}}} \right\|_2^2}  + \alpha \right]_+},
+    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right)
 \end{equation}
 
-where $\alpha$ is the margin between distances from anchor to positive and anchor to negative, N is size of the mini-batch. (+) means greater number between zero or calculated loss.
+where N is size of the mini-batch.
+note that triplet loss can down to 0 when negative distance is longer than positive distance more than margin $\alpha$.
+if we select proper triplet for training, we can avoid this problem and make convergence of the loss function faster. This can be done by selecting hard triplet.
 
@@
 Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.
+
  Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
@@
  we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
-
-% network shape
-
-% network parameters
 
@@
  activation and inverse activation functions are [arctan, tan].
+
+\subsubsection{Results}
+\subsubsection{Training Efficiency}
 

### 2019-07-23 190410_Paper_ACPR/paper_combined.tex
paper_acpr: submit abstract

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath}

\begin{document}
%
\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
%
\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network. 
To refine the triplet inputs for the faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.

\keywords{Wi-Fi signature signal \and in-air handwritten signature verification \and the Kernel and the Range space projection learning \and triplet network}
\end{abstract}
%
%
%
\section{Introduction}

In recent years, several behavioral biometric traits for identity authentication are investigated since they are free from the physical characteristic which user owns~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature based user authentication~\cite{galbally2015line,sanmorino2012survey} is taking considerable interest with the development of the in-air signature recognition systems~\cite{galbally2015line,jeon2012system,malik20183dairsig}. 
With the help of sensors such as a depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition systems could have less spatial limitation in the signature acquisition process compare to other contact-based authentication systems.

Recently, the commercial Wi-Fi device is also proposed to be utilized as a in-air signature acquisition sensor due to its easy accessible property \cite{moon2017air}. By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Components Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal. To achieve not only the promising verification accuracy but also the fast training loss convergence speed for the commercial use, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs for training the triplet network. Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained using the mined triplet inputs based on L-2 distance comparison.
The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using deep triplet network.
\item Adopted the KAR space learning to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in triplet network.
\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
\end{itemize}

The paper is organized as follows: the related works including triplet network and KAR space learning will be introduced in Section 2 for immediate reference. Our proposed method will be discussed in Section 3. Section 4 describes our experimental results and analysis. Some concluding remarks will be followed in Section 5.

\section{Related Works}

\subsection{Triplet Network}
A Triplet network is comprised of 3 instances of the same feedforward network (with shared parameters)\cite{hoffer2015deep}. It is widely used in face recognition \cite{schroff2015facenet} and person re-identification, which solves the matching problem of individuals and identity between camera images\cite{cheng2016person,chen2017beyond}.
The distinction between classes may be ambiguous in the above tasks since the targets may be looking in different directions or taking different positions.
to achieve good ability to distinguish between classes, a triplet network works by extract feature vectors which expand margins between same and different class.

The loss function of triplet network is calculated as the difference in L-2 distance between anchor to each positive and negative triplet outputs.
Optimizing the training process is important because gradient vanishing can occur during training.
It happens when the negative class distance is much greater than positive class distance, the output of the loss function can down to zero as a result.
%Also, outliers in triplet input affects a lot to training since The loss function for triplet network depends on the distance between each triplet input.

There are many ways to optimize training. In \cite{schroff2015facenet}, selects inputs from large mini-batch at each training iteration using the network during training. \cite{cheng2016person} adds second margin for triplet loss to expand intra-class distance.
Following in \cite{chen2017beyond}, quadruplet loss function makes the distance between the same classes is less than the distance between any different classes.

In this paper, we adopt multilayer feedforward networks trained by the kernel and the range space learning to select good triplet input for training the triplet network. It has advantage for reducing computing resources as well as boosting the training optimization.
% Rel works: KAR learning
\subsection{kernel and the range space learning}

Multilayer feedforward neural networks is widely known to be good for feature extractor and classifier.
This network is generally trained by the gradient descent method and backpropagation.
However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.

%This training methods makes networks to fell into problems such as vanishing gradient or local minima.
%To avoid these problems, it is important to set the learning parameters such as learning rate or momentum value before training.

%Recently, according to \cite{guo2004pseudoinverse}, based on linear algebric method and pseudo-inverse, gradient-free learning methods is invented.
%Howeaver, network weights of the hidden layer has to be fixed as equal to the number of examples.

Recently, gradient-free learning framework based on series of kernel and range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
since it is trained by algebric methods, no learning parameters are needed to train the networks.
%there is no problems of vanishing gradient and local minima, 
using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.

% Karnet structure and mining samples.
Let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathrm{R}}^{m \times n}$ is network outputs.
Multilayer neural network structure is shown below:

\begin{equation}
    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathrm{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.

When all weights have been learned, for given anchor signal, hard negative samples can be mined among the distance of network output of desired signal $\mathbf{G}$ is below the threshold.

% training KARnet
Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
After that, we have the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ to train. the weight matrix can be separated into weights and bias term as
$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
$\begin{bmatrix}
\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
\end{bmatrix}
\dots
\begin{bmatrix}
\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
\end{bmatrix}$.

after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we get $\mathbf{W}_{1}$. it is solved as follows:

\begin{equation*}
    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
    \sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
\end{equation*}
\begin{equation*}
    \begin{aligned}
        \Rightarrow
        \biggl[\sigma^{-1}\biggl(
        \dots
        \biggl[\sigma^{-1}\biggl(
            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
        \biggr)
        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
        \dots\biggr)\\
        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
        = \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
    \end{aligned}
\end{equation*}
\begin{equation}
    \begin{aligned}
        \Rightarrow
        \mathbf{X}^{\dagger}\sigma^{-1}\biggl(
        \biggl[\sigma^{-1}\biggl(
        \dots
        \biggl[\sigma^{-1}\biggl(
            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
        \biggr)
        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
        \dots\biggr)\\
        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
        = \mathbf{W}_{1} .
    \end{aligned}
\end{equation}

After deriving the $\mathbf{W}_{1}$, the $\mathbf{W}_{2}$ also can be optimized as:

%\begin{multline*}
\begin{equation}
    \begin{aligned}
        \Rightarrow
        \left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
        \biggl(\dots
        \biggl[\sigma^{-1}\biggl(
            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
        \biggr)
        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
        \dots\biggr)\\
        = \mathbf{W}_{2} .
    \end{aligned}
\end{equation}
%\end{multline*}

By repeating this process recursively until all weight matrix values are obtained, the $\mathbf{W}_{i}$ can be obtained as follows:
\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right).
\end{equation}

%% Methods
\section{Proposed System}

% Methods: System overview(Fig.1)
In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter). An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.

Essentially, the Wi-Fi signature signals are randomly divided to create the training and the validation set. Subsequently, the KAR space projection learning generates the triplet data by mining the hard positve and the hard negative samples for the given anchor signal from the training dataset.

To train the ConvNet structure, generated triplet data flows into the predifined ConvNet structure. The ConvNet extracts feature vectors from given triplet input.
ConvNet training is achieved by the triplet loss, which is formulated by the L-2 distance metrics of feature vectors. The overall ConvNet network is trained by the backpropagation scheme. The following subsections detail the each step of the proposed system.

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v2}
    \caption{Structure of the network} \label{fig1}
\end{figure}

% Methods: Triplet loss
\subsection{Triplet loss}

Triplet loss is used to train ConvNet to extract feature vector from triplet input.
For the $i_{th}$ anchor input signal $\mathbf{X}_{anc,i}$, triplet input is generated by grouping the positive input signal $\mathbf{X}_{pos,i}$ drawn from the same identity with anchor signal and the negative input signal $\mathbf{X}_{neg,i}$ is chosen from the another identity with the anchor signal.
Generated triplet input $\left\{\mathbf{X}_{anc,i},\mathbf{X}_{pos,i},\mathbf{X}_{neg,i}\right\}$ is fed into the ConvNet structure one by one and respectively makes anchor, positive and negative feature vectors.

Let $\mathbf{v}_{anc,i}\in{\mathrm{R}}^{d\times1}$, $\mathbf{v}_{pos,i}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{v}_{neg,i}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure. 
the triplet loss is calculated by comparing positive distance (L-2 distance from the anchor vector to the positive feature vector) and negative distance (L-2 distance from the anchor vector to the negative feature vector).
ConvNet is trained to maximize gap between positive distance to negative distance more than margin $\alpha$.
The triplet loss for the inputs can be calculated as follows:

\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),
\end{equation}

where N is size of the mini-batch.
Note that the triplet loss can down to 0 when the negative distance is bigger than the positive distance more than preset margin $\alpha$.
If we select proper triplet for training, we can avoid this problem and make the convergence of the loss function faster.

% Methods: KAR learning
\subsection{Triplet mining by kernel and the range space learning}
According to \cite{schroff2015facenet}, it is important to take hard positive and hard negative sample for faster convergence of the loss when training triplet networks.
we adopted KAR space learnig methods to approximate the ConvNet structure and mine the hard positive and the hard negative samples from the training dataset.

% importance of selecting hard pos/neg
Hard positive sample means distance between feature vectors from positive signal to anchor signal is the greatest, while hard negative sample means distance between feature vectors from negative signal to anchor signal is the smallest.

% methods of KAR learning
Since we don't know which is the hard sample before training the network, we propose to train multilayer feedforward neural network to mine the hard positive and the hard negative from the traning dataset.
To train the multilayer neural network, we adopted the kernel and the range (KAR) space projection learning (see Section2.2 for details).
% Methods: ConvNets
\subsection{ConvNet Structures}

To design the proposed networks, we firstly need to select the feature extracting networks which convert the triplet data into a feature vector. In this work, we utilize the ConvNet structure \cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.

Our ConvNet structure (See Fig~\ref{fig1} (b)) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$. The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1. The Rectiﬁed Linear (ReLU) function as an activation function and the max-pooling layers are applied between each convolutional layers. The features from the last convolutional layer are directly flattened into a single vector.
We used the sigmoid activation at ConvNet output and L-2 normalize output vectors to prevent negative distance when calculating triplet loss.

%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.

\section{Experiments}

% Dataset
\subsubsection{Dataset}
 In order to evaluate the verification performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used. Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas). Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.

 % pre-processing
 Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy. Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action. Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals. As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.

\subsubsection{Experimental Settings}

\subsubsection{1) Performance Evaluation}
% performance evaluation
The porposed method is evaluated under comparision of the proposed method with other verification methods based on verification accuracy.
verification performance is compared with existing linear methods in literature such as LSE, SVM and TER. Moreover, proposed method is compared by ConvNet based Siamese networks,we used same ConvNet model for our proposed method and Siamese network.

% Evaluation protocols
Validation performance of the proposed and other linear deep learning methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests.

\subsubsection{2) Network Structure}
 We impose a triplet loss as objective function on our classifier. This objective is combined with standard backpropagation algorithm.
 The structure of the ConvNet network is specified in Table \ref{tab1}. we train the network starting with a learning rate of 0.00001 via Cross Entropy loss with a mini-batch sized of 32. We optimize the loss by the Adam optimizer with L-2 penalty of 0.0002 except for output layer. Output layer is regularized with L-2 penalty of 0.0001.
 We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 0.01. Biases were also initialized from a normal distribution of standard deviation of 0.01, but with 0.5 mean.
 Training is conduced with 2000 iterations, which set empirically.

 \begin{table}[]
    \caption{The structure of ConvNet}\label{tab1}
    \centering
    \begin{tabular}{|l|l|l|l|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & 3x3x64 / 1      & 500x30x6   \\
    MaxPool 1 &            & 2x2 / 1         & 500x30x64  \\
    Conv 2    & ReLU       & 3x3x128 / 1     & 250x15x64 \\
    MaxPool 2 &            & 2x2 / 1         & 250x15x128 \\
    Conv 3    & ReLU       & 3x3x256 / 1     & 125x8x128  \\
    MaxPool 3 &            & 2x2 / 1         & 125x8x256  \\
    Dense     & Sigmoid    & 128             & 63x4x256   \\
    L-2 Norm  &            &                 & 1x1x128    \\
    Concat    &            &                 & 1x1x384    \\ \hline
    \end{tabular}
\end{table}

For KARnet trainied multilayer neural networks is shown below (Table \ref{tab2}), we set 2 layer and number of neurons are [1024,16]. initialized as uniform distribution over [0, 1).
Used arctangent as activation function.

\begin{table}[]
    \caption{The structure of KARnet}\label{tab2}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500x30x6 &            \\
    Dense 1 & 1x1x1024 & ArcTan     \\
    Dense 2 & 1x1x128  & ArcTan     \\
    Output  & 1x1x50   &            \\ \hline
    \end{tabular}
\end{table}

\subsubsection{3) Parameter Settings}
For making triplet loss, 0.1 of alpha value is utilized for the proposed method.
we choose output vector size of 16.
For linear methods such as LSE,SVM and TER, we reduced dimension of input signal to 500x30, by averaging through subcarrier axis. Due to limitation of hardware memory.
For PCA-LSE, input dimension is reduced by 40 sized features using PCA.
For Triplet CNN without KAR learning, we choose signature randomly for making input triplets and used triplet loss as used in proposed methods.
for Siamese Networks, we put 2 random signal as input and used binary loss for training the networks.

\subsubsection{Results and Discussion}

Table \ref{tab3} shows the best average EER performances obtained by the compared methods. The test EER was averaged from five runs of two-fold cross-validation.
Comparing with ConvNet based Siamese and Triplet CNN without KAR learning, proposed methods showed the best EER performance. Due to negative mining process included in making triplet loss.
The proposed method showed much better EER than linear methods, such as SVM,LSE and TER. Since linear methods use reduced input signal.

% Loss Curve
Loss curves of proposed method are shown in Fig.\ref{fig2}.
This shows that KAR learning not only helps ConvNet to train faster, but also makes it to extract better features. As the proposed method shows steeper loss curve when training, and the variance of the validation loss is smaller.

\begin{table}[]
    \caption{Verification Performance}\label{tab3}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    Proposed(TripletCNN with KAR learning) &   19.09   &   lr=0.00005, alpha=0.1  \\
    Triplet CNN without KAR learning    &   20.08   &   lr=0.00005, alpha=0.1  \\
    Siamese CNN  &   24.09   &   lr=0.00005, alpha=0.1  \\
    SVM(RBF)    &   24.31   &   c=1, gamma=0.01/3000 \\
    SVM(Linear) &   28.23   &   c=1 \\
    LSE(Dimension Reduction by PCA)    &   30.79   &  40 dimension input    \\
    TER &   35.75   &   order=1   \\
    LSE &   48.44   &   \\  \hline
    \end{tabular}
\end{table}

% Figure 2
\begin{figure}
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30.eps}
    \caption{Training Loss Curve of the Proposed Method} \label{fig2}
\end{figure}
% Figure 3
\begin{figure}
    \includegraphics[width=\textwidth]{fig_roc.pdf}
    \caption{ROC Curve of the Proposed Method} \label{fig3}
\end{figure}

\section{Conclusion}
In this paper, we proposed a novel identity verification system based on Wi-Fi signature signals. 
In order to train the triplet network effectively, triplet input is mined from Wi-Fi signature signals by the kernel and the range space learning. Subsequently, ConvNet structure is adopted for feature extractor which generates feature vectors from input triplets. Finally, the triplet network is trained by matching between extracted feature vectors based on L-2 distance comparison. Our networks show good feature extracting performance, especially in low-dimension outputs and shows encouraging experimental results in terms of verification accuracy.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%

%\begin{thebibliography}{8}

\bibliographystyle{splncs04}
\bibliography{bib_acpr}

%\end{thebibliography}

\end{document}

### 2019-07-23 190410_Paper_ACPR/paper_v2.tex
paper_acpr: submit abstract

--- 2019-07-23 190410_Paper_ACPR/paper_combined.tex
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v2}
+    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v3}
     \caption{Structure of the network} \label{fig1}
@@
 Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}.
-we used only absolute value.
+We used only the absolute value of a complex CSI signal since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal\cite{wang2015understanding}.
 
@@
 Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
-As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
+As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the triplet network.
 
@@
 % performance evaluation
-The porposed method is evaluated under comparision of the proposed method with other verification methods based on verification accuracy.
-verification performance is compared with existing linear methods in literature such as LSE, SVM and TER.
-Moreover, proposed method is compared by ConvNet based Siamese networks,we used same ConvNet model for our proposed method and Siamese network.
+The porposed method is evaluated with other methods based on verification accuracy.
+verification performance is compared with existing linear methods in literature such as Least Square Estimation(LSE), Support Vector Machine(SVM) and Total Error Rate(TER) minimization\cite{toh2008between}.
+Moreover, proposed method is compared by Siamese network\cite{koch2015siamese} and varlinna Triplet network\cite{hoffer2015deep} without mining, which are ConvNet based deep learning structure.
+We used same ConvNet structure for our proposed method and compared deep learning structure.
 

### 2019-07-23 190522_Wisig_KAR/siamkar_v2.py

@@ -8,12 +8,13 @@ from keras.losses import binary_crossentropy
 from siam_utils import get_key
 import numpy.random as rng
 import numpy as np
+from keras.utils.multi_gpu_utils import multi_gpu_model
 
-fc_size = 128
+fc_size = 512
 
 def triplet_loss(y_true, y_pred):
     #fc_size = 128
-    alpha = 0.005
+    alpha = 0.05
     a_pred = y_pred[:, 0:fc_size]
     p_pred = y_pred[:, fc_size:2*fc_size]
     n_pred = y_pred[:, 2*fc_size:3*fc_size]
@@ -166,7 +167,7 @@ siamese_net = Model(inputs=[left_input,right_input],outputs=prediction)
 
 class SiamTri_Loader:
     """For loading batches and testing tasks to a siamese net"""
-    def __init__(self, data_list,lr,data_subsets = ["train", "val"]):
+    def __init__(self, data_list,lr,host,data_subsets = ["train", "val"]):
         self.data = {}
         self.categories = {}
         self.info = {}
@@ -177,11 +178,15 @@ class SiamTri_Loader:
         self.data["val"] = Xval_d
         self.categories["train"] = c_d
         self.categories["val"] = cval_d
+        self.host = host
         self.lr = lr
-        self.net = siamtri_net
+        
+        if(host=='pregpu-2k80'):
+            self.net = multi_gpu_model(siamtri_net, gpus=2)
+        else:
+            self.net = siamtri_net
         self.net.compile(loss=triplet_loss,optimizer=Adam(self.lr))
         self.net.summary()
-
 
     def get_batch(self,batch_size,s):
         """Create batch of n pairs, half same class, half different class"""
@@ -241,14 +246,14 @@ class SiamTri_Loader:
         model.fit_generator(self.generate(batch_size),steps_per_epoch=epochs//batch_size)
 
 class SiamKar_Loader(SiamTri_Loader):
-    def __init__(self,data_list,kar,dist_rate,lr,data_subsets = ["train", "val"]):
-        super(SiamKar_Loader, self).__init__(data_list,lr)
+    def __init__(self,data_list,kar,lr,host,data_subsets = ["train", "val"]):
+        super(SiamKar_Loader, self).__init__(data_list,lr,host)
         #super(SiamKar_Loader, self).__init__(net)
         #super(SiamKar_Loader, self).__init__(lr)
         #super(SiamKar_Loader, self).__init__(alpha)
         self.kar = kar
[…]

### 2019-07-23 190522_Wisig_KAR/wisig_karnet_v2.py

@@ -1,0 +1,219 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy.random as rng
+from keras.utils import to_categorical
+from siam_utils import *
+from importlib import reload
+#from siamkar_v1 import *
+#from karnet_v1 import KARnet
+from datetime import datetime 
+import socket
+import tensorflow as tf
+import siamkar_v2
+import karnet_v1
+#from siamkar_v2 import SiamKar_Loader,SiamTri_Loader,Siamese_Loader,siamtri_net,siamese_net
+#from karnet_v1 import KARnet
+%matplotlib inline
+
+%matplotlib inline
+
+host = socket.gethostname()
+## Data
+if(host=='pregpu-2k80'):
+    PATH = "/home/herokwon/mount_data/Data/Wi-Fi_HC/180_100/"
+    res_path = '/home/herokwon/Git/MILab/190522_Wisig_KAR/res/'
+else:
+    PATH = "D:\\Data\\WIFI\\Wi-Fi_HC\\180_100\\"
+    # save path
+    res_path = 'D:\\Git\\MILab\\190522_Wisig_KAR\\res\\'
+
+
+col_df = (['timenow','host','model_type','rseed',
+'splits','n_val','fc_size','batch_size','n_iter','alpha','lr','eer','trn_time','desc'])
+
+try:
+    res_df = pd.read_csv(res_path + 'res_df_v2.csv')
+except FileNotFoundError:
+    res_df = pd.DataFrame()
+
+alpha=0.05
+fc_size = 512
+host = socket.gethostname()
+
+desc = 'def_siamese_karlast1024_reloadnets'
+
+types = [0,1,2]
+seeds = [10,20,30,40,50]
+
+for rseed  in seeds:
+    for model_type in types:        
+        np.random.seed(rseed)        
+        n_splits = 2
+        data_skf = ReadData(PATH,n_splits,rseed=rseed)
+        loss_every = 100
+        n_val = 10
+        batch_size = 32
+        n_iter = 1500
+        lr = 0.0001
+
+        for splits in range(len(data_skf)):
+            now = datetime.now()
+            timenow = str(now).replace(' ','_').replace(':','_')
+            
+            res_eer = pd.DataFrame()
+            list_losstr = []
+            list_losste = []
+            data_list = data_skf[splits]            
+            
+            if model_type==0:
+                #reimport
+                siamkar_v2 = reload(siamkar_v2)
[…]

### 2019-07-30 190410_Paper_ACPR/combined.tex
acpr2019: submit

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{subfigure}

\begin{document}
%
\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
%
\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
To refine the triplet inputs for faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training set of Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.

\keywords{Wi-Fi signature signal \and in-air handwritten signature verification \and the Kernel and the Range space projection learning \and triplet network}
\end{abstract}
%
%
%
\section{Introduction}

In recent years, several behavioral biometric traits for identity authentication are investigated since they are free from the physical characteristic which user owns~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature based user authentication~\cite{galbally2015line,sanmorino2012survey} is taking considerable interest with the development of the in-air signature recognition systems~\cite{galbally2015line,jeon2012system,malik20183dairsig}. 
With the help of sensors such as a depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition systems could have less spatial limitation in the signature acquisition process compare to other contact-based authentication systems.

Recently, the commercial Wi-Fi device is also proposed to be utilized as a in-air signature acquisition sensor due to its easy accessible property \cite{moon2017air}. By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Components Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal. To achieve not only the promising verification accuracy but also the fast training loss convergence speed for the commercial use, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs for training the triplet network. Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained using the mined triplet inputs based on L-2 distance comparison.
The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using deep triplet network.
\item Adopted the KAR space learning to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in triplet network.
\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
\end{itemize}

The paper is organized as follows: the related works including triplet network and KAR space learning will be introduced in Section 2 for immediate reference. Our proposed method will be discussed in Section 3. Section 4 describes our experimental results and analysis. Some concluding remarks will be followed in Section 5.

\section{Related Works}

\subsection{Triplet Network}
% triplet network
Triplet network is a kind of metric learning model~\cite{} which aims to learn useful representations by distance comparisons~\cite{hoffer2015deep}. It is widely used in person re-identification, which solves the matching problem of individuals and identity between camera images~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. 
Distinction between classes may be ambiguous in this task as the similarity features between an individual is relatively small compare to the background features such as pose, hair and textures.

% training triplet network
To address this problem, the training of the triplet network is making feature vectors to be placed in the appropriate separation space, making the positive (similar) data more closer to the anchor (reference) and the negative (dissimilar) data to keep away from the anchor. Triplet network receives above triplet data as an input, which is the anchor (reference), positive (similar) and negative (dissimilar) data.

% optimize training
Since myriad triplet pairs can be generated in the training set, training with all possible triplets may time-consuming and unnecessary. Optimizing training becomes necessary by mining the efficient triplet pairs out of all possible pairs.
\cite{cheng2016person,ding2015deep,wang2016joint} generates triplet only for small classes, which randomly selected in each iteration.
Recently, \cite{schroff2015facenet} used triplet mining strategy for faster convergence speed. They selects inputs from large mini-batch at each training iteration using the network during training.
However, a lot of training data is necessary to make such a large-sized mini-batch.

% Rel works: KAR learning
\subsection{kernel and the range space learning}\label{kar}

The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation.
However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.

Recently, gradient-free learning framework based on series of the kernel and the range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
Since it is trained by linear equations, no learning parameters nor the iteration are needed to train the networks.
Using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.

% Karnet structure and mining samples.
Let the training dataset $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ is network outputs.
Multilayer neural network structure is shown below:
\begin{equation}
    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.

Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$. $\mathbf{W}_{i}$ can be obtained as follows:

\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right).
\end{equation}

%% Methods
\section{Proposed System}

% Methods: System overview(Fig.1)
In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter) using triplet network. Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network~\cite{schroff2015facenet}.
Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from the each given anchor sample in the training dataset (item (a) in Fig.~\ref{fig1}).
Subsequently, the ConvNet structure in the triplet network (item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (item (c) in Fig.~\ref{fig1}).
The following subsections detail the triplet mining using KAR space learning and the triplet network.

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v3}
    \caption{An overview of the proposed system} \label{fig1}
\end{figure}

% Methods: KAR learning
\subsection{Triplet mining using kernel and the range space learning}
According to \cite{schroff2015facenet}, it is important to select the hard positive sample and the hard negative sample from each given anchor sample for the faster loss convergence when training the triplet network.
The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the smallest (which is most likely to be misclassified as a positive sample). However, there is no information about which sample is the hard positive/negative sample before we train the network.

In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative sample from the given anchor sample. Since the KAR space learning has no iterative learning process, we can mine the triplet samples without train an another network with backpropagation process.

By training the KAR space network with the training samples, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network. For each training sample as an anchor sample $\mathbf{x}_{anc}$ and to measure the distance between $\mathbf{x}_{anc}$ and other samples, we firstly need to train the KAR space learning structure $f\left(.\right)$ using whole training sample matrix $\mathbf{X}\in \mathbb{R}^{n\times m}$ as follows~\cite{toh2018gradient}:
\begin{equation}
    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
where $\mathbf{X}$ is a stacked matrix of $m$ training sample vectors, $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$, $\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$, $\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is an activation function.

Following, the hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ from the input anchor sample $\mathbf{x}_{anc}$ can be respectively selected among the positive samples and the negative samples as follows:
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}, \label{pos}
\end{equation}
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg},\label{neg}
\end{equation}
where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the threshold to make the sample more harder. Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative sample rather than just using the hardest positive/negative sample since the hardest samples are likely to be an outlier which degrades the training process of the triplet network.
We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples match the equations.

% Methods: ConvNets
\subsection{ConvNet Structures}

To design the triplet network, we firstly need to select the feature extractor which converts the input triplet data into feature vectors. In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.

Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$. The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1. The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layers. Following, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.

%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.

% Methods: Triplet loss
\subsection{Triplet loss}

The triplet loss function is proposed in \cite{hoffer2015deep} to train the triplet network.
For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping with the hard positive input sample $\mathbf{x}_{pos,i}$ and the hard negative input sample $\mathbf{x}_{neg,i}$ selected based on the KAR space learning. Generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, positive and negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.

Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:
\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
\end{equation} 
where N denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

\section{Experiments}

% Dataset
\subsection{Dataset}
 In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with single position was utilized in our experiments. After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500 $\times$ 30 $\times$ 6. We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal~\cite{wang2015understanding}.

\subsection{Experimental Settings}

\subsubsection{Performance Evaluation}
The proposed system is evaluated under two cases: i) case I on comparison of the proposed system with other linear methods and deep learning based methods based on verification accuracy, and case II on detailed comparison with the deep learning based methods using receiver operating characteristic (ROC) curve and training loss curve. For the Case I, existing linear methods such as the least squares error estimation (LSE), the principalcomponents analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between} and deep learning based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and baseline triplet network utilized same ConvNet structures with the proposed system and only differed in the input data style and the loss function.

The verification performance of the proposed system and other methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests. Due to the memory constraint caused by the large data size, noting here that deep learning based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number with the number of the positive pairs.

\subsubsection{Network Structure and Parameter Settings}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With an input data size of 500 $\times$ 30 $\times$ 6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used ArcTangent function as an activation function following~\cite{toh2018gradient}.

\begin{table}[]
    \caption{The network structure of KAR space learning}\label{tab2}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500x30x6 &            \\
    Dense 1 & 1x1x1024 & ArcTan     \\
    Dense 2 & 1x1x128  & ArcTan     \\
    Output  & 1x1x50   &            \\ \hline
    \end{tabular}
\end{table}

For the proposed system and the deep learning based methods, we utilized same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 with a mini-batch sized of 32. We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for output layer. The output layer is regularized with L-2 penalty of 0.0001. We initialized all network weights in the convolutional layers with a normal distribution with zero-mean and a standard deviation of 0.01. Biases were also initialized with a normal distribution with 0.5 mean and a standard deviation of 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set to 0.1. The training epochs are set to 1,500 for all three deep learning based algorithms. For the linear methods such as LSE,SVM and TER, the input signal is firstly resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension is reduced to 40.

 \begin{table}[]
    \caption{The structure of ConvNet model.}\label{tab1}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & 3x3x64 / 1      & 500x30x6   \\
    MaxPool 1 &            & 2x2 / 1         & 500x30x64  \\
    Conv 2    & ReLU       & 3x3x128 / 1     & 250x15x64 \\
    MaxPool 2 &            & 2x2 / 1         & 250x15x128 \\
    Conv 3    & ReLU       & 3x3x256 / 1     & 125x8x128  \\
    MaxPool 3 &            & 2x2 / 1         & 125x8x256  \\
    Fully-Connected     & Sigmoid    & 16             & 63x4x256   \\
    L-2 Norm  &            &                 & 1x1x128    \\
    Concat    &            &                 & 1x1x384    \\ \hline
    \end{tabular}
\end{table}

\subsection{Results and Discussion}

Case I: Table~\ref{tab3} shows the best average EER performance from five runs of two-fold cross-validation test and the parameter condition. Among the linear methods, the SVM with RBF kernel function showed best verification performance of 24.31\% EER followed by the SVM with Linear kernel function. However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500 $\times$ 30 $\times$ 6) of the input data in the training stage.

Among the deep learning based methods, the Siamese network which utilize two inputs and calculate their distance as its loss function showed the worst verification performance of 23.53\% EER. The best best average test EER performance was obtained from the proposed system with 19.35\% EER and the baseline triplet network without input mining showed slightly worse performance of 20.34\% EER.

\begin{table}[!h]
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signal dataset.}\label{tab3}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}

Case II: Fig.~\ref{fig3} shows the ROC curve of three deep learning based methods. As shown in the Fig.~\ref{fig3}, the proposed system clearly shows the largest AUC among three compared methods where other two methods showed similar AUC. Moreover in Fig.\ref{fig2} which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has difference starting value based on their function. According to these two observations, it can be concluded that the triplet input mining with KAR space learning not only improves the training loss convergence speed but also improves the verification performance.

\begin{figure}[!h]
   \begin{center}
   \subfigure[][Analysis on image brightness changes]{
        \includegraphics[height=6.2cm]{fig_roc_v9.eps}}
   \subfigure[][Analysis on image contrast changes]{
        \includegraphics[height=6.2cm]{normalized_loss_curve_ma30_v1.eps}}
   \caption{Robustness of the images varying amount of
        brightness and contrast at pixel level. Graph labeled as (a)
        shows the Euclidean distance between Fig.~\ref{shifttern}
        (b) and Fig.~\ref{shifttern} (a), and graph (b) shows the
        Euclidean distance between Fig.~\ref{shifttern} (c) and
        Fig.~\ref{shifttern} (a).}
   \label{shifttern2}
   \end{center}
\end{figure}

\iffalse
% Figure 3
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{fig_roc_v5.eps}
    \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
\end{figure}

% Figure 2
    \begin{figure}[!h]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
    \caption{Training Loss Curve of the Proposed System} \label{fig2}
\end{figure}
\fi

\section{Conclusion}
In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network adopting the kernel and the range (KAR) space learning. 
The kernel and the range space learning is initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%

%\begin{thebibliography}{8}

\bibliographystyle{splncs04}
\bibliography{bib_acpr}

%\end{thebibliography}

\end{document}

### 2019-07-30 190410_Paper_ACPR/combined1.tex
acpr2019: submit

--- 2019-07-30 190410_Paper_ACPR/combined.tex
@@
 \usepackage{amsfonts}
-\usepackage{subfigure}
 
@@
 \subsection{Triplet Network}
+% metric learning
+Metric learning is the training of models to learn a distance function to find similarities between objects. 
 % triplet network
-Triplet network is a kind of metric learning model~\cite{} which aims to learn useful representations by distance comparisons~\cite{hoffer2015deep}.
-It is widely used in person re-identification, which solves the matching problem of individuals and identity between camera images~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
-Distinction between classes may be ambiguous in this task as the similarity features between an individual is relatively small compare to the background features such as pose, hair and textures.
+Triplet network a metric learning model which aims to learn useful representations by distance comparisons \cite{hoffer2015deep}.
+It is widely used in face recognition \cite{schroff2015facenet} and person re-identification, which solves the matching problem of individuals and identity between camera images\cite{cheng2016person,chen2017beyond}.
+In above tasks, distinction between classes may be ambiguous as the textures or features of the targets may be similar looking.
 
 % training triplet network
-To address this problem, the training of the triplet network is making feature vectors to be placed in the appropriate separation space, making the positive (similar) data more closer to the anchor (reference) and the negative (dissimilar) data to keep away from the anchor.
-Triplet network receives above triplet data as an input, which is the anchor (reference), positive (similar) and negative (dissimilar) data.
+Triplet network receives triplet data pairs as input. Triplet is composed of anchor(reference), positive(similar) and negative(dissimilar) data.
+The training of the triplet network is making feature vectors to be placed in the appropriate separation space, making the positive(similar) data is close to the anchor(reference) and the negative(dissimilar) data is kept away from the anchor.
 
 % optimize training
-Since myriad triplet pairs can be generated in the training set, training with all possible triplets may time-consuming and unnecessary.
-Optimizing training becomes necessary by mining the efficient triplet pairs out of all possible pairs.
-\cite{cheng2016person,ding2015deep,wang2016joint} generates triplet only for small classes, which randomly selected in each iteration.
-Recently, \cite{schroff2015facenet} used triplet mining strategy for faster convergence speed. They selects inputs from large mini-batch at each training iteration using the network during training.
-However, a lot of training data is necessary to make such a large-sized mini-batch.
+Since myriad triplet pairs may exist for the training set, training from all possible pairs may time-consuming and unnecessary.
+Optimizing training becomes necessary as it mines the learning-efficient triplet out of large possible inputs.
+There are many ways to optimize training.
+In \cite{schroff2015facenet}, selects inputs from large mini-batch at each training iteration using the network during training.
+\cite{cheng2016person} adds second margin for triplet loss to expand intra-class distance.
+Following in \cite{chen2017beyond}, quadruplet loss function makes the distance between the same classes is less than the distance between any different classes.
 
@@
 
-Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$. $\mathbf{W}_{i}$ can be obtained as follows:
+% training KARnet
+Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
+After that, we have the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ to train. the weight matrix can be separated into weights and bias term as
+$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
+$\begin{bmatrix}
+\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
+\end{bmatrix}
+\dots
+\begin{bmatrix}
+\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
+\end{bmatrix}$.
 
+after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we get $\mathbf{W}_{1}$. it is solved as follows:
+
+\begin{equation*}
+    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
+    \sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
+\end{equation*}
+\begin{equation*}
+    \begin{aligned}
+        \Rightarrow
+        \biggl[\sigma^{-1}\biggl(
+        \dots
+        \biggl[\sigma^{-1}\biggl(
+            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+        \biggr)
+        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+        \dots\biggr)\\
+        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
+        = \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
+    \end{aligned}
+\end{equation*}
+\begin{equation}
+    \begin{aligned}
+        \Rightarrow
+        \mathbf{X}^{\dagger}\sigma^{-1}\biggl(
+        \biggl[\sigma^{-1}\biggl(
+        \dots
+        \biggl[\sigma^{-1}\biggl(
+            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+        \biggr)
+        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+        \dots\biggr)\\
+        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
+        = \mathbf{W}_{1} .
+    \end{aligned}
+\end{equation}
+
+After deriving the $\mathbf{W}_{1}$, the $\mathbf{W}_{2}$ also can be optimized as:
+
+%\begin{multline*}
+\begin{equation}
+    \begin{aligned}
+        \Rightarrow
+        \left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
+        \biggl(\dots
+        \biggl[\sigma^{-1}\biggl(
+            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
+        \biggr)
+        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
+        \dots\biggr)\\
+        = \mathbf{W}_{2} .
+    \end{aligned}
+\end{equation}
+%\end{multline*}
+
+By repeating this process recursively until all weight matrix values are obtained, the $\mathbf{W}_{i}$ can be obtained as follows:
 \begin{equation}
@@
 
-\begin{figure}[!h]
-   \begin{center}
-   \subfigure[][Analysis on image brightness changes]{
-        \includegraphics[height=6.2cm]{fig_roc_v9.eps}}
-   \subfigure[][Analysis on image contrast changes]{
-        \includegraphics[height=6.2cm]{normalized_loss_curve_ma30_v1.eps}}
-   \caption{Robustness of the images varying amount of
-        brightness and contrast at pixel level. Graph labeled as (a)
-        shows the Euclidean distance between Fig.~\ref{shifttern}
-        (b) and Fig.~\ref{shifttern} (a), and graph (b) shows the
-        Euclidean distance between Fig.~\ref{shifttern} (c) and
-        Fig.~\ref{shifttern} (a).}
-   \label{shifttern2}
-   \end{center}
-\end{figure}
-
-\iffalse
 % Figure 3
@@
 \end{figure}
-\fi
 

### 2019-07-30 190410_Paper_ACPR/paper_combined.tex
acpr2019: submit

@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
-\usepackage{amsmath}
+\usepackage{amsmath,amssymb}
+\usepackage{amsfonts}
+\usepackage{subfigure}
 
@@
 %The abstract should briefly summarize the contents of the paper in 15--250 words.
-In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network. 
-To refine the triplet inputs for the faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
+To refine the triplet inputs for faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training set of Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
-Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.
+Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
 
@@
 \subsection{Triplet Network}
-A Triplet network is comprised of 3 instances of the same feedforward network (with shared parameters)\cite{hoffer2015deep}.
-It is widely used in face recognition \cite{schroff2015facenet} and person re-identification, which solves the matching problem of individuals and identity between camera images\cite{cheng2016person,chen2017beyond}.
-The distinction between classes may be ambiguous in the above tasks since the targets may be looking in different directions or taking different positions.
-to achieve good ability to distinguish between classes, a triplet network works by extract feature vectors which expand margins between same and different class.
+% triplet network
+Triplet network is kind of a metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}.
+It is widely used in person re-identification problems, which solves the matching problem of individuals and identity between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
+The distinction between classes is challenging in this task since the distinctive feature is relatively weak compare to the background features such as pose, hair and textures.
 
-The loss function of triplet network is calculated as the difference in L-2 distance between anchor to each positive and negative triplet outputs.
-Optimizing the training process is important because gradient vanishing can occur during training.
-It happens when the negative class distance is much greater than positive class distance, the output of the loss function can down to zero as a result.
-%Also, outliers in triplet input affects a lot to training since The loss function for triplet network depends on the distance between each triplet input.
+To address this problem, the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data.
+The objective function of the triplet network is to make feature vectors to be placed in the appropriate separation space by putting the positive (similar) data more closer to the anchor (reference) data and the negative (dissimilar) data to keep away from the anchor data.
 
-There are many ways to optimize training.
-In \cite{schroff2015facenet}, selects inputs from large mini-batch at each training iteration using the network during training.
-\cite{cheng2016person} adds second margin for triplet loss to expand intra-class distance.
-Following in \cite{chen2017beyond}, quadruplet loss function makes the distance between the same classes is less than the distance between any different classes.
+% optimize training
+Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary.
+To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.
+Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed.
+They utilized large mini-batch at each training iteration and select the triplet based on the training network.
+However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.
 
-In this paper, we adopt multilayer feedforward networks trained by the kernel and the range space learning to select good triplet input for training the triplet network.
-It has advantage for reducing computing resources as well as boosting the training optimization.
 % Rel works: KAR learning
-\subsection{kernel and the range space learning}
+\subsection{Kernel and the Range space learning}\label{kar}
 
-Multilayer feedforward neural networks is widely known to be good for feature extractor and classifier.
-This network is generally trained by the gradient descent method and backpropagation.
+The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation.
 However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.
 
-%This training methods makes networks to fell into problems such as vanishing gradient or local minima.
-%To avoid these problems, it is important to set the learning parameters such as learning rate or momentum value before training.
-
-%Recently, according to \cite{guo2004pseudoinverse}, based on linear algebric method and pseudo-inverse, gradient-free learning methods is invented.
-%Howeaver, network weights of the hidden layer has to be fixed as equal to the number of examples.
-
-Recently, gradient-free learning framework based on series of kernel and range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
-since it is trained by algebric methods, no learning parameters are needed to train the networks.
-%there is no problems of vanishing gradient and local minima, 
-using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.
+Recently, gradient-free learning framework based on series of the kernel and the range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
+Since it is trained by linear equations, no learning parameters nor the iteration are needed to train the networks.
+Using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.
 
 % Karnet structure and mining samples.
-Let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathrm{R}}^{m \times n}$ is network outputs.
-Multilayer neural network structure is shown below:
-
+Let the training dataset $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ as the network outputs.
+Then the multilayer neural network structure can be written in linear equation form as follows:
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
-\in{\mathrm{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
+where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
+\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
+By adopting the one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$, The trained weight matrices $\mathbf{W}_{i}$ using KAR space manipulation can be obtained as follows~\cite{toh2018gradient}:
 
-When all weights have been learned, for given anchor signal, hard negative samples can be mined among the distance of network output of desired signal $\mathbf{G}$ is below the threshold.
-
-% training KARnet
-Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
-After that, we have the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ to train. the weight matrix can be separated into weights and bias term as
-$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
-$\begin{bmatrix}
-\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
-\end{bmatrix}
-\dots
-\begin{bmatrix}
-\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
-\end{bmatrix}$.
-
-after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we get $\mathbf{W}_{1}$. it is solved as follows:
-
-\begin{equation*}
-    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
-    \sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
-\end{equation*}
-\begin{equation*}
-    \begin{aligned}
-        \Rightarrow
-        \biggl[\sigma^{-1}\biggl(
-        \dots
-        \biggl[\sigma^{-1}\biggl(
-            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
-        \biggr)
-        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
-        \dots\biggr)\\
-        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
-        = \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
-    \end{aligned}
-\end{equation*}
-\begin{equation}
-    \begin{aligned}
-        \Rightarrow
-        \mathbf{X}^{\dagger}\sigma^{-1}\biggl(
-        \biggl[\sigma^{-1}\biggl(
-        \dots
-        \biggl[\sigma^{-1}\biggl(
-            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
-        \biggr)
-        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
-        \dots\biggr)\\
-        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
-        = \mathbf{W}_{1} .
-    \end{aligned}
-\end{equation}
-
-After deriving the $\mathbf{W}_{1}$, the $\mathbf{W}_{2}$ also can be optimized as:
-
-%\begin{multline*}
-\begin{equation}
-    \begin{aligned}
-        \Rightarrow
-        \left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
-        \biggl(\dots
-        \biggl[\sigma^{-1}\biggl(
-            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
-        \biggr)
-        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
-        \dots\biggr)\\
-        = \mathbf{W}_{2} .
-    \end{aligned}
-\end{equation}
-%\end{multline*}
-
-By repeating this process recursively until all weight matrix values are obtained, the $\mathbf{W}_{i}$ can be obtained as follows:
 \begin{equation}
@@
 % Methods: System overview(Fig.1)
-In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
-An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.
-
-Essentially, the Wi-Fi signature signals are randomly divided to create the training and the validation set.
-Subsequently, the KAR space projection learning generates the triplet data by mining the hard positve and the hard negative samples for the given anchor signal from the training dataset.
-
-To train the ConvNet structure, generated triplet data flows into the predifined ConvNet structure. The ConvNet extracts feature vectors from given triplet input.
-ConvNet training is achieved by the triplet loss, which is formulated by the L-2 distance metrics of feature vectors.
-The overall ConvNet network is trained by the backpropagation scheme.
-The following subsections detail the each step of the proposed system.
+In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter) using triplet network.
+Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network~\cite{schroff2015facenet}.
+Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from the each given anchor sample in the training dataset (item (a) in Fig.~\ref{fig1}).
+Subsequently, the ConvNet structure in the triplet network (item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (item (c) in Fig.~\ref{fig1}).
+The following subsections detail the triplet mining using KAR space learning and the triplet network.
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v2}
-    \caption{Structure of the network} \label{fig1}
+    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v4}
+    \caption{An overview of the proposed system} \label{fig1}
 \end{figure}
+
+% Methods: KAR learning
+\subsection{Triplet mining using kernel and the range space learning}
+According to \cite{schroff2015facenet}, it is important to select the hard positive sample and the hard negative sample from each given anchor sample for the faster loss convergence when training the triplet network.
+The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the smallest (which is most likely to be misclassified as a positive sample).
+However, there is no information about which sample is the hard positive/negative sample before we train the network.
+
+In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative sample from the given anchor sample.
+Since the KAR space learning has no iterative learning process, we can mine the triplet samples without train an another network with backpropagation process.
+
+By training the KAR space network with the training samples, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network.
+For each training sample as an anchor sample $\mathbf{x}_{anc}$ and to measure the distance between $\mathbf{x}_{anc}$ and other samples, we firstly need to train the KAR space learning structure $f\left(.\right)$ using whole training sample matrix $\mathbf{X}\in \mathbb{R}^{n\times m}$ as follows~\cite{toh2018gradient}:
+\begin{equation}
+    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
+\end{equation}
+where $\mathbf{X}$ is a stacked matrix of $m$ training sample vectors, $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$, $\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$, $\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is an activation function.
+
+Following, the hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ from the input anchor sample $\mathbf{x}_{anc}$ can be respectively selected among the positive samples and the negative samples as follows:
+\begin{equation}
+    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}, \label{pos}
+\end{equation}
+\begin{equation}
+    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg},\label{neg}
+\end{equation}
+where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the threshold to make the sample more harder.
+Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative sample rather than just using the hardest positive/negative sample since the hardest samples are likely to be an outlier which degrades the training process of the triplet network.
+We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples match the equations.
+
+% Methods: ConvNets
+\subsection{ConvNet Structures}
+
+To design the triplet network, we firstly need to select the feature extractor which converts the input triplet data into feature vectors.
+In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
+
+Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
+The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
+The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layers.
+Following, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
+The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.
+
+%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
 
@@
 
-Triplet loss is used to train ConvNet to extract feature vector from triplet input.
-For the $i_{th}$ anchor input signal $\mathbf{X}_{anc,i}$, triplet input is generated by grouping the positive input signal $\mathbf{X}_{pos,i}$ drawn from the same identity with anchor signal and the negative input signal $\mathbf{X}_{neg,i}$ is chosen from the another identity with the anchor signal.
-Generated triplet input $\left\{\mathbf{X}_{anc,i},\mathbf{X}_{pos,i},\mathbf{X}_{neg,i}\right\}$ is fed into the ConvNet structure one by one and respectively makes anchor, positive and negative feature vectors.
+The triplet loss function is proposed in \cite{hoffer2015deep} to train the triplet network.
+For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping with the hard positive input sample $\mathbf{x}_{pos,i}$ and the hard negative input sample $\mathbf{x}_{neg,i}$ selected based on the KAR space learning.
+Generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, positive and negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
 
-Let $\mathbf{v}_{anc,i}\in{\mathrm{R}}^{d\times1}$, $\mathbf{v}_{pos,i}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{v}_{neg,i}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
-the triplet loss is calculated by comparing positive distance (L-2 distance from the anchor vector to the positive feature vector) and negative distance (L-2 distance from the anchor vector to the negative feature vector).
-ConvNet is trained to maximize gap between positive distance to negative distance more than margin $\alpha$.
-The triplet loss for the inputs can be calculated as follows:
-
+Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:
 \begin{equation}
-    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),
+    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
 \end{equation} 
-
-where N is size of the mini-batch.
-Note that the triplet loss can down to 0 when the negative distance is bigger than the positive distance more than preset margin $\alpha$.
-If we select proper triplet for training, we can avoid this problem and make the convergence of the loss function faster.
-
-% Methods: KAR learning
-\subsection{Triplet mining by kernel and the range space learning}
-According to \cite{schroff2015facenet}, it is important to take hard positive and hard negative sample for faster convergence of the loss when training triplet networks.
-we adopted KAR space learnig methods to approximate the ConvNet structure and mine the hard positive and the hard negative samples from the training dataset.
-
-% importance of selecting hard pos/neg
-Hard positive sample means distance between feature vectors from positive signal to anchor signal is the greatest, while hard negative sample means distance between feature vectors from negative signal to anchor signal is the smallest.
-
-% methods of KAR learning
-Since we don't know which is the hard sample before training the network, we propose to train multilayer feedforward neural network to mine the hard positive and the hard negative from the traning dataset.
-To train the multilayer neural network, we adopted the kernel and the range (KAR) space projection learning (see Section2.2 for details).
-% Methods: ConvNets
-\subsection{ConvNet Structures}
-
-To design the proposed networks, we firstly need to select the feature extracting networks which convert the triplet data into a feature vector.
-In this work, we utilize the ConvNet structure \cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
-
-Our ConvNet structure (See Fig~\ref{fig1} (b)) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
-The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
-The Rectiﬁed Linear (ReLU) function as an activation function and the max-pooling layers are applied between each convolutional layers.
-The features from the last convolutional layer are directly flattened into a single vector.
-We used the sigmoid activation at ConvNet output and L-2 normalize output vectors to prevent negative distance when calculating triplet loss.
-
-%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
+where N denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
+The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.
 
@@
 % Dataset
-\subsubsection{Dataset}
- In order to evaluate the verification performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
-Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}.
-we used only absolute value.
+\subsection{Dataset}
+ In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with single position was utilized in our experiments.
+After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500 $\times$ 30 $\times$ 6.
+We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal~\cite{wang2015understanding}.
 
- % pre-processing
- Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy.
-Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action.
-Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
-As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
+\subsection{Experimental Settings}
 
-\subsubsection{Experimental Settings}
+\subsubsection{Performance Evaluation}
+The proposed system is evaluated under two cases: i) case I on comparison of the proposed system with other linear methods and deep learning based methods based on verification accuracy, and case II on detailed comparison with the deep learning based methods using receiver operating characteristic (ROC) curve and training loss curve.
+For the Case I, existing linear methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between} and deep learning based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+The Siamese network and baseline triplet network utilized same ConvNet structures with the proposed system and only differed in the input data style and the loss function.
 
-\subsubsection{1) Performance Evaluation}
-% performance evaluation
-The porposed method is evaluated under comparision of the proposed method with other verification methods based on verification accuracy.
-verification performance is compared with existing linear methods in literature such as LSE, SVM and TER.
-Moreover, proposed method is compared by ConvNet based Siamese networks,we used same ConvNet model for our proposed method and Siamese network.
+The verification performance of the proposed system and other methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests.
+Due to the memory constraint caused by the large data size, noting here that deep learning based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number with the number of the positive pairs.
 
-% Evaluation protocols
-Validation performance of the proposed and other linear deep learning methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests.
-
-\subsubsection{2) Network Structure}
- We impose a triplet loss as objective function on our classifier. This objective is combined with standard backpropagation algorithm.
- The structure of the ConvNet network is specified in Table \ref{tab1}.
-we train the network starting with a learning rate of 0.00001 via Cross Entropy loss with a mini-batch sized of 32.
-We optimize the loss by the Adam optimizer with L-2 penalty of 0.0002 except for output layer.
-Output layer is regularized with L-2 penalty of 0.0001.
- We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 0.01.
-Biases were also initialized from a normal distribution of standard deviation of 0.01, but with 0.5 mean.
- Training is conduced with 2000 iterations, which set empirically.
+\subsubsection{Network Structure and Parameter Settings}
+The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}.
+With an input data size of 500 $\times$ 30 $\times$ 6, we set two network layers where the size of the each layer is 1024 and 16, respectively.
+Each layer is initialized with uniform distribution over [0, 1).
+We used ${tan}^{-1}$ as an activation function following \cite{toh2018analytic}.
 
 \begin{table}[]
-    \caption{The structure of ConvNet}\label{tab1}
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
-    Conv 1    & ReLU       & 3x3x64 / 1      & 500x30x6   \\
-    MaxPool 1 &            & 2x2 / 1         & 500x30x64  \\
-    Conv 2    & ReLU       & 3x3x128 / 1     & 250x15x64 \\
-    MaxPool 2 &            & 2x2 / 1         & 250x15x128 \\
-    Conv 3    & ReLU       & 3x3x256 / 1     & 125x8x128  \\
-    MaxPool 3 &            & 2x2 / 1         & 125x8x256  \\
-    Dense     & Sigmoid    & 128             & 63x4x256   \\
-    L-2 Norm  &            &                 & 1x1x128    \\
-    Concat    &            &                 & 1x1x384    \\ \hline
-    \end{tabular}
-\end{table}
-
-For KARnet trainied multilayer neural networks is shown below (Table \ref{tab2}), we set 2 layer and number of neurons are [1024,16]. initialized as uniform distribution over [0, 1).
-Used arctangent as activation function.
-
-\begin{table}[]
-    \caption{The structure of KARnet}\label{tab2}
+    \caption{The network structure of KAR space learning}\label{tab2}
     \centering
@@
     Input   & 500x30x6 &            \\
-    Dense 1 & 1x1x1024 & ArcTan     \\
-    Dense 2 & 1x1x128  & ArcTan     \\
+    Fully-Connected 1 & 1x1x1024 & ArcTan     \\
+    Fully-Connected 2 & 1x1x16  & ArcTan     \\
     Output  & 1x1x50   &            \\ \hline
@@
 
-\subsubsection{3) Parameter Settings}
-For making triplet loss, 0.1 of alpha value is utilized for the proposed method.
-we choose output vector size of 16.
-For linear methods such as LSE,SVM and TER, we reduced dimension of input signal to 500x30, by averaging through subcarrier axis. Due to limitation of hardware memory.
-For PCA-LSE, input dimension is reduced by 40 sized features using PCA.
-For Triplet CNN without KAR learning, we choose signature randomly for making input triplets and used triplet loss as used in proposed methods.
-for Siamese Networks, we put 2 random signal as input and used binary loss for training the networks.
-
-\subsubsection{Results and Discussion}
-
-Table \ref{tab3} shows the best average EER performances obtained by the compared methods. The test EER was averaged from five runs of two-fold cross-validation.
-Comparing with ConvNet based Siamese and Triplet CNN without KAR learning, proposed methods showed the best EER performance. Due to negative mining process included in making triplet loss.
-The proposed method showed much better EER than linear methods, such as SVM,LSE and TER. Since linear methods use reduced input signal.
-
-% Loss Curve
-Loss curves of proposed method are shown in Fig.\ref{fig2}.
-This shows that KAR learning not only helps ConvNet to train faster, but also makes it to extract better features.
-As the proposed method shows steeper loss curve when training, and the variance of the validation loss is smaller.
+For the proposed system and the deep learning based methods, we utilized same ConvNet structure as specified in Table~\ref{tab1}.
+We trained the network starting with a learning rate of 0.00005 with a mini-batch sized of 32.
+We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for output layer.
+The output layer is regularized with L-2 penalty of 0.0001.
+We initialized all network weights in the convolutional layers with a normal distribution with zero-mean and a standard deviation of 0.01.
+Biases were also initialized with a normal distribution with 0.5 mean and a standard deviation of 0.01.
+For the triplet networks, the hyper-parameter regulating triplet loss is empirically set to 0.1.
+The training epochs are set to 1,500 for all three deep learning based algorithms.
+For the linear methods such as LSE,SVM and TER, the input signal is firstly resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
+For the PCA-LSE, the input dimension is reduced to 40.
 
  \begin{table}[]
-    \caption{Verification Performance}\label{tab3}
+    \caption{
+        The structure of ConvNet model.
+For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride.
+For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride.
+The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.
+    }\label{tab1}
     \centering
-    \begin{tabular}{|l|l|l|}
+    \begin{tabular}{|c|c|c|c|}
     \hline
-    Methology   &   Best EER (\%) &   Condition   \\  \hline
-    Proposed(TripletCNN with KAR learning) &   19.09   &   lr=0.00005, alpha=0.1  \\
-    Triplet CNN without KAR learning    &   20.08   &   lr=0.00005, alpha=0.1  \\
-    Siamese CNN  &   24.09   &   lr=0.00005, alpha=0.1  \\
-    SVM(RBF)    &   24.31   &   c=1, gamma=0.01/3000 \\
-    SVM(Linear) &   28.23   &   c=1 \\
-    LSE(Dimension Reduction by PCA)    &   30.79   &  40 dimension input    \\
-    TER &   35.75   &   order=1   \\
-    LSE &   48.44   &   \\  \hline
+    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
+    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500x30x6   \\
+    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
+    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
+    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
+    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
+    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
+    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
+    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
+    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
     \end{tabular}
@@
 
-% Figure 2
-\begin{figure}
-    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30.eps}
-    \caption{Training Loss Curve of the Proposed Method} \label{fig2}
-\end{figure}
-% Figure 3
-\begin{figure}
-    \includegraphics[width=\textwidth]{fig_roc.pdf}
-    \caption{ROC Curve of the Proposed Method} \label{fig3}
+\subsection{Results and Discussion}
+
+Case I: Table~\ref{tab3} shows the best average EER performance from five runs of two-fold cross-validation test and the parameter condition.
+Among the linear methods, the SVM with RBF kernel function showed best verification performance of 24.31\% EER followed by the SVM with Linear kernel function.
+However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500 $\times$ 30 $\times$ 6) of the input data in the training stage.
+
+Among the deep learning based methods, the Siamese network which is also a metric learning system but utilize two inputs and uses the contrastive loss function for training showed the worst verification performance of 23.53\% EER.
+The best best average test EER performance was obtained from the proposed system with 19.35\% EER and the baseline triplet network without input mining showed slightly worse performance of 20.34\% EER.
+
+\begin{table}[!h]
+    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signal dataset.}\label{tab3}
+    \centering
+    \begin{tabular}{|c|c|c|}
+    \hline
+    Methology   &   Best EER (\%) &   Condition   \\  \hline
+    LSE &   48.44   &  - \\ 
+    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
+    SVM (Linear) &   28.23   &   c=1 \\
+    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
+    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
+    Siamese network  &   23.53   &   lr=0.00005  \\
+    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
+    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
+     \hline
+    \end{tabular}
+\end{table}
+
+Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning based methods.
+As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest AUC among three compared methods where other two methods showed similar AUC.
+Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network.
+We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has difference starting value based on their function.
+According to these two observations, it can be concluded that the triplet input mining with KAR space learning not only improves the training loss convergence speed but also improves the verification performance.
+
+% Figure 2,3
+\begin{figure}[!h]
+    \begin{center}
+    \subfigure[][ROC Curve]{
+         \includegraphics[height=6.4cm]{fig_roc_v9.eps}}
+    \subfigure[][Training Loss Curve]{
+         \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v1.eps}}
+    \caption{(a) shows Receiver Operating Characteristic(ROC) Curve
+    (b) shows Normalized Training Loss Curve of the Proposed System }
+    \label{fig2}
+    \end{center}
  \end{figure}
 
+ % merged 2 graph: omitted separated graph
+ \iffalse
+ % Figure 3
+ \begin{figure}[!h]
+     \includegraphics[width=\textwidth]{fig_roc_v5.eps}
+     \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
+ \end{figure}
+
+ % Figure 2
+     \begin{figure}[!h]
+     \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
+     \caption{Training Loss Curve of the Proposed System} \label{fig2}
+ \end{figure}
+ \fi
+
 \section{Conclusion}
-In this paper, we proposed a novel identity verification system based on Wi-Fi signature signals. 
-In order to train the triplet network effectively, triplet input is mined from Wi-Fi signature signals by the kernel and the range space learning.
-Subsequently, ConvNet structure is adopted for feature extractor which generates feature vectors from input triplets.
-Finally, the triplet network is trained by matching between extracted feature vectors based on L-2 distance comparison.
-Our networks show good feature extracting performance, especially in low-dimension outputs and shows encouraging experimental results in terms of verification accuracy.
+In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network adopting the kernel and the range (KAR) space learning.
+The kernel and the range space learning is initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
+Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.
 %
@@
 %\begin{thebibliography}{8}
-
+\clearpage
 \bibliographystyle{splncs04}

### 2019-07-30 190410_Paper_ACPR/paper_v2.tex
acpr2019: submit

--- 2019-07-23 190410_Paper_ACPR/paper_combined.tex
@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 
@@
 \subsection{Triplet Network}
-A Triplet network is comprised of 3 instances of the same feedforward network (with shared parameters)\cite{hoffer2015deep}.
-It is widely used in face recognition \cite{schroff2015facenet} and person re-identification, which solves the matching problem of individuals and identity between camera images\cite{cheng2016person,chen2017beyond}.
-The distinction between classes may be ambiguous in the above tasks since the targets may be looking in different directions or taking different positions.
-to achieve good ability to distinguish between classes, a triplet network works by extract feature vectors which expand margins between same and different class.
+% metric learning
+Metric learning is the training of models to learn a distance function to find similarities between objects. 
+% triplet network
+Triplet network a metric learning model which aims to learn useful representations by distance comparisons \cite{hoffer2015deep}.
+It is widely used in person re-identification, which solves the matching problem of individuals and identity between camera images\cite{ding2015deep,cheng2016person,chen2017beyond,schroff2015facenet,wang2016joint}.
+In above tasks, distinction between classes may be ambiguous as the textures or features of the targets may be similar looking.
+% add: background change highly, important feature small
 
-The loss function of triplet network is calculated as the difference in L-2 distance between anchor to each positive and negative triplet outputs.
-Optimizing the training process is important because gradient vanishing can occur during training.
-It happens when the negative class distance is much greater than positive class distance, the output of the loss function can down to zero as a result.
-%Also, outliers in triplet input affects a lot to training since The loss function for triplet network depends on the distance between each triplet input.
+% training triplet network
+Triplet network receives triplet data pairs as input. Triplet is composed of anchor(reference), positive(similar) and negative(dissimilar) data.
+The training of the triplet network is making feature vectors to be placed in the appropriate separation space, making the positive(similar) data is close to the anchor(reference) and the negative(dissimilar) data is kept away from the anchor.
 
-There are many ways to optimize training.
-In \cite{schroff2015facenet}, selects inputs from large mini-batch at each training iteration using the network during training.
-\cite{cheng2016person} adds second margin for triplet loss to expand intra-class distance.
-Following in \cite{chen2017beyond}, quadruplet loss function makes the distance between the same classes is less than the distance between any different classes.
+% optimize training
+Since myriad triplet pairs may exist for the training set, training from all possible pairs may time-consuming and unnecessary.
+Optimizing training becomes necessary as it mines the learning-efficient triplet out of large possible inputs.
+\cite{cheng2016person,ding2015deep,wang2016joint} generates triplet only for small classes, which randomly selected in each iteration.
+Rescently, in \cite{schroff2015facenet} used triplet mining stratege for faster convergence speed.
+They selects inputs from large mini-batch at each training iteration using the network during training.
+However, a lot of training data is necessary to make such a large-sized mini-batch. Moreover, in early stages of training, making training data with immature models itself may not help the training.
 
-In this paper, we adopt multilayer feedforward networks trained by the kernel and the range space learning to select good triplet input for training the triplet network.
-It has advantage for reducing computing resources as well as boosting the training optimization.
 % Rel works: KAR learning
-\subsection{kernel and the range space learning}
+\subsection{kernel and the range space learning}\label{kar}
 
-Multilayer feedforward neural networks is widely known to be good for feature extractor and classifier.
-This network is generally trained by the gradient descent method and backpropagation.
+The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation.
 However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.
 
-%This training methods makes networks to fell into problems such as vanishing gradient or local minima.
-%To avoid these problems, it is important to set the learning parameters such as learning rate or momentum value before training.
-
-%Recently, according to \cite{guo2004pseudoinverse}, based on linear algebric method and pseudo-inverse, gradient-free learning methods is invented.
-%Howeaver, network weights of the hidden layer has to be fixed as equal to the number of examples.
-
-Recently, gradient-free learning framework based on series of kernel and range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
-since it is trained by algebric methods, no learning parameters are needed to train the networks.
-%there is no problems of vanishing gradient and local minima, 
-using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.
+Recently, gradient-free learning framework based on series of the kernel and the range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
+Since it is trained by linear equations, no learning parameters nor the iteration are needed to train the networks.
+Using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.
 
 % Karnet structure and mining samples.
-Let the training dataset $\mathbf{X}\in{\mathrm{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathrm{R}}^{m \times n}$ is network outputs.
+Let the training dataset $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ is network outputs.
 Multilayer neural network structure is shown below:
-
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{W}_{1}\in{\mathrm{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathrm{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathrm{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
-\in{\mathrm{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
-
-When all weights have been learned, for given anchor signal, hard negative samples can be mined among the distance of network output of desired signal $\mathbf{G}$ is below the threshold.
+where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
+\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
 
 % training KARnet
-Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathrm{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
+Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
 After that, we have the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ to train. the weight matrix can be separated into weights and bias term as
@@
 % Methods: System overview(Fig.1)
-In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter).
-An overview of the proposed system utilizing the ConvNet \cite{lecun1998gradient} and the kernel and the range space projection learning (KAR space learning) \cite{toh2018learning,toh2018gradient} is shown in Fig.1.
-
-Essentially, the Wi-Fi signature signals are randomly divided to create the training and the validation set.
-Subsequently, the KAR space projection learning generates the triplet data by mining the hard positve and the hard negative samples for the given anchor signal from the training dataset.
-
-To train the ConvNet structure, generated triplet data flows into the predifined ConvNet structure. The ConvNet extracts feature vectors from given triplet input.
-ConvNet training is achieved by the triplet loss, which is formulated by the L-2 distance metrics of feature vectors.
-The overall ConvNet network is trained by the backpropagation scheme.
-The following subsections detail the each step of the proposed system.
+In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter) using triplet network.
+Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network ~\cite{schroff2015facenet}.
+Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from the each given anchor sample in the training dataset (item (a) in Fig.~\ref{fig1}).
+Subsequently, the ConvNet structure in the triplet network (item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (item (c) in Fig.~\ref{fig1}).
+The following subsections detail the triplet mining using KAR space learning and the triplet network.
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v2}
-    \caption{Structure of the network} \label{fig1}
+    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v3}
+    \caption{An overview of the proposed system} \label{fig1}
 \end{figure}
+
+% Methods: KAR learning
+\subsection{Triplet mining using kernel and the range space learning}
+According to \cite{schroff2015facenet}, it is important to select the hard positive sample and the hard negative sample from each given anchor sample for the faster loss convergence when training the triplet network.
+The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the smallest (which is most likely to be misclassified as a positive sample).
+However, there is no information about which sample is the hard positive/negative sample before we train the network.
+
+In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a multilayer feedforward neural network to mine the hard positive/negative sample from the given anchor sample.
+Since the KAR space learning has no iterative learning process, we can mine the triplet samples without train an another network with backpropagation process just for the input mining.
+
+By training the KAR space network with the training samples, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network.
+For every training sample as an anchor sample $\mathbf{x}_{anc}$, positive sample $\mathbf{x}_{pos}$ is selected among the same class with anchor.
+Where negative sample $\mathbf{x}_{neg}$ is selected among the different class with anchor.
+For selected sample $\mathbf{x}$, we can choice the hard samples from output of KAR space learning function $f(\mathbf{x})\in{\mathbb{R}}^{c}$. Where $c$ denotes number of classes.
+
+\begin{equation}
+    f\left(\mathbf{x}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{x}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
+\end{equation}
+
+$\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
+\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
+Here, we randomly select one sample among
+
+\begin{equation}
+    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}
+\end{equation}
+
+as a hard positive sample and one sample among
+
+\begin{equation}
+    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg}
+\end{equation}
+
+Since the hardest positive/negative sample can be an outlier which affects the training of the triplet network, we selected hard samples, which has distance above a certain threshold.
+We empirically set positive threshold to 75 percentile of L-2 distance between anchor to positive samples.
+Negative threshold is set to 25 percentile of L-2 distance between anchor to negative samples.
+
+% Methods: ConvNets
+\subsection{ConvNet Structures}
+
+To design the triplet network, we firstly need to select the feature extractor which converts the input triplet data into feature vectors.
+In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
+
+Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
+The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
+The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layers.
+Following, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
+The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.
+
+%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
 
@@
 
-Triplet loss is used to train ConvNet to extract feature vector from triplet input.
-For the $i_{th}$ anchor input signal $\mathbf{X}_{anc,i}$, triplet input is generated by grouping the positive input signal $\mathbf{X}_{pos,i}$ drawn from the same identity with anchor signal and the negative input signal $\mathbf{X}_{neg,i}$ is chosen from the another identity with the anchor signal.
-Generated triplet input $\left\{\mathbf{X}_{anc,i},\mathbf{X}_{pos,i},\mathbf{X}_{neg,i}\right\}$ is fed into the ConvNet structure one by one and respectively makes anchor, positive and negative feature vectors.
+The triplet loss function is proposed in \cite{schroff2015facenet} to train the triplet network.
+For the $i_{th}$ anchor input sample $\mathbf{X}_{anc,i}$, the triplet input is generated by grouping with the hard positive input sample $\mathbf{X}_{pos,i}$ and the hard negative input sample $\mathbf{X}_{neg,i}$ selected based on the KAR space learning.
+Generated triplet input $\left\{\mathbf{X}_{anc,i},\mathbf{X}_{pos,i},\mathbf{X}_{neg,i}\right\}$ is then respectively transformed to the anchor, positive and negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
 
-Let $\mathbf{v}_{anc,i}\in{\mathrm{R}}^{d\times1}$, $\mathbf{v}_{pos,i}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{v}_{neg,i}\in{\mathrm{R}}^{d\times1}$ be three feature vectors extracted from the ConvNet structure.
-the triplet loss is calculated by comparing positive distance (L-2 distance from the anchor vector to the positive feature vector) and negative distance (L-2 distance from the anchor vector to the negative feature vector).
-ConvNet is trained to maximize gap between positive distance to negative distance more than margin $\alpha$.
-The triplet loss for the inputs can be calculated as follows:
-
+Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:
 \begin{equation}
-    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),
+    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
 \end{equation} 
-
-where N is size of the mini-batch.
-Note that the triplet loss can down to 0 when the negative distance is bigger than the positive distance more than preset margin $\alpha$.
-If we select proper triplet for training, we can avoid this problem and make the convergence of the loss function faster.
-
-% Methods: KAR learning
-\subsection{Triplet mining by kernel and the range space learning}
-According to \cite{schroff2015facenet}, it is important to take hard positive and hard negative sample for faster convergence of the loss when training triplet networks.
-we adopted KAR space learnig methods to approximate the ConvNet structure and mine the hard positive and the hard negative samples from the training dataset.
-
-% importance of selecting hard pos/neg
-Hard positive sample means distance between feature vectors from positive signal to anchor signal is the greatest, while hard negative sample means distance between feature vectors from negative signal to anchor signal is the smallest.
-
-% methods of KAR learning
-Since we don't know which is the hard sample before training the network, we propose to train multilayer feedforward neural network to mine the hard positive and the hard negative from the traning dataset.
-To train the multilayer neural network, we adopted the kernel and the range (KAR) space projection learning (see Section2.2 for details).
-% Methods: ConvNets
-\subsection{ConvNet Structures}
-
-To design the proposed networks, we firstly need to select the feature extracting networks which convert the triplet data into a feature vector.
-In this work, we utilize the ConvNet structure \cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
-
-Our ConvNet structure (See Fig~\ref{fig1} (b)) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
-The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
-The Rectiﬁed Linear (ReLU) function as an activation function and the max-pooling layers are applied between each convolutional layers.
-The features from the last convolutional layer are directly flattened into a single vector.
-We used the sigmoid activation at ConvNet output and L-2 normalize output vectors to prevent negative distance when calculating triplet loss.
-
-%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
+where N denotes the size of the mini-batch, ${\left\| \bullet \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
+The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.
 
@@
 % Dataset
-\subsubsection{Dataset}
+\subsection{Dataset}
  In order to evaluate the verification performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
-Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}.
-we used only absolute value.
+Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples).
+Each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
+We used only the absolute value among the Wi-Fi CSI signals that come in a complex number.
+Since the Wi-Fi devices that is used to collect CSI signals has device firmware issues in their phase value in 2.4Ghz frequency mode \cite{wang2015understanding}.
 
@@
 Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals.
-As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.
+As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the triplet network.
 
-\subsubsection{Experimental Settings}
+\subsection{Experimental Settings}
 
-\subsubsection{1) Performance Evaluation}
-% performance evaluation
-The porposed method is evaluated under comparision of the proposed method with other verification methods based on verification accuracy.
-verification performance is compared with existing linear methods in literature such as LSE, SVM and TER.
-Moreover, proposed method is compared by ConvNet based Siamese networks,we used same ConvNet model for our proposed method and Siamese network.
+\subsubsection{Performance Evaluation}
+The proposed system is evaluated with others based on verification accuracy.
+Verification performance is compared with existing linear methods in literature such as Least Square Estimation(LSE), Support Vector Machine(SVM) and Total Error Rate minimization which adopts the Reduced multivariate polynomial Model as basis function(TER-RM2) \cite{toh2003fingerprint,toh2008between}.
+Moreover, proposed system is compared by  Siamese network \cite{koch2015siamese} and Baseline Triplet network \cite{hoffer2015deep}, which are also deep learning systems based on the same ConvNet structure as our proposed system.
+Howeaver, Siamese network receives data pairs as input and trained by contrastive loss between a pair of samples.
+Baseline Triplet network is similar as our proposed system, but without triplet mining KAR learning process when making input triplet.
 
 % Evaluation protocols
-Validation performance of the proposed and other linear deep learning methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests.
+Validation performance of the proposed and other systems were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests. 
+We note that in triplet network and Siamese network, We did not use every possible pairs in validation set.
+Since every possible triplet pairs for validation set is the number of 3 out of 1000 combinations, which is too huge for our experiment.
+We used randomly sampled negative pairs from validation set until it equals to 9500 positive samples instead.
 
-\subsubsection{2) Network Structure}
+\subsubsection{Network Structure}
  We impose a triplet loss as objective function on our classifier. This objective is combined with standard backpropagation algorithm.
  The structure of the ConvNet network is specified in Table \ref{tab1}.
-we train the network starting with a learning rate of 0.00001 via Cross Entropy loss with a mini-batch sized of 32.
+we train the network starting with a learning rate of 0.00005 via Triplet loss with a mini-batch sized of 32.
 We optimize the loss by the Adam optimizer with L-2 penalty of 0.0002 except for output layer.
@@
 Biases were also initialized from a normal distribution of standard deviation of 0.01, but with 0.5 mean.
- Training is conduced with 2000 iterations, which set empirically.
+ Training is conduced with 1500 iterations.
 
@@
     MaxPool 3 &            & 2x2 / 1         & 125x8x256  \\
-    Dense     & Sigmoid    & 128             & 63x4x256   \\
+    Fully-Connected     & Sigmoid    & 16             & 63x4x256   \\
     L-2 Norm  &            &                 & 1x1x128    \\
@@
 
-For KARnet trainied multilayer neural networks is shown below (Table \ref{tab2}), we set 2 layer and number of neurons are [1024,16]. initialized as uniform distribution over [0, 1).
-Used arctangent as activation function.
+For Table \ref{tab2}, KAR learning trained multilayer feedforward network structure is shown below.
+We set network layers of 2 and size of the layers are 1024 and 16.
+Each layer is initialized as uniform distribution over [0, 1).
+We used arctangent as activation function.
 
@@
 
-\subsubsection{3) Parameter Settings}
-For making triplet loss, 0.1 of alpha value is utilized for the proposed method.
-we choose output vector size of 16.
+\subsubsection{Parameter Settings}
+For the triplet network, 0.1 of alpha value is used to make triplet loss.
+For baseline triplet network, we choose random signals for positive and negative input to make triplet input, instead of mining input using KAR learning.
+For Siamese Networks, we put 2 random signal as input and used binary loss function.
 For linear methods such as LSE,SVM and TER, we reduced dimension of input signal to 500x30, by averaging through subcarrier axis. Due to limitation of hardware memory.
-For PCA-LSE, input dimension is reduced by 40 sized features using PCA.
-For Triplet CNN without KAR learning, we choose signature randomly for making input triplets and used triplet loss as used in proposed methods.
-for Siamese Networks, we put 2 random signal as input and used binary loss for training the networks.
+For PCA-LSE, input signal dimension is reduced again to 40 using PCA.
 
-\subsubsection{Results and Discussion}
+\subsection{Results and Discussion}
 
@@
 Comparing with ConvNet based Siamese and Triplet CNN without KAR learning, proposed methods showed the best EER performance. Due to negative mining process included in making triplet loss.
-The proposed method showed much better EER than linear methods, such as SVM,LSE and TER. Since linear methods use reduced input signal.
+The proposed method showed much better EER than linear methods, such as SVM,LSE and TER-RM2. Since linear methods use reduced input signal.
 
@@
 Loss curves of proposed method are shown in Fig.\ref{fig2}.
-This shows that KAR learning not only helps ConvNet to train faster, but also makes it to extract better features.
-As the proposed method shows steeper loss curve when training, and the variance of the validation loss is smaller.
+As the proposed method shows steeper training loss curve compared with other deep learning methods, KAR learning not only helps ConvNet to extract better features, but also helps it to boost training speed.
 
@@
     Methology   &   Best EER (\%) &   Condition   \\  \hline
-    Proposed(TripletCNN with KAR learning) &   19.09   &   lr=0.00005, alpha=0.1  \\
-    Triplet CNN without KAR learning    &   20.08   &   lr=0.00005, alpha=0.1  \\
-    Siamese CNN  &   24.09   &   lr=0.00005, alpha=0.1  \\
-    SVM(RBF)    &   24.31   &   c=1, gamma=0.01/3000 \\
+    Proposed &   19.35   &   lr=0.00005, $\alpha$=0.1  \\
+    Triplet network without mining    &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
+    Siamese network  &   23.53   &   lr=0.00005  \\
+    SVM(RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
     SVM(Linear) &   28.23   &   c=1 \\
-    LSE(Dimension Reduction by PCA)    &   30.79   &  40 dimension input    \\
-    TER &   35.75   &   order=1   \\
+    LSE(Dimension Reduction by PCA)    &   30.79   &  input dimension=40    \\
+    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\
     LSE &   48.44   &   \\  \hline
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30.eps}
-    \caption{Training Loss Curve of the Proposed Method} \label{fig2}
+    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
+    \caption{Training Loss Curve of the Proposed System} \label{fig2}
 \end{figure}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{fig_roc.pdf}
-    \caption{ROC Curve of the Proposed Method} \label{fig3}
+    \includegraphics[width=\textwidth]{fig_roc_v5.eps}
+    \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
 \end{figure}
@@
 \section{Conclusion}
-In this paper, we proposed a novel identity verification system based on Wi-Fi signature signals. 
-In order to train the triplet network effectively, triplet input is mined from Wi-Fi signature signals by the kernel and the range space learning.
-Subsequently, ConvNet structure is adopted for feature extractor which generates feature vectors from input triplets.
-Finally, the triplet network is trained by matching between extracted feature vectors based on L-2 distance comparison.
-Our networks show good feature extracting performance, especially in low-dimension outputs and shows encouraging experimental results in terms of verification accuracy.
+In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network. 
+To refine the triplet inputs for the faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
+Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.
 %

### 2019-07-30 190410_Paper_ACPR/paper_v3.tex
acpr2019: submit

--- 2019-07-30 190410_Paper_ACPR/paper_combined.tex
@@
 By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
-However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Components Analysis.
+However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis.
 Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
@@
 
-\section{Related Works}
+\section{Related works}
 
-\subsection{Triplet Network}
+\subsection{Triplet network}
 % triplet network
@@
 % Rel works: KAR learning
-\subsection{Kernel and the Range space learning}\label{kar}
+\subsection{Kernel and the range space learning}\label{kar}
 
-The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation.
+The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation \cite{goodfellow2016deep}.
 However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.
@@
 %% Methods
-\section{Proposed System}
+\section{Proposed system}
 
@@
 % Figure 1
-\begin{figure}
-    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v4}
-    \caption{An overview of the proposed system} \label{fig1}
+\begin{figure}[!ht]
+    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v5}
+    \caption{An overview of the proposed system.} \label{fig1}
 \end{figure}
@@
 % Methods: ConvNets
-\subsection{ConvNet Structures}
+\subsection{ConvNet structures}
 
@@
  In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with single position was utilized in our experiments.
-After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500 $\times$ 30 $\times$ 6.
+After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500$\times$30$\times$6.
 We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal~\cite{wang2015understanding}.
 
-\subsection{Experimental Settings}
+\subsection{Experimental settings}
 
-\subsubsection{Performance Evaluation}
+\subsubsection{Performance evaluation}
 The proposed system is evaluated under two cases: i) case I on comparison of the proposed system with other linear methods and deep learning based methods based on verification accuracy, and case II on detailed comparison with the deep learning based methods using receiver operating characteristic (ROC) curve and training loss curve.
@@
 The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}.
-With an input data size of 500 $\times$ 30 $\times$ 6, we set two network layers where the size of the each layer is 1024 and 16, respectively.
+With an input data size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively.
 Each layer is initialized with uniform distribution over [0, 1).
-We used ${tan}^{-1}$ as an activation function following \cite{toh2018analytic}.
+We used $\sigma = {tan}^{-1}$ as an activation function following \cite{toh2018analytic}.
 
 \begin{table}[]
-    \caption{The network structure of KAR space learning}\label{tab2}
+    \caption{The network structure of the KAR space learning.}\label{tab2}
     \centering
@@
     Layer   & Size     & Activation \\ \hline
-    Input   & 500x30x6 &            \\
-    Fully-Connected 1 & 1x1x1024 & ArcTan     \\
-    Fully-Connected 2 & 1x1x16  & ArcTan     \\
-    Output  & 1x1x50   &            \\ \hline
+    Input   & 500$\times$30$\times$6 &            \\
+    Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
+    Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
+    Output  & 1$\times$1$\times$50   &            \\ \hline
     \end{tabular}
@@
     Layer     & Activation & Kernel / Stride & Input Size \\ \hline
-    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500x30x6   \\
+    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
@@
 
-\subsection{Results and Discussion}
+\subsection{Results and discussion}
 
@@
 \begin{table}[!h]
-    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signal dataset.}\label{tab3}
+    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab3}
     \centering
@@
 Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning based methods.
-As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest AUC among three compared methods where other two methods showed similar AUC.
+As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods where other two methods showed similar AUC.
 Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network.
@@
 % Figure 2,3
-\begin{figure}[!h]
+\begin{figure}[!ht]
     \begin{center}
     \subfigure[][ROC Curve]{
-         \includegraphics[height=6.4cm]{fig_roc_v9.eps}}
-    \subfigure[][Training Loss Curve]{
-         \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v1.eps}}
-    \caption{(a) shows Receiver Operating Characteristic(ROC) Curve
-    (b) shows Normalized Training Loss Curve of the Proposed System }
+        \includegraphics[height=6.4cm]{fig_roc_v11.eps}}
+    \subfigure[][Normalized training loss curve]{
+        \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
+    \caption{(a) shows the Receiver Operating Characteristic(ROC) Curve and 
+    (b) shows the normalized training loss curve of the deep learning based methods. }
     \label{fig2}
@@
  \end{figure}
-
- % merged 2 graph: omitted separated graph
- \iffalse
- % Figure 3
- \begin{figure}[!h]
-     \includegraphics[width=\textwidth]{fig_roc_v5.eps}
-     \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
- \end{figure}
-
- % Figure 2
-     \begin{figure}[!h]
-     \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
-     \caption{Training Loss Curve of the Proposed System} \label{fig2}
- \end{figure}
- \fi
 

### 2019-07-30 190410_Paper_ACPR/paper_v4.tex
acpr2019: submit

--- 2019-07-30 190410_Paper_ACPR/paper_v3.tex
@@
 In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
-To refine the triplet inputs for faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training set of Wi-Fi signature signals. 
+To refine the triplet inputs for fast loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
@@
 
-In recent years, several behavioral biometric traits for identity authentication are investigated since they are free from the physical characteristic which user owns~\cite{bailador2011analysis}.
-Among the behavioral biometrics, the signature based user authentication~\cite{galbally2015line,sanmorino2012survey} is taking considerable interest with the development of the in-air signature recognition systems~\cite{galbally2015line,jeon2012system,malik20183dairsig}.
-With the help of sensors such as a depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition systems could have less spatial limitation in the signature acquisition process compare to other contact-based authentication systems.
+In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}.
+Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
+% more in-air ref
+With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than contact-based authentication systems.
 
-Recently, the commercial Wi-Fi device is also proposed to be utilized as a in-air signature acquisition sensor due to its easy accessible property \cite{moon2017air}.
-By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
-However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis.
-Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
+Recently, the commercial Wi-Fi device has been adopted for in-air signature authentication due to its easy accessible property \cite{moon2017air}.
+Based on the distortion of the  Wi-Fi CSI signal according to the user gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
+% omitted
+%However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis.
+Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data,
+More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
 
 In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal.
-To achieve not only the promising verification accuracy but also the fast training loss convergence speed for the commercial use, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs for training the triplet network.
-Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained using the mined triplet inputs based on L-2 distance comparison.
+To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs.
+Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on L-2 distance comparison.
+
 The main contributions of our work can be summarized as follows:
 \begin{itemize}
-\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using deep triplet network.
+\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
 \item Adopted the KAR space learning to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in triplet network.
@@
 
-The paper is organized as follows: the related works including triplet network and KAR space learning will be introduced in Section 2 for immediate reference.
+The paper is organized as follows: related works including the triplet network and KAR space learning will be introduced in Section 2 for immediate reference.
 Our proposed method will be discussed in Section 3.
 Section 4 describes our experimental results and analysis.
-Some concluding remarks will be followed in Section 5.
+Some concluding remarks will be given in Section 5.
 
@@
 \section{Conclusion}
-In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network adopting the kernel and the range (KAR) space learning.
-The kernel and the range space learning is initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
-Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
-Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.
+In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using a triplet network adopting the kernel and the range (KAR) space learning.
+The kernel and the range space learning was initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
+Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the basic triplet network and the Siamese network.
 %

### 2019-08-07 190410_Paper_ACPR/paper_v4.tex
siamkar: make spectrogram

@@
 Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
-% more in-air ref
 With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than contact-based authentication systems.
@@
 Among the linear methods, the SVM with RBF kernel function showed best verification performance of 24.31\% EER followed by the SVM with Linear kernel function.
-However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500 $\times$ 30 $\times$ 6) of the input data in the training stage.
+However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
 

### 2019-08-07 190522_Wisig_KAR/karnet_v1_old.py

@@ -1,0 +1,78 @@
+import numpy as np
+
+class KARnet:
+    def __init__(self,data,h,rseed):
+        self.x = data[0]
+        self.y = data[1]
+        self.xte = data[2]
+        self.yte = data[3]
+        
+        self.bias = np.ones([self.x.shape[0],1])
+        self.X = np.hstack([self.bias,self.x])
+        self.rseed = rseed
+        self.h = h
+        self.W = []
+        
+    def f(self,x): # activation func
+        return(np.arctan(x)) # arctan
+        #return(np.log(x/(1-x))) # logit
+    def finv(self,x): # inverse of activation func
+        return(np.tan(x)) # tan
+        #return(1/(1+np.exp(-x))) # sigmoid
+        
+    
+    def pre_eq(self,X,bias,W):
+        return 1*(np.hstack([bias,self.f(1*X.dot(W))]))
+    def sur_eq(self,y,bias,v,w):
+        return (self.finv(y)-1*bias.dot(v)).dot(1*np.linalg.pinv(w))
+
+    def train(self):
+        # initialize w
+        np.random.seed(self.rseed)
+        w,v = [],[]
+        for m in np.arange(len(self.h)):
+            w_row = self.h[len(self.h)-1-m]
+            if m==0:
+                w_col = self.y.shape[1]
+            else:
+                w_col = self.h[len(self.h)-m]
+
+            w.append(np.random.rand(w_row,w_col))
+            v.append(np.random.rand(1,w_col))   
+        w.reverse()
+        v.reverse()
+        
+        # get weight
+        for pre_num in range(len(self.h)+1):
+            sur_num = len(self.h) - 1
+            sur_calc = self.y
+            for s in np.arange(sur_num,pre_num-1,-1):
+                sur_calc = self.sur_eq(sur_calc,self.bias,v[s],w[s])
+            pre_calc = self.X
+            for p in np.arange(0,pre_num,1):
+                pre_calc = self.pre_eq(pre_calc,self.bias,self.W[p])
+                
+            W_calc = np.linalg.pinv(pre_calc).dot(self.finv(sur_calc))
+            self.W.append(W_calc)
+    
+    # calc output
+    def output(self,x):
+        bias = np.ones([x.shape[0],1])
+        x_calc = x
+        for i in range(len(self.W)):
+            x_calc = 1*self.f(np.hstack([bias,x_calc]).dot(self.W[i]))
+        return(x_calc)
+    
+    # get accuracy
[…]

### 2019-08-07 190522_Wisig_KAR/siam_utils_old.py

@@ -49,7 +49,7 @@ def ReadData(PATH,n_splits,rseed):
         label_table = pd.Series(np.arange(len(uniq_label)),index=uniq_label)
         data_y = np.array([label_table[num] for num in lab_read]).reshape([-1,10])
         
-        # use half of the dataset
+        # use all of the dataset
         #idx_half = (data_y[:,0] < 50)
         
         list_csi.append(data_x)#[idx_half])

### 2019-08-07 190522_Wisig_KAR/siamkar_v2_hp.py

@@ -1,0 +1,459 @@
+import tensorflow as tf
+from keras.layers import Input, Conv2D, Lambda, merge, Dense, Flatten,MaxPooling2D, concatenate
+from keras.models import Model, Sequential
+from keras.regularizers import l2
+from keras import backend as K
+from keras.optimizers import SGD,Adam
+from keras.losses import binary_crossentropy
+from siam_utils import get_key
+import numpy.random as rng
+import numpy as np
+from keras.utils.multi_gpu_utils import multi_gpu_model
+
+fc_size = 128
+
+def triplet_loss(y_true, y_pred):
+    #fc_size = 128
+    alpha = 0.1
+    a_pred = y_pred[:, 0:fc_size]
+    p_pred = y_pred[:, fc_size:2*fc_size]
+    n_pred = y_pred[:, 2*fc_size:3*fc_size]
+    pos_dist = tf.reduce_sum(tf.square(tf.subtract(a_pred, p_pred)), axis=-1)
+    neg_dist = tf.reduce_sum(tf.square(tf.subtract(a_pred, n_pred)), axis=-1)
+    basic_loss = tf.add(tf.subtract(pos_dist, neg_dist), alpha)
+    loss = tf.reduce_mean(tf.maximum(basic_loss, 0.0),0)
+    #basic_loss = tf.add(tf.subtract(pos_dist, neg_dist), fc_size)
+    #loss = tf.reduce_sum(basic_loss)
+    
+    return loss
+def W_init(shape,name=None):
+    """Initialize weights as in paper"""
+    values = rng.normal(loc=0,scale=1e-2,size=shape)
+    return K.variable(values,name=name)
+#//TODO: figure out how to initialize layer biases in keras.
+def b_init(shape,name=None):
+    """Initialize bias as in paper"""
+    values=rng.normal(loc=0.5,scale=1e-2,size=shape)
+    return K.variable(values,name=name)
+# Network: Siamese with Triplet loss
+input_shape = (500, 30, 6)
+ank_input = Input(input_shape)
+pos_input = Input(input_shape)
+neg_input = Input(input_shape)
+#build convnet to use in each siamese 'leg'
+
+convnet = Sequential()
+convnet.add(Conv2D(64,(3,3),activation='relu',input_shape=input_shape,padding='same',
+                   kernel_initializer=W_init,kernel_regularizer=l2(2e-4)))
+convnet.add(MaxPooling2D())
[…]

### 2019-08-07 190522_Wisig_KAR/siamkar_v2_hp_old.py

@@ -1,0 +1,459 @@
+import tensorflow as tf
+from keras.layers import Input, Conv2D, Lambda, merge, Dense, Flatten,MaxPooling2D, concatenate
+from keras.models import Model, Sequential
+from keras.regularizers import l2
+from keras import backend as K
+from keras.optimizers import SGD,Adam
+from keras.losses import binary_crossentropy
+from siam_utils import get_key
+import numpy.random as rng
+import numpy as np
+from keras.utils.multi_gpu_utils import multi_gpu_model
+
+fc_size = 16
+
+def triplet_loss(y_true, y_pred):
+    #fc_size = 128
+    alpha = 0.1
+    a_pred = y_pred[:, 0:fc_size]
+    p_pred = y_pred[:, fc_size:2*fc_size]
+    n_pred = y_pred[:, 2*fc_size:3*fc_size]
+    pos_dist = tf.reduce_sum(tf.square(tf.subtract(a_pred, p_pred)), axis=-1)
+    neg_dist = tf.reduce_sum(tf.square(tf.subtract(a_pred, n_pred)), axis=-1)
+    basic_loss = tf.add(tf.subtract(pos_dist, neg_dist), alpha)
+    loss = tf.reduce_mean(tf.maximum(basic_loss, 0.0),0)
+    #basic_loss = tf.add(tf.subtract(pos_dist, neg_dist), fc_size)
+    #loss = tf.reduce_sum(basic_loss)
+    
+    return loss
+def W_init(shape,name=None):
+    """Initialize weights as in paper"""
+    values = rng.normal(loc=0,scale=1e-2,size=shape)
+    return K.variable(values,name=name)
+#//TODO: figure out how to initialize layer biases in keras.
+def b_init(shape,name=None):
+    """Initialize bias as in paper"""
+    values=rng.normal(loc=0.5,scale=1e-2,size=shape)
+    return K.variable(values,name=name)
+# Network: Siamese with Triplet loss
+input_shape = (500, 30, 6)
+ank_input = Input(input_shape)
+pos_input = Input(input_shape)
+neg_input = Input(input_shape)
+#build convnet to use in each siamese 'leg'
+
+convnet = Sequential()
+convnet.add(Conv2D(64,(3,3),activation='relu',input_shape=input_shape,padding='same',
+                   kernel_initializer=W_init,kernel_regularizer=l2(2e-4)))
+convnet.add(MaxPooling2D())
[…]

### 2019-08-07 190522_Wisig_KAR/wisig_siamkar_v2_hp.py

@@ -1,0 +1,217 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy.random as rng
+from keras.utils import to_categorical
+from siam_utils import *
+from importlib import reload
+#from siamkar_v1 import *
+#from karnet_v1 import KARnet
+from datetime import datetime 
+import socket
+import tensorflow as tf
+import siamkar_v2_hp
+import karnet_v1
+#from siamkar_v2 import SiamKar_Loader,SiamTri_Loader,Siamese_Loader,siamtri_net,siamese_net
+#from karnet_v1 import KARnet
+%matplotlib inline
+
+host = socket.gethostname()
+## Data
+if(host=='pregpu-2k80'):
+    PATH = "/home/herokwon/mount_data/Data/Wi-Fi_HC/180_100/"
+    res_path = '/home/herokwon/Git/MILab/190522_Wisig_KAR/res/'
+else:
+    PATH = "D:\\Data\\WIFI\\Wi-Fi_HC\\180_100\\"
+    # save path
+    res_path = 'D:\\Git\\MILab\\190522_Wisig_KAR\\res\\'
+
+
+col_df = (['timenow','host','model_type','rseed',
+'splits','n_val','fc_size','batch_size','n_iter','alpha','lr','eer','trn_time','desc'])
+
+try:
+    res_df = pd.read_csv(res_path + 'res_df_v4.csv')
+except FileNotFoundError:
+    res_df = pd.DataFrame()
+
+alpha=0.1
+fc_size = 16
+host = socket.gethostname()
+
+desc = 'def_siamese_karlast1024_hardpos'
+
+types = [0,1,2]
+seeds = [10,20,30,40,50]
+
+for rseed  in seeds:
+    for model_type in types:        
+        np.random.seed(rseed)        
+        n_splits = 2
+        data_skf = ReadData(PATH,n_splits,rseed=rseed)
+        loss_every = 100
+        n_val = 10
+        batch_size = 32
+        n_iter = 3000
+        lr = 0.00005
+
+        for splits in range(len(data_skf)):
+            now = datetime.now()
+            timenow = str(now).replace(' ','_').replace(':','_')
+            
+            res_eer = pd.DataFrame()
+            list_losstr = []
+            list_losste = []
+            data_list = data_skf[splits]            
+            
+            if model_type==0:
+                #reimport
+                siamkar_v2_hp = reload(siamkar_v2_hp)
[…]

### 2019-09-03 190410_Paper_ACPR/paper_v5.tex
ACPR_paper: rev 7

--- 2019-08-07 190410_Paper_ACPR/paper_v4.tex
@@
 In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
-To refine the triplet inputs for fast loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+To refine the triplet inputs for fast loss convergence, the kernel and the range space learning is adopted in order to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
@@
 Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
-With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than contact-based authentication systems.
+With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than the contact-based authentication systems.
 
 Recently, the commercial Wi-Fi device has been adopted for in-air signature authentication due to its easy accessible property \cite{moon2017air}.
-Based on the distortion of the  Wi-Fi CSI signal according to the user gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
+Based on the distortion of the  Wi-Fi CSI signal according to the user's gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
 % omitted
@@
 Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data,
-More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
+More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal-based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
 
 In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal.
-To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs.
+To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs.
 Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on L-2 distance comparison.
@@
 \item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
-\item Adopted the KAR space learning to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in triplet network.
+\item Adopted the KAR space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in triplet network.
 \item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
@@
 % triplet network
-Triplet network is kind of a metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}.
-It is widely used in person re-identification problems, which solves the matching problem of individuals and identity between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
-The distinction between classes is challenging in this task since the distinctive feature is relatively weak compare to the background features such as pose, hair and textures.
+Triplet network is a kind of metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}.
+It is widely used in person re-identification problems, which solves the problem of matching individual identities between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
+The distinction between classes is challenging in this task since the distinctive feature is relatively weak compared to the background features such as pose, hair and textures.
 
 To address this problem, the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data.
-The objective function of the triplet network is to make feature vectors to be placed in the appropriate separation space by putting the positive (similar) data more closer to the anchor (reference) data and the negative (dissimilar) data to keep away from the anchor data.
+The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive (similar) data closer to the anchor (reference) data and keeping the negative (dissimilar) data away from the anchor data.
 
@@
 Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed.
-They utilized large mini-batch at each training iteration and select the triplet based on the training network.
+They utilized large mini-batch at each training iteration and selected the triplet based on the training network.
 However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.
@@
 % Methods: System overview(Fig.1)
-In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (will be called Wi-Fi signature signals hereafter) using triplet network.
+In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using triplet network.
 Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network~\cite{schroff2015facenet}.
@@
 Subsequently, the ConvNet structure in the triplet network (item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (item (c) in Fig.~\ref{fig1}).
-The following subsections detail the triplet mining using KAR space learning and the triplet network.
+The following subsections will show the details of the triplet mining using KAR space learning and the triplet network.
 
@@
 \subsection{Triplet mining using kernel and the range space learning}
-According to \cite{schroff2015facenet}, it is important to select the hard positive sample and the hard negative sample from each given anchor sample for the faster loss convergence when training the triplet network.
-The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the smallest (which is most likely to be misclassified as a positive sample).
-However, there is no information about which sample is the hard positive/negative sample before we train the network.
+According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for the faster loss convergence when training the triplet network.
+The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the least (which is most likely to be misclassified as a positive sample).
+However, there is no information about which sample is the hard positive or negative before we train the network.
 
-In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative sample from the given anchor sample.
-Since the KAR space learning has no iterative learning process, we can mine the triplet samples without train an another network with backpropagation process.
+In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative samples from the given anchor sample.
+Since the KAR space learning has no iterative learning process, we can mine the triplet samples without training an another network with backpropagation process.
 
 By training the KAR space network with the training samples, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network.
-For each training sample as an anchor sample $\mathbf{x}_{anc}$ and to measure the distance between $\mathbf{x}_{anc}$ and other samples, we firstly need to train the KAR space learning structure $f\left(.\right)$ using whole training sample matrix $\mathbf{X}\in \mathbb{R}^{n\times m}$ as follows~\cite{toh2018gradient}:
+Taking each training sample as an anchor sample $\mathbf{x}_{anc}$, to measure the distance between $\mathbf{x}_{anc}$ and other samples, we first need to train the KAR space learning structure $f\left(.\right)$ using whole training sample matrix $\mathbf{X}\in \mathbb{R}^{n\times m}$ as follows~\cite{toh2018gradient}:
 \begin{equation}
@@
 \end{equation}
-where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the threshold to make the sample more harder.
-Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative sample rather than just using the hardest positive/negative sample since the hardest samples are likely to be an outlier which degrades the training process of the triplet network.
-We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples match the equations.
+where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the thresholds which make the sample harder.
+Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative samples instead of just using the hardest positive/negative samples since the hardest samples are likely to be outliers which degrade the training process of the triplet network.
+We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples which match the equations.
 
@@
 
-To design the triplet network, we firstly need to select the feature extractor which converts the input triplet data into feature vectors.
+To design the triplet network, we first need to select the feature extractor which converts the input triplet data into feature vectors.
 In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
@@
 The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
-The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layers.
+The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layer.
 Following, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
@@
 For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping with the hard positive input sample $\mathbf{x}_{pos,i}$ and the hard negative input sample $\mathbf{x}_{neg,i}$ selected based on the KAR space learning.
-Generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, positive and negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
+Generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, the positive and the negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
 
@@
 After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500$\times$30$\times$6.
-We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal~\cite{wang2015understanding}.
+We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals have issues of device firmware in their phase signal~\cite{wang2015understanding}.
 
@@
 \subsubsection{Performance evaluation}
-The proposed system is evaluated under two cases: i) case I on comparison of the proposed system with other linear methods and deep learning based methods based on verification accuracy, and case II on detailed comparison with the deep learning based methods using receiver operating characteristic (ROC) curve and training loss curve.
-For the Case I, existing linear methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between} and deep learning based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
-The Siamese network and baseline triplet network utilized same ConvNet structures with the proposed system and only differed in the input data style and the loss function.
+The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other linear or deep learning-based methods based on verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using receiver operating characteristic (ROC) curve and training loss curve.
+For the Case I, existing linear methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.
 
-The verification performance of the proposed system and other methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation tests.
-Due to the memory constraint caused by the large data size, noting here that deep learning based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number with the number of the positive pairs.
+The verification performance of the proposed system and other methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation test.
+Due to the memory constraint caused by the large data size, noting here that the deep learning-based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number as the number of the positive pairs.
 
@@
 The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}.
-With an input data size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively.
+With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively.
 Each layer is initialized with uniform distribution over [0, 1).
@@
 
-For the proposed system and the deep learning based methods, we utilized same ConvNet structure as specified in Table~\ref{tab1}.
-We trained the network starting with a learning rate of 0.00005 with a mini-batch sized of 32.
-We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for output layer.
+For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}.
+We trained the network starting with a learning rate of 0.00005 and a mini-batch, size of 32.
+We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for the output layer.
 The output layer is regularized with L-2 penalty of 0.0001.
-We initialized all network weights in the convolutional layers with a normal distribution with zero-mean and a standard deviation of 0.01.
-Biases were also initialized with a normal distribution with 0.5 mean and a standard deviation of 0.01.
+We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation of 0.01.
+Biases were also initialized with normal distribution of 0.5 mean and standard deviation of 0.01.
 For the triplet networks, the hyper-parameter regulating triplet loss is empirically set to 0.1.
-The training epochs are set to 1,500 for all three deep learning based algorithms.
-For the linear methods such as LSE,SVM and TER, the input signal is firstly resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
+The training epochs are set to 1,500 for all three deep learning-based algorithms.
+For the linear methods such as LSE,SVM and TER, the input signal is initially resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
 For the PCA-LSE, the input dimension is reduced to 40.
@@
 
-Case I: Table~\ref{tab3} shows the best average EER performance from five runs of two-fold cross-validation test and the parameter condition.
-Among the linear methods, the SVM with RBF kernel function showed best verification performance of 24.31\% EER followed by the SVM with Linear kernel function.
-However, all three deep learning based methods showed better performance than the SVM with RBF kernel function since the deep learning based methods can utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
-
-Among the deep learning based methods, the Siamese network which is also a metric learning system but utilize two inputs and uses the contrastive loss function for training showed the worst verification performance of 23.53\% EER.
-The best best average test EER performance was obtained from the proposed system with 19.35\% EER and the baseline triplet network without input mining showed slightly worse performance of 20.34\% EER.
+Case I: Table~\ref{tab3} shows the best average of EER performance from five runs of two-fold cross-validation test and the parameter condition.
+Among the linear methods, the SVM with RBF kernel function showed the best verification performance of 24.31\% EER followed by the SVM with Linear kernel function.
+However, all three deep learning-based methods showed better performance than the SVM with RBF kernel function since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
+Among the deep learning-based methods, the Siamese network is also a metric learning system, but it differs from our system in that it receives two inputs and uses the contrastive loss function for training.
+The best average of test EER performance was obtained from the proposed system with 19.35\% EER.
+The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER.
+The Siamese network showed the worst verification performance of 23.53\% EER.
 
@@
 
-Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning based methods.
-As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods where other two methods showed similar AUC.
+Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning-based methods.
+As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods while other two methods show similar AUC.
 Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network.
-We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has difference starting value based on their function.
-According to these two observations, it can be concluded that the triplet input mining with KAR space learning not only improves the training loss convergence speed but also improves the verification performance.
+We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value based on their function.
+According to these two observations, it can be concluded that the triplet input mining with KAR space learning improves not only the training loss convergence speed but also the verification performance.
 
@@
 In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using a triplet network adopting the kernel and the range (KAR) space learning.
-The kernel and the range space learning was initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+The kernel and the range space learning was initially adopted in order to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
-Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the basic triplet network and the Siamese network.
+Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
 %

### 2019-09-03 190410_Paper_ACPR/paper_v5_r3-1.tex
ACPR_paper: rev 7

--- 2019-09-03 190410_Paper_ACPR/paper_v5.tex
@@
 %The abstract should briefly summarize the contents of the paper in 15--250 words.
-In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
-To refine the triplet inputs for fast loss convergence, the kernel and the range space learning is adopted in order to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi CSI signals. 
+The kernel and the range space learning is initially adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
@@
 In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}.
-Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
+Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is attracting considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
 With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than the contact-based authentication systems.
@@
 
-In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal.
+In this paper, we utilize the deep triplet network for identity verification based on the Wi-Fi CSI signature signal.
 To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs.
-Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on L-2 distance comparison.
+Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on the L-2 distance comparison.
 
@@
 \item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
-\item Adopted the KAR space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in triplet network.
+\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in triplet network.
 \item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
@@
 % triplet network
-Triplet network is a kind of metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}.
-It is widely used in person re-identification problems, which solves the problem of matching individual identities between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
-The distinction between classes is challenging in this task since the distinctive feature is relatively weak compared to the background features such as pose, hair and textures.
+The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
+\textbf{It is often seen in person re-identification~
+\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
+Re-identification is an identification problem using the images/videos taken from a different camera~\cite{bedagkar2014survey}.
+The individual identities are matched based on identity discriminative features.
+In these problems, the distinction among the classes is challenging since the features are relatively weak compared to the background features.
+To address this problem, the triplet network optimizes the embedding training data space such that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.}
 
-To address this problem, the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data.
+\textbf{The triplet network receives triplet pairs as its input which is made from a combination of the input data.
+Since not all triplet samples are contribute to the training ~\cite{schroff2015facenet}, recent issues have highlighted which input pairs will be used for training.
+To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.}
+
+\textbf{Recently, \cite{schroff2015facenet} adopted additional triplet mining process for the faster convergence speed.
+They utilized large mini-batch at each training iteration and selected the triplet based on the training network rather than the random sampling.
+However, this strategy needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs which burden the time.}
+
+%the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data.
 The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive (similar) data closer to the anchor (reference) data and keeping the negative (dissimilar) data away from the anchor data.
+%.... (1. tell how the triplet network solves the problem and not unrelated parts of it. 2. Tell what further issues arise from triplet network?)
 
 % optimize training
-Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary.
+%Not clear and no link to above, rewrite this sentence.
+%Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary.
 To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.
-Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed.
+%Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed.
 They utilized large mini-batch at each training iteration and selected the triplet based on the training network.
-However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.
+%However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.
 
@@
 
-The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation \cite{goodfellow2016deep}.
-However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.
+The multilayer feedforward neural networks is generally trained by the gradient descent method based on backpropagation \cite{goodfellow2016deep}.
+However, setting the learning parameters such as learning rate or momentum value is time consuming and yet important to arrive at reasonable solution.
 
-Recently, gradient-free learning framework based on series of the kernel and the range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
-Since it is trained by linear equations, no learning parameters nor the iteration are needed to train the networks.
-Using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.
+Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh2018learning,toh2018gradient}.
+The learning method is grounded on linear algebra with neither learning parameters nor iteration are needed in training.
 
@@
 %% Methods
-\section{Proposed system}
+\section{Proposed System}
 
 % Methods: System overview(Fig.1)
-In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using triplet network.
-Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network~\cite{schroff2015facenet}.
-Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from the each given anchor sample in the training dataset (item (a) in Fig.~\ref{fig1}).
-Subsequently, the ConvNet structure in the triplet network (item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (item (c) in Fig.~\ref{fig1}).
-The following subsections will show the details of the triplet mining using KAR space learning and the triplet network.
+In this section, we propose an identity verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}.
+Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network.
+Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample in the training dataset (see item (a) in Fig.~\ref{fig1}).
+Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
+The following subsections describe the details of the triplet mining using KAR space learning and the triplet network.
 
@@
 \subsection{Triplet mining using kernel and the range space learning}
-According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for the faster loss convergence when training the triplet network.
-The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the least (which is most likely to be misclassified as a positive sample).
-However, there is no information about which sample is the hard positive or negative before we train the network.
+%1. Need to explain what is "hard" first.
+%2. Also, need to explain "anchor sample" before using it.
+% description of anchor sample
+% loss convergence problem
+% we need hard sample selection
+
+\textbf{The triplet network receives triplet data as an input, which consists of the reference data (will be called anchor hereafter) and corresponding positive (same class with the anchor) and negative data (different class with the anchor).
+The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive data closer to the anchor data and keeping the negative data away from the anchor data.}
+
+According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for faster loss convergence when training the triplet network.
+The hard positive sample denotes the positive sample whose distance to the anchor sample is the greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is the smaller (which is most likely to be misclassified as a positive sample).
+However, there is no information about which sample is hard positive or negative before we train the network.
 
 In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative samples from the given anchor sample.
-Since the KAR space learning has no iterative learning process, we can mine the triplet samples without training an another network with backpropagation process.
+Since the KAR space learning has no iterative learning process, we can mine the triplet samples without using the time consuming backpropagation training process.
 
-By training the KAR space network with the training samples, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network.
-Taking each training sample as an anchor sample $\mathbf{x}_{anc}$, to measure the distance between $\mathbf{x}_{anc}$ and other samples, we first need to train the KAR space learning structure $f\left(.\right)$ using whole training sample matrix $\mathbf{X}\in \mathbb{R}^{n\times m}$ as follows~\cite{toh2018gradient}:
+By training the network with using the single shot KAR space learning method, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network.
+Taking each training sample as an anchor sample $\mathbf{x}_{anc}$, to measure the distance between $\mathbf{x}_{anc}$ and other samples, the trained network output given by:
+
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{X}$ is a stacked matrix of $m$ training sample vectors, $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$, $\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$, $\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is an activation function.
 
-Following, the hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ from the input anchor sample $\mathbf{x}_{anc}$ can be respectively selected among the positive samples and the negative samples as follows:
+is used to generate the hard positive and hard negative samples.
+The hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can be respectively to determined by:
+
 \begin{equation}
@@
 \end{equation}
-where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the thresholds which make the sample harder.
+
+where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the thresholds which determines whether a sample is hard positive/negative.
 Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative samples instead of just using the hardest positive/negative samples since the hardest samples are likely to be outliers which degrade the training process of the triplet network.
@@
 The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layer.
-Following, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
+Subsequently, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
 The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.
@@
 
-The triplet loss function is proposed in \cite{hoffer2015deep} to train the triplet network.
-For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping with the hard positive input sample $\mathbf{x}_{pos,i}$ and the hard negative input sample $\mathbf{x}_{neg,i}$ selected based on the KAR space learning.
-Generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, the positive and the negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
+The triplet loss function was first seen in \cite{hoffer2015deep} to train the triplet network.
+For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping the hard positive input samples $\mathbf{x}_{pos,i}$ and the hard negative input samples $\mathbf{x}_{neg,i}$ selected based on the KAR space learning.
+The generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, the positive and the negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
 
 Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:
+
 \begin{equation}
@@
 \end{equation}
-where N denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
+
+where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
 The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.
@@
 \section{Conclusion}
-In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using a triplet network adopting the kernel and the range (KAR) space learning.
-The kernel and the range space learning was initially adopted in order to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
+In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi CSI signals. 
+The kernel and the range space learning was initially adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 

### 2019-09-03 190410_Paper_ACPR/paper_v6_r4-1.tex
ACPR_paper: rev 7

--- 2019-09-03 190410_Paper_ACPR/paper_v5_r3-1.tex
@@
 Based on the distortion of the  Wi-Fi CSI signal according to the user's gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
-% omitted
-%However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis.
-Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data,
+
 More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal-based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
@@
 The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
-\textbf{It is often seen in person re-identification~
-\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}.
-Re-identification is an identification problem using the images/videos taken from a different camera~\cite{bedagkar2014survey}.
-The individual identities are matched based on identity discriminative features.
-In these problems, the distinction among the classes is challenging since the features are relatively weak compared to the background features.
-To address this problem, the triplet network optimizes the embedding training data space such that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.}
+\textbf{It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features.
+The main difference between person re-identification and identification is the person re-identification is more challenging task by associating images of the same person taken from different cameras or from the same camera in different occasions.
+}
 
-\textbf{The triplet network receives triplet pairs as its input which is made from a combination of the input data.
-Since not all triplet samples are contribute to the training ~\cite{schroff2015facenet}, recent issues have highlighted which input pairs will be used for training.
-To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.}
+In these problem, to distinguish among the classes is a challenging task since the features are relatively weak compared to the background features.
+To address this problem, the triplet network optimizes the embedding data space such that those data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.
 
-\textbf{Recently, \cite{schroff2015facenet} adopted additional triplet mining process for the faster convergence speed.
+The triplet network receives triplet pairs as its input.
+These triplets pairs are constructed based on a combination of the input data.
+Since not all triplet samples contribute to the training, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training.
+To optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplet \textbf{from a small number of classes (persons) in each iteration.}
+
+Recently, \cite{schroff2015facenet} adopted a triplet mining process to speed up the training convergence.
 They utilized large mini-batch at each training iteration and selected the triplet based on the training network rather than the random sampling.
-However, this strategy needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs which burden the time.}
-
-%the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data.
-The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive (similar) data closer to the anchor (reference) data and keeping the negative (dissimilar) data away from the anchor data.
-%.... (1. tell how the triplet network solves the problem and not unrelated parts of it. 2. Tell what further issues arise from triplet network?)
-
-% optimize training
-%Not clear and no link to above, rewrite this sentence.
-%Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary.
-To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.
-%Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed.
-They utilized large mini-batch at each training iteration and selected the triplet based on the training network.
-%However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.
+However, this strategy needed a few thousands of exemplars mini-batch in every training iteration to select the triplet pairs.
+This results in a heavy computational load in training.
 
@@
 Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh2018learning,toh2018gradient}.
-The learning method is grounded on linear algebra with neither learning parameters nor iteration are needed in training.
+The learning method is grounded on linear algebra with neither learning parameters nor iteration is needed in training.
 
 % Karnet structure and mining samples.
-Let the training dataset $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ as the network outputs.
+Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
 Then the multilayer neural network structure can be written in linear equation form as follows:
 \begin{equation}
-    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
+    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right), i=1,\dotsc,n,
 \end{equation}
@@
 \begin{equation}
-    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right).
+    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), i=1,\dotsc,n.
 \end{equation}
@@
 % Methods: System overview(Fig.1)
-In this section, we propose an identity verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}.
-Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network.
+In this section, we propose an identity verification system based on the Wi-Fi in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}.
+Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet input mining together with the triplet network.
 Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample in the training dataset (see item (a) in Fig.~\ref{fig1}).
+\textbf{The hard positive and hard negative samples refer to positive and negative class data which are likely to be misclassified by the network.}
 Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
@@
 \subsection{Triplet mining using kernel and the range space learning}
-%1. Need to explain what is "hard" first.
-%2. Also, need to explain "anchor sample" before using it.
-% description of anchor sample
-% loss convergence problem
-% we need hard sample selection
 
-\textbf{The triplet network receives triplet data as an input, which consists of the reference data (will be called anchor hereafter) and corresponding positive (same class with the anchor) and negative data (different class with the anchor).
-The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive data closer to the anchor data and keeping the negative data away from the anchor data.}
+The triplet network receives a triplet of data as its inputs.
+These triplet data set consists of the reference data (will be called anchor samples hereafter) and the corresponding positive class (same class with that of the anchor) and negative class data (different class from that of the anchor).
+\textbf{The goal of the triplet network is to position the feature vectors in appropriate separation space by putting the positive sample closer to the anchor sample and keeping the negative sample away from the anchor sample.}
 
-According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for faster loss convergence when training the triplet network.
-The hard positive sample denotes the positive sample whose distance to the anchor sample is the greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is the smaller (which is most likely to be misclassified as a positive sample).
-However, there is no information about which sample is hard positive or negative before we train the network.
+\textbf{According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for the faster loss convergence when training the triplet network.
+The hard positive sample denotes the positive sample whose distance to the anchor sample is greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is smaller (which is most likely to be misclassified as a positive sample).
+However, there is no information about which sample is the hard positive or negative before we train the network.}
 

### 2019-09-03 190410_Paper_ACPR/paper_v7_r5-1.tex
ACPR_paper: rev 7

--- 2019-09-03 190410_Paper_ACPR/paper_v6_r4-1.tex
@@
 %
-\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
+\title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
 %
-\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
+\titlerunning{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
 % If the paper title is too long for the running head, you can set
@@
 %The abstract should briefly summarize the contents of the paper in 15--250 words.
-In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi CSI signals. 
-The kernel and the range space learning is initially adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
-Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
+In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
+To enable a fast loss convergence, a kernel and the range space learning is initially adopted for refining the triplet inputs by mining the distinctive inputs. 
+Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
 Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
@@
 
-In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}.
-Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is attracting considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
-With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than the contact-based authentication systems.
+Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}.
+Among these behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
+With the help of sensors such as the depth camera~\cite{malik20183dairsig} or a mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems.
 
@@
 Based on the distortion of the  Wi-Fi CSI signal according to the user's gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.
-
 More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal-based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.
@@
 In this paper, we utilize the deep triplet network for identity verification based on the Wi-Fi CSI signature signal.
-To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs.
-Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on the L-2 distance comparison.
+To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs.
+Subsequently, the triplet network which utilizes the ConvNet structure as a feature extractor is trained based on the L-2 distance comparison.
 
@@
 \item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
-\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in triplet network.
-\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
+\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
+\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
 \end{itemize}
 
-The paper is organized as follows: related works including the triplet network and KAR space learning will be introduced in Section 2 for immediate reference.
-Our proposed method will be discussed in Section 3.
+The paper is organized as follows: related works including the triplet network and KAR space learning are introduced in Section 2 for immediate reference.
+Our proposed method are discussed in Section 3.
 Section 4 describes our experimental results and analysis.
-Some concluding remarks will be given in Section 5.
+Some concluding remarks are given in Section 5.
 
@@
 The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
-\textbf{It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features.
-The main difference between person re-identification and identification is the person re-identification is more challenging task by associating images of the same person taken from different cameras or from the same camera in different occasions.
-}
+It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features.
+The main difference between person identification and re-identification is that the later is a more challenging task where images of the same person taken from different cameras or from the same camera in different occasions are to be associated.
+In this re-identification problem, to distinguish among the classes is a challenging task since the features are relatively weak compared with the background features.
+To address this problem, we adopt a triplet network which optimizes the embedding data space so that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.
 
-In these problem, to distinguish among the classes is a challenging task since the features are relatively weak compared to the background features.
-To address this problem, the triplet network optimizes the embedding data space such that those data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.
-
-The triplet network receives triplet pairs as its input.
-These triplets pairs are constructed based on a combination of the input data.
-Since not all triplet samples contribute to the training, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training.
-To optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplet \textbf{from a small number of classes (persons) in each iteration.}
-
+The triplet network receives triplet pairs of data as its input.
+These data triplets are constructed based on a combination of the input data.
+Since not all triplet samples contribute to the desired classification, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training.
+In order to optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplet from a small number of classes (persons) in each iteration.
 Recently, \cite{schroff2015facenet} adopted a triplet mining process to speed up the training convergence.
-They utilized large mini-batch at each training iteration and selected the triplet based on the training network rather than the random sampling.
-However, this strategy needed a few thousands of exemplars mini-batch in every training iteration to select the triplet pairs.
+They utilized a large mini-batch at each training iteration and selected the triplet based on the training network rather than random sampling.
+However, this strategy needed a few thousands of exemplar mini-batches in every training iteration for triplet pairs selection.
 This results in a heavy computational load in training.
@@
 % Rel works: KAR learning
-\subsection{Kernel and the range space learning}\label{kar}
+\subsection{Kernel and the range space learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient}}\label{kar}
 
-The multilayer feedforward neural networks is generally trained by the gradient descent method based on backpropagation \cite{goodfellow2016deep}.
-However, setting the learning parameters such as learning rate or momentum value is time consuming and yet important to arrive at reasonable solution.
+Generally, the multilayer feedforward neural networks is trained based on the gradient descent method via backpropagation~\cite{goodfellow2016deep}.
+However, setting the learning parameters such as the learning rate or the learning momentum is a time consuming task.
 
@@
 % Karnet structure and mining samples.
-Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
+Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
 Then the multilayer neural network structure can be written in linear equation form as follows:
@@
 where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
-\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
-By adopting the one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$, The trained weight matrices $\mathbf{W}_{i}$ using KAR space manipulation can be obtained as follows~\cite{toh2018gradient}:
+\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is the activation function.
+By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
 
@@
 % Methods: System overview(Fig.1)
-In this section, we propose an identity verification system based on the Wi-Fi in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}.
-Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet input mining together with the triplet network.
-Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample in the training dataset (see item (a) in Fig.~\ref{fig1}).
-\textbf{The hard positive and hard negative samples refer to positive and negative class data which are likely to be misclassified by the network.}
-Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
+In this section, we propose an identity verification system based on the Wi-Fi in-air handwritten signature (which will be called Wi-Fi signature hereafter) using the triplet network~\cite{hoffer2015deep}.
+Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for mining the triplet input.
+Essentially, the KAR space projection learning is utilized to learn the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample (see item (a) in Fig.~\ref{fig1}).
+The hard positive and the hard negative samples refer to positive and negative class samples which are likely to be misclassified by the network.
+Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on a triplet loss function using the L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
 The following subsections describe the details of the triplet mining using KAR space learning and the triplet network.
@@
 
-The triplet network receives a triplet of data as its inputs.
-These triplet data set consists of the reference data (will be called anchor samples hereafter) and the corresponding positive class (same class with that of the anchor) and negative class data (different class from that of the anchor).
-\textbf{The goal of the triplet network is to position the feature vectors in appropriate separation space by putting the positive sample closer to the anchor sample and keeping the negative sample away from the anchor sample.}
+The network receives a triplet set of data as its inputs.
+These triplet data consist of the reference data (will be called anchor samples hereafter) and the corresponding positive class data (same class with that of the anchor) and negative class data (different class from that of the anchor).
+The goal of the triplet network is to position the feature vectors with appropriate separation space by putting the positive samples close to the anchor sample and keeping the negative sample away from the anchor sample.
 
-\textbf{According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for the faster loss convergence when training the triplet network.
-The hard positive sample denotes the positive sample whose distance to the anchor sample is greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is smaller (which is most likely to be misclassified as a positive sample).
-However, there is no information about which sample is the hard positive or negative before we train the network.}
+According to \cite{schroff2015facenet}, it is important to select the hard positive samples and the hard negative samples with reference to the given anchor sample for fast loss convergence when training the triplet network.
+A hard positive sample is defined as a sample whose distance to the anchor sample is large (which is most likely to be misclassified as a negative sample).
+On the other hand, a hard negative sample is defined as a sample whose distance to the anchor sample is small (which is most likely to be misclassified as a positive sample).
+However, from the raw data, there is no information about regarding whether a sample is considered hard positive or hard negative before we train the network.
 
@@
 
-By training the network with using the single shot KAR space learning method, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network.
-Taking each training sample as an anchor sample $\mathbf{x}_{anc}$, to measure the distance between $\mathbf{x}_{anc}$ and other samples, the trained network output given by:
-
+By training the network with the single shot KAR space learning, we can map the L-2 distance between every samples by using the output vector of the KAR space network.
+\textbf{For training dataset $\mathbf{X}$, the trained network output is given by:}
 \begin{equation}
@@
 \end{equation}
-
-is used to generate the hard positive and hard negative samples.
-The hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can be respectively to determined by:
-
+\textbf{For anchor sample $\mathbf{x}_{anc}$ which is randomly selected from training dataset X, the output of the KAR learning makes it possible to measure the distance between each sample.}
+A hard positive sample $\mathbf{x}_{pos}$ and a hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can each be respectively determined based on:
 \begin{equation}
@@
 \end{equation}
-
-where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the thresholds which determines whether a sample is hard positive/negative.
-Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative samples instead of just using the hardest positive/negative samples since the hardest samples are likely to be outliers which degrade the training process of the triplet network.
-We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples which match the equations.
+where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ respectively denote the thresholds that determine whether a sample is hard positive or hard negative.
+Since the hardest samples are likely to be outliers which can degrade the training process of the triplet network, we empirically set the $\mathrm{t}_{pos}$ at 75 percentile of the L-2 distance and $\mathrm{t}_{neg}$ at 25 percentile of the L-2 distance.
+The final set of $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ samples is randomly selected from those samples threshold by~\eqref{pos} and~\eqref{neg}.
 
 % Methods: ConvNets
-\subsection{ConvNet structures}
+\subsection{ConvNet structure}
 
-To design the triplet network, we first need to select the feature extractor which converts the input triplet data into feature vectors.
+The next step is to design a feature extractor which converts the input triplet data into feature vectors.
 In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
 
-Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$.
-The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1.
-The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layer.
-Subsequently, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
-The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.
-
-%Since the networks utilize three ConvNet structures which ties the weights each other, noting here that three structures described in Fig~\ref{fig1} (b) are actually the same model.
+Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of three convolutional layers and one fully-connected layer.
+The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, 256\}$, with fixed filter size of $3\times3$, each of stride 1.
+The Rectiﬁed Linear (ReLU) activation function and the Max-pooling layer are applied between each convolutional layer.
+Subsequently, the extracted features from the last convolutional layer are flattened into a vector before feeding into the fully-connected network.
+The output vectors from the fully-connected layer are finally transformed using the sigmoid function followed by a L-2 normalization.
 
 % Methods: Triplet loss
-\subsection{Triplet loss}
+\subsection{The triplet loss}
 
-The triplet loss function was first seen in \cite{hoffer2015deep} to train the triplet network.
-For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping the hard positive input samples $\mathbf{x}_{pos,i}$ and the hard negative input samples $\mathbf{x}_{neg,i}$ selected based on the KAR space learning.
-The generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, the positive and the negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.
-
-Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:
-
+The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network.
+\textbf{For selected anchor input sample $\mathbf{x}_{anc,i}$, the $i_{th}$ triplet input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$ is generated by grouping positive input sample $\mathbf{x}_{pos,i}$ and the negative input sample $\mathbf{x}_{neg,i}$.
+The generated triplet input is fed into ConvNet structure and make feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$.}
+The triplet loss function is formulated based on a summation of the difference between the positive distance (the L-2 distance between the anchor vector and the positive vector) and the negative distance (the L-2 distance between the anchor vector and the negative vector) as follows:
 \begin{equation}
@@
 \end{equation}
-
 where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
-The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.
+The ConvNet structure using equation~\eqref{triplet} is trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.
 
@@
 \subsection{Dataset}
- In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with single position was utilized in our experiments.
-After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500$\times$30$\times$6.
-We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals have issues of device firmware in their phase signal~\cite{wang2015understanding}.
+ In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with the user located at a single position is utilized in our experiments.
+The Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with sample size 500$\times$30$\times$6.
+We utilize only the absolute value from each complex CSI signal in our experiments.
 
@@
 
-\subsubsection{Performance evaluation}
-The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other linear or deep learning-based methods based on verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using receiver operating characteristic (ROC) curve and training loss curve.
-For the Case I, existing linear methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+\subsubsection{Performance evaluation:}
+The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve.
+For Case I, existing handcraft methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel functions and a total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
 The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.
 
-The verification performance of the proposed system and other methods were evaluated in terms of Equal Error Rates (EER, \%) averaged from five runs of two-fold cross-validation test.
-Due to the memory constraint caused by the large data size, noting here that the deep learning-based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number as the number of the positive pairs.
+The verification performance of the proposed system and other methods are evaluated in terms of the Equal Error Rate (EER, \%) which are taken from averaging the results of five runs of two-fold cross-validation tests.
+Due to the memory constraint caused by the large data size, the deep learning-based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number as the number of positive pairs.
 
-\subsubsection{Network Structure and Parameter Settings}
+\subsubsection{Network Structure and Parameter Settings:}
 The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}.
@@
 \begin{table}[]
-    \caption{The network structure of the KAR space learning.}\label{tab2}
+    \caption{The network structure of KAR space learning.}\label{tab2}
     \centering
@@
 For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}.
-We trained the network starting with a learning rate of 0.00005 and a mini-batch, size of 32.
+We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32.
 We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for the output layer.
-The output layer is regularized with L-2 penalty of 0.0001.
+The output layer was regularized using an L-2 penalty of 0.0001.
 We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation of 0.01.
-Biases were also initialized with normal distribution of 0.5 mean and standard deviation of 0.01.
-For the triplet networks, the hyper-parameter regulating triplet loss is empirically set to 0.1.
-The training epochs are set to 1,500 for all three deep learning-based algorithms.
-For the linear methods such as LSE,SVM and TER, the input signal is initially resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
-For the PCA-LSE, the input dimension is reduced to 40.
-
+The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01.
+For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1.
+The training epochs were set at 1,500 for all three deep learning-based algorithms.
+For the linear methods such as LSE,SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
+For the PCA-LSE, the input dimension was reduced to 40.
  \begin{table}[]
@@
 Case I: Table~\ref{tab3} shows the best average of EER performance from five runs of two-fold cross-validation test and the parameter condition.
-Among the linear methods, the SVM with RBF kernel function showed the best verification performance of 24.31\% EER followed by the SVM with Linear kernel function.
+Among the handcraft methods, the SVM with RBF kernel showed the best verification accuracy of 24.31\% EER followed by the SVM with Linear kernel function.
 However, all three deep learning-based methods showed better performance than the SVM with RBF kernel function since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
@@
 The Siamese network showed the worst verification performance of 23.53\% EER.
-
 \begin{table}[!h]
@@
 \end{table}
-
 Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning-based methods.
@@
 \section{Conclusion}
-In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi CSI signals. 
-The kernel and the range space learning was initially adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
+In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI).
+The kernel and the range space learning was adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
 Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
-Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
+Our experiments on an in-house Wi-Fi handwritten signature dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
 %

### 2019-09-03 190805_Wisig_Spec/siam_utils.py

@@ -1,0 +1,189 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from sklearn.model_selection import StratifiedKFold
+import time
+from sklearn.metrics import confusion_matrix
+import seaborn as sns
+from sklearn.utils import shuffle
+from scipy.optimize import brentq
+from scipy.interpolate import interp1d
+from sklearn.metrics import roc_curve
+from datetime import datetime 
+import socket
+
+# function to return key for any value 
+def get_key(val,my_dict): 
+    for key, list_val in my_dict.items(): 
+         if val in list_val: 
+             return key 
+  
+    return "key doesn't exist"
+
+
+def ReadData(PATH,n_splits,rseed):
+    print("loading data from {}".format(PATH))
+    list_csi = []
+    list_lab = []
+    
+    locs = [1]
+    dirs = [1,2,3,4]
+
+    # Filter Loc,Dir
+    file_list = []
+    for i in locs:
+        for j in dirs:
+            filename = 'csi_v2_csi_' + str(i) + '_' + str(j) + '.npy'
+            file_list.append(filename)
+    # Filter Dir
+    
+    for file in file_list:
+        data_read = np.load(PATH + file)
+        lab_read = np.load(PATH + 'csi_v2_lab_' + str(i) + '_' + str(j) + '.npy')
+        csi_read = np.abs(data_read).astype('float32')
+        #lab_read = data_read[:,0].astype('int')
+
+        data_x = csi_read#.reshape([-1,10,6,30,500]).swapaxes(2,4)
+
+        uniq_label = np.unique(lab_read[:,0])
+        label_table = pd.Series(np.arange(len(uniq_label)),index=uniq_label)
+        data_y = np.array([label_table[num] for num in lab_read[:,0]]).reshape([-1,10])
+        
+        # use half of the dataset
+        
+        list_csi.append(data_x)#[idx_half])
+        list_lab.append(data_y)#[idx_half])
+        
+    arr_csi = np.array(list_csi).swapaxes(0,1).reshape([98*len(file_list),10,1500,30,6])
+    arr_lab = np.array(list_lab).swapaxes(0,1).reshape([98*len(file_list),10])
+
[…]

### 2019-09-07 190904_Paper_Thesis/Proposed_Method.tex
Conf_BDML

\label{chp:Method}
\section{Overview of the Proposed System}
In this chapter, we present the overall architecture of the proposed in-air signature identification system called SigniFi. We first describe the system setup and the data acquisition method of the proposed system in Section \ref{sec:System}, and \ref{sec:data_acquisition}, respectively. Subsequently, we introduce the proposed methodology of the system for identification in Section \ref{sec:methodology}. Each section is described in detail in the following sections.

\section{System Setup}
\label{sec:System}
The proposed system utilizes commercial Wi-Fi devices (e.g. Intel 5300 NIC and IpTime A1004) for data collection. A VPCSB16FK VAIO laptop with Intel Core i5-2410M 2.3GHz 64bit CPU and 8Gb memory (Fig. \ref{fig:Devices_Laptop}) was utilized as the signal receiver. The receiver uses the Linux 802.11n CSI tool \cite{Halperin2011} with an Intel 5300 network interface controller (NIC) to collect the channel state information (CSI) of Wi-Fi signals. To the best of our knowledge, there are two CSI analysis tools for commercial Wi-Fi devices. The Linux 802.11n CSI tool is one of the tools which is mainly used for CSI based human activity recognition system. The Atheros CSI tool \cite{Xie2015} is another CSI analysis tool which works with Atheros NIC, such as the AR9590 and the AR9565. Both the CSI tools operate on the Linux operating system based on the IEEE 802.11n standard \cite{IEEE802} and are publicly accessible. However, the Atheros NIC tool requires at least two computers to monitor the CSI of Wi-Fi signals. Hence, in the proposed system, we adopted the Linux CSI tool with the Intel 5300 NIC (Fig. \ref{fig:Devices_NIC}).

%\begin{figure}[!ht]
%	
%	\begin{minipage}{.6\linewidth}
%		\centering
%		\subfloat[The VPCSB16FK VAIO Latptop]{\label{fig:Devices_Laptop}\includegraphics[scale=.7]{Laptop.eps}}
%	\end{minipage}
%	\begin{minipage}{.4\linewidth}
%		\centering
%		\subfloat[The Intel 5300 NIC]{\label{fig:Devices_NIC}\includegraphics[scale=.02]{NIC.eps}}
%	\end{minipage}\par\medskip
%	\centering
%	\subfloat[The ipTIME A1004]{\label{fig:Devices_ipTIME}\includegraphics[scale=1.7]{ipTIME.eps}}
%	
%	\caption{Images of VPCSB16FK VAIO laptop, Intel 5300 NIC, and ipTIME A1004}
%	\label{fig:Devices}
%\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[t]{.6\linewidth}
		\centering
		\includegraphics[scale=.07]{Laptop.eps}
		\caption{The VPCSB16FK VAIO laptop}\label{fig:Devices_Laptop}
	\end{subfigure} %
	\hfill
	\begin{subfigure}[t]{.37\linewidth}
		\centering
		\includegraphics[scale=.12]{NIC.eps}
		\caption{The Intel 5300 NIC}\label{fig:Devices_NIC}
	\end{subfigure} %

	\begin{subfigure}[t]{.3\linewidth}
		\centering
		\includegraphics[scale=1.7]{ipTIME.eps}
		\caption{The ipTIME A1004}\label{fig:Devices_ipTIME}
	\end{subfigure}

	\RawCaption{\caption{Images of VPCSB16FK VAIO laptop, Intel 5300 NIC, and ipTIME A1004 \cite{A1004}}
		\label{fig:Devices}}
\end{figure}

The Linux 802.11n CSI tool was designed to report 30 subcarriers for each 802.11n packet according to \cite{Halperin2011}.  The subcarriers are evenly spaced within a 20MHz channel and within a 40MHz channel. The tool was implemented on the Ubuntu 12.04.05 LTS desktop and the receiver was set to receive each CSI packet for every 0.00001 second in order to gather as many packets as possible. In addition, we developed a program based on the Linux CSI tool to automate the data collection process utilizing the MATLAB graphical user interface (GUI). Three external antennas at the receiver were deployed to cover signals from multiple paths and to improve the signal reception quality.

An IpTime A1004 router was used as the transmitter (Fig \ref{fig:Devices_ipTIME}). The router supports IEEE 802.11n standard and two 2.4GHz antennas. The router was set to transmit signals in the 2.4GHz frequency band under the IEEE 802.11n standard without authentication or Wi-Fi security setting.

\section{Data Acquisition}
\label{sec:data_acquisition}
The Linux CSI tool provides the CSI collection routines that use text-based user interface. In this interface, a set of commands should be typed on a computer keyboard by the users to control the data collection process for each sample. Consequently, this type of user interface requires the users to be familiar with the commands and spend a lot of time to control the data collection process. Furthermore, movement for typing the commands by experimenters can negatively affect the CSI data by interfering the data collection during the experiment.

\begin{figure}
	\begin{center}
		\includegraphics[scale=0.4]{GUI.eps}
	\end{center}
	\caption{The GUI of the data collection tool }
	\label{GUI}
\end{figure}

To enhance the data collection process, a graphical user interface (GUI) was built over the CSI tool (Fig. \ref{GUI}). In the GUI, users can control program using a mouse or the touch screen other than typing commands on the keyboard. This can ease the burden of learning the necessary commands to control program and save time for typing the commands. By adopting the GUI, it was empirically proved that the data collection time for each subject reduces by about 10$\sim$15 minutes.

In the proposed system, the GUI for the Linux CSI tool was designed using MATLAB \cite{MATLAB}. The GUI development environment (GUIDE) in MATLAB \cite{MATLAB:GUI} is a built-in tool for GUI creation. GUIDE provides the graphical editor for creating visual interfaces, such as menus, toolbars, buttons and so on. It automatically generates MATLAB codes for the layout designed by developer.

To further facilitate the data collection process, several functions are added onto the GUI. Firstly, the CSI tool was automated to collect 10 samples for each experimental scenario. Specifically, for each sample, it was programmed to beep three times before starting the process of data collection to announce the start of an experiment to the participant. Afterwards, it starts to collect the data for 10 seconds. Secondly, in case of data collection error, the recollection button was implemented to collect the data again. Thirdly, it informs which data is being collected using text display. Finally, the CSI tool was set to automatically name the collected data.

\section{Proposed Methodology}
\label{sec:methodology}
In this section, we present the overall architecture of the proposed in-air signature identification system called SigniFi. SigniFi has five main processing stages as shown in Fig. \ref{fig:flowchart}. At the data acquisition stage, the in-air signature data is captured via a receiver and recorded using a laptop.
Then, the acquired data is averaged and normalized in the preprocessing stage. The data acquisition and preprocessing stages are explained in Section \ref{sec:data_acquisition}, and \ref{sec:Preprocessing}, respectively. Subsequently, features are extracted, and further processed at the post-processing stage. Finally, the processed features are fed into the matching stage for identification. The feature extraction, the post processing and the matching stages are described in detail in the following sections.

\begin{landscape}
	\begin{figure}
		\begin{center}
			\includegraphics[scale=0.5]{Flowchart_Identification.pdf}
		\end{center}
		\caption{Overview of the proposed system}
		\label{fig:flowchart}
	\end{figure}
\end{landscape}

\subsection{Preprocessing}
\label{sec:Preprocessing}
Our system only extracts the CSI magnitude value from the acquired data. The acquired data tend to contain missing values. At the same time, the number of captured packets varies by data. In addition, the large number of CSI streams increases the computational complexity. To deal with these issues, the CSI streams are averaged into fewer number of streams. Subsequently, a linear-interpolation is performed to fill up the missing values. Finally, the length of the CSI stream is normalized using a Fourier transform based sampling method and the max pooling operation is performed to reduce variances and generalize the data.

\subsubsection{Averaging}
The acquired data contains 30 subcarrier-streams for each transmitter-receiver pair. Under 2$\times$3 MIMO configuration, there are in total 180 subcarrier-streams for each data. In order to reduce the computational cost, the subcarrier-streams of each $M_{r}\times M_{t}$ transmitter-receiver pair are averaged into one stream as shown in Fig. \ref{fig:Averaging} . The $M_{r}$, and $M_{t}$ denote the number of antennas at the receiver, and the transmitter, respecitvely. Let $\textbf{h}^{(p)}_{\scalebox{1}{$\scriptscriptstyle M_{r}, M_{t}$}}$ be the one of captured CSI packets from a $M_{r}\times M_{t}$ transmitter-receiver pair. Then, the amplitude of the CSI of subcarrier $f_{c}$ is $|h^{(p)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}(f_{c})|$ where $c=\{1,2,\hdots,C\}$ is the subcarrier index, and $p=\{1,2,\hdots,P\}$ is the packet index. Finally, an averaged CSI amplitude of $C$ subcarriers can be expressed as follows:

\begin{equation}
\tilde{h}^{(p)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}=
\frac{1}{C}\sum^{C}_{c=1}
|h^{(p)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}(f_{c})|. 
\label{eq:avg}
\end{equation}
Then, the averaged stream can be expressed in a vector form   $\tilde{\textbf{h}}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$=\Big[$\tilde{h}^{(1)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$, $\tilde{h}^{(2)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$, $\hdots$, $\tilde{h}^{(P)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$\Big]. Note that only the amplitude of the CSI is utilized in the proposed system.

%Then, the averaged stream is defined as a vector $\tilde{\textbf{h}}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}\in\mathbb{R}^{1\times P}$. Note that only the amplitude of CSI is utilized in the proposed system.

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.5]{Averaging_v2.pdf}
	\end{center}
	\caption{The CSI stream averaging scheme. $P\times C$ CSI amplitude streams are averaged into a $P$ dimensional stream. $\tilde{h}$ denotes the averaged CSI.} 
	\label{fig:Averaging}
\end{figure}

\subsubsection{Interpolation}
\label{sec:Interpolation}
When signals are transmitted through the Wi-Fi channel, where multiple devices and users share the same resource, time delay in packet transmission and packet loss could happen. The packet loss causes discontinuity in the received signals. Hence, even though our system is set to transmit signals at every 0.00001 seconds, the total number of collected packets may differ. In order to fill up the gaps, we use a one-dimensional linear interpolation to preserve the continuity of the received signals using two packet values.

\subsubsection{Re-sampling}
\label{sec:resampling}
Since the collected signature data has different lengths, they are re-sampled uniformly based on the Fast Fourier Transform (FFT) and the inverse FFT \cite{Python:Resampling} to normalize the length of the data. In the proposed system the length of re-sampled data $P'$ is chosen to be smaller than the original length of data $P$.

\subsubsection{Max Pooling}
Pooling operation summarizes the local information of certain region in the data by sliding over the data. Typically, pooling operation calculates the maximum or average value of a neighborhood. Our proposed system employs the max pooling for data generalization.

Finally, the input CSI streams preprocessed at the previous stages can be packed into a matrix $\tilde{\textbf{H}}\in \mathbb{R}^{S\times P'}$:
\begin{equation}
\tilde{\textbf{H}}=
\begin{bmatrix}
\tilde{\textbf{h}}_{1}\\ 
\tilde{\textbf{h}}_{2}\\
\vdots\\
\tilde{\textbf{h}}_{s}
\end{bmatrix},
\end{equation}
where $\tilde{\textbf{h}}_{s}\in \mathbb{R}^{1\times P'}$. For the ease of notation, the stream index $(M_{r}, M_{t})$ is replaced by $s=\{1,2,\dots, S\}$, where $S$ is the maximum number of streams. The superscript $P'$ denotes the length of the re-sampled packet.

\subsection{Feature Extraction}

Our system adopts the feature extraction method proposed in \cite{Kim2016}. Fig. \ref{fig:Feature} shows an overview of the feature extraction method. First, a shifting operation is applied to the Wi-Fi signal by matrix projection. Then, the difference between the shifted signal and the original signal is computed to extract the high frequency component information. The difference signal is then fed into a sigmoid function to further enhance the contrast in the signal. Finally, the discrete Fourier transform is applied to the resulting signal to extract the magnitude of the frequency components. The following subsections explain the details of the proposed feature extraction scheme.

\begin{figure}[!h]
	\begin{center}
		\includegraphics[scale=0.6]{Feature_Extraction.pdf}
	\end{center}
	\caption{The illustration of feature extraction. For the visual simplicity, only one averaged stream is used for explanation. }
	\label{fig:Feature}
\end{figure}

\subsubsection{Shift and Subtraction}
\label{sec:shift_subtract}
In the static environment, the Wi-Fi signals show a generally stable pattern except for some minor noises caused by the external sensing conditions. This static pattern can be considered as the DC component of the signal \cite{Wang2015}. A slight change in the experimental environment can lead to a large variation in the DC component. To extract the Wi-Fi signal fluctuations caused by a person's in-air signature, it is important to reduce the impact of the DC component in the signal for robust identification. The proposed method utilizes a shift plus a subtraction operation to extract the fluctuation information in the signal: (1) shifts the preprocessed input signals horizontally by $k$ positions using a shifting matrix (cf. Sec. \ref{sec:Shift}), and (2) subtracts the shifted signals from the input signals. The shifted signal $\textbf{O}_{k}\in \mathbb{R}^{S\times P'}$ can be expressed as follows:
\begin{align}
\textbf{O}_{k}&=\tilde{\textbf{H}}\cdot \textbf{U}_{k}\\[1.8em]
&=
\begin{bmatrix}
\bovermat{$\textbf{0}_{S \times k}$}{\vspace{0.2cm}0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&\bovermat{$\tilde{\textbf{H}}_{S \times (P'-k)}$}{\vspace{0.2cm}\tilde{h}^{(1)}_{1} \hspace{0.3cm} \tilde{h}^{(2)}_{1} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P'-k)}_{1}}\\%[0.01em]
%
{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(1)}_{2} \hspace{0.3cm} \tilde{h}^{(2)}_{2} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P'-k)}_{2}}\\
%
\hspace{0.5cm} \vdots&\vdots \hspace{0.4cm} \ddots \hspace{0.4cm}\vdots\\
%
{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(1)}_{S} \hspace{0.3cm} \tilde{h}^{(2)}_{S} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P'-k)}_{S}}\nonumber
%RIGHT BRACKET
\end{bmatrix},\!\!\!
%
%\begin{array}{l}
%\MyLBrace{3.5ex}{13} \\
%\\
%\end{array}
\end{align}
where $\tilde{\textbf{H}}\in \mathbb{R}^{S\times P'}$ is the matrix of preprocessed CSI streams, and $\textbf{U}_{k}\in\mathbb{Z^{*}}^{P' \times P'}$ is the shift matrix as illustrated in equation \ref{eq:shift_matrix}. $\textbf{0}_{S \times k}$ is a matrix of "0"s, and $\tilde{\textbf{H}}_{S \times (P'-k)}$ is the preprocessed data matrix that is size of ${S \times (P'-k)}$. The variable $k$ is the shifting parameter that can be tuned. During the shifting operation, the last $k$ columns of the shifted signal matrix are discarded by overflow.
The horizontal difference signal can then be obtained by 
\begin{align}
\textbf{Q}_{k}&=\tilde{\textbf{H}} - \textbf{O}_{k}\\[2em]
&\approx
\begin{bmatrix}
\bovermat{$\textbf{0}_{S \times k}$}{\vspace{0.2cm}0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&\bovermat{$\textbf{Q}_{S \times (P'-k)}$}{\vspace{0.2cm}\tilde{h}^{(k+1)}_{1}-\tilde{h}^{(1)}_{1} \hspace{0.3cm} \tilde{h}^{(k+2)}_{1}-\tilde{h}^{(2)}_{1} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P')}_{1}-\tilde{h}^{(P'-k)}_{1}}\\[0.5em]
%
{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(k+1)}_{2}-\tilde{h}^{(1)}_{2} \hspace{0.3cm} \tilde{h}^{(k+2)}_{2}-\tilde{h}^{(2)}_{2} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P')}_{2}-\tilde{h}^{(P'-k)}_{2}}\\
%
\hspace{0.5cm} \vdots& \vdots \kern 6em \ddots \kern 7em \vdots\\
%
{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(k+1)}_{S}-\tilde{h}^{(1)}_{S} \hspace{0.3cm} \tilde{h}^{(k+2)}_{S}-\tilde{h}^{(2)}_{S} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P')}_{S}-\tilde{h}^{(P'-k)}_{S}}\nonumber
%RIGHT BRACKET
\end{bmatrix}.\!\!\!
%
%\begin{array}{l}
%\MyLBrace{3.5ex}{13} \\
%\\
%\end{array}
\end{align}
Note that the first $k$ columns of the difference signal matrix are filled with zeros.

\subsubsection{Contrast Enhancement using the Sigmoid Function}
To enhance the contrast information in the difference signal $\textbf{Q}_{k}$, a sigmoid function is applied. This operation also has an effect of normalizing the data into a range of [0,1]. The Sigmoid function is defined as follows:
\begin{equation}
\sigma (x) = \frac{1}{1+e^{-x}}.
\end{equation}
For a given resulting difference matrix $\textbf{Q}_{k}$, the output of the Sigmoid function is given by
\begin{equation}
\textbf{G} = \sigma \big(\textbf{Q}_{k}\big),
\end{equation}
where $\textbf{G}\in\mathbb{R}^{S \times P'}$. The sigmoid operation is element-wise for the entire matrix $\textbf{Q}_{k}$.

\subsubsection{Fourier Magnitude Spectrum}
The collected Wi-Fi signal captures the dynamics of the in-air signature with regard to the time variance. Therefore, the starting and the ending points of the in-air signature can change from sample to sample. To extract translation invariant features from the signal, the Fourier transform is calculated for each stream of $\textbf{G}$ as follows:
\begin{equation}
f^{(\nu)}_{s} = \sum_{p=0}^{P'-1} g^{(p)}_{s}\cdot e^{-j2\pi ap/P'},
\end{equation}
where $g^{(p)}_{s}\in\mathbb{R}^{P'}$ denotes $p$-th element of one of streams in $\textbf{G}$. The index $\nu$ is the frequency component index, and the index $s=\{1,2,\hdots,S\}$ is the CSI streams index.

Then, Fourier magnitude spectrum can be calculated as follows:
\begin{equation}
|f^{(\nu)}_{s}| = \sqrt{\textrm{Re}(f^{(\nu)}_{s})^{2}+\textrm{Im}(f^{(\nu)}_{s})^{2}},
\end{equation}
where $\textrm{Re}(f^{(\nu)}_{s})$ and $\textrm{Im}(f^{(\nu)}_{s})$ represent the real and imaginary parts of $f^{(\nu)}_{s}$, respectively.

\subsection{Post Processing}
In this section, we illustrate the sequence of post-processing to further improve the identification performance. Firstly, the Fourier spectrum features are smoothed by a moving average filter. The resulting features are then weighted by the energy of the CSI streams. These two processes are described in detail below.

\subsubsection{Moving Average}
To reduce noises in the extracted Fourier magnitude spectrum, the features are smoothed by a moving average filter. The moving average filtering can be expressed as follows:
\begin{equation}
\tilde{f}^{(\nu)}_{s}=\frac{1}{W}\sum_{i=0}^{W-1}|f^{(\nu+i)}_{s}|,
\end{equation}
where $\tilde{f}^{(\nu)}_{s}$ denotes the filtered feature, and $W$ is the size of moving average window. the $i$ is the index of the element inside the window.

\subsubsection{Energy based Weights}
\label{sec:energy}
One observation is that some CSI streams show relatively high fluctuations, while the others have more stable patterns for the same in-air signature. To emphasize on the  fluctuation information caused by the in-air signature, the extracted features are weighted by the energy of the CSI stream. The energy of the $s$-th stream is calculated from the averaged CSI stream $\tilde{\textbf{h}}_{s}$ as follows:
\begin{align}
e_{s}=\sum_{p=1}^{P'}||\tilde{h}^{(p)}_{s}||^{2},
\end{align} 
where $\tilde{h}^{(p)}_{s}$ is the $p$-th averaged CSI amplitude of $\tilde{\textbf{h}}_{s}$ (cf. Eq.\ref{eq:avg}).
Then, the energy based weight can be computed by
\begin{equation}
w_{s}=\frac{e_{s}}{E},
\label{eq:weight}
\end{equation}
where $E$ is the total energy of CSI streams. In equation \ref{eq:weight}, the weights are normalized by the total energy $E$ given by:
\begin{equation}
E=\sum_{s=1}^{S}e_{s}.
\end{equation}    
Fianlly, the weighted feature of $s$-th stream $\boldsymbol{\xi}_{w_{s}}$ is computed as follows:
\begin{equation}
\boldsymbol{\xi}_{w_{s}}=w_{s}\tilde{\textbf{f}}_{s},
\end{equation}
where $\tilde{\textbf{f}}_{s}=\big[\tilde{f}^{(1)}_{s}, \tilde{f}^{(2)}_{s}, \hdots, \tilde{f}^{(P')}_{s}\big]$.

\newpage
\subsection{Person Identification using the Support Vector Machine}
In order to make a decision regarding the identity of a person, we use the support vector machine (SVM) classifier with the radial basis function (RBF) kernel. The input of the SVM is a concatenated vector form of the post-processed weighted features  $\boldsymbol{\xi}_{w}=[\boldsymbol{\xi}_{w_{1}}, \boldsymbol{\xi}_{w_{2}}, \hdots , \boldsymbol{\xi}_{w_{S}}]$.

### 2019-09-07 190906_Paper_BDML/bdml_v0.tex
Conf_BDML

--- 2019-09-03 190410_Paper_ACPR/paper_v7_r5-1.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+%%
+%% This is file `sample-sigconf.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `sigconf')
+%% 
+%% IMPORTANT NOTICE:
+%% 
+%% For the copyright see the source file.
+%% 
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf.tex.
+%% 
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%% 
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigconf]{acmart}
+
 \usepackage{amsmath,amssymb}
@@
 \usepackage{subfigure}
+\usepackage{multirow}
 
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+\copyrightyear{2019}
+\acmYear{2019}
+\setcopyright{rightsretained}
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+%\acmConference{SIGGRAPH '19 Talks}{July 28 - August 01, 2019}{Los Angeles, CA, USA}
+%\acmDOI{10.1145/3306307.3328180}
+%\acmISBN{978-1-4503-6317-4/19/07}
+%\acmBooktitle{SIGGRAPH '19 Talks, 
+%  July 28 - August 01, 2019, Los Angeles, CA}
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+
+%%
+%% end of the preamble, start of the body of the document source.
 \begin{document}
-%
+
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
 \title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
-%
-\titlerunning{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
-%
-\authorrunning{Y. Kwon et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{
-School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
-\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
-%
-\maketitle              % typeset the header of the contribution
-%
+
+%%
+%% The "author" command and its associated commands are used to define
+%% the authors and their affiliations.
+%% Of note is the shared affiliation of the first two authors, and the
+%% "authornote" and "authornotemark" commands
+%% used to denote shared contribution to the research.
+\author{Young-Woong Kwon}
+%\authornote{Both authors contributed equally to this research.}
+\email{herokwon@yonsei.ac.kr}
+\affiliation{%
+  \institution{School of Electrical and Electronic Engineering, Yonsei University}
+  \streetaddress{50 Yonsei-ro}
+  \city{Seodaemun-gu}
+  \state{Seoul}
+  \postcode{03722}
+}
+
+\author{Jooyoung Kim}
+%\authornote{Both authors contributed equally to this research.}
+\email{harrykim@yonsei.ac.kr}
+\affiliation{%
+  \institution{School of Electrical and Electronic Engineering, Yonsei University}
+  \streetaddress{50 Yonsei-ro}
+  \city{Seodaemun-gu}
+  \state{Seoul}
+  \postcode{03722}
+}
+
+\author{Kar-Ann Toh}
+%\authornote{Both authors contributed equally to this research.}
+\email{katoh@yonsei.ac.kr}
+\affiliation{%
+  \institution{School of Electrical and Electronic Engineering, Yonsei University}
+  \streetaddress{50 Yonsei-ro}
+  \city{Seodaemun-gu}
+  \state{Seoul}
+  \postcode{03722}
+}
+
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+\renewcommand{\shortauthors}{Y.Kwon, et al.}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
 \begin{abstract}
-%The abstract should briefly summarize the contents of the paper in 15--250 words.
     In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
@@
     Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
+\end{abstract}
 
-\keywords{Wi-Fi signature signal \and in-air handwritten signature verification \and the Kernel and the Range space projection learning \and triplet network}
-\end{abstract}
-%
-%
-%
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+
+\begin{CCSXML}
+    <ccs2012>
+    <concept>
+    <concept_id>10002978.10002991.10002992.10003479</concept_id>
+    <concept_desc>Security and privacy~Biometrics</concept_desc>
+    <concept_significance>500</concept_significance>
+    </concept>
+    <concept>   
+    <concept_id>10010147.10010257.10010293.10010294</concept_id>
+    <concept_desc>Computing methodologies~Neural networks</concept_desc>
+    <concept_significance>500</concept_significance>
+    </concept>
+    </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Security and privacy~Biometrics}
+\ccsdesc[500]{Computing methodologies~Neural networks}
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{Wi-Fi signature signal, in-air handwritten signature verification, the Kernel and the Range space projection learning, triplet network}
+
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+%\begin{teaserfigure}
+%  \includegraphics[width=\textwidth]{sampleteaser}
+%  \caption{Seattle Mariners at Spring Training, 2010.}
+%  \Description{Enjoying the baseball game from the third-base
+%  seats. Ichiro Suzuki preparing to bat.}
+%  \label{fig:teaser}
+%\end{teaserfigure}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
+\maketitle
+
+%Intro
 \section{Introduction}
-
 Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}.
@@
 \begin{equation}
-    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right), i=1,\dotsc,n,
+\begin{split}    
+    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),\\ i=1,\dotsc,n,
+\end{split}
 \end{equation}
-where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
-\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is the activation function.
+where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,\\$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is the activation function.
 By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
-
 \begin{equation}
-    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), i=1,\dotsc,n.
+\begin{split}
+    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \\ i=1,\dotsc,n.
+\end{split}
 \end{equation}
@@
 % Figure 1
-\begin{figure}[!ht]
-    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v5}
-    \caption{An overview of the proposed system.} \label{fig1}
-\end{figure}
+\begin{figure*}[!ht]
+    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v6}
+    \caption{An overview of the proposed system} \label{fig1}
+\end{figure*}
 
@@
 By training the network with the single shot KAR space learning, we can map the L-2 distance between every samples by using the output vector of the KAR space network.
-\textbf{For training dataset $\mathbf{X}$, the trained network output is given by:}
+\textbf{For training data set $\mathbf{X}$, the trained network output is given by:}
 \begin{equation}
@@
 The next step is to design a feature extractor which converts the input triplet data into feature vectors.
-In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
+In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
 
@@
 The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network.
-\textbf{For selected anchor input sample $\mathbf{x}_{anc,i}$, the $i_{th}$ triplet input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$ is generated by grouping positive input sample $\mathbf{x}_{pos,i}$ and the negative input sample $\mathbf{x}_{neg,i}$.
+\textbf{For the $i^{th}$ network input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$, anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set.
+Positive sample $\mathbf{x}_{pos,i}$ is selected among the same class with the anchor while negative sample $\mathbf{x}_{neg,i}$ is selected among the different class with the anchor.
 The generated triplet input is fed into ConvNet structure and make feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$.}
@@
 \begin{equation}
-    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
+    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]},0 \right),\label{triplet}
 \end{equation}
@@
 The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve.
-For Case I, existing handcraft methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel functions and a total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+\textbf{We considered in-air signature data could be entered in any direction of the Wi-Fi router.
+For 4-way inputs, we take into account with signatures facing Wi-Fi router's front, rear and both sides.
+For 1-way inputs, we considered only the entered signatures facing the forward face of the Wi-Fi router.} For Case I, existing handcraft methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel functions and a total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
 The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.
@@
 We used $\sigma = {tan}^{-1}$ as an activation function following \cite{toh2018analytic}.
-
-\begin{table}[]
-    \caption{The network structure of KAR space learning.}\label{tab2}
-    \centering
-    \begin{tabular}{|l|l|l|}
-    \hline
-    Layer   & Size     & Activation \\ \hline
+\begin{table}
+    \caption{The network structure of KAR space learning}
+    \label{tab2}
+    \begin{tabular}{ccc}
+     \toprule
+     Layer   & Size     & Activation \\
+     \midrule
      Input   & 500$\times$30$\times$6 &            \\
@@
      Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
-    Output  & 1$\times$1$\times$50   &            \\ \hline
+     Output  & 1$\times$1$\times$50   &            \\
+     \bottomrule
     \end{tabular}
@@
 The output layer was regularized using an L-2 penalty of 0.0001.
-We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation of 0.01.
+We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01.
 The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01.
@@
 For the PCA-LSE, the input dimension was reduced to 40.
- \begin{table}[]
-    \caption{
-        The structure of ConvNet model.
+\begin{table}
+    \caption{The structure of ConvNet model.
 For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride.
 For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride.
-The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.
-    }\label{tab1}
-    \centering
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
+The input sizes are denoted as rows $\times$ cols $\times$ \# of filters}
+    \label{tab1}
+    \begin{tabular}{cccc}
+     \toprule
+     Layer     & Activation & Kernel / Stride & Input Size \\
+     \midrule
      Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
@@
      L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
-    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
+     Concat    &            &                 & 1$\times$1$\times$16    \\
+     \bottomrule
     \end{tabular}
@@
 Case I: Table~\ref{tab3} shows the best average of EER performance from five runs of two-fold cross-validation test and the parameter condition. 
-Among the handcraft methods, the SVM with RBF kernel showed the best verification accuracy of 24.31\% EER followed by the SVM with Linear kernel function.
-However, all three deep learning-based methods showed better performance than the SVM with RBF kernel function since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
-Among the deep learning-based methods, the Siamese network is also a metric learning system, but it differs from our system in that it receives two inputs and uses the contrastive loss function for training.
+\textbf{For 1-way inputs, SVM showed best verification accuracy of 1.55\% EER.
+However, For 4-way inputs, all three deep learning-based methods showed better performance since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.} Among the deep learning-based methods, the Siamese network is also a metric learning system, but it differs from our system in that it receives two inputs and uses the contrastive loss function for training.
 The best average of test EER performance was obtained from the proposed system with 19.35\% EER.
@@
 The Siamese network showed the worst verification performance of 23.53\% EER.
-\begin{table}[!h]
-    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab3}
-    \centering
-    \begin{tabular}{|c|c|c|}
-    \hline
-    Methology   &   Best EER (\%) &   Condition   \\  \hline
-    LSE &   48.44   &  - \\ 
-    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
-    SVM (Linear) &   28.23   &   c=1 \\
-    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
-    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
-    Siamese network  &   23.53   &   lr=0.00005  \\
-    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
-    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
-     \hline
+\begin{table}
+    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset}
+    \label{tab3}
+    \begin{tabular}{cccl}
+    \toprule
+    \multirow{2}{*}{Methology} & \multicolumn{2}{c}{Best EER (\%)} & \multirow{2}{*}{Condition} \\ \cline{2-3}
+                            & 1-way     & 4-way     &                            \\
+    \midrule
+    LSE                                    & 35.40 & 48.44           &                           \\ 
+    PCA-LSE                                & 16.87 & 30.79           & $d_{3000} \rightarrow d_{40}$       \\ 
+    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\ 
+    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\ 
+    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\
+    \midrule
+    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\ 
+    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\ 
+    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\
+    \bottomrule
     \end{tabular}
 \end{table}
+
 Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning-based methods.
@@
 According to these two observations, it can be concluded that the triplet input mining with KAR space learning improves not only the training loss convergence speed but also the verification performance.
-
 % Figure 2,3
@@
     \subfigure[][ROC Curve]{
-        \includegraphics[height=6.4cm]{fig_roc_v11.eps}}
+        \includegraphics[height=6.4cm]{fig_roc_v12.eps}}
     \subfigure[][Normalized training loss curve]{
@@
     \caption{(a) shows the Receiver Operating Characteristic(ROC) Curve and 
-    (b) shows the normalized training loss curve of the deep learning based methods. }
+    (b) shows the normalized training loss curve of the deep learning based methods}
     \label{fig2}
@@
 Our experiments on an in-house Wi-Fi handwritten signature dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-%\bibliographystyle{splncs04}
-%\bibliography{mybibliography}
-%
-
-%\begin{thebibliography}{8}
-\clearpage
-\bibliographystyle{splncs04}
-\bibliography{bib_acpr}
-
-%\end{thebibliography}
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{bib_conf}
+%\bibliography{sample-base}
 
 \end{document}
+\endinput
+%%
+%% End of file `sample-sigconf.tex'.

### 2019-09-07 190906_Paper_BDML/sample-authordraft.tex
Conf_BDML

%%
%% This is file `sample-authordraft.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `authordraft')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-authordraft.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,authordraft]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{rightsretained}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference{SIGGRAPH '19 Talks}{July 28 - August 01, 2019}{Los Angeles, CA, USA}
\acmDOI{10.1145/3306307.3328180}
\acmISBN{978-1-4503-6317-4/19/07}
\acmBooktitle{SIGGRAPH '19 Talks, 
  July 28 - August 01, 2019, Los Angeles, CA}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf,authordraft]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for all short- and
full-length articles, and optional for two-page abstracts.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-authordraft.tex'.

### 2019-09-21 190904_Paper_Thesis/Conclusion.tex
Paper_Thesis

\label{chp:Conclusions}
\section{Conclusions}
...

\section{Future Works}
...
\begin{enumerate}
	\setlength{\itemsep}{1pt}
	\item Recognizing the in-air signature written along non-LOS. 
	\item Repeating the same data acquisition experiments in a different place
	\item Studying identification performances when multiple people are staying in the same room.
	\item To secure a reliable identification system, spoofing attack scenario should be investigated. 
\end{enumerate}

### 2019-09-21 190904_Paper_Thesis/Experiments.tex
Paper_Thesis

\label{chp:Experiments}
..
\section{Data set}
\label{sec:Dataset}
..
\section{Experimental Settings}
..
\subsection{Evaluation Scenarios}
\label{sec:scenario}
..
\subsection{Evaluation Protocols}
\label{sec:protocols}
..
\subsection{Parameter Settings}
\label{sec:parameter}
..
\section{Experimental Results}
\label{sec:results}
..
\subsection{Effect of the DC Component}
\label{sec:DC}
..
\subsection{Effect of the Weighting Scheme}
..
\subsection{Effect of the Facing Direction and the Position of the Subject}
..
\subsection{Comparison with the ConvNet}
..

### 2019-09-21 190904_Paper_Thesis/Introduction.tex
Paper_Thesis

\section{Background}
\label{sec:Intro}
...
%\newpage
\section{Motivation and Contributions}
...
..
\newpage
\section{Organization of Thesis}
..

### 2019-09-21 190904_Paper_Thesis/Preliminaries.tex
Paper_Thesis

\label{chp:Preliminary}
..
\section{Biometric Identification System}
\label{sec:Biometrics}
..
\section{Evaluation metrics}
\label{sec:Evaluation}
..
\section{Received Signal Strength Indicator}
\label{sec:RSSI}
..
\section{Channel State Information}
\label{sec:CSI}
..
\subsection{Multiple-Input and Multiple-Output}
\label{sec:MIMO}
..
\section{Shift Matrix}
\label{sec:Shift}
..
\section{Metric Learning}
\label{sec:metric_learning}

### 2019-09-21 190904_Paper_Thesis/Proposed_Method.tex
Paper_Thesis

@@
 \label{chp:Method}
+% 4.1. Overview
 \section{Overview of the Proposed System}
-In this chapter, we present the overall architecture of the proposed in-air signature identification system called SigniFi.
-We first describe the system setup and the data acquisition method of the proposed system in Section \ref{sec:System}, and \ref{sec:data_acquisition}, respectively.
-Subsequently, we introduce the proposed methodology of the system for identification in Section \ref{sec:methodology}.
-Each section is described in detail in the following sections.
+..
+\cite{Leal-Taixe_2016_CVPR_Workshops}
 
-\section{System Setup}
-\label{sec:System}
-The proposed system utilizes commercial Wi-Fi devices (e.g.
-Intel 5300 NIC and IpTime A1004) for data collection.
-A VPCSB16FK VAIO laptop with Intel Core i5-2410M 2.3GHz 64bit CPU and 8Gb memory (Fig.
-\ref{fig:Devices_Laptop}) was utilized as the signal receiver.
-The receiver uses the Linux 802.11n CSI tool \cite{Halperin2011} with an Intel 5300 network interface controller (NIC) to collect the channel state information (CSI) of Wi-Fi signals.
-To the best of our knowledge, there are two CSI analysis tools for commercial Wi-Fi devices.
-The Linux 802.11n CSI tool is one of the tools which is mainly used for CSI based human activity recognition system.
-The Atheros CSI tool \cite{Xie2015} is another CSI analysis tool which works with Atheros NIC, such as the AR9590 and the AR9565.
-Both the CSI tools operate on the Linux operating system based on the IEEE 802.11n standard \cite{IEEE802} and are publicly accessible.
-However, the Atheros NIC tool requires at least two computers to monitor the CSI of Wi-Fi signals.
-Hence, in the proposed system, we adopted the Linux CSI tool with the Intel 5300 NIC (Fig.
-\ref{fig:Devices_NIC}).
+% 4.2. Data Acquisition
+\section{Preprocessing}
+\label{sec:preprocessing}
 
-%\begin{figure}[!ht]
-%	
-%	\begin{minipage}{.6\linewidth}
-%		\centering
-%		\subfloat[The VPCSB16FK VAIO Latptop]{\label{fig:Devices_Laptop}\includegraphics[scale=.7]{Laptop.eps}}
-%	\end{minipage}
-%	\begin{minipage}{.4\linewidth}
-%		\centering
-%		\subfloat[The Intel 5300 NIC]{\label{fig:Devices_NIC}\includegraphics[scale=.02]{NIC.eps}}
-%	\end{minipage}\par\medskip
-%	\centering
-%	\subfloat[The ipTIME A1004]{\label{fig:Devices_ipTIME}\includegraphics[scale=1.7]{ipTIME.eps}}
-%	
-%	\caption{Images of VPCSB16FK VAIO laptop, Intel 5300 NIC, and ipTIME A1004}
-%	\label{fig:Devices}
-%\end{figure}
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[t]{.6\linewidth}
-		\centering
-		\includegraphics[scale=.07]{Laptop.eps}
-		\caption{The VPCSB16FK VAIO laptop}\label{fig:Devices_Laptop}
-	\end{subfigure} %
-	\hfill
-	\begin{subfigure}[t]{.37\linewidth}
-		\centering
-		\includegraphics[scale=.12]{NIC.eps}
-		\caption{The Intel 5300 NIC}\label{fig:Devices_NIC}
-	\end{subfigure} %
-
-	\begin{subfigure}[t]{.3\linewidth}
-		\centering
-		\includegraphics[scale=1.7]{ipTIME.eps}
-		\caption{The ipTIME A1004}\label{fig:Devices_ipTIME}
-	\end{subfigure}
-
-	\RawCaption{\caption{Images of VPCSB16FK VAIO laptop, Intel 5300 NIC, and ipTIME A1004 \cite{A1004}}
-		\label{fig:Devices}}
-\end{figure}
-
-The Linux 802.11n CSI tool was designed to report 30 subcarriers for each 802.11n packet according to \cite{Halperin2011}.
-The subcarriers are evenly spaced within a 20MHz channel and within a 40MHz channel.
-The tool was implemented on the Ubuntu 12.04.05 LTS desktop and the receiver was set to receive each CSI packet for every 0.00001 second in order to gather as many packets as possible.
-In addition, we developed a program based on the Linux CSI tool to automate the data collection process utilizing the MATLAB graphical user interface (GUI).
-Three external antennas at the receiver were deployed to cover signals from multiple paths and to improve the signal reception quality.
-
-An IpTime A1004 router was used as the transmitter (Fig \ref{fig:Devices_ipTIME}).
-The router supports IEEE 802.11n standard and two 2.4GHz antennas.
-The router was set to transmit signals in the 2.4GHz frequency band under the IEEE 802.11n standard without authentication or Wi-Fi security setting.
-
-\section{Data Acquisition}
-\label{sec:data_acquisition}
-The Linux CSI tool provides the CSI collection routines that use text-based user interface.
-In this interface, a set of commands should be typed on a computer keyboard by the users to control the data collection process for each sample.
-Consequently, this type of user interface requires the users to be familiar with the commands and spend a lot of time to control the data collection process.
-Furthermore, movement for typing the commands by experimenters can negatively affect the CSI data by interfering the data collection during the experiment.
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale=0.4]{GUI.eps}
-	\end{center}
-	\caption{The GUI of the data collection tool }
-	\label{GUI}
-\end{figure}
-
-To enhance the data collection process, a graphical user interface (GUI) was built over the CSI tool (Fig.
-\ref{GUI}).
-In the GUI, users can control program using a mouse or the touch screen other than typing commands on the keyboard.
-This can ease the burden of learning the necessary commands to control program and save time for typing the commands.
-By adopting the GUI, it was empirically proved that the data collection time for each subject reduces by about 10$\sim$15 minutes.
-
-In the proposed system, the GUI for the Linux CSI tool was designed using MATLAB \cite{MATLAB}.
-The GUI development environment (GUIDE) in MATLAB \cite{MATLAB:GUI} is a built-in tool for GUI creation.
-GUIDE provides the graphical editor for creating visual interfaces, such as menus, toolbars, buttons and so on.
-It automatically generates MATLAB codes for the layout designed by developer.
-
-To further facilitate the data collection process, several functions are added onto the GUI.
-Firstly, the CSI tool was automated to collect 10 samples for each experimental scenario.
-Specifically, for each sample, it was programmed to beep three times before starting the process of data collection to announce the start of an experiment to the participant.
-Afterwards, it starts to collect the data for 10 seconds.
-Secondly, in case of data collection error, the recollection button was implemented to collect the data again.
-Thirdly, it informs which data is being collected using text display.
-Finally, the CSI tool was set to automatically name the collected data.
-
+% 4.3. Proposed Methodology
 \section{Proposed Methodology}
 \label{sec:methodology}
-In this section, we present the overall architecture of the proposed in-air signature identification system called SigniFi.
-SigniFi has five main processing stages as shown in Fig.
-\ref{fig:flowchart}.
-At the data acquisition stage, the in-air signature data is captured via a receiver and recorded using a laptop.
-Then, the acquired data is averaged and normalized in the preprocessing stage.
-The data acquisition and preprocessing stages are explained in Section \ref{sec:data_acquisition}, and \ref{sec:Preprocessing}, respectively.
-Subsequently, features are extracted, and further processed at the post-processing stage.
-Finally, the processed features are fed into the matching stage for identification.
-The feature extraction, the post processing and the matching stages are described in detail in the following sections.
+%purpose
+In this paper, we propose person identity verification system based on the in-air handwritten Wi-Fi signature signals (which will be called Wi-Fi signature hereafter). 
+%function
+In order to learn the direction-invariant deep representations for in-air signature, we used the triplet network[] which utilizes ConvNet[] as a feature extractor.
+Moreover, to achieve a faster loss convergence, we adopt the kernel and the range (KAR) space learning[] for mining the triplet input.
+% figure
+\begin{figure*}[!ht]
+    \includegraphics[width=\textwidth]
+        {fig_system_overview_v1.pdf}
+    \caption{An overview of the proposed methodology.} \label{fig1}
+\end{figure*}
+Figure~\ref{fig1} shows an overview of the proposed system. 
+Essentially, the KAR space projection learning is applied to mine the hard samples from the training dataset for making the triplet input (see item (a) in Fig.~\ref{fig1}).
+The anchor sample is randomly selected from the training dataset as the reference data.
+The hard samples refer to which likely to be misclassified by the triplet network for given anchor sample.
+Subsequently, the ConvNet structure that forms triplet network (see item (b) in Fig.~\ref{fig1}) is trained based on a triplet loss function based on the distance comparison for network output vector (see item (c) in Fig.~\ref{fig1}).
+% following~
+In the following subsections, we introduce the triplet network architecture, triplet loss, and triplet mining using KAR space learning in detail.
 
-\begin{landscape}
-	\begin{figure}
-		\begin{center}
-			\includegraphics[scale=0.5]{Flowchart_Identification.pdf}
-		\end{center}
-		\caption{Overview of the proposed system}
-		\label{fig:flowchart}
-	\end{figure}
-\end{landscape}
+% 4.4.1. Triplet loss
+\subsection{Triplet loss}
+% purpose
+The purpose of the triplet loss [] is training the ConvNet structure to learn discriminative features that allocates the samples of the same class closer and the samples of the different class far away in the feature space.
+% Triplet input
+The triplet input is made up of a combination of three samples, anchor sample $x_0$, positive sample $x_+$ and negative sample $x_-$.
+The anchor sample, which is the reference for the triplet input, is selected from the training data set.
+For selected anchor sample $x_0$, positive sample is selected from same identity with that of the anchor while negative sample is selected from different identity from that of the anchor.
+% function
+To make the discriminative feature vectors, we need $dist\{f(x_0),f(x_+)\}$, the distance  between feature vectors of anchor $f(x_0)$ and positive sample $f(x_+)$ is larger than $dist\{f(x_0),f(x_-)\}$, distance between feature vectors of anchor and negative sample  plus preset margin $\alpha$.
+Distance measurement function is shown below:
+\begin{equation}
+    dist\{f(x_0),f(x_-)\} - dist\{f(x_0),f(x_+)\} \geqq \alpha
+    \label{triplet_condition}
+\end{equation}
+By using $L2$ distance as distance function, triplet loss is calculated as below:
+\begin{equation}
+    triplet\_loss = \sum_i^N max\left({ \left[ {\left\| {{f(x_0)} - {f(x_+)}} \right\|_2^2} - {\left\| {{f(x_0)} - {f(x_-)}} \right\|_2^2}  + \alpha \right]},0 \right),
+    \label{triplet_loss}
+\end{equation}
+% need to make hard triplets
+Note that if $dist\{f(x_0),f(x_-)\}$ is much larger than $dist\{f(x_0),f(x_+)\} + \alpha$, the output of the loss function would be zero.
+In this case, it may slow down the convergence speed of the training of deep network.
+However, it is likely to fall into this condition if we randomly select training samples to make a triplet input.
+For fast loss convergence, we need to mine the triplet input that make the output of our network satisfy the condition~\ref{triplet_condition} to ensure that the output of the loss function is non-zero.
 
-\subsection{Preprocessing}
-\label{sec:Preprocessing}
-Our system only extracts the CSI magnitude value from the acquired data.
-The acquired data tend to contain missing values.
-At the same time, the number of captured packets varies by data.
-In addition, the large number of CSI streams increases the computational complexity.
-To deal with these issues, the CSI streams are averaged into fewer number of streams.
-Subsequently, a linear-interpolation is performed to fill up the missing values.
-Finally, the length of the CSI stream is normalized using a Fourier transform based sampling method and the max pooling operation is performed to reduce variances and generalize the data.
+% 4.4.2. Triplet mining
+\subsection{Triplet Mining based on the Kernel and the Range space learning}
+% purpose
+In order to train the network faster, we propose training a sub-network for minining the hard positive and the hard negative sample from the training dataset.
 
-\subsubsection{Averaging}
-The acquired data contains 30 subcarrier-streams for each transmitter-receiver pair.
-Under 2$\times$3 MIMO configuration, there are in total 180 subcarrier-streams for each data.
-In order to reduce the computational cost, the subcarrier-streams of each $M_{r}\times M_{t}$ transmitter-receiver pair are averaged into one stream as shown in Fig.
-\ref{fig:Averaging} .
-The $M_{r}$, and $M_{t}$ denote the number of antennas at the receiver, and the transmitter, respecitvely.
-Let $\textbf{h}^{(p)}_{\scalebox{1}{$\scriptscriptstyle M_{r}, M_{t}$}}$ be the one of captured CSI packets from a $M_{r}\times M_{t}$ transmitter-receiver pair.
-Then, the amplitude of the CSI of subcarrier $f_{c}$ is $|h^{(p)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}(f_{c})|$ where $c=\{1,2,\hdots,C\}$ is the subcarrier index, and $p=\{1,2,\hdots,P\}$ is the packet index.
-Finally, an averaged CSI amplitude of $C$ subcarriers can be expressed as follows:
+% hard sample
+The hard positive sample is the samples which is likely to be misclassified as a negative sample by the triplet network.
+In other words, the distance between feature vectors of anchor and hard positive sample is larger than other positive samples.
+On the other hand, the hard negative sample is likely to be misclassified as a positive sample since the distance between feature vectors of anchor and this hard negative sample is smaller than other negative samples.
+Hard triplet input is made by combining hard positive and hard negative samples for selected anchor samples.
+By using hard triplet as input to the triplet network, it is easier to satisfy the conditions of~\ref{triplet_condition}.
+However, we don't know which sample is the hard sample before training the triplet network.
 
+% functions
+To make the hard triplet input before tranining the triplet network, we propose training a small sub-network before triplet network.
+This small sub-network is made of Multi Layer Perceptron (MLP) and we adopt the Kernel And the Range (KAR) space learning to train the MLP sub-network.
+As the KAR space learning has no backpropagation and no iterative learning process, we can train this sub-network with the single shot utilizing the entire training dataset $X$.
+Given entire training dataset $X$, the sub-network output is given as: 
 \begin{equation}
-\tilde{h}^{(p)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}=
-\frac{1}{C}\sum^{C}_{c=1}
-|h^{(p)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}(f_{c})|. 
-\label{eq:avg}
+    KAR\left(\mathbf{X}\right)=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right).
 \end{equation}
-Then, the averaged stream can be expressed in a vector form   $\tilde{\textbf{h}}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$=\Big[$\tilde{h}^{(1)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$, $\tilde{h}^{(2)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$, $\hdots$, $\tilde{h}^{(P)}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}$\Big].
-Note that only the amplitude of the CSI is utilized in the proposed system.
+After training the sub-network, we can mine the hard sample by measuring the $L2$ distance between every output vector of the sub-network and output vector of anchor sample.
+The sub-network output of a given anchor sample $x_0$ is $KAR(x_0)$, To mine hard-positive sample, select one sample among the sub-network output which distance to anchor feature vector $KAR(x_0)$ is larger than threshold $t_+$.
+For hard-negative sample, choose one among the sub-network output which distance to anchor feature vector is smaller than threshold $t_-$.
+Selected hard-positve and hard-negative sample satisfies this property:
+\begin{equation}
+    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{+}\right)}} \right\|_2^2} \geq \mathrm{t}_{+}, 
+    \label{thres_pos}
+\end{equation}
+\begin{equation}
+    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{-}\right)}} \right\|_2^2} \leq \mathrm{t}_{-},\label{thres_neg}
+\end{equation}
+If the hardest sample, it is known that the outlier data is likely to be selected and there is a risk of overfishing[].
+To avoid this problem, threshold for the hard-positive and the hard-negative samples are empirically chosen as 25 and 75 percentiles of the distance between anchor and sub-network outputs.
 
-%Then, the averaged stream is defined as a vector $\tilde{\textbf{h}}_{\scalebox{.7}{$\scriptscriptstyle M_{r}, M_{t}$}}\in\mathbb{R}^{1\times P}$.
-Note that only the amplitude of CSI is utilized in the proposed system.
-
-\begin{figure}[!ht]
-	\begin{center}
-		\includegraphics[scale=0.5]{Averaging_v2.pdf}
-	\end{center}
-	\caption{The CSI stream averaging scheme. $P\times C$ CSI amplitude streams are averaged into a $P$ dimensional stream. $\tilde{h}$ denotes the averaged CSI.} 
-	\label{fig:Averaging}
-\end{figure}
-
-\subsubsection{Interpolation}
-\label{sec:Interpolation}
-When signals are transmitted through the Wi-Fi channel, where multiple devices and users share the same resource, time delay in packet transmission and packet loss could happen.
-The packet loss causes discontinuity in the received signals.
-Hence, even though our system is set to transmit signals at every 0.00001 seconds, the total number of collected packets may differ.
-In order to fill up the gaps, we use a one-dimensional linear interpolation to preserve the continuity of the received signals using two packet values.
-
-\subsubsection{Re-sampling}
-\label{sec:resampling}
-Since the collected signature data has different lengths, they are re-sampled uniformly based on the Fast Fourier Transform (FFT) and the inverse FFT \cite{Python:Resampling} to normalize the length of the data.
-In the proposed system the length of re-sampled data $P'$ is chosen to be smaller than the original length of data $P$.
-
-\subsubsection{Max Pooling}
-Pooling operation summarizes the local information of certain region in the data by sliding over the data.
-Typically, pooling operation calculates the maximum or average value of a neighborhood.
-Our proposed system employs the max pooling for data generalization.
-
-Finally, the input CSI streams preprocessed at the previous stages can be packed into a matrix $\tilde{\textbf{H}}\in \mathbb{R}^{S\times P'}$:
-\begin{equation}
-\tilde{\textbf{H}}=
-\begin{bmatrix}
-\tilde{\textbf{h}}_{1}\\ 
-\tilde{\textbf{h}}_{2}\\
-\vdots\\
-\tilde{\textbf{h}}_{s}
-\end{bmatrix},
-\end{equation}
-where $\tilde{\textbf{h}}_{s}\in \mathbb{R}^{1\times P'}$.
-For the ease of notation, the stream index $(M_{r}, M_{t})$ is replaced by $s=\{1,2,\dots, S\}$, where $S$ is the maximum number of streams.
-The superscript $P'$ denotes the length of the re-sampled packet.
-
-\subsection{Feature Extraction}
-
-Our system adopts the feature extraction method proposed in \cite{Kim2016}.
-Fig.
-\ref{fig:Feature} shows an overview of the feature extraction method.
-First, a shifting operation is applied to the Wi-Fi signal by matrix projection.
-Then, the difference between the shifted signal and the original signal is computed to extract the high frequency component information.
-The difference signal is then fed into a sigmoid function to further enhance the contrast in the signal.
-Finally, the discrete Fourier transform is applied to the resulting signal to extract the magnitude of the frequency components.
-The following subsections explain the details of the proposed feature extraction scheme.
-
-\begin{figure}[!h]
-	\begin{center}
-		\includegraphics[scale=0.6]{Feature_Extraction.pdf}
-	\end{center}
-	\caption{The illustration of feature extraction. For the visual simplicity, only one averaged stream is used for explanation. }
-	\label{fig:Feature}
-\end{figure}
-
-\subsubsection{Shift and Subtraction}
-\label{sec:shift_subtract}
-In the static environment, the Wi-Fi signals show a generally stable pattern except for some minor noises caused by the external sensing conditions.
-This static pattern can be considered as the DC component of the signal \cite{Wang2015}.
-A slight change in the experimental environment can lead to a large variation in the DC component.
-To extract the Wi-Fi signal fluctuations caused by a person's in-air signature, it is important to reduce the impact of the DC component in the signal for robust identification.
-The proposed method utilizes a shift plus a subtraction operation to extract the fluctuation information in the signal: (1) shifts the preprocessed input signals horizontally by $k$ positions using a shifting matrix (cf.
-Sec.
-\ref{sec:Shift}), and (2) subtracts the shifted signals from the input signals.
-The shifted signal $\textbf{O}_{k}\in \mathbb{R}^{S\times P'}$ can be expressed as follows:
-\begin{align}
-\textbf{O}_{k}&=\tilde{\textbf{H}}\cdot \textbf{U}_{k}\\[1.8em]
-&=
-\begin{bmatrix}
-\bovermat{$\textbf{0}_{S \times k}$}{\vspace{0.2cm}0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&\bovermat{$\tilde{\textbf{H}}_{S \times (P'-k)}$}{\vspace{0.2cm}\tilde{h}^{(1)}_{1} \hspace{0.3cm} \tilde{h}^{(2)}_{1} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P'-k)}_{1}}\\%[0.01em]
-%
-{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(1)}_{2} \hspace{0.3cm} \tilde{h}^{(2)}_{2} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P'-k)}_{2}}\\
-%
-\hspace{0.5cm} \vdots&\vdots \hspace{0.4cm} \ddots \hspace{0.4cm}\vdots\\
-%
-{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(1)}_{S} \hspace{0.3cm} \tilde{h}^{(2)}_{S} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P'-k)}_{S}}\nonumber
-%RIGHT BRACKET
-\end{bmatrix},\!\!\!
-%
-%\begin{array}{l}
-%\MyLBrace{3.5ex}{13} \\
-%\\
-%\end{array}
-\end{align}
-where $\tilde{\textbf{H}}\in \mathbb{R}^{S\times P'}$ is the matrix of preprocessed CSI streams, and $\textbf{U}_{k}\in\mathbb{Z^{*}}^{P' \times P'}$ is the shift matrix as illustrated in equation \ref{eq:shift_matrix}.
-$\textbf{0}_{S \times k}$ is a matrix of "0"s, and $\tilde{\textbf{H}}_{S \times (P'-k)}$ is the preprocessed data matrix that is size of ${S \times (P'-k)}$.
-The variable $k$ is the shifting parameter that can be tuned.
-During the shifting operation, the last $k$ columns of the shifted signal matrix are discarded by overflow.
-The horizontal difference signal can then be obtained by 
-\begin{align}
-\textbf{Q}_{k}&=\tilde{\textbf{H}} - \textbf{O}_{k}\\[2em]
-&\approx
-\begin{bmatrix}
-\bovermat{$\textbf{0}_{S \times k}$}{\vspace{0.2cm}0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&\bovermat{$\textbf{Q}_{S \times (P'-k)}$}{\vspace{0.2cm}\tilde{h}^{(k+1)}_{1}-\tilde{h}^{(1)}_{1} \hspace{0.3cm} \tilde{h}^{(k+2)}_{1}-\tilde{h}^{(2)}_{1} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P')}_{1}-\tilde{h}^{(P'-k)}_{1}}\\[0.5em]
-%
-{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(k+1)}_{2}-\tilde{h}^{(1)}_{2} \hspace{0.3cm} \tilde{h}^{(k+2)}_{2}-\tilde{h}^{(2)}_{2} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P')}_{2}-\tilde{h}^{(P'-k)}_{2}}\\
-%
-\hspace{0.5cm} \vdots& \vdots \kern 6em \ddots \kern 7em \vdots\\
-%
-{0 \hspace{0.3cm} 0\hspace{0.3cm}\cdots \hspace{0.3cm}0}&{\tilde{h}^{(k+1)}_{S}-\tilde{h}^{(1)}_{S} \hspace{0.3cm} \tilde{h}^{(k+2)}_{S}-\tilde{h}^{(2)}_{S} \hspace{0.3cm} \cdots \hspace{0.3cm} \tilde{h}^{(P')}_{S}-\tilde{h}^{(P'-k)}_{S}}\nonumber
-%RIGHT BRACKET
-\end{bmatrix}.\!\!\!
-%
-%\begin{array}{l}
-%\MyLBrace{3.5ex}{13} \\
-%\\
-%\end{array}
-\end{align}
-Note that the first $k$ columns of the difference signal matrix are filled with zeros.
-
-\subsubsection{Contrast Enhancement using the Sigmoid Function}
-To enhance the contrast information in the difference signal $\textbf{Q}_{k}$, a sigmoid function is applied.
-This operation also has an effect of normalizing the data into a range of [0,1].
-The Sigmoid function is defined as follows:
-\begin{equation}
-\sigma (x) = \frac{1}{1+e^{-x}}.
-\end{equation}
-For a given resulting difference matrix $\textbf{Q}_{k}$, the output of the Sigmoid function is given by
-\begin{equation}
-\textbf{G} = \sigma \big(\textbf{Q}_{k}\big),
-\end{equation}
-where $\textbf{G}\in\mathbb{R}^{S \times P'}$. The sigmoid operation is element-wise for the entire matrix $\textbf{Q}_{k}$.
-
-\subsubsection{Fourier Magnitude Spectrum}
-The collected Wi-Fi signal captures the dynamics of the in-air signature with regard to the time variance.
-Therefore, the starting and the ending points of the in-air signature can change from sample to sample.
-To extract translation invariant features from the signal, the Fourier transform is calculated for each stream of $\textbf{G}$ as follows:
-\begin{equation}
-f^{(\nu)}_{s} = \sum_{p=0}^{P'-1} g^{(p)}_{s}\cdot e^{-j2\pi ap/P'},
-\end{equation}
-where $g^{(p)}_{s}\in\mathbb{R}^{P'}$ denotes $p$-th element of one of streams in $\textbf{G}$.
-The index $\nu$ is the frequency component index, and the index $s=\{1,2,\hdots,S\}$ is the CSI streams index.
-
-Then, Fourier magnitude spectrum can be calculated as follows:
-\begin{equation}
-|f^{(\nu)}_{s}| = \sqrt{\textrm{Re}(f^{(\nu)}_{s})^{2}+\textrm{Im}(f^{(\nu)}_{s})^{2}},
-\end{equation}
-where $\textrm{Re}(f^{(\nu)}_{s})$ and $\textrm{Im}(f^{(\nu)}_{s})$ represent the real and imaginary parts of $f^{(\nu)}_{s}$, respectively.
-
-\subsection{Post Processing}
-In this section, we illustrate the sequence of post-processing to further improve the identification performance.
-Firstly, the Fourier spectrum features are smoothed by a moving average filter.
-The resulting features are then weighted by the energy of the CSI streams.
-These two processes are described in detail below.
-
-\subsubsection{Moving Average}
-To reduce noises in the extracted Fourier magnitude spectrum, the features are smoothed by a moving average filter. The moving average filtering can be expressed as follows:
-\begin{equation}
-\tilde{f}^{(\nu)}_{s}=\frac{1}{W}\sum_{i=0}^{W-1}|f^{(\nu+i)}_{s}|,
-\end{equation}
-where $\tilde{f}^{(\nu)}_{s}$ denotes the filtered feature, and $W$ is the size of moving average window. the $i$ is the index of the element inside the window.
-
-\subsubsection{Energy based Weights}
-\label{sec:energy}
-One observation is that some CSI streams show relatively high fluctuations, while the others have more stable patterns for the same in-air signature.
-To emphasize on the  fluctuation information caused by the in-air signature, the extracted features are weighted by the energy of the CSI stream.
-The energy of the $s$-th stream is calculated from the averaged CSI stream $\tilde{\textbf{h}}_{s}$ as follows:
-\begin{align}
-e_{s}=\sum_{p=1}^{P'}||\tilde{h}^{(p)}_{s}||^{2},
-\end{align} 
-where $\tilde{h}^{(p)}_{s}$ is the $p$-th averaged CSI amplitude of $\tilde{\textbf{h}}_{s}$ (cf. Eq.\ref{eq:avg}).
-Then, the energy based weight can be computed by
-\begin{equation}
-w_{s}=\frac{e_{s}}{E},
-\label{eq:weight}
-\end{equation}
-where $E$ is the total energy of CSI streams. In equation \ref{eq:weight}, the weights are normalized by the total energy $E$ given by:
-\begin{equation}
-E=\sum_{s=1}^{S}e_{s}.
-\end{equation}    
-Fianlly, the weighted feature of $s$-th stream $\boldsymbol{\xi}_{w_{s}}$ is computed as follows:
-\begin{equation}
-\boldsymbol{\xi}_{w_{s}}=w_{s}\tilde{\textbf{f}}_{s},
-\end{equation}
-where $\tilde{\textbf{f}}_{s}=\big[\tilde{f}^{(1)}_{s}, \tilde{f}^{(2)}_{s}, \hdots, \tilde{f}^{(P')}_{s}\big]$.
-
-\newpage
-\subsection{Person Identification using the Support Vector Machine}
-In order to make a decision regarding the identity of a person, we use the support vector machine (SVM) classifier with the radial basis function (RBF) kernel.
-The input of the SVM is a concatenated vector form of the post-processed weighted features  $\boldsymbol{\xi}_{w}=[\boldsymbol{\xi}_{w_{1}}, \boldsymbol{\xi}_{w_{2}}, \hdots , \boldsymbol{\xi}_{w_{S}}]$.
+% 4.4.3. ConvNet Structures
+\subsection{The ConvNet structures}
+% Purpose
+Since the three-dimensional formats of our input signature signal can be considerd as an image data, we utilized deep ConvNet structure as a feature extractor.
+This ConvNet structure are made of three layers of ConvNet with triplet loss.
+Each layers of ConvNet shares their weights.
+% figure
+\begin{figure*}[!ht]
+    \includegraphics[width=\textwidth]
+        {fig_convnet_v1.pdf}
+    \caption{ConvNet structure.} \label{fig2}
+\end{figure*}
+% Structure
+Our ConvNet model is consists of three filters and output fully-connected (FC) layer as seen in (item (b) in Fig.~\ref{fig1}).
+The depth of 3x3 sized ConvNet filters are empirically chosen as (64,128,256) with stride 1 and ReLU activation function.
+The size of FC layer is 16.
+Output FC layers are go through sigmoid activation function and normalized using $L2$ distance.

### 2019-09-21 190904_Paper_Thesis/abstract.tex
Paper_Thesis

\begin{center}
	\LARGE An In-Air Signature Identification System using Commercial Wi-Fi Devices
\end{center}

\parbox[t]{0.4\textwidth}

{
	\begin{flushright}
		Han-Cheol Moon\\
		School of Electrical and Electronic Engineering\\
		The Graduate School\\
		Yonsei University
	\end{flushright}
}
\vspace{0.1em}

...

\vspace{\stretch{1}}
\noindent
\hrulefill\\
{\bf Key words : Biometrics, Identification, In-Air Signature, Channel State Information, and
	Wi-Fi}
\parbox[t]{0.8\textwidth}
{}

### 2019-09-21 190906_Paper_BDML/bdml_v1.tex
Paper_Thesis

--- 2019-09-07 190906_Paper_BDML/bdml_v0.tex
@@
 \usepackage{multirow}
+\usepackage{IEEEtrantools}
 
@@
 %% used to denote shared contribution to the research.
-\author{Young-Woong Kwon}
+\author{Young-Woong Kwon, Jooyoung Kim and Kar-Ann Toh}
 %\authornote{Both authors contributed equally to this research.}
-\email{herokwon@yonsei.ac.kr}
 \affiliation{%
@@
   \state{Seoul}
+  \country{Korea}
   \postcode{03722}
 }
-
-\author{Jooyoung Kim}
-%\authornote{Both authors contributed equally to this research.}
-\email{harrykim@yonsei.ac.kr}
-\affiliation{%
-  \institution{School of Electrical and Electronic Engineering, Yonsei University}
-  \streetaddress{50 Yonsei-ro}
-  \city{Seodaemun-gu}
-  \state{Seoul}
-  \postcode{03722}
-}
-
-\author{Kar-Ann Toh}
-%\authornote{Both authors contributed equally to this research.}
-\email{katoh@yonsei.ac.kr}
-\affiliation{%
-  \institution{School of Electrical and Electronic Engineering, Yonsei University}
-  \streetaddress{50 Yonsei-ro}
-  \city{Seodaemun-gu}
-  \state{Seoul}
-  \postcode{03722}
-}
+%\email{herokwon@yonsei.ac.kr}
 
@@
     In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
-    To enable a fast loss convergence, a kernel and the range space learning is initially adopted for refining the triplet inputs by mining the distinctive inputs. 
+    To facilitate a fast converging loss model, a kernel and the range space learning is initially adopted for mining the triplet inputs. 
     Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Wi-Fi signature signal, in-air handwritten signature verification, the Kernel and the Range space projection learning, triplet network}
+\keywords{Wi-Fi signature signal, in-air handwritten signature verification, the Kernel and the Range space projection learning, triplet network.}
 
@@
 Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}.
-Among these behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
-With the help of sensors such as the depth camera~\cite{malik20183dairsig} or a mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems.
+Among these behavioral biometrics, the signature-based user authentication~\cite{fahmy2010online,sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic}.
+With the help of sensors such as the depth camera~\cite{jeon2012system,malik20183dairsig} or a mobile sensor~\cite{ketabdar2012magnetic}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic,sesa2012information}.
 
@@
 
-In this paper, we utilize the deep triplet network for identity verification based on the Wi-Fi CSI signature signal.
+In this paper, we utilize a deep triplet network for identity verification based on the Wi-Fi CSI signature signal.
 To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs.
-Subsequently, the triplet network which utilizes the ConvNet structure as a feature extractor is trained based on the L-2 distance comparison.
+Subsequently, the triplet network which utilizes the ConvNet structure as a feature extractor is trained based on the $L2$ distance comparison.
 
@@
 The paper is organized as follows: related works including the triplet network and KAR space learning are introduced in Section 2 for immediate reference.
-Our proposed method are discussed in Section 3.
+Our proposed method is discussed in Section 3.
 Section 4 describes our experimental results and analysis.
@@
 It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features.
-The main difference between person identification and re-identification is that the later is a more challenging task where images of the same person taken from different cameras or from the same camera in different occasions are to be associated.
-In this re-identification problem, to distinguish among the classes is a challenging task since the features are relatively weak compared with the background features.
-To address this problem, we adopt a triplet network which optimizes the embedding data space so that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.
+The main difference between person identification and re-identification is that the later is a more challenging task where images of the same person taken from different cameras or under different occasions are to be associated.
+In order to address our challenging Wi-Fi based verification task, we adopt a triplet network which optimizes the input data space so that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.
 
@@
 Since not all triplet samples contribute to the desired classification, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training.
-In order to optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplet from a small number of classes (persons) in each iteration.
+In order to optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplets from a small number of classes (persons) in each iteration.
 Recently, \cite{schroff2015facenet} adopted a triplet mining process to speed up the training convergence.
-They utilized a large mini-batch at each training iteration and selected the triplet based on the training network rather than random sampling.
+They utilized a large mini-batch at each training iteration and selected the triplets based on network training instead of random sampling.
 However, this strategy needed a few thousands of exemplar mini-batches in every training iteration for triplet pairs selection.
 This results in a heavy computational load in training.
+In order to make use of the small sample training size as well as to speed up the triplet training process, we adopt the kernel and range space method for the learning.
 
 % Rel works: KAR learning
-\subsection{Kernel and the range space learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient}}\label{kar}
+\subsection{Kernel and the range space learning}\label{kar}
 
 Generally, the multilayer feedforward neural networks is trained based on the gradient descent method via backpropagation~\cite{goodfellow2016deep}.
-However, setting the learning parameters such as the learning rate or the learning momentum is a time consuming task.
+However, setting the learning parameters such as the learning rate and the learning momentum is a time consuming task.
 
-Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh2018learning,toh2018gradient}.
+Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient}.
 The learning method is grounded on linear algebra with neither learning parameters nor iteration is needed in training.
@@
 % Karnet structure and mining samples.
-Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
-Then the multilayer neural network structure can be written in linear equation form as follows:
+Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network output.
+Then the multilayer neural network can be written in equation form as follows:
 \begin{equation}
-\begin{split}    
-    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),\\ i=1,\dotsc,n,
-\end{split}
+    \mathbf{G}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right),
 \end{equation}
-where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,\\$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is the activation function.
+where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
 By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
-\begin{equation}
-\begin{split}
-    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \\ i=1,\dotsc,n.
-\end{split}
-\end{equation}
+\begin{IEEEeqnarray}{rCl}
+    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
+\end{IEEEeqnarray}
 
@@
 In this section, we propose an identity verification system based on the Wi-Fi in-air handwritten signature (which will be called Wi-Fi signature hereafter) using the triplet network~\cite{hoffer2015deep}.
-Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for mining the triplet input.
-Essentially, the KAR space projection learning is utilized to learn the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample (see item (a) in Fig.~\ref{fig1}).
+Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for mining the triplet inputs.
+Essentially, the KAR space projection learning is utilized to learn the triplet input data by mining the hard positive and the hard negative samples from each of the given anchor sample (see item (a) in Fig.~\ref{fig1}).
 The hard positive and the hard negative samples refer to positive and negative class samples which are likely to be misclassified by the network.
-Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on a triplet loss function using the L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
+Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on a triplet loss function using the $L2$ distance comparison (see item (c) in Fig.~\ref{fig1}).
 The following subsections describe the details of the triplet mining using KAR space learning and the triplet network.
@@
     \includegraphics[width=\textwidth]{fig1_tcnn_kar_v6}
-    \caption{An overview of the proposed system} \label{fig1}
+    \caption{An overview of the proposed system.} \label{fig1}
 \end{figure*}
@@
 % Methods: KAR learning
-\subsection{Triplet mining using kernel and the range space learning}
+\subsection{Triplet mining using the kernel and the range space learning}
 
 The network receives a triplet set of data as its inputs.
-These triplet data consist of the reference data (will be called anchor samples hereafter) and the corresponding positive class data (same class with that of the anchor) and negative class data (different class from that of the anchor).
-The goal of the triplet network is to position the feature vectors with appropriate separation space by putting the positive samples close to the anchor sample and keeping the negative sample away from the anchor sample.
+These triplet data consist of the reference data (will be called anchor samples hereafter) and the corresponding positive class data (same class with that of the anchor) and the negative class data (different class from that of the anchor).
+The goal of the triplet network is to position the feature vectors with appropriate separation space by putting the positive samples close to the anchor sample while keeping the negative sample away from the anchor sample.
 
@@
 On the other hand, a hard negative sample is defined as a sample whose distance to the anchor sample is small (which is most likely to be misclassified as a positive sample).
-However, from the raw data, there is no information about regarding whether a sample is considered hard positive or hard negative before we train the network.
+However, from the raw data, there is no information regarding whether a sample is considered hard positive or hard negative before we train the network.
 
@@
 
-By training the network with the single shot KAR space learning, we can map the L-2 distance between every samples by using the output vector of the KAR space network.
-\textbf{For training data set $\mathbf{X}$, the trained network output is given by:}
+By training the network with the single shot KAR space learning, we can map the $L2$ distance between every sample by using the output vector of the KAR space network.
+Given a set of training data which is packed in matrix $\mathbf{X}$, the network output can be written as:
 \begin{equation}
-    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
+    f\left(\mathbf{X}\right)=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right).
 \end{equation}
-\textbf{For anchor sample $\mathbf{x}_{anc}$ which is randomly selected from training dataset X, the output of the KAR learning makes it possible to measure the distance between each sample.}
-A hard positive sample $\mathbf{x}_{pos}$ and a hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can each be respectively determined based on:
+After training based on the KAR space projection, the given anchor sample $\mathbf{x}_{anc}$ can be used as the reference to decide whether the network output of a sample is far away from this anchor sample.
+In other words, a hard positive sample $\mathbf{x}_{pos}$ and a hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can each be determined based on:
 \begin{equation}
@@
 where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ respectively denote the thresholds that determine whether a sample is hard positive or hard negative.
-Since the hardest samples are likely to be outliers which can degrade the training process of the triplet network, we empirically set the $\mathrm{t}_{pos}$ at 75 percentile of the L-2 distance and $\mathrm{t}_{neg}$ at 25 percentile of the L-2 distance.
-The final set of $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ samples is randomly selected from those samples threshold by~\eqref{pos} and~\eqref{neg}.
+Since the hardest samples are likely to be outliers which can degrade the training process of the triplet network, we empirically set the $\mathrm{t}_{pos}$ at 75 percentile of the $L2$ distance and $\mathrm{t}_{neg}$ at 25 percentile of the $L2$ distance.
+The final set of $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ samples is randomly selected based on equations~\eqref{pos} and~\eqref{neg}.
 
 % Methods: ConvNets
-\subsection{ConvNet structure}
+\subsection{The ConvNet structure}
 
-The next step is to design a feature extractor which converts the input triplet data into feature vectors.
+The next step is to design a feature extractor which converts the  triplet input data into feature vectors.
 In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.
 
-Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of three convolutional layers and one fully-connected layer.
+Our ConvNet design (item (b) in Fig~\ref{fig1}) consists of three convolutional layers and one fully-connected layer.
 The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, 256\}$, with fixed filter size of $3\times3$, each of stride 1.
@@
 Subsequently, the extracted features from the last convolutional layer are flattened into a vector before feeding into the fully-connected network.
-The output vectors from the fully-connected layer are finally transformed using the sigmoid function followed by a L-2 normalization.
+The output vectors from the fully-connected layer are finally transformed using the sigmoid function followed by a $L2$ normalization.
 
@@
 The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network.
-\textbf{For the $i^{th}$ network input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$, anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set.
-Positive sample $\mathbf{x}_{pos,i}$ is selected among the same class with the anchor while negative sample $\mathbf{x}_{neg,i}$ is selected among the different class with the anchor.
-The generated triplet input is fed into ConvNet structure and make feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$.}
-The triplet loss function is formulated based on a summation of the difference between the positive distance (the L-2 distance between the anchor vector and the positive vector) and the negative distance (the L-2 distance between the anchor vector and the negative vector) as follows:
+For the $i^{th}$ network input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$, an anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set.
+The positive and negative samples (respectively $x_{pos,i}$ and $x_{neg,i}$) are then determined and being selected for training the ConvNet based on the feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$, for i=1,...,N.
+The triplet loss function is formulated based on a summation of the difference between the positive distance (the $L2$ distance between the anchor vector and the positive vector) and the negative distance (the $L2$ distance between the anchor vector and the negative vector) as follows:
 \begin{equation}
@@
 \end{equation}
-where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
+where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the $L2$ distance and $\alpha$ denotes the preset margin.
 The ConvNet structure using equation~\eqref{triplet} is trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.
@@
 \subsection{Dataset}
- In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with the user located at a single position is utilized in our experiments.
+ In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} is utilized in our experiments.
 The Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with sample size 500$\times$30$\times$6.
@@
 The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve.
-\textbf{We considered in-air signature data could be entered in any direction of the Wi-Fi router.
-For 4-way inputs, we take into account with signatures facing Wi-Fi router's front, rear and both sides.
-For 1-way inputs, we considered only the entered signatures facing the forward face of the Wi-Fi router.} For Case I, existing handcraft methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel functions and a total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+For both cases, Wi-Fi signal measurements based on a single-orientation and 4-orientations of the user are recorded.
+For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM)~\cite{vapnik2013nature} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
 The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.
 
-The verification performance of the proposed system and other methods are evaluated in terms of the Equal Error Rate (EER, \%) which are taken from averaging the results of five runs of two-fold cross-validation tests.
+The verification performance of the proposed system and the compared methods are evaluated in terms of the Equal Error Rate (EER, \%) which are taken from averaging the results of five runs of two-fold cross-validation tests.
 Due to the memory constraint caused by the large data size, the deep learning-based methods utilized randomly sampled 9,500 negative pairs in the validation stage, which is the same number as the number of positive pairs.
@@
 Each layer is initialized with uniform distribution over [0, 1).
-We used $\sigma = {tan}^{-1}$ as an activation function following \cite{toh2018analytic}.
+We used $\sigma = {tan}^{-1}$ as the activation function following \cite{toh2018analytic}.
 \begin{table}
-    \caption{The network structure of KAR space learning}
+    \caption{The network structure of KAR space learning.}
     \label{tab2}
@@
 We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32.
-We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for the output layer.
-The output layer was regularized using an L-2 penalty of 0.0001.
+We optimized the loss by the Adam optimizer with $L2$ penalty of 0.0002 except for the output layer.
+The output layer was regularized using an $L2$ penalty of 0.0001.
 We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01.
@@
 The training epochs were set at 1,500 for all three deep learning-based algorithms.
-For the linear methods such as LSE,SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
+For the linear methods such as LSE, SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory.
 For the PCA-LSE, the input dimension was reduced to 40.
@@
     \caption{The structure of ConvNet model.
-For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride.
+For the convolution layer, the kernel is specified as (m$\times$m) sized filter $\times$ (\# of filters) / (\# of stride).
 For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride.
-The input sizes are denoted as rows $\times$ cols $\times$ \# of filters}
+The input sizes are denoted as rows $\times$ cols $\times$ \# of filters.}
     \label{tab1}
@@
      Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
-     L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
+     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\
      Concat    &            &                 & 1$\times$1$\times$16    \\
@@
 
-Case I: Table~\ref{tab3} shows the best average of EER performance from five runs of two-fold cross-validation test and the parameter condition. 
-\textbf{For 1-way inputs, SVM showed best verification accuracy of 1.55\% EER.
-However, For 4-way inputs, all three deep learning-based methods showed better performance since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.} Among the deep learning-based methods, the Siamese network is also a metric learning system, but it differs from our system in that it receives two inputs and uses the contrastive loss function for training.
-The best average of test EER performance was obtained from the proposed system with 19.35\% EER.
+Case I: Table~\ref{tab3} shows the average of EER performance from five runs of two-fold cross-validation tests under the optimal parameter setting.
+For 1-orientation inputs, SVM showed the best verification accuracy of 1.55\% EER.
+However, For 4-orientation inputs, all three deep learning-based methods showed better performance than hand-craft methods.
+This is, perhaps, due to the utilization of the original size (500$\times$30$\times$6) of the input data in the training stage for the deep learning based methods.
+The test EER performance of the proposed system is 19.35\%.
 The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER.
 The Siamese network showed the worst verification performance of 23.53\% EER.
-\begin{table}
-    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset}
+The Siamese network is also a metric learning system, but differs from our system in that it receives two inputs and uses the contrastive loss function for training.
+\begin{table*}
+    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
     \label{tab3}
@@
     \toprule
-    \multirow{2}{*}{Methology} & \multicolumn{2}{c}{Best EER (\%)} & \multirow{2}{*}{Condition} \\ \cline{2-3}
-                            & 1-way     & 4-way     &                            \\
+    \multirow{2}{*}{Methology} & \multicolumn{2}{c}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\
     \midrule
     LSE                                    & 35.40 & 48.44           &                           \\ 
-    PCA-LSE                                & 16.87 & 30.79           & $d_{3000} \rightarrow d_{40}$       \\ 
+    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\ 
     SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\ 
@@
     \end{tabular}
-\end{table}
+\end{table*}
 
-Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning-based methods.
-As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods while other two methods show similar AUC.
-Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network.
-We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value based on their function.
-According to these two observations, it can be concluded that the triplet input mining with KAR space learning improves not only the training loss convergence speed but also the verification performance.
+Case II: Fig.~\ref{fig2} (a) shows the ROC curves of the three compared deep learning-based methods.
+As shown in the figure, the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods.
+In Fig.\ref{fig2} (b) the training loss trends are plotted with respect to along the number of training iterations.
+Here, the proposed system shows the fastest training loss convergence followed by the baseline triplet network.
+In the figure, the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value.
+According to these observations, it can be concluded that the triplet input mining with KAR space learning improves not only the verification performance but also the training loss convergence speed.
 % Figure 2,3
@@
     \subfigure[][ROC Curve]{
-        \includegraphics[height=6.4cm]{fig_roc_v12.eps}}
+        \includegraphics[height=6.4cm]{fig_roc_v14.eps}}
     \subfigure[][Normalized training loss curve]{
         \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
-    \caption{(a) shows the Receiver Operating Characteristic(ROC) Curve and 
-    (b) shows the normalized training loss curve of the deep learning based methods}
+    \caption{(a) Receiver Operating Characteristic (ROC) Curves and 
+    (b) normalized training loss trends}
     \label{fig2}
@@
 In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
-The kernel and the range space learning was adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
-Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
-Our experiments on an in-house Wi-Fi handwritten signature dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
+The kernel and the range space learning was adopted for mining the triplet inputs for fast loss convergence. 
+Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on the $L2$ distance comparison. 
+Our experiments on an in-house Wi-Fi handwritten signature dataset showed not only an encouraging verification accuracy but also a faster training loss convergence compared with the baseline triplet network and the Siamese network.
+%%
+%% The acknowledgments section is defined using the "acks" environment
+%% (and NOT an unnumbered section). This ensures the proper
+%% identification of the section in the article metadata, and the
+%% consistent spelling of the heading.
+\begin{acks}
+    This research was supported by Basic Science Research
+    Program through the National Research Foundation of Korea
+    (NRF) funded by the Ministry of Education, Science and
+    Technology.
+
+    \noindent(NRF-2018R1D1A1A09081956)
+\end{acks}
+
 %%
@@
 
+\begin{table*}[]
+    \caption{Authors' background}
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    Your Name        & Title          & Research Field      & Personal website \\ \hline
+    Young-Woong Kwon & master student & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
+    Jooyoung Kim & Phd candidate & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
+    Kar-Ann Toh & full professor & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
+    \end{tabular}
+\end{table*}
+
 \end{document}

### 2019-09-27 190904_Paper_Thesis/Experiments.tex
paper_thesis_intro

@@
 \label{sec:Dataset}
-..
+The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was implemented in our experiment to mesure the performance of our proposed system.
+These are in-house Wi-Fi signature datasets that comprise 980 signatures per direction, as shown in~\ref{tab_dataset}.
+The size of each sample was 500 x 30 x 6.
+We utilized only the magnitues of the complex values, since the signal have device firmware issues in their phase information~\cite{wang2015understanding}. 
+\begin{table}
+    \caption{Description of the Dataset.}
+    \label{tab_dataset}
+    \begin{tabular}{ccc}
+    \hline
+    Direction of signature & \# of identities & \# of data \\ 
+    \hline
+    1                      & 98               & 980        \\ 
+    2                      & 98               & 980        \\ 
+    3                      & 98               & 980        \\ 
+    4                      & 98               & 980        \\ 
+    \hline
+    \end{tabular}
+\end{table}
+
 \section{Experimental Settings}
-..
+This section details the evaluation scenarios and experimental settings.
+
 \subsection{Evaluation Scenarios}
-\label{sec:scenario}
-..
-\subsection{Evaluation Protocols}
-\label{sec:protocols}
-..
+%performance
+In this paper, the verification performance of the proposed method was evaluated in three ways:
+I) In the first experiment, verification performance was compared between the proposed system and other systems including handcraft and deep-learning based methods.
+II) Under the second experiments, Comparison of convergence speed was conducted between the proposed system other deep-learning based methods. 
+III) The third experiments was conducted to compare the performance degradation between the proposed system and other deep-learning based methods when using a small sized feature vectors. 
+In order to compare the feature extraction performance of the proposed system with other deep-learning based methods, we visualized feature space into 2d euclidean space by using PCA. 
+% handcraft
+We compared the proposed system both with handcraft methods and deep learning based methods.
+For handcraft methods, least square estimations (LSE)~\cite{duda2012pattern}, the principal components analysis(PCA)~\cite{turk1991eigenfaces} with LSE, the supprot vector machine~\cite{vapnik2013nature} and the total error minimization with the reduced multivariate polynomal~\cite{toh2003fingerprint,toh2008between} were used.
+We selected parameters that perform optimally in each handcraft methods.
+For LSE,SVM and TER, the input signatures were reduced to 500$\times$30 by averaging the subcarrier Axis.
+For PCA-LSE, input signature dimension was reduced to 40 following~\cite{moon2017air}.
+For SVM with Gaussian kernel function (RBF), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$.
+For TER, parameter M is chosen among $M\in\{1,2,3\}$ and set $\tau=\eta=0.5$ following~\cite{toh2008between}.
+For comparison with deep learning based methods, Siamese network~\cite{koch2015siamese} and baseline triplet network~\cite{hoffer2015deep} were used.
+%protocols
+The verification performance was evaluated in terms of the Equal Error Rate (EER, \%). We implemented a random 5-runs of 2-fold cross validation tests.
+Due to the hardware memory limitations, we used downsized negative pairs according to the number of positive data pairs for calculating the EER.
+The size of positive data pairs and downsized negative pairs were 18620.
+
+%5.2.2. Parameter settings
 \subsection{Parameter Settings}
-\label{sec:parameter}
-..
+% KAR structure
+For the proposed system, the structure of the KAR learning MLP sub-networks is shown in~\ref{kar_structure}.
+We empirically chosen two layers size of 1024 and 16.
+The size of the second layer was equivalent as feature vectors of the proposed ConvNet.
+The weights in the layers weree initialized as a normal distribution of 0 to 1 before training.
+We used $tan^{-1}$ as an active function following~\cite{toh2018analytic}.
+\begin{table}[]
+    \caption{The network structure of KAR space learning.}
+    \label{kar_structure}
+    \centering
+    \begin{tabular}{|l|l|l|}
+    \hline
+    Layer   & Size     & Activation \\ \hline
+    Input   & 500$\times$30$\times$6 &            \\
+    Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
+    Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
+    Output  & 1$\times$1$\times$50   &            \\ \hline
+    \end{tabular}
+\end{table}
+% conv structure
+We used the same ConvNet structure shown in~\ref{conv_structure} and parameter settings for the proposed system and the deep-learning based methods.
+The CovNet structure consists of 3  convolution filters size of 3$\times$3 and stride 1.
+A ReLU activation function and 2$\times$2 max-pooling layers is applied between the filters.
+The depth of each layer was chosen as \{64,128,256\}.
+The output layer with sigmoid activation was regularized using $L2$ penalty of 0.0001.
+The size of the final feature vectors was 16.
+\begin{table}[]
+    \caption{The structure of ConvNet model.}
+    \label{conv_structure}
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
+    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
+    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
+    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
+    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
+    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
+    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
+    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
+    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
+    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
+    \end{tabular}
+\end{table}
+% traning parameters
+The parameter settings for traning the deep learing network was 
+learning rate of 0.0005, the number of iteration as 3000, and set the mini-batch size as 32.
+We used adam optimatizer for calculating the loss function.
+We initialized the ConvNet structures following ~\cite{koch2015siamese} before training.
+For convolution filters, we used a normal distribution of 0 mean and standard deviation of 0.0001.
+For the biases, parameters for normal distribution was 0.5 mean and standard deviation of 0.01.
+For calculating triplet loss, we set the alpha value as 0.5.
+
+%5.3. Experimental results
 \section{Experimental Results}
-\label{sec:results}
-..
-\subsection{Effect of the DC Component}
-\label{sec:DC}
-..
-\subsection{Effect of the Weighting Scheme}
-..
-\subsection{Effect of the Facing Direction and the Position of the Subject}
-..
-\subsection{Comparison with the ConvNet}
-..
+%5.3.1. verification performance
+\subsection{Performance}
+For experiment I,~\ref{tab_performance} shows the average EER from 5-runs of 2-fold cross-validation tests under the optimal parameter settings.
+As shown in Table~\ref{tab_performance}, the proposed system shows best performance among the handcraft and deep-learning based methods with 19.35\% EER.
+Deep learning based methods performed better performance than handcraft methods since they were able to utilize the entire input signal, and their ability to feature extraction were better than handcraft methods.
+\begin{table}[!h]
+    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab_performance}
+    \centering
+    \begin{tabular}{|c|c|c|}
+    \hline
+    Methology   &   Best EER (\%) &   Condition   \\  \hline
+    LSE &   48.44   &  - \\ 
+    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
+    SVM (Linear) &   28.23   &   c=1 \\
+    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
+    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
+    Siamese network  &   23.53   &   lr=0.00005  \\
+    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
+    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
+     \hline
+    \end{tabular}
+\end{table}
+
+%roc
+As shown in~\ref{fig_roc}, the proposed system also showed the widest Area under ROC curve (AUC).
+\begin{figure*}[!ht]
+    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
+    \caption{Normalized training loss curve.} \label{fig_roc}
+\end{figure*}
+ %5.3.1. conv speed
+~\ref{fig_loss} shows the convergence of the normalized loss function during the training.
+The convergence speed of the proposed system was the fastest among the deep learning-based methods, meaning that KAR running has accelerated the learning speed.
+\subsection{Convergence speed}
+ \begin{figure*}[!ht]
+    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v3.eps}
+    \caption{normalized training loss trends} \label{fig_loss}
+\end{figure*}
+%5.3.2. feature vector
+\subsection{Effect of the size of Feature Vector}
+- Case3) FC layer
+○ Picture
+○ The smaller the mapping to a characteristic space, the lower the performance degradation of the proposed method is.
+§ Reason 1: Triplet network has better space placement capability than Siamese
+Reason 2: Triplet network with KAR learning is better performance
+
+\begin{table}[]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|}
+    \hline
+    Size of the Feature Vector & 16    & 8     & 4     & 2     \\ \hline
+    Siamese network            & 20.34 & 22.05 & 29.39 & 34.26 \\ \hline
+    Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
+    Proposed system            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
+    \end{tabular}
+\end{table}
+\begin{figure}[!ht]
+    \includegraphics[width=\textwidth]{fclayer_v1.eps}
+    \caption{Size of FC layer.} \label{fclayer}
+\end{figure}
+
+\begin{figure}[!ht]
+    \includegraphics[width=\textwidth]{fig_2d_triKAR_10_v1.eps}
+    \caption{2D Feature Representation : Proposed System.} \label{fig_2d_triKAR_10}
+\end{figure}
+\begin{figure}[!ht]
+    \includegraphics[width=\textwidth]{fig_2d_tribase_10_v1.eps}
+    \caption{2D Feature Representation : Baseline triplet network.} \label{fig_2d_tribase_10}
+\end{figure}
+\begin{figure}[!ht]
+    \includegraphics[width=\textwidth]{fig_2d_siam_10_v1.eps}
+    \caption{2D Feature Representation : Siamese network.} \label{fig_2d_siam_10}
+\end{figure}

### 2019-09-27 190904_Paper_Thesis/Introduction.tex
paper_thesis_intro

@@
 \section{Background}
-\label{sec:Intro}
-...
+% biometric
+As mobile devices increase, identity verification using biometrics traits is becoming more widely used.
+Compared to the use of complex passwords, using biometric systems to user verification has advantages of increased security, convinience and accountability~\ref{hutton2004biometrics}.
+
+among the biometric traits, signatures have also been widely used as a way of identification [].
+With the development of various sensors such as depth camera and mobile camera, in-air signature [] have also become available.
+
+A system has been developed to recognize signatures written in the air.
+- Easy to use and no tools required
+Signatures written in Wi-Fi CSI signals are also recognizable
+- Low accuracy and difficult recognition of signatures in different directions
+- Due to the nature of the hollow signature, it is important to recognize the different directions of signature.
+We are trying to solve this problem by using deep learning.
+
 %\newpage
@@
 ...
-..
 \newpage

### 2019-09-27 190904_Paper_Thesis/Related_Works.tex
paper_thesis_intro

\label{chp:Preliminary}
%3.1 Deep Metric Learning
\section{Deep Metric Learning}
% What is metric running?
Metric learning aims to learn a distance function that places similar data close together in a feature space and dissimilar data away from each other.
By metric learning, multi-dimensional input data is converted to low-level feature vectors to measure the distance between data for a specific task.
% Recent Trends
Metric running has been used for computer vision tasks such as image classification and content-based image retrieval~\cite{yang2006distance}. Previously, features are extracted using HOG, LBP, and so on. Simailarity measured based on these features.
In recent years, deep learning-based methods have been widely used, as they have enabled feature extraction and metric running in one framework~\cite{yi2014deep}.
The features for image classification are automatically learned by the deep learning network.
% Target Model
Deep Learning-based models include the Siamise network and the Triplet network, which are described below.

%3.1.1 Triplet network
\subsection{Triplet network}
% Triplet Network
Triplet network is also a metric running model~\cite{weinberger2006distance} which receives triplet data as its inputs and aims to learn distance metric of the data in feature space~\cite{yang2006distance}.
Triplet network receives triplet data pairs as input.
% Recent Trends : person re-id tasks
Triplet network is widely used for person re-identification tasks which aims to identify individuals in several images. 
Person re-identification handles similar objectives with the biometric identification task, but it is more challanging due to the low quality and high variety of its target images~\cite{yi2014deep}. Since person re-identification task usually deals with images taken from low-resolution devices such as surveilance cameras. Also, different occasions such as the clothes, poses, and angle of the target person makes it difficult to identify.

% training triplet network
Input triplet data is composed of anchor(reference), positive(similar) and negative(dissimilar) samples. The training of the triplet network is making feature vectors to be placed in the appropriate feature space, making the positive(similar) data is close to the anchor(reference) and the negative(dissimilar) data is kept away from the anchor.
% optimize training
Since myriad triplet pairs may exist for the training set, training from all possible pairs may time-consuming and unnecessary. Optimizing training becomes necessary as it mines the learning-efficient triplet out of large possible inputs.
\cite{cheng2016person,ding2015deep,wang2016joint} generates triplet only for small number of classes, which randomly selected in iteration.
Rescently, in \cite{schroff2015facenet} used triplet mining stratege for faster convergence speed. They selects inputs from large mini-batch at each training iteration using the network during training.
However, to make such a large-sized mini-batch, a lot of training data is needed for every iteration. Real-world data obtained from in-house experiments is not suitable for this training stratege since it is usually small in size and consists of dozens of classes.
In order to optimize input triplet data with relatively small sized data, we adopt the kernel and range space manipulation method for the training.

%3.1.2 Siamese
\subsection{Siamese networks}
% structure
A Siamese neural networks consists of twin networks which accept distinct inputs but are joined by an energy function at the top~\cite{koch2015siamese}. By using a constrative loss function, Siamese networks classifies the two input if the entered two samples are of the same class or of the other class.
% history of siamese net
In~\cite{bromley1994signature}, LeCun et al. Introduced Siamese networks as parts of their handwritten signature verification system.
% another research which used Siamese Nets
In a recent related study, pedestrian tracking~\cite{Leal-Taixe_2016_CVPR_Workshops}, object cosegmedtation~\cite{mukherjee2018object} showed that Siamese Networks can be used for image classification tasks and~\cite{maheshwary2018matching} captures semantics from job resumes.

%3.2. KAR
\section{the Kernel and the Range space learning}
% MLP and gradient
Multi Layer Perceptron (MLP) neural networks has been widely used in machine running. In general, MLP is trained by the gradient descent method and backpropagation~\cite{goodfellow2016deep}.
Since the learning parameters such as learning rate or momentum value have a great impact on the performance of the gradient descent method, it is important to set these parameters carefully.
However, finding the appropriate values for these parameters through the trial and error is a time-consuming task.

% KAR
Recently, gradient-free learning framework for MLP has developed. By using this novel framework, the MLP is trained based on the kernel and range (KAR) space manipulation~\cite{toh2018analytic,toh100,toh2018learning,toh2018gradient}.
Since this learning framework stands on linear algebra and pseudo-inverse, no parameters and no iteration are need to train the network.

% KAR learning method
Given $m$ samples, let the training dataset is denoted by $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and the network output is denoted by $\tilde{Y}$. Then the MLP networks composed of $n-1$ hidden layers $\{ h_{1},\dotsc,h_{n-1} \}$ can be represented by the following equation:
\begin{equation}
    \tilde{Y}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right),
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
We can train this network by adopting the one-hot encoded target matrix $\tilde{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\tilde{Y}$, The trained weight matrices $\mathbf{W}_{i}$ using KAR space manipulation learning can be obtained as below~\cite{toh2018gradient}:
\begin{IEEEeqnarray}{rCl}
    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
\end{IEEEeqnarray}

### 2019-09-27 190906_Paper_BDML/bdml_v1.tex
paper_thesis_intro

@@
 For both cases, Wi-Fi signal measurements based on a single-orientation and 4-orientations of the user are recorded.
-For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM)~\cite{vapnik2013nature} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA)~\cite{turk1991eigenfaces} with LSE, the support vector machine (SVM)~\cite{vapnik2013nature} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
 The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.

### 2019-09-27 190805_Wisig_Spec/MI_make_spec.py
DIP_A1

@@ -1,0 +1,99 @@
+# Made by : HERO Kwon
+# Date : 190805
+
+import os
+import numpy as np
+import pandas as pd
+import pickle
+import gzip
+import matplotlib.pyplot as plt
+from scipy import signal
+import time
+
+# data path
+path_info = 'D:\\Data\\WIFI\\Wi-Fi_meta\\'
+path_csi = 'D:\\Data\\WIFI\\Wi-fi_processed\\'
+res_path = 'D:\\Data\\WIFI\\Wi-Fi_CARM\\'
+
+# data info
+df_sel = pd.read_csv(path_info+'df_subc_sel.csv')
+
+# save res df
+col_df = (['version','csi_time','eig_list','nperseg','desc'])
+
+try:
+    ver_df = pd.read_csv(res_path + 'ver_df.csv')
+except FileNotFoundError:
+    ver_df = pd.DataFrame()
+
+
+#params
+version = 'carm_v1'
+csi_time = 5500
+eig_list = np.arange(1,4)
+nperseg=110
+desc = ''
+
+def prep_CARM(x,eig_list,nperseg):
+    #x = np.abs(data1).reshape([1,-1,30*2*3])
+    x_specs = list()
+    for i in range(len(x)):
+        nn = x[i].T.dot(x[i])
+        w,v = np.linalg.eig(nn)
+        recon_x = x[i].dot(v[eig_list].T)
+        x_spec = list()
+        for j in range(len(eig_list)):
+            f,t,Sxx = signal.spectrogram(recon_x[:,j],nperseg=nperseg,mode='psd')
+            x_spec.append(Sxx)
+        x_specs.append(np.array(x_spec).swapaxes(0,1).swapaxes(1,2))
+    return(np.array(x_specs))
+
+# data generator
+def gen_csi(df1):
+    for file in df1.name.values:
+        # read sample data
+        # load and uncompress.
+        with gzip.open(path_csi+file+'.pickle.gz','rb') as f:
+            data1 = pickle.load(f)
+
+        # fixed length sampling
+        idx_s = np.linspace(0,len(data1)-1,csi_time).astype('int')
+        data1_s = data1[idx_s]
+
+        # flatten array for PCA
+        flat_data = np.abs(data1_s).reshape([1,-1,30*2*3])
+        spec_data = prep_CARM(flat_data,eig_list,nperseg)
+
+        # slicing
+        spec_data_sl = spec_data[0,3:56-3,3:56-3,:]
+
+        # label
[…]

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/PowerLawTr.m

@@ -1,0 +1,4 @@
+function output = PowerLawTr(input, gamma)
+% Returns transformed image by power law transformation with gamma where INPUT is a gray scale input image
+
+% Complete the remaining part

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/SigmoidTr.m

@@ -1,0 +1,4 @@
+function output = SigmoidTr(input, gamma)
+% Returns transformed image by sigmoid transformation with gamma where INPUT is a gray scale input image
+
+% Complete the remaining part

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/hw1_1.m

@@ -1,0 +1,23 @@
+c = im2double(imread('input1.png'));
+
+cTr = PiecewiseLinearTr(c, [0,1], [1,0]);
+cTr2 = PiecewiseLinearTr(c, [0 .25 .5 .75 1],[0 .75 .25 .5 1]);
+
+figure(1);
+x_axis = [0:1/255:1];
+subplot(1,2,1);
+plot(x_axis, PiecewiseLinearTr(x_axis, [0,1], [1,0]));
+subplot(1,2,2);
+plot(x_axis, PiecewiseLinearTr(x_axis, [0 .25 .5 .75 1],[0 .75 .25 .5 1]));
+
+figure(2);
+subplot(1,2,1);
+imshow(cTr);
+subplot(1,2,2);
+imshow(cTr2);
+
+figure(3);
+subplot(1,2,1);
+imhist(cTr);
+subplot(1,2,2);
+imhist(cTr2);

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/hw1_2.m

@@ -1,0 +1,28 @@
+im = im2double(imread('input1.png'));
+
+gamma = [5, 10, 20, 40];
+
+figure(1);
+ for i = 1:length(gamma)
+     hold on;
+     x_axis = [0:1/255:1];
+     f_Tr =  SigmoidTr(x_axis, gamma(i));
+     plot(x_axis, f_Tr);
+     legend({'\gamma = 5', '\gamma = 10', '\gamma = 20', '\gamma = 40'}, 'Location','northwest');
+ end
+
+ figure(2);
+for i = 1:length(gamma)
+    im_Tr = SigmoidTr(im, gamma(i));
+    subplot(2,2,i);
+    imshow(im_Tr);
+    title(['\gamma = ',num2str(gamma(i))]);
+end
+
+figure(3);
+for i = 1:length(gamma)
+    im_Tr = SigmoidTr(im, gamma(i));
+    subplot(2,2,i);
+    imhist(im_Tr);
+    title(['\gamma = ',num2str(gamma(i))]);
+end

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/hw1_3.m

@@ -1,0 +1,28 @@
+im = im2double(imread('input2.png'));
+
+gamma = [0.2, 0.4, 2.5, 5];
+
+figure(1);
+for i = 1:length(gamma)
+    hold on;
+    x_axis = [0:1/255:1];
+    f_Tr =  PowerLawTr(x_axis, gamma(i));
+    plot(x_axis, f_Tr);
+    legend({'\gamma = 0.2', '\gamma = 0.4', '\gamma = 2.5', '\gamma = 5'}, 'Location','northwest');
+end
+
+figure(2);
+for i = 1:length(gamma)
+    im_Tr = PowerLawTr(im, gamma(i));
+    subplot(2,2,i);
+    imshow(im_Tr);
+    title(['\gamma = ',num2str(gamma(i))]);
+end
+
+figure(3);
+for i = 1:length(gamma)
+    im_Tr = PowerLawTr(im, gamma(i));
+    subplot(2,2,i);
+    imhist(im_Tr);
+    title(['\gamma = ',num2str(gamma(i))]);
+end

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/hw2.m
dip_a1_ver1

@@ -1,0 +1,38 @@
+
+%2-1 Load image and Display histogram
+% load image
+im = im2double(imread('input3.png'));
+% fig 1: histogram of the input image
+figure(1);
+imhist(im);
+title(['2-1. Histogram of Input Image']);
+
+%2-2 implement histogram equalization function;
+
+% image size
+size_im = size(im);
+MN = size_im(1) * size_im(2);
+% make 256bins of histogram
+hist = imhist(im,256);
+L = length(hist);
+% calculate pdf,cdf
+pdf = hist ./ MN;
+cdf = cumsum(pdf);
+% histogram equalized array
+s_arr = round((L-1).*cdf);
+% map input image to histogram-equalized image
+output = zeros(size(im));
+for i = 1:L
+    mask = (im >= (i-1)/L) & (im <= i/L);
+    output = output + mask .* (s_arr(i)/L);
+end
+
+% fig 2: histogram of the output image
+figure(2);
+imhist(output);
+title(['2-2. Histogram of Output Image']);
+% fig 3: Output image
+figure(3);
+imshow(output);
+title(['2-3. Output Image']);
+

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/hw3.m

@@ -1,0 +1,52 @@
+%3-1 Load images
+% load image
+im = im2double(imread('input4.png'));
+im_match = im2double(imread('input4_match.png'));
+
+%3-2 Display histogram
+% fig 1: histogram of the input image
+figure(1);
+imhist(im);
+title(['3-2-1. Histogram of Input Image']);
+% fig 1: histogram of the input image
+figure(2);
+imhist(im_match);
+title(['3-2-2. Histogram of the Matching Image']);
+
+%2-2 implement histogram matching function;
+% image size
+size_im = size(im);
+MN = size_im(1) * size_im(2);
+% make 256bins of histogram
+L = 256;
+hist = imhist(im,L);
+hist_match = imhist(im_match,L);
+
+% calculate pdf,cdf
+pdf = hist ./ MN;
+pdf_match = hist_match ./ MN;
+
+s_k = round((L-1).*cumsum(pdf));
+G_zq = round((L-1).*cumsum(pdf_match));
+
+% map input image to histogram-equalized image
+output = zeros(size(im));
+for i = 1:L
+    mask = (im >= (i-1)/L) & (im <= i/L);
+    T_rk = s_k(i);
+    
+    dist = abs(G_zq-T_rk);
+    [val_dist,idx_dist] = min(dist);
+    
+    T_sk = idx_dist;
+    output = output + mask .* (T_sk/L);
+end
+
+% fig 2: histogram of the output image
+figure(3);
+imhist(output);
+title(['3-3-1. Histogram of Output Image']);
+% fig 3: Output image
+figure(4);
+imshow(output);
+title(['3-3-2. Output Image']);

### 2019-09-27 190927_DIP_A1/[2019-2]DIP_HW1/hw3.m
dip_a1_v1

@@ -22,31 +22,34 @@ L = 256;
 hist = imhist(im,L);
 hist_match = imhist(im_match,L);
 
-% calculate pdf,cdf
+% calculate pdf
 pdf = hist ./ MN;
 pdf_match = hist_match ./ MN;
-
+% calculate transformation function
 s_k = round((L-1).*cumsum(pdf));
 G_zq = round((L-1).*cumsum(pdf_match));
 
 % map input image to histogram-equalized image
 output = zeros(size(im));
 for i = 1:L
+    % select from input image
     mask = (im >= (i-1)/L) & (im <= i/L);
+    % apply 1st transfer function
     T_rk = s_k(i);
-    
+    % find closest distance from G(zq)
     dist = abs(G_zq-T_rk);
     [val_dist,idx_dist] = min(dist);
-    
+    % apply 2nd transfer function
     T_sk = idx_dist;
+    % merge output
     output = output + mask .* (T_sk/L);
 end
 
-% fig 2: histogram of the output image
+% fig 3: histogram of the output image
 figure(3);
 imhist(output);
 title(['3-3-1. Histogram of Output Image']);
-% fig 3: Output image
+% fig 4: Output image
 figure(4);
 imshow(output);
 title(['3-3-2. Output Image']);

### 2019-09-30 190904_Paper_Thesis/Introduction.tex
paper_thesis: intro

--- 2019-09-21 190904_Paper_Thesis/Introduction.tex
@@
 \section{Background}
-\label{sec:Intro}
-...
+% signature
+Signatures written on paper have long been used as an identification tool, and various methods for verify individuals have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
+% biometric
+As mobile devices increase, identity verification using biometrics traits is becoming more widely used.
+Compared to the use of complex passwords, using biometric systems to user verification has advantages of increased security, convinience and accountability~\cite{hutton2004biometrics}.
+% camera sensor
+With the development of various sensors such as depth camera and mobile camera, in-air signature have also become available~\cite{bailador2011analysis}.
+However, they had to use a special sensor prepared for signature.
+~\cite{jeon2012system,malik20183dairsig} used depth camera, \cite{ketabdar2012magnetic} used mobile device to record position of hand.
+% WiFI CSI
+On the other hand, there are studies that use Wi-Fi CSI signals to identify the biometric characteristics of the human body.
+Since they use commercial devices that are already widespread, they do not need any special input devices.
+~\cite{hong2016wfid,liu2015tracking,yousefi2017survey} studied CSI signals to identify the various biometrics characteristics of the body.
+~\cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to enable users to recognize their gestures.
+% CSI signature
+Recently, a study was conducted to identify signatures written in the air using CSI signals~\cite{moon2017air}.
+However, in this study, only the signals entered in one direction were recognized.
+Due to the nature of the in-air signature, which is difficult to specify the direction in which the signal is input, a verification system is required regardless of the direction in which the signal is entered.
+% Deep learning
+More recently, there have been studies using deep learning technology to characterize CSI signals.
+Deep Learning-based models are spotlighted for their automated feature extractors and superior classification capabilities based on them, compared to traditional handcraft models.
+Deep learning was used to recognize users based on the body shape~\cite{pokkunuru2018neuralwave}, or to identify them with the characteristics shown in their behavior~\cite{shi2017smart}.
+% our methods
+We used deep learning technology to create a system that can be identity-recognizable even for multi-way air signatures entered with Wi-Fi CSI.
+The deep learning model used a triplet network to increase the accuracy of feature extraction while allowing accurate classification, and also improved the model's convergence speed using the kernel and range space running~\cite{toh2018gradient}.
+
 %\newpage

### 2019-10-01 190904_Paper_Thesis/Experiments.tex
paper_bdml: new format

@@
 \label{chp:Experiments}
-..
 \section{Data set}
 \label{sec:Dataset}
-The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was implemented in our experiment to mesure the performance of our proposed system.
+The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was implemented in our experiment to measure the performance of our proposed system.
 These are in-house Wi-Fi signature datasets that comprise 980 signatures per direction, as shown in~\ref{tab_dataset}.
 The size of each sample was 500 x 30 x 6.
-We utilized only the magnitues of the complex values, since the signal have device firmware issues in their phase information~\cite{wang2015understanding}. 
 \begin{table}
@@
 II) Under the second experiments, Comparison of convergence speed was conducted between the proposed system other deep-learning based methods. 
-III) The third experiments was conducted to compare the performance degradation between the proposed system and other deep-learning based methods when using a small sized feature vectors. 
-In order to compare the feature extraction performance of the proposed system with other deep-learning based methods, we visualized feature space into 2d euclidean space by using PCA. 
+III) The third experiments were conducted to compare the performance degradation between the proposed system and other deep-learning based methods when using a small-sized feature vectors. 
+To compare the feature extraction performance of the proposed system with other deep-learning based methods, we visualized feature space into 2d euclidean space by using PCA. 
 % handcraft
-We compared the proposed system both with handcraft methods and deep learning based methods.
+We compared the proposed system both with handcraft methods and deep-learning based methods.
 For handcraft methods, least square estimations (LSE)~\cite{duda2012pattern}, the principal components analysis(PCA)~\cite{turk1991eigenfaces} with LSE, the supprot vector machine~\cite{vapnik2013nature} and the total error minimization with the reduced multivariate polynomal~\cite{toh2003fingerprint,toh2008between} were used.
@@
 For TER, parameter M is chosen among $M\in\{1,2,3\}$ and set $\tau=\eta=0.5$ following~\cite{toh2008between}.
-For comparison with deep learning based methods, Siamese network~\cite{koch2015siamese} and baseline triplet network~\cite{hoffer2015deep} were used.
+For comparison with deep-learning based methods, Siamese network~\cite{koch2015siamese} and baseline triplet network~\cite{hoffer2015deep} were used.
 %protocols
-The verification performance was evaluated in terms of the Equal Error Rate (EER, \%). We implemented a random 5-runs of 2-fold cross validation tests.
+The verification performance was evaluated in terms of the Equal Error Rate (EER, \%). We implemented a random 5-runs of 2-fold cross-validation tests.
 Due to the hardware memory limitations, we used downsized negative pairs according to the number of positive data pairs for calculating the EER.
@@
 For the proposed system, the structure of the KAR learning MLP sub-networks is shown in~\ref{kar_structure}.
-We empirically chosen two layers size of 1024 and 16.
+We empirically chose two layers size of 1024 and 16.
 The size of the second layer was equivalent as feature vectors of the proposed ConvNet.
-The weights in the layers weree initialized as a normal distribution of 0 to 1 before training.
+The weights in the layers were initialized as a normal distribution of 0 to 1 before training.
 We used $tan^{-1}$ as an active function following~\cite{toh2018analytic}.
@@
 \subsection{Performance}
-For experiment I,~\ref{tab_performance} shows the average EER from 5-runs of 2-fold cross-validation tests under the optimal parameter settings.
-As shown in Table~\ref{tab_performance}, the proposed system shows best performance among the handcraft and deep-learning based methods with 19.35\% EER.
+For the first experiment,~\ref{tab_performance} shows the average EER from 5-runs of 2-fold cross-validation tests under the optimal parameter settings.
+As shown in Table~\ref{tab_performance}, the proposed system shows the best performance among the handcraft and deep-learning based methods with 19.35\% EER.
 Deep learning based methods performed better performance than handcraft methods since they were able to utilize the entire input signal, and their ability to feature extraction were better than handcraft methods.
@@
  %5.3.1. conv speed
+\subsection{Convergence speed}
 ~\ref{fig_loss} shows the convergence of the normalized loss function during the training.
 The convergence speed of the proposed system was the fastest among the deep learning-based methods, meaning that KAR running has accelerated the learning speed.
-\subsection{Convergence speed}
  \begin{figure*}[!ht]
@@
 \subsection{Effect of the size of Feature Vector}
-- Case3) FC layer
-○ Picture
-○ The smaller the mapping to a characteristic space, the lower the performance degradation of the proposed method is.
-§ Reason 1: Triplet network has better space placement capability than Siamese
-Reason 2: Triplet network with KAR learning is better performance
-
+Figure~\ref{fclayer} shows EER for different sizes of feature vectors in the feature space.
+In general, in metric learning systems, the smaller the size of the feature vectors, the less performance of the system.
+From the results, we can see the proposed system shows less performance degradation by a small size feature vector.
 \begin{table}[]
@@
 \end{figure}
-
+%5.3.3. 2D visualization of feature vector
+\subsection{2D visualization of the feature vector}
 \begin{figure}[!ht]
@@
 \end{figure}
+To visualize the performance of feature extraction property of the proposed system, we project the feature space to two-dimensional euclidean space by using PCA in Figs.
+~\ref{fig_2d_siam_10},\ref{fig_2d_triKAR_10},\ref{fig_2d_tribase_10}.
+Through the feature space projected in the 2d euclidean space, we were able to intuitively verify the feature extraction performance of each system by making sure that the point of being close to the space belongs to the same identity.
+To easily check the distance between points in 2d space, we marked only the first 10 identities.
+As shown in the figure, the proposed system used the 2d euclidean space most efficiently.
+The Siamese network linearly arranged feature vectors, making it difficult to distinguish between classes, and in the case of the baseline triplet network, there were many overlapping areas between identities.

### 2019-10-01 190904_Paper_Thesis/Introduction.tex
paper_bdml: new format

@@
 % signature
-Signatures written on paper have long been used as an identification tool, and various methods for verify individuals have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
+Signatures written on paper have long been used as an identification tool, and various methods for verifying individuals have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
 % biometric
 As mobile devices increase, identity verification using biometrics traits is becoming more widely used.
-Compared to the use of complex passwords, using biometric systems to user verification has advantages of increased security, convinience and accountability~\cite{hutton2004biometrics}.
+Compared to the use of complex passwords, using biometric systems to user verification has advantages of increased security, convenience, and accountability~\cite{hutton2004biometrics}.
 % camera sensor
-With the development of various sensors such as depth camera and mobile camera, in-air signature have also become available~\cite{bailador2011analysis}.
+With the development of various sensors such as depth camera and mobile camera, in-air signature has also become available~\cite{bailador2011analysis}.
 However, they had to use a special sensor prepared for signature.
@@
 % WiFI CSI
-On the other hand, there are studies that use Wi-Fi CSI signals to identify the biometric characteristics of the human body.
+On the other hand, some studies use Wi-Fi CSI signals to identify the biometric characteristics of the human body.
 Since they use commercial devices that are already widespread, they do not need any special input devices.
@@
 %\newpage
+\newpage
 \section{Motivation and Contributions}
-...
-\newpage
+The main contributions of our work can be summarized as follows:
+\begin{itemize}
+\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
+\item Adopted the kernel and the range (KAR) space learning to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
+\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
+\end{itemize}
+
 \section{Organization of Thesis}
-..
+The paper is organized as follows: related works including the triplet network and KAR space learning are introduced in Section 2 for immediate reference.
+Our proposed method is discussed in Section 3.
+Section 4 describes our experimental results and analysis.
+Some concluding remarks are given in Section 5.

### 2019-10-01 190904_Paper_Thesis/Preliminaries.tex
paper_bdml: new format

@@
-\label{chp:Preliminary}
-..
-\section{Biometric Identification System}
-\label{sec:Biometrics}
-..
-\section{Evaluation metrics}
-\label{sec:Evaluation}
-..
-\section{Received Signal Strength Indicator}
-\label{sec:RSSI}
-..
-\section{Channel State Information}
-\label{sec:CSI}
-..
-\subsection{Multiple-Input and Multiple-Output}
-\label{sec:MIMO}
-..
-\section{Shift Matrix}
-\label{sec:Shift}
-..
-\section{Metric Learning}
-\label{sec:metric_learning}
+\label{chp:Survey}
+
+\section{ConvNets}
+% description of convnet
+Convolutional Neural Networks is a special case of Multi Layer Perceptron and it has unified feature extractor and classifier in one network.
+It has been widely applied to visual objects such as image, video or 2D array input.
+Several factors make ConvNets attractive in image-related tasks.
+Local connectivity captures local correlation property of the image. It is applicable by using ConvNet filter. Weight sharing helps to reduce the number of weights in feature maps.
+Also, CUDA libraries make the training feature maps easier to reduce training time.
+
+%3.3. CSI
+\section{Wi-FI Channel State Information}
+CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
+It runs on a commodity 802.11n NIC and records Channel State Information (CSI based on the 802.11 standards.
+The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmitting and receive antennas.
+%[From Halperin End]
+% Structure of CSI %[From HC's ELM paper]
+In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
+$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
+The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
+The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
+\begin{equation}
+    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
+\end{equation}
+where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
+%[From HC's ELM end]

### 2019-10-01 190904_Paper_Thesis/Proposed_Method.tex
paper_thesis_intro
paper_bdml: new format

@@
 \label{chp:Method}
-% 4.1. Overview
-\section{Overview of the Proposed System}
-..
-\cite{Leal-Taixe_2016_CVPR_Workshops}
-
 % 4.2. Data Acquisition
@@
 \label{sec:preprocessing}
-
+To be used as an input to a proposed system, the Wi-Fi signature data must be pre-processed.
+First, the signal has to converted to non-complex form.
+Due to the device firmware issues for the phase value of the 2.4Ghz Wi-Fi signal~\cite{wang2015understanding}, we utilized only the magnitude value of the complex signal.
+Second, all inputs must be arranged of the same size. Since all signals have different length, we used equal length sampling to match all data to a certain length.
+Third, outlier issues.
+Wi-Fi signals are exposed to various electromagnetic noise.
+Among them, Burst noise~\cite{wang2015understanding} has a lot of unexpected effects because its value is larger than the normal signal.
+To minimize the effects of burst noise, we used values corresponding to the median $\pm1$ standard deviation were used.
 % 4.3. Proposed Methodology
@@
 %purpose
-In this paper, we propose person identity verification system based on the in-air handwritten Wi-Fi signature signals (which will be called Wi-Fi signature hereafter). 
+In this paper, we propose an identity verification system based on the in-air handwritten Wi-Fi signature signals (which will be called Wi-Fi signature hereafter). 
 %function
-In order to learn the direction-invariant deep representations for in-air signature, we used the triplet network[] which utilizes ConvNet[] as a feature extractor.
-Moreover, to achieve a faster loss convergence, we adopt the kernel and the range (KAR) space learning[] for mining the triplet input.
+In order to learn the direction-invariant deep representations for in-air signature, we used the triplet network~\cite{hoffer2015deep} which utilizes ConvNet~\cite{lecun1998gradient} as a feature extractor.
+Moreover, to achieve a faster loss convergence, we adopt the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for mining the triplet input.
 % figure
@@
 The anchor sample is randomly selected from the training dataset as the reference data.
-The hard samples refer to which likely to be misclassified by the triplet network for given anchor sample.
+The hard samples refer to which likely to be misclassified by the triplet network for a given anchor sample.
 Subsequently, the ConvNet structure that forms triplet network (see item (b) in Fig.~\ref{fig1}) is trained based on a triplet loss function based on the distance comparison for network output vector (see item (c) in Fig.~\ref{fig1}).
@@
 % purpose
-The purpose of the triplet loss [] is training the ConvNet structure to learn discriminative features that allocates the samples of the same class closer and the samples of the different class far away in the feature space.
+The purpose of the triplet loss~\cite{hoffer2015deep} is training the ConvNet structure to learn discriminative features that allocate the samples of the same class closer and the samples of the different class far away in the feature space.
 % Triplet input
@@
 The anchor sample, which is the reference for the triplet input, is selected from the training data set.
-For selected anchor sample $x_0$, positive sample is selected from same identity with that of the anchor while negative sample is selected from different identity from that of the anchor.
+For selected anchor sample $x_0$, positive sample is selected from the same identity with that of the anchor while a negative sample is selected from different identity from that of the anchor.
 % function
@@
 % purpose
-In order to train the network faster, we propose training a sub-network for minining the hard positive and the hard negative sample from the training dataset.
-
+To train the network faster, we propose training a sub-network for mining the hard positive and the hard negative sample from the training dataset.
 % hard sample
-The hard positive sample is the samples which is likely to be misclassified as a negative sample by the triplet network.
-In other words, the distance between feature vectors of anchor and hard positive sample is larger than other positive samples.
+The hard positive sample is the sample which is likely to be misclassified as a negative sample by the triplet network.
+In other words, the distance between feature vectors of anchor and the hard positive sample is larger than other positive samples.
 On the other hand, the hard negative sample is likely to be misclassified as a positive sample since the distance between feature vectors of anchor and this hard negative sample is smaller than other negative samples.
@@
 However, we don't know which sample is the hard sample before training the triplet network.
-
+% figure
+\begin{figure*}[!ht]
+    \includegraphics[width=\textwidth]
+        {fig_hardsample_v1.pdf}
+    \caption{Selection of hard samples.} \label{fig2}
+\end{figure*}
 % functions
-To make the hard triplet input before tranining the triplet network, we propose training a small sub-network before triplet network.
+In order to make the hard triplet input before tranining the triplet network, we propose training a small sub-network before triplet network.
 This small sub-network is made of Multi Layer Perceptron (MLP) and we adopt the Kernel And the Range (KAR) space learning to train the MLP sub-network.
-As the KAR space learning has no backpropagation and no iterative learning process, we can train this sub-network with the single shot utilizing the entire training dataset $X$.
+As the KAR space learning has no backpropagation and no iterative learning process, we can train this sub-network with the single-shot utilizing the entire training dataset $X$.
 Given entire training dataset $X$, the sub-network output is given as: 
@@
 For hard-negative sample, choose one among the sub-network output which distance to anchor feature vector is smaller than threshold $t_-$.
-Selected hard-positve and hard-negative sample satisfies this property:
+Selected hard-positive and hard-negative sample satisfy this property:
 \begin{equation}
@@
 \end{equation}
-If the hardest sample, it is known that the outlier data is likely to be selected and there is a risk of overfishing[].
-To avoid this problem, threshold for the hard-positive and the hard-negative samples are empirically chosen as 25 and 75 percentiles of the distance between anchor and sub-network outputs.
+If the hardest sample, it is known that the outlier data is likely to be selected and there is a risk of overfitting~\cite{schroff2015facenet}.
+To avoid this problem, the threshold for the hard-positive and the hard-negative samples are empirically chosen as 25 and 75 percentiles of the distance between anchor and sub-network outputs.
 
@@
 % Purpose
-Since the three-dimensional formats of our input signature signal can be considerd as an image data, we utilized deep ConvNet structure as a feature extractor.
-This ConvNet structure are made of three layers of ConvNet with triplet loss.
-Each layers of ConvNet shares their weights.
+Since the three-dimensional formats of our input signature signal can be considered as an image data, we utilized deep ConvNet structure as a feature extractor.
+This ConvNet structure is made of three layers of ConvNet with triplet loss.
+Each layer of ConvNet shares their weights.
 % figure
@@
         {fig_convnet_v1.pdf}
-    \caption{ConvNet structure.} \label{fig2}
+    \caption{ConvNet structure.} \label{fig3}
 \end{figure*}

### 2019-10-01 190906_Paper_BDML_v1/bdml_v0.tex
paper_bdml: v2

--- 2019-09-21 190906_Paper_BDML/bdml_v1.tex
@@
 Then the multilayer neural network can be written in equation form as follows:
-\begin{equation}
-    \mathbf{G}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right),
-\end{equation}
-where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
+\begin{IEEEeqnarray}{rCl}
+    \mathbf{G}&=&\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right), \nonumber \\ i&=&1,\dotsc,n,
+\end{IEEEeqnarray}
+where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
 By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
@@
 Given a set of training data which is packed in matrix $\mathbf{X}$, the network output can be written as:
-\begin{equation}
-    f\left(\mathbf{X}\right)=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right).
-\end{equation}
+\begin{IEEEeqnarray}{rCl}
+    f\left(\mathbf{X}\right) &=& \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right), \nonumber \\ i&=&1,\dotsc,n.
+\end{IEEEeqnarray}
 After training based on the KAR space projection, the given anchor sample $\mathbf{x}_{anc}$ can be used as the reference to decide whether the network output of a sample is far away from this anchor sample.

### 2019-10-01 191001_Paper_BDML_v2/bdml_v2.tex
paper_bdml: v2

--- 2019-09-27 190906_Paper_BDML/bdml_v1.tex
@@
-%%
-%% This is file `sample-sigconf.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigconf.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
+% This is "sig-alternate.tex" V2.1 April 2013
+% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
+%
+% This example file demonstrates the use of the 'sig-alternate.cls'
+% V2.5 LaTeX2e document class file. It is for those submitting
+% articles to ACM Conference Proceedings WHO DO NOT WISH TO
+% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
+% The 'sig-alternate.cls' file will produce a similar-looking,
+% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+%
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.5) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
+%
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
+%
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+%
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
+%
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
+%
+% For tracking purposes - this is V2.0 - May 2012
+
+\documentclass{sig-alternate-05-2015}
 
@@
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\copyrightyear{2019}
-\acmYear{2019}
-\setcopyright{rightsretained}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-%\acmConference{SIGGRAPH '19 Talks}{July 28 - August 01, 2019}{Los Angeles, CA, USA}
-%\acmDOI{10.1145/3306307.3328180}
-%\acmISBN{978-1-4503-6317-4/19/07}
-%\acmBooktitle{SIGGRAPH '19 Talks, 
-%  July 28 - August 01, 2019, Los Angeles, CA}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
+% Copyright
+\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+\doi{10.475/123_4}
+
+% ISBN
+\isbn{123-4567-24-567/08/06}
+
+%Conference
+\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+
+\acmPrice{\$15.00}
+
+%
+% --- Author Metadata here ---
+\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
+
 \title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
+%\subtitle{[Extended Abstract]
+%\titlenote{A full version of this paper is available as
+%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
+%\LaTeX$2_\epsilon$\ and BibTeX} at
+%\texttt{www.acm.org/eaddress.htm}}}
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Young-Woong Kwon, Jooyoung Kim and Kar-Ann Toh}
-%\authornote{Both authors contributed equally to this research.}
-\affiliation{%
-  \institution{School of Electrical and Electronic Engineering, Yonsei University}
-  \streetaddress{50 Yonsei-ro}
-  \city{Seodaemun-gu}
-  \state{Seoul}
-  \country{Korea}
-  \postcode{03722}
+\numberofauthors{1} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+%\alignauthor
+Young-Woong Kwon, Jooyoung Kim and Kar-Ann Toh\\
+       \affaddr{School of Electrical and Electronic Engineering}\\
+       \affaddr{Yonsei University}\\
+       \affaddr{Seoul, Korea}\\
+       %\email{trovato@corporation.com}
 }
-%\email{herokwon@yonsei.ac.kr}
+% There's nothing stopping you putting the seventh, eighth, etc.
+% author on the opening page (as the 'third row') but we ask,
+% for aesthetic reasons that you place these 'additional authors'
+% in the \additional authors block, viz.
+\date{1 October 2019}
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
 
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Y.Kwon, et al.}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
+\maketitle
 \begin{abstract}
@@
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
 \begin{CCSXML}
@@
 \ccsdesc[500]{Computing methodologies~Neural networks}
+%
+% End generated code
+%
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{Wi-Fi signature signal, in-air handwritten signature verification, the Kernel and the Range space projection learning, triplet network.}
+%
+%  Use this command to print the description
+%
+\printccsdesc
 
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-%\begin{teaserfigure}
-%  \includegraphics[width=\textwidth]{sampleteaser}
-%  \caption{Seattle Mariners at Spring Training, 2010.}
-%  \Description{Enjoying the baseball game from the third-base
-%  seats. Ichiro Suzuki preparing to bat.}
-%  \label{fig:teaser}
-%\end{teaserfigure}
+% We no longer use \terms command
+%\terms{Theory}
 
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
+%\keywords{ACM proceedings; \LaTeX; text tagging}
+\keywords{Wi-Fi signature signal; in-air handwritten signature verification; the Kernel and the Range space projection learning; triplet network}
 
@@
 
+% related works
 \section{Related works}
-
 \subsection{Triplet network}
@@
 % Figure 1
-\begin{figure*}[!ht]
+\begin{figure*}%[!ht]
+\centering
     \includegraphics[width=\textwidth]{fig1_tcnn_kar_v6}
@@
 \begin{table}
+\centering
     \caption{The network structure of KAR space learning.}
     \label{tab2}
-    \begin{tabular}{ccc}
-     \toprule
-     Layer   & Size     & Activation \\
-     \midrule
-     Input   & 500$\times$30$\times$6 &            \\
-     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
-     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
-     Output  & 1$\times$1$\times$50   &            \\
-     \bottomrule
+    \begin{tabular}{|c|c|c|} \hline
+     Layer   & Size     & Activation \\ \hline
+     Input   & 500$\times$30$\times$6 &            \\ \hline
+     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\ \hline
+     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\ \hline
+     Output  & 1$\times$1$\times$50   &            \\\hline
     \end{tabular}
@@
 \begin{table}
+\centering
     \caption{The structure of ConvNet model.
@@
     \label{tab1}
-    \begin{tabular}{cccc}
-     \toprule
-     Layer     & Activation & Kernel / Stride & Input Size \\
-     \midrule
-     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
-     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
-     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
-     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
-     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
-     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
-     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
-     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\
-     Concat    &            &                 & 1$\times$1$\times$16    \\
-     \bottomrule
+    \begin{tabular}{|c|c|c|c|} \hline
+     Layer     & Activation & Kernel / Stride & Input Size \\ \hline
+     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\ \hline
+     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\ \hline
+     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\ \hline
+     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\ \hline
+     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\ \hline
+     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\ \hline
+     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\ \hline
+     $L2$ Norm  &            &                 & 1$\times$1$\times$16    \\ \hline
+     Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
     \end{tabular}
@@
 \begin{table*}
+\centering
     \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
     \label{tab3}
-    \begin{tabular}{cccl}
-    \toprule
-    \multirow{2}{*}{Methology} & \multicolumn{2}{c}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\
-    \midrule
-    LSE                                    & 35.40 & 48.44           &                           \\ 
-    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\ 
-    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\ 
-    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\ 
-    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\
-    \midrule
-    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\ 
-    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\ 
-    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\
-    \bottomrule
+    \begin{tabular}{|c|c|c|l|} \hline
+    \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
+    LSE                                    & 35.40 & 48.44           &                           \\  \hline
+    PCA-LSE                                & 16.87 & 30.79           & Reduced dimension=40        \\  \hline
+    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\  \hline
+    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\  \hline
+    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\ \hline
+    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\  \hline
+    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\  \hline
+    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\ \hline
     \end{tabular}
@@
 % Figure 2,3
-\begin{figure}[!ht]
+\begin{figure}%[!ht]
+\centering
     \begin{center}
@@
 Our experiments on an in-house Wi-Fi handwritten signature dataset showed not only an encouraging verification accuracy but also a faster training loss convergence compared with the baseline triplet network and the Siamese network.
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
+%\end{document}  % This is where a 'short' article might terminate
+
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
 This research was supported by Basic Science Research
@@
 \noindent(NRF-2018R1D1A1A09081956)
-\end{acks}
 
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{bib_conf}
-%\bibliography{sample-base}
-
-\begin{table*}[]
-    \caption{Authors' background}
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    Your Name        & Title          & Research Field      & Personal website \\ \hline
-    Young-Woong Kwon & master student & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
-    Jooyoung Kim & Phd candidate & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
-    Kar-Ann Toh & full professor & Pattern Recognition & https://sites.google.com/site/machineintelligencelab/                \\ \hline
-    \end{tabular}
-\end{table*}
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{bib_conf}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
 
 \end{document}
-\endinput
-%%
-%% End of file `sample-sigconf.tex'.

### 2019-10-07 190904_Paper_Thesis/Conclusion.tex
paper_thesis:v0

@@
 \section{Conclusions}
-...
-
+In this paper, we proposed a system for identity verification from Wi-Fi in-air signature signals based on triplet network.
+Three-channel ConvNet structures was adopted in order to learn discriminative features from the in-air signatures.
+Moreover, we proposed a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
+Our experimental results on in-house Wi-Fi handwritten signature dataset showed the proposed network outperforms handcraft methods and Siamese network by improved verification accuracy and faster loss convergence.
+\iffalse
 \section{Future Works}
-...
 \begin{enumerate}
@@
 \end{enumerate} 
+\fi

### 2019-10-07 190904_Paper_Thesis/Introduction.tex
paper_thesis:v0

@@
 \begin{itemize}
-\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
-\item Adopted the kernel and the range (KAR) space learning to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
-\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
+\item A system to utilize Wi-Fi handwritten signature signals for identity verification is proposed. We used the deep triplet network to obtain the discriminative features in limited training dataset.
+\item In training of the triplet network, we propose hard triplet mining strategy using the kernel and range (KAR) space learning to faster the convergence speed.
+\item We propose an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 98 subjects.
 \end{itemize}
@@
 \section{Organization of Thesis}
-The paper is organized as follows: related works including the triplet network and KAR space learning are introduced in Section 2 for immediate reference.
-Our proposed method is discussed in Section 3.
-Section 4 describes our experimental results and analysis.
-Some concluding remarks are given in Section 5.
+The rest of this paper is organized as follows: Section 2 introduces the triplet network and the Kernel and Range space learning.
+Our proposed system is described in Section 3.
+In Section 4, experimental results is discussed.
+Conclusions and future works  are presented in Section 5.

### 2019-10-07 190904_Paper_Thesis/abstract.tex
paper_thesis:v0

@@
 	\begin{flushright}
-		Han-Cheol Moon\\
+		Young-Woong Kwon\\
 		School of Electrical and Electronic Engineering\\
@@
 
-...
+Identity verification using Wi-Fi in-air handwritten signature is a challenge task in signature verification since the shape of the signal varies according to the direction in which the signature is written.
+By using the handcraft features, it was difficult to verify identity from signatures entered in various directions.
+Moreover, the limited size of dataset also limited the training of deep learning models.
+In this paper, we propose a system for identity verification from Wi-Fi in-air signature signals based on triplet network.
+Three-channel ConvNet structures is adopted in order to learn discriminative features from the in-air signatures.
+Moreover, we propose a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
+Our experimental results on in-house Wi-Fi handwritten signature dataset shows the proposed network outperforms handcraft methods and Siamese network by improved verification accuracy and faster loss convergence.
 
@@
 \hrulefill\\
-{\bf Key words : Biometrics, Identification, In-Air Signature, Channel State Information, and
-	Wi-Fi}
+{\bf Key words : Biometrics, In-air handwritten signature verification, Wi-Fi Channel State Information, triplet network and the Kernel and Range space learning}
 \parbox[t]{0.8\textwidth}

### 2019-10-08 191001_Paper_BDML_v2/bdml_v2_R1.tex
paper_conf: v2_r1

--- 2019-10-01 191001_Paper_BDML_v2/bdml_v2.tex
@@
 \begin{abstract}
+Attributed to the omnipresence of the radio signals for communications, sensing and recognition utilizing the Wi-Fi signals has significant advantage  in terms of accessibility over conventional sensing means such as the camera.
+However, utilizing the raw Wi-Fi signals to capture in-air handwritten signatures for identity verification is yet a challenging task.
 In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
+A triplet network is adopted to learn the correlation between the captured signals and the user identities.
 To facilitate a fast converging loss model, a kernel and the range space learning is initially adopted for mining the triplet inputs. 
-       Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
-       Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
+Subsequently, the triplet network is trained on a ConvNet structure based on the mined triplet inputs. 
+Our experiments on a Wi-Fi dataset collected in-house show encouraging verification accuracy with faster training loss convergence comparing with that of the baseline triplet network and the Siamese network.
 \end{abstract}
@@
 \section{Introduction}
-Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}.
-Among these behavioral biometrics, the signature-based user authentication~\cite{fahmy2010online,sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic}.
-With the help of sensors such as the depth camera~\cite{jeon2012system,malik20183dairsig} or a mobile sensor~\cite{ketabdar2012magnetic}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic,sesa2012information}.
+Over recent years, several behavioral biometric traits have attracted attention in view of their rigid physical body independence.
+Among these behavioral biometrics, the signature-based user authentication~\cite{fahmy2010online,sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,malik20183dairsig,ketabdar2012magnetic,moon2017air}.
+With the help of sensors such as the depth camera~\cite{jeon2012system,malik20183dairsig} or a mobile sensor~\cite{ketabdar2012magnetic}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems~\cite{zhu2000biometric,jain2002line,sesa2012information}.
 
@@
 \item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
-\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
+\item Provision of an experimental study using Wi-Fi handwritten signature dataset which was collected in-house based on 50 subjects.
 \end{itemize}
@@
 % triplet network
-The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
-It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features.
+The triplet network is considered a metric learning based model which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
+It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,wang2016joint} where the individual identities are matched based on discriminative image features.
 The main difference between person identification and re-identification is that the later is a more challenging task where images of the same person taken from different cameras or under different occasions are to be associated.
@@
 These data triplets are constructed based on a combination of the input data.
-Since not all triplet samples contribute to the desired classification, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training.
+Since not all triplet samples contribute to the desired classification, recent attention has been paid to the choice of relevant input pairs for training.
 In order to optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplets from a small number of classes (persons) in each iteration.
-Recently, \cite{schroff2015facenet} adopted a triplet mining process to speed up the training convergence.
+In~\cite{schroff2015facenet}, a triplet mining process was implemented to speed up the training convergence.
 They utilized a large mini-batch at each training iteration and selected the triplets based on network training instead of random sampling.
@@
 This results in a heavy computational load in training.
-In order to make use of the small sample training size as well as to speed up the triplet training process, we adopt the kernel and range space method for the learning.
+In order to make use of the small sample training size as well as to speed up the triplet training process, we adopt the kernel and the range space method for the learning.
 
@@
 \end{equation}
-where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
+where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\\\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
 By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
@@
 The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network.
-For the $i^{th}$ network input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$, an anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set.
+For the $i^{th}$ network input $\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \\ \mathbf{x}_{neg,i}\}$, an anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set.
 The positive and negative samples (respectively $x_{pos,i}$ and $x_{neg,i}$) are then determined and being selected for training the ConvNet based on the feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$, for i=1,...,N.
@@
 For both cases, Wi-Fi signal measurements based on a single-orientation and 4-orientations of the user are recorded.
-For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA)~\cite{turk1991eigenfaces} with LSE, the support vector machine (SVM)~\cite{vapnik2013nature} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
+For Case I, existing handcraft methods such as the least squares error estimation (LSE)~\cite{duda2012pattern}, the principal components analysis (PCA)~\cite{turk1991eigenfaces} with LSE, the support vector machine (SVM)~\cite{boser1992training} with different kernel functions, the total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese}, and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking.
 The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.
@@
     \label{tab2}
-    \begin{tabular}{|c|c|c|} \hline
+    \begin{tabular}{|l|l|l|} \hline
      Layer   & Size     & Activation \\ \hline
@@
     \label{tab1}
-    \begin{tabular}{|c|c|c|c|} \hline
+    \begin{tabular}{|l|l|l|l|} \hline
      Layer     & Activation & Kernel / Stride & Input Size \\ \hline
@@
     \label{tab3}
-    \begin{tabular}{|c|c|c|l|} \hline
+    \begin{tabular}{|l|c|c|l|} \hline
     \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
@@
 (NRF) funded by the Ministry of Education, Science and
-Technology.
+Technology (NRF-2018R1D1A1A09081956).
 
-\noindent(NRF-2018R1D1A1A09081956)
+%\noindent(NRF-2018R1D1A1A09081956)
 
@@
 % produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
+%\bibliographystyle{abbrv}
+\bibliographystyle{unsrt}
 \bibliography{bib_conf}  % sigproc.bib is the name of the Bibliography in this case

### 2019-10-14 191001_Paper_BDML_v2/bdml_v2_R1.tex
DIP_A2

@@
 \begin{document}
-
+%noindent all
+\setlength\parindent{0pt}
 % Copyright
@@
 %\alignauthor
-Young-Woong Kwon, Jooyoung Kim and Kar-Ann Toh\\
+Young-Woong Kwon, Jooyoung Kim, and Kar-Ann Toh\\
        \affaddr{School of Electrical and Electronic Engineering}\\
@@
 To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs.
-Subsequently, the triplet network which utilizes the ConvNet structure as a feature extractor is trained based on the $L2$ distance comparison.
+Subsequently, the triplet network which utilizes the ConvNet~\cite{lecun1998gradient} structure as a feature extractor is trained based on the $L2$ distance comparison.
 
@@
 \item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
-\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
-\item Provision of an experimental study using Wi-Fi handwritten signature dataset which was collected in-house based on 50 subjects.
+\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in the triplet network.
+\item Provision of an experimental study using a Wi-Fi handwritten signature dataset which was collected in-house based on 50 subjects.
 \end{itemize}
@@
 Some concluding remarks are given in Section 5.
+
+\clearpage
 
@@
 Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient}.
-The learning method is grounded on linear algebra with neither learning parameters nor iteration is needed in training.
+The learning method is grounded on linear algebra without needing any training iteration.
 
@@
 Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network output.
-Then the multilayer neural network can be written in equation form as follows:
+Then the multilayer neural network can be written as follows:
+\begingroup\makeatletter\def\f@size{8}\check@mathfonts
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\\\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$ are the network weight matrices, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ is the bias vector, and $\sigma(.)$ is the activation function.
+\endgroup
+where
+\begin{tiny}
+$\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$
+\end{tiny}
+are the network weight matrices,
+$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$
+ is the bias vector, and $\sigma(.)$ is the activation function.
 By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
+\begingroup\makeatletter\def\f@size{8}\check@mathfonts
 \begin{IEEEeqnarray}{rCl}
@@
 \end{IEEEeqnarray}
-
+\endgroup
 %% Methods
@@
 Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for mining the triplet inputs.
-Essentially, the KAR space projection learning is utilized to learn the triplet input data by mining the hard positive and the hard negative samples from each of the given anchor sample (see item (a) in Fig.~\ref{fig1}).
+Essentially, the KAR space projection learning is utilized to learn the triplet input data by mining those hard positive and the hard negative samples from each of the given anchor sample (see item (a) in Fig.~\ref{fig1}).
 The hard positive and the hard negative samples refer to positive and negative class samples which are likely to be misclassified by the network.
@@
 
-By training the network with the single shot KAR space learning, we can map the $L2$ distance between every sample by using the output vector of the KAR space network.
+By training the network with the single shot KAR space learning, we can map the $L2$ distance among the samples by using the output vector of the KAR space network.
 Given a set of training data which is packed in matrix $\mathbf{X}$, the network output can be written as:
+\begingroup\makeatletter\def\f@size{8}\check@mathfonts
 \begin{equation}
@@
 \end{equation}
+\endgroup
 After training based on the KAR space projection, the given anchor sample $\mathbf{x}_{anc}$ can be used as the reference to decide whether the network output of a sample is far away from this anchor sample.
@@
 The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, 256\}$, with fixed filter size of $3\times3$, each of stride 1.
-The Rectiﬁed Linear (ReLU) activation function and the Max-pooling layer are applied between each convolutional layer.
+The Rectified Linear (ReLU) activation function and the Max-pooling layer are applied between each convolutional layer.
 Subsequently, the extracted features from the last convolutional layer are flattened into a vector before feeding into the fully-connected network.
@@
 For the $i^{th}$ network input $\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \\ \mathbf{x}_{neg,i}\}$, an anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set.
-The positive and negative samples (respectively $x_{pos,i}$ and $x_{neg,i}$) are then determined and being selected for training the ConvNet based on the feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$, for i=1,...,N.
+The positive and negative samples (respectively $\mathbf{x}_{pos,i}$ and $\mathbf{x}_{neg,i}$) are then determined and being selected for training the ConvNet based on the feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$, for i=1,...,N.
 The triplet loss function is formulated based on a summation of the difference between the positive distance (the $L2$ distance between the anchor vector and the positive vector) and the negative distance (the $L2$ distance between the anchor vector and the negative vector) as follows:
+\begin{scriptsize}
 \begin{equation}
@@
 \end{equation}
+\end{scriptsize}
 where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the $L2$ distance and $\alpha$ denotes the preset margin.
@@
 \subsubsection{Performance evaluation:}
-The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve.
+The proposed system is evaluated under two cases: Case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification error rate.
+Case II on comparing between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve.
 For both cases, Wi-Fi signal measurements based on a single-orientation and 4-orientations of the user are recorded.
@@
 The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}.
-With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively.
-Each layer is initialized with uniform distribution over [0, 1).
+The weights of each layer have been initialized with values of uniform distribution in [0, 1).
 We used $\sigma = {tan}^{-1}$ as the activation function following \cite{toh2018analytic}.
@@
 \begin{table}
+\begin{small}
 \centering
@@
     \begin{tabular}{|l|l|l|l|} \hline
-     Layer     & Activation & Kernel / Stride & Input Size \\ \hline
+     Layer     & Activation & Kernel/Stride & Input Size \\ \hline
      Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\ \hline
@@
     \end{tabular}
+\end{small}
 \end{table}
@@
 Case I: Table~\ref{tab3} shows the average of EER performance from five runs of two-fold cross-validation tests under the optimal parameter setting.
-For 1-orientation inputs, SVM showed the best verification accuracy of 1.55\% EER.
-However, For 4-orientation inputs, all three deep learning-based methods showed better performance than hand-craft methods.
+For 1-orientation inputs, the SVM with Linear kernel shows the best verification accuracy of 1.55\% EER.
+However, For 4-orientation inputs, all three deep learning-based methods show better performance than hand-craft methods.
 This is, perhaps, due to the utilization of the original size (500$\times$30$\times$6) of the input data in the training stage for the deep learning based methods.
@@
 \centering
-    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation tests.}
+    \caption{Performance in terms of EER (\%) averaged from five runs of two-fold cross-validation tests.}
     \label{tab3}
     \begin{tabular}{|l|c|c|l|} \hline
-    \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Best EER (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
+    \multirow{2}{*}{Methology} & \multicolumn{2}{|c|}{Equal Error Rate (\%)} & \multirow{2}{*}{Parameter setting} \\ \cline{2-3}           & 1-orientation & 4-orientation     &    \\ \hline
     LSE                                    & 35.40 & 48.44           &                           \\  \hline
@@
     \begin{center}
-    \subfigure[][ROC Curve]{
-        \includegraphics[height=6.4cm]{fig_roc_v14.eps}}
-    \subfigure[][Normalized training loss curve]{
-        \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
+    \subfigure[][ROC Curves]{
+        \includegraphics[height=6.4cm]{fig_roc_v15.eps}}
+    \subfigure[][Normalized training loss trends]{
+        \includegraphics[height=6.4cm]{Normalized_loss_curve_ma30_v2.eps}}
     \caption{(a) Receiver Operating Characteristic (ROC) Curves and 
-    (b) normalized training loss trends}
+    (b) Normalized training loss trends}
     \label{fig2}
@@
 
+\newpage
+
 \section{Conclusion}
 In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
-The kernel and the range space learning was adopted for mining the triplet inputs for fast loss convergence. 
-Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on the $L2$ distance comparison. 
+A triplet network adopting the ConvNet structure was used to learn the Wi-Fi information.
+In order to facilitate a fast training convergence, the inputs were first mined by a recent kernel and range space learning for samples which were likely to be misclassified.
+Subsequently, the network was trained with the mined triplet inputs based on the $L2$ distance comparison. 
 Our experiments on an in-house Wi-Fi handwritten signature dataset showed not only an encouraging verification accuracy but also a faster training loss convergence compared with the baseline triplet network and the Siamese network.

### 2019-10-14 191014_DIP_A2/PiecewiseLinearTr.m

@@ -1,0 +1,17 @@
+function output = PiecewiseLinearTr(input,a,b) %
+% PiecewiseLinearTr(IM,A,B) applies a piecewise linear transformation to the pixel values
+% of the input image INPUT, where A and B are vectors containing the x and y coordinates
+% of the ends of the line segments. INPUT can be of type DOUBLE,
+% and the values in A and B must be between 0 and 1 (normalized intensity values). %
+% For example:
+%
+% PiecewiseLinearTr(x,[0,1],[1,0])
+%
+% simply do negative transform inverting the pixel values.
+%
+
+if length(a) ~= length (b)
+    error('Vectors A and B must be of equal size');
+end
+
+% Complete the remaining part

### 2019-10-16 191014_DIP_A2/GaussianFilter.m
DIP_A2: question 1

@@ -1,0 +1,22 @@
+function output = GaussianFilter (I,SIGMA) %
+% where I is and Gaussian noise images(std : 7,12,17),, SIGMA is standard deviation of Gaussian function 
+% Each dimension of filter is determined automatically by 2*ceil(2*sigma)+1
+
+% filter dimension
+G_len = 2*ceil(2*SIGMA)+1;
+% make zero matrix corresponding to filter size
+G_mat = zeros(G_len,G_len);
+% x,y range
+range = linspace(-G_len/2,G_len/2,G_len);
+% calculate filter matrix values
+for x = 1:G_len
+    for y = 1:G_len
+        % Gaussian distribution
+        G_sigma =   1./(2*pi*SIGMA*SIGMA).*exp(-1 .* (range(x)*range(x) + range(y)*range(y))./(2*SIGMA*SIGMA));
+        G_mat(x,y) = G_sigma;
+    end
+end
+% return filter matrix
+output = G_mat;
+
+% Complete the remaining part

### 2019-10-16 191014_DIP_A2/GaussianNoise.m

@@ -1,0 +1,5 @@
+function output = GaussianNoise (I,SIGMA) %
+% random number from SIGMA std Gaussian distrubution
+output = I + SIGMA.*randn(size(I));
+end 
+

### 2019-10-16 191014_DIP_A2/BilateralFilter.m
DIP_A2: question 2

@@ -1,0 +1,32 @@
+function output = BilateralFilter (I,SIGMA_d, SIGMA_r, kernel_size) %
+% where I is and Gaussian noise images(std : 7,12,17), SIGMA_d and SIGMA_r are standard deviations of Bilateral function. Kernel size n is nxn box.
+
+%padding
+pad_len = floor(kernel_size/2);
+I_pad = padarray(I, [pad_len pad_len]);
+% size of padded image
+shape_pad = size(I_pad);
+% calculate Gaussian bilateral filter function
+I_b = zeros(size(I));
+% padded image
+for r_I = 1+pad_len : shape_pad(1)-pad_len
+    for c_I = 1+pad_len : shape_pad(2)-pad_len
+        W_p = 0;
+        I_p = 0;
+        % kernel
+        for r_k = r_I-pad_len:r_I+pad_len
+            for c_k = c_I-pad_len:c_I+pad_len
+                % calculate w value
+                w = exp(-1*((r_I-r_k)^2+(c_I-c_k)^2) / (2*(SIGMA_d^2)) - ((I_pad(r_I,c_I)-I_pad(r_k,c_k))^2 / (2*(SIGMA_r^2))));
+                % sum w values in the kernel
+                W_p = W_p + w;
+                I_p = I_p + I_pad(r_k,c_k)*w;
+            end
+        end
+        I_b(r_I-pad_len,c_I-pad_len) = I_p / W_p;
+    end
+end
+% return
+output = I_b;
+end 
+

### 2019-10-16 191014_DIP_A2/hw2_1.m

@@ -1,45 +1,57 @@
+% image read
 im = im2double(imread('input1.jpg'));
+% adjust intensity to max 255
 im = im(:,:,1) .* 255;
 
+% parameters
 std_list=[7, 12, 17];
 filter_list = [1, 3, 5];
 
+% 1. add Gaussian noise
 figure(1);
 subplot(2,2,1);
 imshow(im ./ 255);
 title('input image');
 im_Trs = cell(3,1);
+% calculate noise
 for i = 1:length(std_list)
     im_Tr = GaussianNoise(im, std_list(i));
+    % store image matrix
     im_Trs{i} = im_Tr;
     subplot(2,2,i+1);
+    % show image correspoiding to std value
     imshow(im_Tr ./ 255);
     title(['Noise: std = ',num2str(std_list(i))]);
 end
 
+% 2. make Gaussian filter
 figure(2);
 g_filters = cell(3,1);
 for i = 1:length(filter_list)
     g_filter = GaussianFilter(im,filter_list(i));
     g_filters{i} = g_filter;
+    % plot filter matrix
     subplot(2,2,i);
+    % normalize intensity for visualization
     imshow(g_filter,[min(min(g_filter)),max(max(g_filter))]);
     title(['Filter: std = ',num2str(filter_list(i))]);
 end
 
-
-
+% 3. filter noisy images
 for i = 1:length(std_list)
     im_Tr = im_Trs{i};
-    
+    % plot noisy image
     figure(2+i);
     subplot(2,2,1);
     imshow(im_Tr ./ 255);
     title(['Noise: std = ',num2str(std_list(i))]);
     for j = 1:length(filter_list)
         g_filter = g_filters{j};
+        % apply filter using convolution function
+        % padding = 'same' for set output size = input size
         w = conv2(im_Tr,g_filter,'same');
         
+        % plot filtered image
         subplot(2,2,j+1);
         imshow(w ./ 255);
         title(['Filter: std = ',num2str(filter_list(j))]);

### 2019-10-17 191014_DIP_A2/MedianFilter.m
DIP_A2: hw2_4

@@ -1,0 +1,20 @@
+function output = MedianFilter (I, kernel_size) %
+% where I is and input image, and kernel_size n is nxn size of the filter
+
+%padding
+pad_len = floor(kernel_size/2);
+I_pad = padarray(I, [pad_len pad_len]);
+% size of padded image
+shape_pad = size(I_pad);
+% make kernel function
+for r_I = 1+pad_len : shape_pad(1)-pad_len
+    for c_I = 1+pad_len : shape_pad(2)-pad_len
+        % get values in the filter
+        k_values = I_pad(r_I-pad_len:r_I+pad_len,c_I-pad_len:c_I+pad_len);
+        % input median value to padded image
+        I_pad(r_I,c_I) = median(median(k_values));
+    end
+end 
+% return
+output = I_pad;
+% Complete the remaining part

### 2019-10-17 191014_DIP_A2/hw2_3.m

@@ -1,0 +1,44 @@
+% image read
+im = im2double(imread('input1.jpg'));
+% adjust intensity to max 255
+im = im(:,:,1) .* 255;
+
+% parameters
+noise_list=[0.1, 0.2, 0.3, 0.4, 0.5];
+filter_list = [3, 5, 7];
+
+% 1. add Salt&Pepper noise
+figure(1);
+subplot(2,3,1);
+imshow(im ./ 255);
+title('input image');
+im_Trs = cell(length(noise_list),1);
+% calculate noise
+for i = 1:length(noise_list)
+    im_Tr = SaltAndPepper(im, noise_list(i));
+    % store image matrix
+    im_Trs{i} = im_Tr;
+    subplot(2,3,i+1);
+    % show image correspoiding to noise value
+    imshow(im_Tr ./ 255);
+    title(['ND : ',num2str(noise_list(i))]);
+end
+
+% 2. filter noisy images
+for i = 1:length(noise_list)
+    im_Tr = im_Trs{i};
+    % plot noisy image
+    figure(1+i);
+    subplot(2,2,1);
+    imshow(im_Tr ./ 255);
+    title(['ND : ',num2str(noise_list(i))]);
+    
+    for j = 1:length(filter_list)
+        % apply filter
+        im_m = MedianFilter(im,filter_list(j));
+        % plot filtered image
+        subplot(2,2,j+1);
+        imshow(im_m ./ 255);
+        title(['ND : ',num2str(noise_list(i)),' / Filter : [',num2str(filter_list(j)),',',num2str(filter_list(j)),']']);
+    end
+end

### 2019-10-17 191016_Paper_Thesis_v2/Experiments.tex
thesis_v1

\label{chp:Experiments}
\section{Data set}
\label{sec:Dataset}
The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was used to test the proposed system. These dataset contained 10 signatures made by 98 people in each direction for a total of 980 signatures made in each direction. The size of each sample had a data resolution of 500 x 30 x 6.

\section{Experimental Parameters}
%performance
The proposed method's performance, convergence speed, and degradation were compared to those of other traditional methods.
To compare the proposed method's feature extraction performance to that of traditional and deep-learning based methods, feature space was visualized as a 2D Euclidean plane using principal component analysis ("PCA"). 
% handcraft
The proposed method's and traditional methods and deep-learning based methods.
For handcraft methods' least square estimations ("LSE")~\cite{duda2012pattern}, PCA with LSE~\cite{turk1991eigenfaces}, support vector machine~\cite{vapnik2013nature} and the total error minimization with reduced multivariate polynomials~\cite{toh2003fingerprint,toh2008between} were compared. Parameters were selected that performed optimally in each traditional method. For LSE,SVM, and TER, the input signatures were reduced to 500$\times$30 by averaging the subcarrier axis. For PCA-LSE, the input signature dimension was reduced to 40 following~\cite{moon2017air}. For SVM with a Gaussian kernel function ("RBF"), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$. For TER, the parameter M was chosen from among $M\in\{1,2,3\}$ and $\tau=\eta=0.5$ following~\cite{toh2008between}.
For comparison with deep-learning based methods, Siamese network~\cite{koch2015siamese} and baseline triplet network~\cite{hoffer2015deep} were used.
The proposed method was compared to Siamese networks~\cite{koch2015siamese} and baseline triplet networks~\cite{hoffer2015deep} as deep learning based methods.
%protocols
Verification performance was evaluated in terms of the equal error rate ("EER"). Random five-runs of two-fold cross-validation tests were conducted.
Due to hardware memory limitations, the number of negative pairs used was reduced to the number of positive data pairs used for calculating the EER for a total of 18,620 pairs.
% KAR structure
The structure of the KAR learning MLP sub-networks in the proposed system is shown in~\ref{kar_structure}. The two layers' sizes were set to 1,024 and 16. The size of the second layer was equal to the number of feature vectors of the proposed ConvNet. The weights in the layers were initialized in a normal distribution between 0 and 1 before training.
$tan^{-1}$ was used as an active function following~\cite{toh2018analytic}.
\begin{table}[]
    \caption{KAR space learning network structure.}
    \label{kar_structure}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation Function \\ \hline
    Input   & 500$\times$30$\times$6 &            \\
    Fully-connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
    Fully-connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
    Output  & 1$\times$1$\times$50   &            \\ \hline
    \end{tabular}
\end{table}
% conv structure
The same ConvNet structure shown in~\ref{conv_structure} and parameters were used for the proposed and deep learning based methods. The CovNet structure consisted of three 3$\times$3 convolution filters and stride one. A ReLU activation function and 2$\times$2 max-pooling layers were applied between the filters. The depth of each layer was set to \{64,128,256\}. The output layer with sigmoid activation was regularized according to $L2$ with a penalty of 0.0001. The size of the final feature vectors was 16.
\begin{table}[]
    \caption{ConvNet model structuer.}
    \label{conv_structure}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation Function & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
    Fully-connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}
% traning parameters
The deep learing network was trained with a learning rate of 0.0005, 3,000 iteration, and a mini-batch size of 32. The Adam optimizer was used to calculate the loss function. The ConvNet structures were initialized before training following~\cite{koch2015siamese}. The convolution filters used a normal distribution with a mean of 0 and a standard deviation of 0.0001. The biases used normal distribution with a mean of 0.5 and a standard deviation of 0.01. Triplet loss was calculated with an alpha value of 0.5.

%5.3. Experimental results
\section{Experimental Results}
%5.3.1. verification performance
\subsection{Performance}
\ref{tab_performance} shows the average EER from the first experiment generated by five-runs of two-fold cross-validation tests under optimal parameter settings. The proposed method had an EER of 19.35\%, out-performing both the traditional and deep learning based methods (Table~\ref{tab_performance}).
Deep learning based methods out-performed the traditional methods because they utilized the entire input signal and had better feature extraction abilities.
\begin{table}[!h]
    \caption{Average EER of five-runs of two-fold cross-validation tests.}\label{tab_performance}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methodology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}

%roc
The proposed method had the widest area under the receiver operating characteristic ("ROC") curve (Fig.~\ref{fig_roc}).
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
    \caption{Normalized training loss curve.} \label{fig_roc}
\end{figure*}
 %5.3.1. conv speed
\subsection{Convergence Speed}
Fig.~\ref{fig_loss} shows the convergence of the normalized loss function during training. The proposed method had a faster convergence speed than the deep learning based methods, indicating that KAR learning accelerated the learning speed.
 \begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v3.eps}
    \caption{normalized training loss trends} \label{fig_loss}
\end{figure*}
%5.3.2. feature vector
\subsection{Feature Vector Size Effect}
Fig.~\ref{fclayer} shows the EERs for different sizes of feature vectors in the feature space. 
For metric learning systems, feature vector size is generally positively correlated with system performance.
The proposed system's performance was negatively correlated with feature vector size.
\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Feature vector size        & 16    & 8     & 4     & 2     \\ \hline
    Siamese network            & 20.34 & 22.05 & 29.39 & 34.26 \\ \hline
    Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
    Proposed method            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
    \end{tabular}
\end{table}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fclayer_v1.eps}
    \caption{Feature Vector Size Effect.} \label{fclayer}
\end{figure}
%5.3.3. 2D visualization of feature vector
\subsection{2D Visualization of the Feature Vectors}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_triKAR_10_v1.eps}
    \caption{2D Feature Representation : Proposed System.} \label{fig_2d_triKAR_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_tribase_10_v1.eps}
    \caption{2D Feature Representation : Baseline triplet network.} \label{fig_2d_tribase_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_siam_10_v1.eps}
    \caption{2D Feature Representation : Siamese network.} \label{fig_2d_siam_10}
\end{figure}
To visualize the proposed system's feature extraction performance, the feature space was projecgted onto two-dimensional Euclidean space using PCA (Figs.~\ref{fig_2d_siam_10},~\ref{fig_2d_triKAR_10}, and~\ref{fig_2d_tribase_10}). each system's feature extraction performance by determining whether proximate points shared the same identity. Only the first 10 identities were visualized to facilitate the visual confirmation process.
The proposed method used the space most efficiently. The Siamese network linearly arranged feature vectors, making it difficult to distinguish between classes. The baseline triplet network caused many identities to overlap.

### 2019-10-17 191016_Paper_Thesis_v2/Introduction.tex
thesis_v1

\section{Background}
% signature
Written signatures have long been used as an identification tool and various methods for verifying individuals base on them have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
% biometric
The use of biometric identity verification is growing with the popularity of mobile devices. Biometric identity verification systems are more secure, convinient, and provide greater accountability than traditional complex passwords~\cite{hutton2004biometrics}.
% camera sensor
In-air signatures have become possible with the development of specialized sensors, such as depth cameras and magnetic sensors~\cite{bailador2011analysis, jeon2012system,ketabdar2012magnetic,malik20183dairsig}.
% WiFI CSI
In-air signatures can be made using Wi-fi Channel State Information ("CSI") signals. Typically people make a certain gesture when signing their signature on a piece of paper. With in-air signatures, people simply make the same gesture in the air. Their movements are detected by Wi-fi receivers with appropriate software installed. The software detects changes in the Wi-fi signals caused by hand movements. This technique uses widespread devices, so it does not require the use of any special input devices. 
\cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to recognize users' gestures and~\cite{moon2017air} used them to specifically identify signatures written in the air. 
However, due to limitations of the traditional feature extractor,~\cite{moon2017air} was only able to identify in-air signatures entering from the specific direction. This makes the user difficult to input their signatures.
% Deep learning
Recent studies have been conducted on the feasibility of using deep learning technology to characterize CSI signals. Deep learning-based models are popular often studied as solutions to this situaiton because of their automated feature extractors and the fact that they have superior classification capabilities than traditional models. Deep learning has been used to recognize users based on their body shape~\cite{pokkunuru2018neuralwave} and behavior~\cite{shi2017smart}.
% our methods
In this thesis, deep learning technology was used to create a Wi-Fi CSI system that can recognize a user's identity with multi-direction in-air signatures.
The deep learning model tested in this study used a triplet network to increase classification and feature extraction accuracy, and to improve the model's convergence speed using the kernel and range space learning techniques~\cite{toh2018gradient}.

%\newpage
\newpage
\section{Motivation and Contributions}
The main contributions of this thesis were
\begin{itemize}
\item Proposing a system to verify user identities using Wi-Fi handwritten signature signals using a deep triplet network;
\item Using the kernel and range (KAR) space learning to mine distinctive triplet inputs which boost convergence speed and reduce triplet network training loss; and
\item Empirically testing the proposed system on a dataset of Wi-Fi handwritten signatures collected from 98 subjects.
\end{itemize}

\section{Paper Organization}
The rest of this paper is organized as follows.  Section 2 discusses related works about triplet networks and KAR space learning. Section 3 discusses the proposed system. Section 4 describes this thesis's experimental and analysis results. Section 5 concludes the thesis.

### 2019-10-17 191016_Paper_Thesis_v2/Literature_Survey.tex
thesis_v1

--- 2019-05-17 190410_Paper_ACPR/paper_v1.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+\label{chp:Survey}
 
-\begin{document}
-%
-\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{YoungWoong KWON\inst{1} \and
-JooYoung KIM\inst{1} \and
-Kar-Ann TOH\inst{1}}
-%
-\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Yonsei University \and
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-15--250 words.
-
-\keywords{First keyword  \and Second keyword \and Another keyword.}
-\end{abstract}
-%
-%
-%
-\section{Introduction}
-
-\subsection{Motivation}
-i. Pros of In-Air WIFI CSI signature system
-1) Cheap: Use commercial device
-2) Easy: No additional devices is needed
-3) Secure: Hard to forgery
-ii. Cons of In-Air WIFI CSI signature system
-1) Setting direction problem
-a) Different direction -> Different feature is needed
-b) Hard to set exactly same direction as authentication before
-Size of signature can varies
-
-\subsection{Contribution}
-- Overcome cons of WIFI signature systems
-- Robust to signal direction, size
-
-\section{Related Works}
-
-\subsection{ConvNets}
+\section{ConvNets}
 % description of convnet
@@
 Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
-%
 
-\subsection{Siamese Networks}
-
-% description of siamese net
-In \cite{bromley1994signature}, LeCun et al. Introduced Siamese nets as parts of their handwritten signature verification system. 
-A siamese neural network consists of twin networks which accept distinct inputs but are joined by an energy function at the top.\cite{koch2015siamese}
-% differences in feature extractor
-They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector.
-
-\section{Proposed System}
-
-\subsection{System Overview}
-
-%system overview
-
-In this section, we propose a direction-free identify verification system based on the Wi-Fi based in-air handwritten signature which utilizes the Siamese network learning.
-\iffalse
-An overview of the proposed system is shown in Fig.1.
-% Figure 1
-\begin{figure}
-    \includegraphics[width=\textwidth]{methods1.eps}
-    \caption{Overview of the proposed system} \label{method1}
-\end{figure}
-\fi
-Essentially, we train the verification model to identify the input pairs according to the probability on whether they belong to the same class or different classes.\cite{koch2015siamese} Subsequently, the
-
-\iffalse
-% main purpose2: direction free
-Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
-\fi
-
-Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
-To classify regardless of the direction of the signal, we focused on the model shall be capable of extracting features unrelated to the direction.
-
-%% Pre-processing
-\subsection{Data Preprocessing}
-
-In order to be used as an input to a siamese network, the signal must be pre-processed.
-
-% used only abs value
-First, the signal has to be converted to non-complex form.
-Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.
-
-% preprocessing
-% From HC's Papaer
-Second, all inputs must be arranged of the same size.
-Since all signals have different length, the gradient operation with respect to the time instance is adapted to measure the short time energy. 
-Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
-And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}% HC's end
-
-% Methods
-
-\subsection{Siamese Network For Verification}
-
-% Functions of Siamese in our system
-% Introduce Siamese Net
-
-Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
-\cite{koch2015siamese}
-
-Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
-The model outputs the probability that the two signals are of the same class.
-%it is learned by the back-propagation.
-This network consists of feature extraction and feature matching part.
-
-% Section: Feature Extraction
-\subsubsection{Feature Extraction}
-
-% structure of siamese network
-To perform the feature extraction, we first need to have convolutional neural networks to serve as the feature extractor
-Based on the ConvNet structure.\cite{lecun1998gradient}
-
-% structure of siamese network
-When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
-%Symmetric Architecture
-Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that help to classify signatures.
-some may be heavily influenced by the direction in which the signature was entered.
-Structure of the network is shown in Fig.2.
-% Figure 2
-\begin{figure}
-    \includegraphics[width=\textwidth]{network2.eps}
-    \caption{Structure of Siamese network} \label{network2}
-\end{figure}
-% weight tying
-We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
-To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
-It was also designed to have the same weight on the symmetrical CNN network.
-
-% sister networks
-This feature extractor is composed of two sister network, which are identical ConvNets with the exact same weights
-
-% CNN: purpose
-Purpose of ConvNet in our model is to extract a feature vector from the CSI signal.
-
-% parameters of convnet
-this ConvNets are consists of a number of consecutive convolution layers with active functions, and a pooling layer in the end.
-the Convolution Layer has n convolution filters in it.
-
-% functions of convnet
-Their weights are tied to extract the same characteristics from signals in different directions.
-By sharing their feature map, this ConvNet is trained to learn characteristics regardless of the direction.
-
-% outputs feature vector
-Through a convolution filter, each CSI signal is transformed into a feature vector. this entire process is jointly optimized by backpropagation.
-
-\subsubsection{Feature Matching}
-
-% Use L1 distances of Feature vector of 2 input images
-% From HC's In-Air paper below:
-Let $\mathbf{m}\in{\mathrm{R}}^{d\times1}$ and $\mathbf{n}\in{\mathrm{R}}^{d\times1}$ be feature vectors extracted from two samples.
-The L-1 distance between the two features can be calculated as  follows:
-Where $\mathbf{p}$ denotes the L-1 distance. In the Siamese networks, this L-1 distance is utilized to match between two feature vectors.
-
-% From HC's End
-% From Oneshot paper below
-\begin{equation}
-    \mathbf{p} = 
-    \sigma(\sum_j\alpha_{j}\mid
-    \mathbf{m}_{1,L-1}^{(j)} - 
-    \mathbf{n}_{1,L-1}^{(j)}\mid)  
-\end{equation}
-where σ is the sigmoidal
-activation function.
-This final layer induces a metric on the learned feature space of the (L − 1)th hidden layer and scores the similarity between the two feature vectors.
-The αj are additional parameters that are learned by the model during training, weighting the importance of the component-wise distance.
-This defines a final Lth fully-connected layer for the network which joins the two Siamese twins.
-% From oneshot end
-
-The output of the CNN is feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
-In the proposed system, this Euclidean distance is utilized to match between two feature vectors.
-
-\section{Experiments}
-% Dataset
-\subsubsection{Dataset}
- To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
- % description
- we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).
-
-% network shape
-
-% network parameters
-
-% Network Learning
-\subsubsection{Loss and Backpropagation}
- We impose a regularized cross-entropy objective on our binary classifier.
-This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
- We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2.
-Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
-
-\section{Conclusion}
-
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-%\bibliographystyle{splncs04}
-%\bibliography{mybibliography}
-%
-
-%\begin{thebibliography}{8}
-
-\bibliographystyle{splncs04}
-\bibliography{bib_acpr}
-
-%\end{thebibliography}
-
-\end{document}
-
-% old parts
-
-% Meaning of CSI
-%[From Halperin paper]
+%3.3. CSI
+\section{Wi-FI Channel State Information}
 CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
-It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
+It runs on a commodity 802.11n NIC and records Channel State Information (CSI based on the 802.11 standard.
 The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
 %[From Halperin End]
-
-% Structure of CSI
-%[From HC's ELM paper]
+% Structure of CSI %[From HC's ELM paper]
 In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
-$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively.
-The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix.
-The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
+$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively. The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix. The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
 \begin{equation}
@@
 %[From HC's ELM end]
-
-% description of siamese
-In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
-% advantages of using Convnet filter
-Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
-The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.

### 2019-10-17 191016_Paper_Thesis_v2/Proposed_Method.tex
thesis_v1

\label{chp:Method}
% 4.2. Data Acquisition
\section{Preprocessing}
\label{sec:preprocessing}
Wi-Fi signature data must be pre-processed to be used as an input in the proposed system.
First, data must be simplified. In this study, only the magnitude of the complex signal was utilized due to device firmware issues with the phase value of the 2.4Ghz Wi-Fi signal~\cite{wang2015understanding}.
Second, the data must be made to be the same size. All signals have different lengths, so equal length sampling was used to ensure that all data had the same length.
Third, outliers must be addressed. Wi-Fi signals are interrupted by other electromagnetic radiation of which burst noise~\cite{wang2015understanding} can have significant effects. Thus, only data within one standard deviation of the median were analyzed to minimize the effects of burst noise.
% 4.3. Proposed Methodology
\section{Proposed Methodology}
\label{sec:methodology}
%purpose
This thesis proposed an identity verification system based on the Wi-Fi signals produced by in-air handwritten signatures ("Wi-Fi signature"). 
%function
Triplet networks which utilized ConvNet as the feature extractor were used to learn the direction-invariant deep representations of in-air signatures~\cite{hoffer2015deep}. KAR space learning was used to mine triplet inputs to achieve faster loss convergence~\cite{toh2018learning,toh2018gradient}. 
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_system_overview_v1.pdf}
    \caption{An overview of the proposed methodology.} \label{fig1}
\end{figure*}
Figure~\ref{fig1} shows an overview of the proposed system. 
KAR space projection learning is used to mine hard samples from the training dataset to create triplets (Fig.~\ref{fig1}(a)). The anchor sample is randomly selected from the training dataset. The hard samples are those which are likely to be misclassified by the triplet network for a given anchor sample.
After the data is selected, the triplet network (Fig.~\ref{fig1}(b)) is trained based on the network output vector distance comparison (Fig.~\ref{fig1}(c)).
% following~
The following subsections discuss the triplet network architecture, triplet loss, and triplet mining using KAR space learning.

% 4.4.1. Triplet loss
\subsection{Triplet Loss}
% purpose
Triplet loss~\cite{hoffer2015deep} trains the ConvNet structure to learn the features that define data position in the feature space.
% Triplet input
Triplet inputs are composed of a combination of three samples, an anchor sample $x_0$, a positive sample $x_+$ and a negative sample $x_-$. The anchor sample, the reference for the triplet input, is selected from the training data set. The positive sample has the same identity as the anchor sample while the negative sample has a different identity.
% function
$dist\{f(x_0),f(x_+)\}$, the distance between the feature vectors of anchor $f(x_0)$ and positive sample $f(x_+)$ is larger than $dist\{f(x_0),f(x_-)\}$, the distance between feature vectors of the anchor and the negative sample plus a preset margin $\alpha$ to produce discriminative feature vectors. 
The distance measurement function is:
\begin{equation}
    dist\{f(x_0),f(x_-)\} - dist\{f(x_0),f(x_+)\} \geqq \alpha
    \label{triplet_condition}
\end{equation}
By using the $L2$ distance as the distance function, triplet loss is defined as:
\begin{equation}
    triplet\_loss = \sum_i^N max\left({ \left[ {\left\| {{f(x_0)} - {f(x_+)}} \right\|_2^2} - {\left\| {{f(x_0)} - {f(x_-)}} \right\|_2^2}  + \alpha \right]},0 \right),
    \label{triplet_loss}
\end{equation}
% need to make hard triplets
Note that if $dist\{f(x_0),f(x_-)\}$ is much larger than $dist\{f(x_0),f(x_+)\} + \alpha$, the output of the loss function is zero, significantly slowing deep network convergence. This condition is likely to occur if triplets are composed by randomly selecting training samples. Thus, triplet inputs must be selected that cause the loss function to produce a non-zero result.

% 4.4.2. Triplet mining
\subsection{Triplet Mining Based on KAR Space Learning}
% purpose
To train the triplet network faster, a sub-network for mining the hard positive and negative samples from the training dataset was trained.
% hard sample
The hard positive sample is likely to be misclassified as a negative sample by the triplet network (Fig.~ref{fig2}).
The distance between the feature vectors of the anchor and hard positive samples is larger than other positive samples.
The hard negative sample is likely to be misclassified as a positive sample because the distance between the feature vectors of the anchor and the hard negative sample is smaller than the difference between the feature vectors of the anchor and other negative samples.
Hard triplet inputs are made by combining hard positive and hard negative samples with selected anchor samples. Using hard triplets as triplet network inputs more easily, satisfies~\ref{triplet_condition}. However, before training the triplet network, it is impossible to identify hard samples.
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_hardsample_v1.pdf}
    \caption{Selection of hard samples.} \label{fig2}
\end{figure*}
% functions
In order to make hard triplets before tranining the triplet network, a smaller sub-network was trained before training the main triplet network.
This smaller sub-network was made of an MLP and was trained using KAR space learning. As KAR space learning has no backpropagation and no iterative learning process, it was trained all at once on the entire training dataset $X$. 
The sub-network output was defined as: 
\begin{equation}
    KAR\left(\mathbf{X}\right)=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right).
\end{equation}
After training the sub-network, the hard samples were mined by measuring the $L2$ distance between every output vector of the sub-network and the output vector of anchor sample.
The sub-network output for a given anchor sample $x_0$ was $KAR(x_0)$. To mine hard-positive samples, one sample was selected from among the sub-network outputs for which the distance to the anchor feature vector $KAR(x_0)$ was larger than $t_+$. Hard-negative samples were chosen, from among the sub-network outputs for which the anchor feature vector was smaller than $t_-$.
The selected hard-positive and hard-negative samples satisfied the following properties, respectively:
\begin{equation}
    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{+}\right)}} \right\|_2^2} \geq \mathrm{t}_{+}, 
    \label{thres_pos}
\end{equation}
\begin{equation}
    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{-}\right)}} \right\|_2^2} \leq \mathrm{t}_{-},\label{thres_neg}
\end{equation}
If the hardest sample, outlier data is more likely to be selected than other data, resulting in an increased risk of overfitting~\cite{schroff2015facenet}.
To avoid this problem, the threshold for the hard-positive and the hard-negative samples were empirically chosen as the 25th and 75th percentiles of the distance between the anchor and sub-network outputs.

% 4.4.3. ConvNet Structures
\subsection{ConvNet Structures}
% Purpose
The three-dimensional format of the input signature signal is similar to that of image data, so deep ConvNet structures were used as the feature extractor. The ConvNets used in this thesis were made of three layers of ConvNets with triplet loss. Each layer of ConvNet shared their weights. 
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_convnet_v1.pdf}
    \caption{ConvNet structure.} \label{fig3}
\end{figure*}
% Structure
The ConvNets in this study consisted of three filters and a fully-connected output layer (Fig.~\ref{fig3}). The depth of the ConvNet filters was set at 64,128,256 with stride 1 and ReLU activation functions. The size of the fully-connected layer was 16. The fully-connected output layers were processed through sigmoid activation functions and were normalized according to the $L2$ distance.

### 2019-10-17 191016_Paper_Thesis_v2/Related_Works.tex
thesis_v1

\label{chp:Preliminary}
%3.1 Deep Metric Learning
\section{Deep Metric Learning}
% What is metric running?
Metric learning converts multi-dimensional data to group data in a feature space.
% Recent Trends
It has been used for computer vision tasks such as image classification and content-based image retrieval~\cite{yang2006distance}. In the past, features were extracted and similarity was measured using traditional algorithms like HOG and LBP. Rescently, deep learning-based methods have been widely used instead as they have enabled feature extraction and metric learning in a single framework~\cite{yi2014deep}. The deep networks automatically learns image classification features.
% Target Model
Deep learning-based models include the Siamise network and the Triplet network.

%3.1.1 Triplet network
\subsection{Triplet Network}
% Triplet Network
Triplet network is a metric learning model which group triplet data in a feature space~\cite{weinberger2006distance,yang2006distance}.
It is widely used to identify a person based on  several images in a process known as person re-identification, which is similar to butis more challanging than biometric identification due to the low quality and high variety of input images~\cite{yi2014deep}. Other factors, such as changing clothes, poses, and image angles makes it difficult to identify the target person in question.

% training triplet network
Triplet data is composed of anchor, positive, and negative data points. Training of the triplet network involves the creation of feature vectors to be placed in the appropriate feature space in which positive data is close to the anchor and negative data is far from the anchor.
% optimize training
It may not be necessary to train an algorithm using a large number of triplets. Training can be optimized by using only the most learning-efficient triplet. \cite{cheng2016person,ding2015deep,wang2016joint} used triplet networks with used triplets for only a small number of classes, which were used in a random order.
Recently,~\cite{schroff2015facenet} used triplet mining to speed up convergence. They selected inputs from a large set at each training iteration using the network.
However, these sets required the availability of a large amount of training data. This type of training requires the use of large amounts of data separated into only a few classes. Empirical data is not suitable for this type of training strategy because there is usually not enough of it and it is divided into too many classes.
The kernel and range space manipulation methods were used for training to reduce the number of required triplets.

%3.1.2 Siamese
\subsection{Siamese Networks}
% structure
Siamese neural networks consist of twin networks which accept distinct inputs but are joined by an energy function at the top~\cite{koch2015siamese}. By using a constrative loss function, Siamese networks determine whether two inputs are in the same class.
% history of siamese net
LeCun et al. introduced Siamese networks as parts of their handwritten signature verification system.
% another research which used Siamese Nets
Recent studies used Siamese networks to track pedestrians~\cite{Leal-Taixe_2016_CVPR_Workshops}, group objects~\cite{mukherjee2018object}, and~\cite{maheshwary2018matching} capture information from resumes, indicating that they are suitable for image classification tasks.

%3.2. KAR
\section{the Kernel and the Range space learning}
% MLP and gradient
Multi Layer Perceptron (MLP) neural networks have been widely used in machine learning. In general, MLPs are trained using the gradient descent and backpropagation methods~\cite{goodfellow2016deep}.
Learning parameters, such as learning rate and momentum value, have a significant impact on gradient descent performance, they must be set carefully.
However, finding the best values through trial and error is time-consuming.

% KAR
Recently, gradient-free learning frameworks for MLP have been developed which rely on KAR space manipulation~\cite{toh2018analytic,toh100,toh2018learning,toh2018gradient}.
This learning framework is based on linear algebra and pseudo-inverse functions, so it does not require any parameters or iterations.

% KAR learning method
Given $m$ samples, the training dataset can be denoted by $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and the network output can be denoted by $\tilde{Y}$. An MLP network composed of $n-1$ hidden layers $\{ h_{1},\dotsc,h_{n-1} \}$ can be represented by the following equation:
\begin{equation}
    \tilde{Y}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right)
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
This network can be trained by adopting the one-hot encoded target matrix $\tilde{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\tilde{Y}$. The weighted matrices $\mathbf{W}_{i}$ trained using KAR space manipulation learning can be written as follows~\cite{toh2018gradient}:
\begin{IEEEeqnarray}{rCl}
    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
\end{IEEEeqnarray}

### 2019-10-17 191016_Paper_Thesis_v2/abstract.tex
thesis_v1

\begin{center}
	\LARGE An In-Air Signature Identification System using Commercial Wi-Fi Devices
\end{center}

\parbox[t]{0.4\textwidth}

{
	\begin{flushright}
		Young-Woong Kwon\\
		School of Electrical and Electronic Engineering\\
		The Graduate School\\
		Yonsei University
	\end{flushright}
}
\vspace{0.1em}

Identity verification using Wi-Fi in-air handwritten signature is a challenging task in signature verification since the shape of the signal varies according to the direction in which the signature is written.
By using the traditional methods, it was difficult to verify identity from signatures entered in various directions. Moreover, limited size of the dataset also limited the training of deep learning models.
In this paper, we propose a method for identity verification from Wi-Fi in-air signatures based on triplet network. Three-channel ConvNet structures is adopted to learn discriminative features from relatively small size of in-air signature datasets. Moreover, we propose a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
Our experimental results on the Wi-Fi CSI signature dataset shows that the proposed method out-outperforms both the traditional and deep learning based methods by improved verification accuracy and faster loss convergence.

\vspace{\stretch{1}}
\noindent
\hrulefill\\
{\bf Key words : In-air handwritten signature verification, Wi-Fi Channel State Information, triplet network and the Kernel and Range space learning}
\parbox[t]{0.8\textwidth}
{}

### 2019-10-17 191016_Paper_Thesis_v2/thanks.tex
thesis_v1

\newpage
{\LARGE \bf
\noindent ACKNOWLEDGEMENT}\\[11pt]
\vskip 1em \pagestyle{empty}
\renewcommand{\baselinestretch}{0.85}

\begin{flushright}
{October 2019 \\ \textbf{Young-Woong Kwon}}
\renewcommand{\baselinestretch}{1.0}
\end{flushright}
First of all, I would like to thank Professor Kar-Ann Toh for steering the direction of my research. His warm encouragement and careful guidance were very helpful for me.
Thank you for my director Kiheon Kim and my manager Jongman Kim for recommending me to study at graduate school.
Thanks for my company, Samsung SDI for supporting me to study at graduate school.
I also want to give my special thanks to Jooyoung, Kim. His consideration and positive attitude always motivated me to do better.
Thank you to all my lab members for helping to enjoy school life.
Last but not least, I couldn't have finished this work without my dear wife, who always trusted and waited for me despite going back to graduate school at a late age.

### 2019-11-06 191016_Paper_Thesis_v2/Conclusion.tex
paper_thesis:update

\label{chp:Conclusion}
%\section{Conclusion}
In this thesis, a system for identity verification was developed based on the hand gesture signature signals sensed by the Wi-Fi Channel State Information (CSI).
A three-channel ConvNet structure was adopted to learn the discriminative features based on a relatively small size in-air handwritten signature dataset. We proposed an input triplet mining based on the kernel and range space learning to improve the convergence speed of the triplet network training.
Our experimental results on the Wi-Fi CSI signature dataset showed encouraging accuracy and convergence performances.

\iffalse
\section{Future Work}
\begin{enumerate}
	\setlength{\itemsep}{1pt}
	\item Recognizing the in-air signature written along non-LOS. 
	\item Repeating the same data acquisition experiments in a different place
	\item Studying identification performances when multiple people are staying in the same room.
	\item To secure a reliable identification system, spoofing attack scenario should be investigated. 
\end{enumerate} 
\fi

### 2019-11-06 191016_Paper_Thesis_v2/Experiments.tex
paper_thesis:update

@@
 %performance
-The proposed method's performance, convergence speed, and degradation were compared to those of other traditional methods.
-To compare the proposed method's feature extraction performance to that of traditional and deep-learning based methods, feature space was visualized as a 2D Euclidean plane using principal component analysis ("PCA").
+To compare the proposed method's feature extraction performance to that of traditional and deep-learning based methods, feature space was visualized as a 2D Euclidean plane using principal component analysis (``PCA'').
 % handcraft
 The proposed method's and traditional methods and deep-learning based methods.
-For handcraft methods' least square estimations ("LSE")~\cite{duda2012pattern}, PCA with LSE~\cite{turk1991eigenfaces}, support vector machine~\cite{vapnik2013nature} and the total error minimization with reduced multivariate polynomials~\cite{toh2003fingerprint,toh2008between} were compared.
+For handcraft methods' least square estimations (``LSE'')~\cite{duda2012pattern}, PCA with LSE~\cite{turk1991eigenfaces}, support vector machine~\cite{vapnik2013nature} and the total error minimization with reduced multivariate polynomials~\cite{toh2003fingerprint,toh2008between} were compared.
 Parameters were selected that performed optimally in each traditional method.
@@
 For PCA-LSE, the input signature dimension was reduced to 40 following~\cite{moon2017air}.
-For SVM with a Gaussian kernel function ("RBF"), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$.
+For SVM with a Gaussian kernel function (``RBF''), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$.
 For TER, the parameter M was chosen from among $M\in\{1,2,3\}$ and $\tau=\eta=0.5$ following~\cite{toh2008between}.
@@
 %protocols
-Verification performance was evaluated in terms of the equal error rate ("EER"). Random five-runs of two-fold cross-validation tests were conducted.
+Verification performance was evaluated in terms of the equal error rate (``EER''). Random five-runs of two-fold cross-validation tests were conducted.
 Due to hardware memory limitations, the number of negative pairs used was reduced to the number of positive data pairs used for calculating the EER for a total of 18,620 pairs.
@@
 %roc
-The proposed method had the widest area under the receiver operating characteristic ("ROC") curve (Fig.~\ref{fig_roc}).
+The proposed method had the widest area under the receiver operating characteristic (``ROC'') curve (Fig.~\ref{fig_roc}).
 \begin{figure*}[!ht]

### 2019-11-06 191016_Paper_Thesis_v2/Introduction.tex
paper_thesis:update

@@
 % signature
-Written signatures have long been used as an identification tool and various methods for verifying individuals base on them have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
+Handwritten signatures have long been used as an identification tool and various methods for verifying individuals based on them have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
 % biometric
 The use of biometric identity verification is growing with the popularity of mobile devices.
-Biometric identity verification systems are more secure, convinient, and provide greater accountability than traditional complex passwords~\cite{hutton2004biometrics}.
+Biometric identity verification systems are more secure, convinient, and provide greater accountability than traditional passwords~\cite{hutton2004biometrics,jain2006biometrics,ross2006handbook}.
 % camera sensor
@@
 % WiFI CSI
-In-air signatures can be made using Wi-fi Channel State Information ("CSI") signals.
-Typically people make a certain gesture when signing their signature on a piece of paper.
-With in-air signatures, people simply make the same gesture in the air.
+Recently, the in-air signatures can also be acquired using the Wi-fi Channel State Information (``CSI'') signals.
+Typically the user makes a certain gesture when signing their signature on a piece of paper.
+With in-air signatures, the user simply makes the same gesture in the air.
 Their movements are detected by Wi-fi receivers with appropriate software installed.
-The software detects changes in the Wi-fi signals caused by hand movements.
-This technique uses widespread devices, so it does not require the use of any special input devices.
+The software detects changes in the Wi-fi signals caused by the hand movements.
+This technique uses the existing widespread Wi-Fi devices, so it does not require the use of any special input devices.
 \cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to recognize users' gestures and~\cite{moon2017air} used them to specifically identify signatures written in the air. 
-However, due to limitations of the traditional feature extractor,~\cite{moon2017air} was only able to identify in-air signatures entering from the specific direction.
+However, due to limitations of the traditional feature extractor,~\cite{moon2017air} was only able to identify in-air signatures entering from a specific direction.
 This makes the user difficult to input their signatures.
 % Deep learning
-Recent studies have been conducted on the feasibility of using deep learning technology to characterize CSI signals.
-Deep learning-based models are popular often studied as solutions to this situaiton because of their automated feature extractors and the fact that they have superior classification capabilities than traditional models.
-Deep learning has been used to recognize users based on their body shape~\cite{pokkunuru2018neuralwave} and behavior~\cite{shi2017smart}.
+Recent studies have been conducted on the feasibility of using deep learning to characterize the CSI signals.
+Deep learning-based models are popular because of their automated feature extractors and the fact that they have superior classification capabilities than traditional models.
+Deep learning has been used to recognize users based on their vital sign~\cite{zhang2017pulseprint,szankin2018long} and behavior~\cite{shi2017smart,pokkunuru2018neuralwave}.
 % our methods
-In this thesis, deep learning technology was used to create a Wi-Fi CSI system that can recognize a user's identity with multi-direction in-air signatures.
-The deep learning model tested in this study used a triplet network to increase classification and feature extraction accuracy, and to improve the model's convergence speed using the kernel and range space learning techniques~\cite{toh2018gradient}.
+In this thesis, the deep learning technology is used to create a Wi-Fi CSI system that can recognize a user's identity with multi-direction in-air signatures.
+The deep learning model tested in this study is a triplet network where our task is to improve the model's convergence speed using the kernel and range space learning technique~\cite{toh2018gradient}.
 
@@
 \section{Motivation and Contributions}
-The main contributions of this thesis were
+The main contributions of this thesis
 \begin{itemize}
@@
 \section{Paper Organization}
-The rest of this paper is organized as follows.
+The rest of this thesis is organized as follows.
 Section 2 discusses related works about triplet networks and KAR space learning.

### 2019-11-06 191016_Paper_Thesis_v2/Proposed_Method.tex
paper_thesis:update

@@
 Wi-Fi signature data must be pre-processed to be used as an input in the proposed system.
-First, data must be simplified.
 In this study, only the magnitude of the complex signal was utilized due to device firmware issues with the phase value of the 2.4Ghz Wi-Fi signal~\cite{wang2015understanding}.
@@
 %purpose
-This thesis proposed an identity verification system based on the Wi-Fi signals produced by in-air handwritten signatures ("Wi-Fi signature"). 
+This thesis proposed an identity verification system based on the Wi-Fi signals produced by in-air handwritten signatures (``Wi-Fi signature''). 
 %function
@@
 % hard sample
-The hard positive sample is likely to be misclassified as a negative sample by the triplet network (Fig.~ref{fig2}).
+The hard positive sample is likely to be misclassified as a negative sample by the triplet network (Fig.~\ref{fig2}).
 The distance between the feature vectors of the anchor and hard positive samples is larger than other positive samples.
@@
     \includegraphics[width=\textwidth]
-        {fig_hardsample_v1.pdf}
+        {fig_hardsample_v2.pdf}
     \caption{Selection of hard samples.} \label{fig2}

### 2019-11-06 191016_Paper_Thesis_v2/Related_Works.tex
paper_thesis:update

@@
 % Target Model
-Deep learning-based models include the Siamise network and the Triplet network.
+Our focus in this thesis is the Triplet network.
 
@@
 % Triplet Network
-Triplet network is a metric learning model which group triplet data in a feature space~\cite{weinberger2006distance,yang2006distance}.
-It is widely used to identify a person based on  several images in a process known as person re-identification, which is similar to butis more challanging than biometric identification due to the low quality and high variety of input images~\cite{yi2014deep}.
-Other factors, such as changing clothes, poses, and image angles makes it difficult to identify the target person in question.
+Triplet network is a metric learning model which group triplet data in the feature space~\cite{weinberger2006distance,yang2006distance}.
+It is widely used to identify a person based on  several images in a process known as person re-identification, which is more challanging than biometric identification due to the low quality and high variety of input images~\cite{yi2014deep}.
+Other factors, such as variation of clothes, poses, and image angles makes it difficult to identify the target person in question.
 
 % training triplet network
-Triplet data is composed of anchor, positive, and negative data points.
+The triplet data is composed of anchor, positive, and negative data points.
 Training of the triplet network involves the creation of feature vectors to be placed in the appropriate feature space in which positive data is close to the anchor and negative data is far from the anchor.
@@
 % MLP and gradient
-Multi Layer Perceptron (MLP) neural networks have been widely used in machine learning. In general, MLPs are trained using the gradient descent and backpropagation methods~\cite{goodfellow2016deep}.
+Multi Layer Perceptron (``MLP'') neural networks have been widely used in machine learning. In general, the MLPs are trained using the gradient descent and backpropagation~\cite{goodfellow2016deep}.
 Learning parameters, such as learning rate and momentum value, have a significant impact on gradient descent performance, they must be set carefully.
@@
 % KAR
-Recently, gradient-free learning frameworks for MLP have been developed which rely on KAR space manipulation~\cite{toh2018analytic,toh100,toh2018learning,toh2018gradient}.
-This learning framework is based on linear algebra and pseudo-inverse functions, so it does not require any parameters or iterations.
+Recently, a gradient-free learning framework for MLP have been developed which rely on KAR space manipulation~\cite{toh2018analytic,toh100,toh2018learning,toh2018gradient}.
+This learning framework is based on linear algebra and pseudo-inverse functions, so it does not require any iterations.
 
@@
 \in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
-This network can be trained by adopting the one-hot encoded target matrix $\tilde{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\tilde{Y}$.
+This network can be trained by adopting the one-hot encoded target matrix ${Y}\in{\mathbb{R}}^{m \times n}$.
 The weighted matrices $\mathbf{W}_{i}$ trained using KAR space manipulation learning can be written as follows~\cite{toh2018gradient}:

### 2019-11-06 191016_Paper_Thesis_v2/abstract.tex
paper_thesis:update

@@
 \begin{center}
-	\LARGE An In-Air Signature Identification System using Commercial Wi-Fi Devices
+	\LARGE Improving the Triplet Network for Wi-Fi Based Handwritten Signature Verification
 \end{center}
@@
 
-Identity verification using Wi-Fi in-air handwritten signature is a challenging task in signature verification since the shape of the signal varies according to the direction in which the signature is written.
-By using the traditional methods, it was difficult to verify identity from signatures entered in various directions.
-Moreover, limited size of the dataset also limited the training of deep learning models.
-In this paper, we propose a method for identity verification from Wi-Fi in-air signatures based on triplet network.
-Three-channel ConvNet structures is adopted to learn discriminative features from relatively small size of in-air signature datasets.
-Moreover, we propose a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
-Our experimental results on the Wi-Fi CSI signature dataset shows that the proposed method out-outperforms both the traditional and deep learning based methods by improved verification accuracy and faster loss convergence.
+Identity verification using Wi-Fi signals is a challenging task since the shape of the signal varies according both the orientation and the position of the user.
+In this thesis, a system for identity verification is developed based on the hand gesture signature signals sensed by the Wi-Fi Channel State Information (``CSI'').
+A three-channel ConvNet structure is adopted to learn the discriminative features based on a relatively small size in-air handwritten signature dataset.
+We propose an input triplet mining based on the kernel and range space learning to improve the convergence speed of the triplet network training.
+Our experimental results on the Wi-Fi CSI signature dataset shows encouraging accuracy and convergence performances.
 
@@
 \hrulefill\\
-{\bf Key words : In-air handwritten signature verification, Wi-Fi Channel State Information, triplet network and the Kernel and Range space learning}
+{\bf Key words : In-air handwritten signature verification, Wi-Fi Channel State Information, Triplet network, and the Kernel and Range space learning}
 \parbox[t]{0.8\textwidth}

### 2019-11-06 191016_Paper_Thesis_v2/abstract_kor.tex
paper_thesis:update

{\large
	\noindent 국문요약}\\[11pt]
\begin{center}
	\vskip 2em \Large 개선된 트리플렛 네트워크를 이용한 와이파이 서명 인식 방법 
\end{center}
\vskip 2em

와이파이 신호를 활용해 입력된 수기 서명으로 사용자의 신원을 확인하는 것은 서명이 입력된 방향에 따라 신호의 형태가 변하기 때문에 해석하기 어려운 과제로 인식되어 왔다.
서명 인식에 전통적인 방법을 사용하면 다양한 방향으로 입력된 서명으로부터 신원을 확인하기 어려웠고, 실험 데이터의 크기가 제한되어 딥러닝 모델의 활용 역시 제한되어 왔다.
본 논문에서는 트리플렛 네트워크에 기반하여 와이파이 신호를 이용해 작성된 서명으로부터 신원을 확인하는 새로운 방법을 제안한다.
트리플렛 네트워크의 채택으로 소규모의 실험 데이터셋에서도 차별적인 특징을 학습하며, 커널과 레인지 공간 학습에 기반한 입력 데이터의 추출로 트리플렛 네트워크의 학습 속도를 빠르게 하였다.
와이파이 서명 데이터셋을 이용한 실험을 통해, 제안된 방법이 서명 검증의 정확도와 손실함수의 수렴 속도에서 전통적인 방법과 딥러닝 모델을 능가함을 보여, 다양한 방향으로 입력된 와이파이 신호 기반의 수기 서명을 인식할 수 있음을 검증하였다.

\vspace{\stretch{1}}

\noindent
\hrulefill\\
핵심되는 말:
\parbox[t]{0.8\textwidth}
{수기 서명 확인, Wi-Fi 채널 상태 정보, 트리플렛 네트워크, 커널과 레인지 공간 학습}

### 2019-12-02 190522_Wisig_KAR/LinearModel_v4.py
DIP_HW3,4

@@ -1,0 +1,522 @@
+# Linear V4: SVM, TERd
+# Linear V3 : Normal, SVM
+
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import time
+import random
+from sklearn.model_selection import StratifiedKFold
+from sklearn.metrics import confusion_matrix
+from sklearn.utils import shuffle
+import matplotlib.pyplot as plt
+import seaborn as sns
+from scipy.optimize import brentq
+from scipy.interpolate import interp1d
+from sklearn.metrics import roc_curve
+from sklearn.svm import SVC
+
+## Functions
+# function to return key for any value 
+def get_key(val,my_dict): 
+    for key, list_val in my_dict.items(): 
+         if val in list_val: 
+             return key 
+  
+    return "key doesn't exist"
+
+def ReadCSIData(PATH,ratio,locs,dirs):
+    print("loading data from {}".format(PATH))
+    list_csi = []
+    list_lab = []
+    list_res_csi = []
+    list_res_lab = []
+    
+    ids = int(ratio * 100)
+    res_ids = int((1-ratio)*100)
+
+    # Filter Loc,Dir
+    file_list = []
+    for i in locs:
+        for j in dirs:
+            filename = 'Dataset_' + str(i) + '_' + str(j) + '.npy'
+            file_list.append(filename)
+
+    for file in file_list:
+        data_read = np.load(PATH + file)
+        csi_read = data_read[:,4:].astype('float32')
+        lab_read = data_read[:,0].astype('int')
+
+        data_x = csi_read.reshape([-1,10,6,30,500]).swapaxes(2,4)
+
+        uniq_label = np.unique(lab_read)
+        label_table = pd.Series(np.arange(len(uniq_label)),index=uniq_label)
+        data_y = np.array([label_table[num] for num in lab_read]).reshape([-1,10])
+        
+        # use half of the dataset
+        idx_ids = (data_y[:,0] < ids)
+        list_csi.append(data_x[idx_ids])
+        list_lab.append(data_y[idx_ids])
+        
+        reserve_ids = (data_y[:,0] >= ids)
+        list_res_csi.append(data_x[reserve_ids])
+        list_res_lab.append(data_y[reserve_ids])
+
[…]

### 2019-12-02 191111_DIP_A3/ImprovedMedianFilter.m

@@ -1,0 +1,38 @@
+function output = ImprovedMedianFilter(I, kernel_size)
+% where I is and input image, and kernel_size n is nxn size of the filter
+
+%padding
+pad_len = floor(kernel_size/2);
+I_pad = padarray(I, [pad_len pad_len],0,'both');
+% parameters
+shape_pad = size(I_pad);
+mtp_param = ceil(kernel_size*kernel_size/2);
+alpha = 26;
+isnoise = zeros(size(I_pad));
+% Calc MTP
+for r_I = 1+pad_len : shape_pad(1)-pad_len
+    for c_I = 1+pad_len : shape_pad(2)-pad_len
+        % NLD
+        k_values = I_pad(r_I-pad_len:r_I+pad_len,c_I-pad_len:c_I+pad_len);
+        nld = abs(I_pad(r_I,c_I) - k_values);
+        %RLD
+        v_nld = reshape(nld,1,[]);
+        v_nld(mtp_param) = [];
+        rld = sort(v_nld);
+        %MTP
+        mtp = 1/mtp_param * sum(rld(1:mtp_param));
+        i_th = alpha + log2(mtp);
+        % check the pixel is noisy or not
+        isnoise(r_I,c_I) = I_pad(r_I,c_I) > i_th;
+        % if noisy : perform median filtering
+        if(isnoise(r_I,c_I))
+            I_pad(r_I,c_I) = median(median(k_values));
+        end        
+    end
+end
+
+% return
+output = I_pad(1+pad_len:shape_pad(1)-pad_len,1+pad_len:shape_pad(2)-pad_len);
+
+end
+

### 2019-12-02 191111_DIP_A3/MedianFilter.m

@@ -1,0 +1,20 @@
+function output = MedianFilter (I, kernel_size) %
+% where I is and input image, and kernel_size n is nxn size of the filter
+
+%padding
+pad_len = floor(kernel_size/2);
+I_pad = padarray(I, [pad_len pad_len]);
+% size of padded image
+shape_pad = size(I_pad);
+% make kernel function
+for r_I = 1+pad_len : shape_pad(1)-pad_len
+    for c_I = 1+pad_len : shape_pad(2)-pad_len
+        % get values in the filter
+        k_values = I_pad(r_I-pad_len:r_I+pad_len,c_I-pad_len:c_I+pad_len);
+        % input median value to padded image
+        I_pad(r_I,c_I) = median(median(k_values));
+    end
+end 
+% return
+output = I_pad(1+pad_len:shape_pad(1)-pad_len,1+pad_len:shape_pad(2)-pad_len);
+% Complete the remaining part

### 2019-12-02 191111_DIP_A3/Resize.m

@@ -1,0 +1,14 @@
+function output = Resize(I,SCALE)
+%RESIZE Summary of this function goes here
+%   Detailed explanation goes here
+
+mat_size = size(I);
+% sampling by ratio
+row_vec = 1:SCALE:mat_size(1);
+col_vec = 1:SCALE:mat_size(2);
+sampled_im = I(row_vec,col_vec);
+
+output = sampled_im;
+
+end
+

### 2019-12-02 191111_DIP_A3/hw3_1.m

@@ -1,0 +1,49 @@
+% image read
+im = im2double(imread('mandrill.png'));
+% adjust intensity to max 255
+im = im(:,:,1) .* 255;
+
+% sampling parameters
+sampling_factors = [2 4];
+
+% plot original
+figure(1);
+subplot(1,3,1);
+imshow(im ./ 255);
+title('input image');
+
+% 1. down-sampling
+for i = 1:length(sampling_factors)
+    sampled_im = Resize(im,sampling_factors(i));
+    % plot sampled image
+    subplot(1,3,1+i);
+    imshow(sampled_im ./ 255,'InitialMagnification', sampling_factors(i)*100);
+    title({['Sampling Factors of ',num2str(sampling_factors(i))];
+    ['(',num2str(sampling_factors(i)),' x zoom)']});
+end
+
+% 2. gaussian blur
+figure(2);
+subplot(2,2,1);
+imshow(im ./ 255);
+title('input image');
+% calculate noise
+noise_std = 17;
+im_Tr = GaussianNoise(im, noise_std);
+% store image matrix
+im_Trs{i} = im_Tr;
+% show image correspoiding to std value
+subplot(2,2,2);
+imshow(im_Tr ./ 255);
+title(['Noise: std = ',num2str(noise_std)]);
+
+% down-sampling
+for i = 1:length(sampling_factors)
+    sampled_imTr = Resize(im_Tr,sampling_factors(i));
+    % plot sampled image
+    subplot(2,2,2+i);
+    imshow(sampled_imTr ./ 255,'InitialMagnification', sampling_factors(i)*100);
+    title({['Noise: std = ',num2str(noise_std)];
+    ['Sampling Factors of ',num2str(sampling_factors(i))];
+    ['(',num2str(sampling_factors(i)),' x zoom)']});
+end

### 2019-12-02 191111_DIP_A3/hw3_2.m

@@ -1,0 +1,52 @@
+% image read
+im = im2double(imread('noisy.png'));
+% adjust intensity to max 255
+im = im(:,:,1) .* 255;
+
+% Fourier Transform
+f_im = fftshift(fft2(im));
+% shifted magnitude image
+abs_f_im = abs(f_im);
+% plot magnitude
+figure(1);
+imshow(abs_f_im / max(max(abs_f_im)) * 255);
+
+% find peaks
+row_sum = sum(abs_f_im,1);
+col_sum = sum(abs_f_im,2);
+% plot peaks
+figure(2);
+subplot(2,1,1);
+[pks_r,locs_r,w_r,p_r] = findpeaks(row_sum,'SortStr','descend');
+plot(row_sum)
+text(locs_r(1:5),pks_r(1:5)+10^6,num2str(locs_r(1:5)'))
+title('Peaks:RowSum');
+subplot(2,1,2);
+[pks_c,locs_c,w_c,p_c] = findpeaks(col_sum,'SortStr','descend');
+plot(col_sum)
+text(locs_c(1:5),pks_c(1:5)+10^5,num2str(locs_c(1:5)))
+title('Peaks:ColSum');
+
+% make filter
+filter_freq = ones(size(abs_f_im));
+for i = 2:length(locs_r)
+    filter_freq(locs_c(i),locs_r(i)) = 0;
+end
+
+%apply filter
+ff_im = f_im .* filter_freq;
+abs_ff_im = abs(ff_im);
+% plot frequency filtered image
+figure(4);
+imshow(abs_ff_im / max(max(abs_ff_im)) * 255);
+
+%inverse fourier transform
+if_im = abs(ifft2(ff_im));
+% plot filtered original image
+figure(5);
+subplot(1,2,1);
+imshow(im ./ 255);
+title('Original Image');
+subplot(1,2,2);
+imshow(if_im ./ 255);
+title('Freq. Filtered Image');

### 2019-12-02 191111_DIP_A3/hw3_3.m

@@ -1,0 +1,48 @@
+% image read
+im = im2double(imread('image1.png'));
+% adjust intensity to max 255
+im = im(:,:,1) .* 255;
+
+% parameters
+noise_list=[0.1, 0.2, 0.3];
+filter_list = [3, 5];
+
+% plot original image
+figure(1);
+subplot(1,4,1);
+imshow(im ./ 255);
+title('input image');
+im_Trs = cell(length(noise_list),1);
+% 1. add Salt&Pepper noise
+for i = 1:length(noise_list)
+    im_Tr = SaltAndPepper(im, noise_list(i));
+    % store image matrix
+    im_Trs{i} = im_Tr;
+    subplot(1,4,i+1);
+    % show image correspoiding to noise value
+    imshow(im_Tr ./ 255);
+    title(['ND : ',num2str(noise_list(i))]);
+end
+
+% 2. filter noisy images
+for i = 1:length(noise_list)
+    im_Tr = im_Trs{i};
+    % plot noisy image
+    figure(2);
+    subplot(3,3,3*(i-1)+1);
+    imshow(im_Tr ./ 255);
+    title(['ND : ',num2str(noise_list(i))]);
+    
+    for j = 1:length(filter_list)
+        % apply filter
+        % 3. improved median filter
+        im_m = ImprovedMedianFilter(im,filter_list(j));
+        %im_m = MedianFilter(im,filter_list(j));
+        % plot filtered image
+        subplot(3,3,3*(i-1)+(j+1));
+        imshow(im_m ./ 255);
+        title(['ND : ',num2str(noise_list(i)),' / Filter : [',num2str(filter_list(j)),',',num2str(filter_list(j)),']']);
+    end
+end
+
+

### 2019-12-02 191125_DIP_A4/LaplacianFilter.m

@@ -1,0 +1,17 @@
+function output = LaplacianFilter(I,M)
+size_I = size(I);
+filtered = zeros(size_I);
+% for color image
+if length(size_I) == 3
+    ch = size_I(3);
+    % apply Laplacian filter
+    for i=1:ch
+        filtered(:,:,i) = conv2(I(:,:,i),M,'same');
+    end
+else % for grayscale image
+    filtered = conv2(I,M,'same');
+end
+
+output = filtered;
+end
+

### 2019-12-02 191125_DIP_A4/hw4_1.m

@@ -1,0 +1,26 @@
+% image read
+im = im2double(imread('pepper.png'));
+
+% 1. RGB to HSI conversion
+im_hsi = toHSI(im);
+% plot
+figure(1);
+subplot(1,3,1);
+imshow(im_hsi(:,:,1)./360);
+title('Hue');
+subplot(1,3,2);
+imshow(im_hsi(:,:,2));
+title('Saturation');
+subplot(1,3,3);
+imshow(im_hsi(:,:,3));
+title('Intensity');
+
+% 2. HSI to RGB conversion
+im_rgb2 = toRGB(im_hsi);
+figure(2);
+subplot(1,2,1);
+imshow(im);
+title('Original Image');
+subplot(1,2,2);
+imshow(im_rgb2);
+title('Converted from HSI image');

### 2019-12-02 191125_DIP_A4/hw4_2.m

@@ -1,0 +1,36 @@
+% image read
+im = im2double(imread('cameraman.png'));
+% change scale to maximum 255
+im = rgb2gray(im) .* 255;
+
+% Pseudo coloring
+[size_w,size_h] = size(im);
+pc_im = zeros([size_w size_h 3]);
+pc_rgb = [54 21 203 16;128 154 213 233;33 233 62 59];
+
+for i = 1:size_w
+    for j = 1:size_h
+        % get intensity from the pixel of gray image
+        intensity = fix(im(i,j)/72);
+        switch intensity
+            % set color according to intensity value
+            case 0
+                pc_im(i,j,:) = pc_rgb(:,1);
+            case 1
+                pc_im(i,j,:) = pc_rgb(:,2);
+            case 2
+                pc_im(i,j,:) = pc_rgb(:,3);
+            case 3
+                pc_im(i,j,:) = pc_rgb(:,4);
+        end
+    end
+end
+
+% Plot
+figure(1);
+subplot(1,2,1);
+imshow(im./255);
+title('Original Image');
+subplot(1,2,2);
+imshow(pc_im./255);
+title('pseudo-colored Image');

### 2019-12-02 191125_DIP_A4/hw4_3.m

@@ -1,0 +1,56 @@
+% i. image read
+im = im2double(imread('bird.png'));
+
+% ii. Laplacian filtering
+% make Laplacian filter mask
+mask = [0 1 0;1 -4 1;0 1 0];
+% apply Laplacian filter
+laped_im = LaplacianFilter(im,mask);
+
+% iii. Show Laplacian filtered image
+figure(1);
+subplot(1,2,1);
+imshow(im);
+title('Original Image');
+subplot(1,2,2);
+imshow(laped_im);
+title('Laplacian-filtered Image');
+
+% iii. HSI conversion
+hsi_im = toHSI(im);
+
+% iv. apply Laplacian filter to HSI intensity
+laped_hsi = hsi_im;
+laped_hsi(:,:,3) = LaplacianFilter(laped_hsi(:,:,3),mask);
+
+% v. HSI to RGB
+laped_rgb = toRGB(laped_hsi);
+% show conversion
+figure(2);
+subplot(1,2,1);
+imshow(im);
+title('Original Image');
+subplot(1,2,2);
+imshow(laped_rgb);
+title('Laplacian filter to HSI and converted to RGB');
+
+% vi. show difference
+% plotting
+figure(3);
+subplot(1,2,1);
+imshow(laped_im);
+title('Laplacian filter to Original Image');
+subplot(1,2,2);
+imshow(laped_rgb);
+title('Laplacian filter to HSI and converted to RGB');
+% histogram
+figure(4)
+d = 0:0.01:1;
+subplot(1,2,1);
+hist(reshape(laped_im,[],3),d);
+colormap([1 0 0;0 1 0;0 0 1]);
+ylim([0 200]);
+subplot(1,2,2);
+hist(reshape(laped_rgb,[],3),d);
+colormap([1 0 0;0 1 0;0 0 1]);
+ylim([0 200]);

### 2019-12-02 191125_DIP_A4/toHSI.m

@@ -1,0 +1,30 @@
+function output = toHSI(im_rgb)
+
+im_hsi = zeros(size(im_rgb));
+[size_w,size_h] = size(im_rgb(:,:,3));
+sum_rgb = sum(im_rgb,3);
+
+%I
+im_hsi(:,:,3) = (1/3) .* sum_rgb;
+%S
+im_hsi(:,:,2) = ones(size(im_rgb(:,:,2))) - 3 ./ (sum_rgb+0.000001) .* min(im_rgb,[],3);
+%H
+for i = 1:size_w
+    for j = 1:size_h
+        p_r = im_rgb(i,j,1);
+        p_g = im_rgb(i,j,2);
+        p_b = im_rgb(i,j,3);
+        nume = 1/2*((p_r-p_g) + (p_r-p_b));
+        denom = ((p_r-p_g)^2 + ((p_r-p_b)*(p_g-p_b)))^(1/2);
+        h = acosd( nume / (denom+0.000001) );
+        if p_g >= p_b
+            im_hsi(i,j,1) = h;
+        else
+            im_hsi(i,j,1) = 360 - h;
+        end
+    end
+end
+
+output = im_hsi;
+end
+

### 2019-12-02 191125_DIP_A4/toRGB.m

@@ -1,0 +1,34 @@
+function output = toRGB(im_hsi)
+im_rgb = zeros(size(im_hsi));
+[size_w,size_h] = size(im_hsi(:,:,2));
+
+% calc RGB value
+for i = 1:size_w
+    for j = 1:size_h
+        p_h = im_hsi(i,j,1);
+        p_s = im_hsi(i,j,2);
+        p_i = im_hsi(i,j,3);
+        
+        if ((p_h >= 0) && (p_h < 120))
+            p_r = p_i*(1+p_s*cosd(p_h)/cosd(60-p_h));
+            p_b = p_i*(1-p_s);
+            p_g = 3*p_i-(p_r + p_b);
+        elseif ((p_h >= 120) &&  (p_h < 240))
+            p_r = p_i*(1-p_s);
+            p_g = p_i*(1+p_s*cosd(p_h-120)/cosd(p_h-180));
+            p_b = 3*p_i-(p_r + p_g);
+        elseif ((p_h >= 240) && (p_h <= 360))
+            p_g = p_i*(1-p_s);
+            p_b = p_i*(1 + p_s*cosd(p_h-240)/cosd(p_h-300));
+            p_r = 3*p_i-(p_g + p_b);
+        end
+        
+        im_rgb(i,j,1) = p_r;
+        im_rgb(i,j,2) = p_g;
+        im_rgb(i,j,3) = p_b;        
+    end
+end
+% output
+output = im_rgb;
+end
+

### 2019-12-03 191016_Paper_Thesis_v2/Experiments.tex
Paper_thesis: final defence update

@@
 The Wi-Fi CSI signature dataset~\cite{moon2017air} at position 1 was used to test the proposed system.
-These dataset contained 10 signatures made by 98 people in each direction for a total of 980 signatures made in each direction.
+These dataset contained 10 signatures made by 98 people in each direction for a total of 980 signatures made in each direction, as shown in~\ref{tab_dataset}.
 The size of each sample had a data resolution of 500 x 30 x 6.
+\textbf{
+Visualization of CSI signature data is shown in Fig.~\ref{fig_csi}.}
+%fig:csi
+\begin{figure}[!ht]
+    \includegraphics[width=\textwidth]{fig_csi_v2.pdf}
+    \caption{Visualization of CSI signal.
+This data consists of signal strengths for 30 subcarriets per 500 time packet with 6 channels.
+Each subcarrier corresponds to the frequency, and the intensity value indicates the signal strength.} \label{fig_csi}
+\end{figure}
+%tab:dataset
+\begin{table}
+    \caption{Description of the Dataset.}
+    \label{tab_dataset}
+    \begin{tabular}{ccc}
+    \hline
+    Direction of signature & \# of identities & \# of data \\ 
+    \hline
+    1                      & 98               & 980        \\ 
+    2                      & 98               & 980        \\ 
+    3                      & 98               & 980        \\ 
+    4                      & 98               & 980        \\ 
+    \hline
+    \end{tabular}
+\end{table}
 
@@
 The structure of the KAR learning MLP sub-networks in the proposed system is shown in~\ref{kar_structure}.
-The two layers' sizes were set to 1,024 and 16.
-The size of the second layer was equal to the number of feature vectors of the proposed ConvNet.
+The three layers' sizes were set to 1,024, 64 and 16.
+The size of the third layer was equal to the number of feature vectors of the proposed ConvNet.
 The weights in the layers were initialized in a normal distribution between 0 and 1 before training.
@@
     Fully-connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
-    Fully-connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
+    Fully-connected 2 & 1$\times$1$\times$64 & $\sigma = {tan}^{-1}$     \\
+    Fully-connected 3 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
     Output  & 1$\times$1$\times$50   &            \\ \hline
@@
     Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
-    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
+    \textbf{Proposed system} &   \textbf{16.67}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
      \hline
@@
     Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
-    Proposed method            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
+    Proposed method            & 16.67 & 18.03 & 18.08 & 26.64 \\ \hline
     \end{tabular}
@@
 \end{figure}
-%5.3.3. 2D visualization of feature vector
+\iffalse
+% Omitted: 5.3.3. 2D visualization of feature vector
 \subsection{2D Visualization of the Feature Vectors}
@@
 The baseline triplet network caused many identities to overlap.
+\fi
+%5.3.3. Comparision between mining methods
+\subsection{Comaprison between mining algorithms}
+\textbf{
+In this section, the proposed system is compared to a triplet network that adopted different mining methods. The methods used for mining are the traditional methods given in Table \ref{tab_dataset}. 
+We also compared Extreme Learning Machine (``ELM'').
+ELM is a fast-learning SLFN network which uses an analistic method for calculating the weight of the network~\cite{huang2006extreme}.
+For the traditional methods, the input signals are resized to 500 × 30 by averaging along the subcarrier axes due to limitation of hardware memory.}
+
+\textbf{
+Table \ref{tab_mining} shows the test EER of proposed and compared triplet mining methods. 
+TER-RM2 showed the best test EER performance in this case. Proposed system (KAR learning) showed slightly worse performance of 16.67\% EER. SVM also showed good performance.
+From this result, it can be seen that the traditional method can increase the accuracy of the triplet network when applied to the triplet mining.
+}
+
+\begin{table}[!h]
+    \caption{Average EER between mining methods.}\label{tab_mining}
+    \centering
+    \begin{tabular}{|c|c|c|}
+    \hline
+    Methodology   &   Best EER (\%) &   Condition   \\  \hline
+    LSE &   19.03   &  - \\ 
+    SVM (Linear) &   17.48   &   c=1 \\
+    SVM (RBF)    &   17.31   &   c=1, $\gamma$=0.01/3000 \\
+    ELM &   17.02   &   layer=[1024,16] \\
+    TER-RM2 &   16.37   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
+    \textbf{Proposed System} &   \textbf{16.67}   &  \textbf{layer=[1024,64,16]}  \\
+     \hline
+    \end{tabular}
+\end{table}

### 2019-12-24 191016_Paper_Thesis_v2/Experiments.tex
clear: 20191224

@@
 The size of each sample had a data resolution of 500 x 30 x 6.
-\textbf{
-Visualization of CSI signature data is shown in Fig.~\ref{fig_csi}.}
+Visualization of CSI signature data is shown in Fig.~\ref{fig_csi}.
 %fig:csi
@@
 \begin{figure*}[!ht]
-    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
-    \caption{Normalized training loss curve.} \label{fig_roc}
+    \includegraphics[width=\textwidth]{fig_roc_v17.eps}
+    \caption{ROC curves} \label{fig_roc}
 \end{figure*}
@@
 \subsection{Feature Vector Size Effect}
-Fig.~\ref{fclayer} shows the EERs for different sizes of feature vectors in the feature space. 
+Fig.~\ref{fclayer} and~\ref{tab_feature_vectors} shows the EERs for different sizes of feature vectors in the feature space. 
 For metric learning systems, feature vector size is generally positively correlated with system performance.
@@
 \begin{table}[]
+    \caption{Feature Vector Size Effect.}\label{tab_feature_vectors}
     \centering
@@
 %5.3.3. Comparision between mining methods
-\subsection{Comaprison between mining algorithms}
-\textbf{
+\subsection{Comparison between mining algorithms}
 In this section, the proposed system is compared to a triplet network that adopted different mining methods. The methods used for mining are the traditional methods given in Table \ref{tab_dataset}. 
-We also compared Extreme Learning Machine (``ELM'').
-ELM is a fast-learning SLFN network which uses an analistic method for calculating the weight of the network~\cite{huang2006extreme}.
-For the traditional methods, the input signals are resized to 500 × 30 by averaging along the subcarrier axes due to limitation of hardware memory.}
-
-\textbf{
-Table \ref{tab_mining} shows the test EER of proposed and compared triplet mining methods. 
-TER-RM2 showed the best test EER performance in this case. Proposed system (KAR learning) showed slightly worse performance of 16.67\% EER. SVM also showed good performance.
+We also compared Extreme Learning Machine (``ELM'')~\cite{huang2006extreme}.
+ELM is a fast-learning SLFN network which uses an analytic method for calculating the weight of the network.
+For the traditional methods, the input signals are resized to 500 × 30 by averaging along the subcarrier axes due to limitation of hardware memory.
+Table \ref{tab_mining} shows the best test EER of proposed and compared triplet mining methods. TER-RM2 showed slightly worse performance of 16.67\% EER. SVM also showed good performance.
 From this result, it can be seen that the traditional method can increase the accuracy of the triplet network when applied to the triplet mining.
-}
 
@@
     ELM &   17.02   &   layer=[1024,16] \\
-    TER-RM2 &   16.37   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
+    TER-RM2 &   16.79   &  M=2,$\tau$=$\eta$=0.5   \\     \hline
     \textbf{Proposed System} &   \textbf{16.67}   &  \textbf{layer=[1024,64,16]}  \\

### 2019-12-24 191204_DIP_Fin/191212_dip/OBNLM.m

@@ -1,0 +1,81 @@
+function output = OBNLM(input)
+
+%params
+M = 20;      % search area size (2*M + 1)^2
+alpha = 3;  % patch size (2*alpha + 1)^2  %3
+h = 1;    % smoothing parameter [0-infinite]. %1
+% If you can see structures in the "Residual image" decrease this parameter
+% If you can see speckle in the "denoised image" increase this parameter
+
+offset = 100; % to avoid Nan in Pearson divergence computation
+% According to the gain used by your US device this offset can be adjusted.
+
+
+        img = input;
+        %img = imread([pathin namein]);
+        %info = imfinfo([pathin namein]);
+        
+        [dimxy dimt] = size(size(img));
+        if ( dimt > 2)
+            img = rgb2gray(img);
+        end
+        
+        % Intensity normalization
+        imgd = double(img);
+        mini = (min(imgd(:)));
+        imgd = (imgd - mini);
+        maxi = max(imgd(:));
+        imgd = (imgd / maxi) * 255;
+        imgd = imgd + offset; % add offset to enable the pearson divergence computation (i.e. avoid division by zero).
+        s = size(imgd);
+        
+        % Padding
+        imgd = padarray(imgd,[alpha alpha],'symmetric');
+        fimgd=bnlm2D(imgd,M,alpha,h);
+        fimgd = fimgd - offset;
+        imgd = imgd - offset;
+        imgd = imgd(alpha+1: s(1)+alpha, alpha+1: s(2)+alpha);
+        fimgd = fimgd(alpha+1: s(1)+alpha, alpha+1: s(2)+alpha);
+        
+        % Display
+        %minds = min(imgd(:));
+        %maxds = max(imgd(:));
+        %figure;
+        %imagesc(imgd,[minds maxds]);
+        %title('Original')
+        %colormap(gray);
+        %colorbar;
+        %figure;
+        %colormap(gray);
+        %imagesc(fimgd,[minds maxds]);
+        %title('Denoised by Bayesian NLM')
+        %colorbar;
+        %figure;
+        %colormap(gray);
+        %speckle = abs(imgd(:,:) - fimgd(:,:));
+        %imagesc(speckle);
+        %title('Residual image')
+        %colorbar;
+        
+        
[…]

### 2019-12-24 191204_DIP_Fin/191212_dip/diffimage.m

@@ -1,0 +1,7 @@
+function diffimage = diffimage(imagered,imageblue,alpha)
+image_red_double = double(imagered);
+image_blue_double= double(imageblue);
+minmax_red = minmax(image_red_double);
+minmax_blue = minmax(image_blue_double);
+
+diffimage = minmax_red - alpha*minmax_blue;

### 2019-12-24 191204_DIP_Fin/191212_dip/gaborcanny.m

@@ -1,0 +1,26 @@
+function gaborcanny = gaborcanny(diffimage)
+I = OBNLM(diffimage);
+I = I/255;
+I = imgaussfilt(I,4);
+
+gaborArray = gabor([8],[30 60 90 120 150 180]);
+
+gaborMag = imgaborfilt(I,gaborArray);
+BW2 = zeros(size(I,1),size(I,2), 6);
+
+%figure(1);
+%subplot(2,6,1);
+for p = 1:6
+    %subplot(2,3,p)
+    %imshow(gaborMag(:,:,p),[]);
+    %theta = gaborArray(p).Orientation;
+    %lambda = gaborArray(p).Wavelength;
+    %title(sprintf('Orientation=%d, Wavelength=%d',theta,lambda));
+    BW2(:,:,p) = (gaborMag(:,:,p));
+end
+
+ Ma = min(BW2,[],3);
+ b = imsharpen(Ma,'Radius',5,'Amount',4,'Threshold',1);
+ T = edge(b,'Canny');
+ 
+ gaborcanny = T;

### 2019-12-24 191204_DIP_Fin/191212_dip/minmax.m

@@ -1,0 +1,9 @@
+function minmax = minmax(im)
+
+
+maxval = max(max(im));
+minval = min(min(im));
+denom = maxval-minval;
+vector = im - minval*ones(128,128);
+minmax = vector./denom;
+end

### 2019-12-24 191204_DIP_Fin/191212_dip/run.m

@@ -1,0 +1,10 @@
+clear;
+
+img1_red = imread('train98_1_red.jpg');
+img2_blue = imread('train98_1_blue.jpg');
+
+diffimage = diffimage(img1_red,img2_blue,0.5);
+gaborcanny = gaborcanny(diffimage);
+
+figure(1);
+imshow(gaborcanny);

### 2019-12-24 191204_DIP_Fin/OBNLM.m

@@ -1,0 +1,81 @@
+function output = OBNLM(input)
+
+%params
+M = 20;      % search area size (2*M + 1)^2
+alpha = 3;  % patch size (2*alpha + 1)^2
+h = 1;    % smoothing parameter [0-infinite].
+% If you can see structures in the "Residual image" decrease this parameter
+% If you can see speckle in the "denoised image" increase this parameter
+
+offset = 100; % to avoid Nan in Pearson divergence computation
+% According to the gain used by your US device this offset can be adjusted.
+
+
+        img = input;
+        %img = imread([pathin namein]);
+        %info = imfinfo([pathin namein]);
+        
+        [dimxy dimt] = size(size(img));
+        if ( dimt > 2)
+            img = rgb2gray(img);
+        end
+        
+        % Intensity normalization
+        imgd = double(img);
+        mini = (min(imgd(:)));
+        imgd = (imgd - mini);
+        maxi = max(imgd(:));
+        imgd = (imgd / maxi) * 255;
+        imgd = imgd + offset; % add offset to enable the pearson divergence computation (i.e. avoid division by zero).
+        s = size(imgd);
+        
+        % Padding
+        imgd = padarray(imgd,[alpha alpha],'symmetric');
+        fimgd=bnlm2D(imgd,M,alpha,h);
+        fimgd = fimgd - offset;
+        imgd = imgd - offset;
+        imgd = imgd(alpha+1: s(1)+alpha, alpha+1: s(2)+alpha);
+        fimgd = fimgd(alpha+1: s(1)+alpha, alpha+1: s(2)+alpha);
+        
+        % Display
+        %minds = min(imgd(:));
+        %maxds = max(imgd(:));
+        %figure;
+        %imagesc(imgd,[minds maxds]);
+        %title('Original')
+        %colormap(gray);
+        %colorbar;
+        %figure;
+        %colormap(gray);
+        %imagesc(fimgd,[minds maxds]);
+        %title('Denoised by Bayesian NLM')
+        %colorbar;
+        %figure;
+        %colormap(gray);
+        %speckle = abs(imgd(:,:) - fimgd(:,:));
+        %imagesc(speckle);
+        %title('Residual image')
+        %colorbar;
+        
+        
[…]

### 2019-12-24 191204_DIP_Fin/OBNLMpackage/OBNLMpackage/SpeckleRemoval.m

@@ -1,0 +1,141 @@
+% /* Pierrick Coupe - pierrick.coupe@gmail.com                               */
+% /* Brain Imaging Center, Montreal Neurological Institute.                  */
+% /* Mc Gill University                                                      */
+% /*                                                                         */
+% /* Copyright (C) 2008 Pierrick Coupe                                       */
+%
+%
+%
+% /*                 Details on Bayesian NLM filter                         */
+% /***************************************************************************
+%  *  The bayesian NLM filter is described in:                               *
+%  *                                                                         *
+%  * P. Coupe, P. Hellier, C. Kervrann, C. Barillot.                         *
+%  * NonLocal Means-based Speckle Filtering for Ultrasound Images.           *
+%  * IEEE Transactions on Image Processing, 18(10):2221-9, 2009.             *
+%  ***************************************************************************/
+%
+%
+% /*                 Details on blockwise NLM filter                        */
+% /***************************************************************************
+%  *  The blockwise NLM filter is described in:                              *
+%  *                                                                         *
+%  *  P. Coupe, P. Yger, S. Prima, P. Hellier, C. Kervrann, C. Barillot.     *
+%  *  An Optimized Blockwise Non Local Means Denoising Filter for 3D Magnetic*
+%  *  Resonance Images. IEEE Transactions on Medical Imaging, 27(4):425-441, *
+%  *  Avril 2008                                                             *
+%  ***************************************************************************/
+%
+%
+%
+% /*                 This method is patented as follows                     */
+% /***************************************************************************
+% * P. Coupe, P. Hellier, C. Kervrann, C. Barillot. Dispositif de traitement *
+% * d'images ameliore. INRIA, Patent: 08/02206, 2008.                        *
+% * Publication No. : WO/2009/133307.                                        *
+% * International Application No. : PCT/FR2009/000445                        *
+% *                                                                          *
[…]

### 2019-12-24 191204_DIP_Fin/surf.m

@@ -1,0 +1,20 @@
+
+
+%im_s = target_tbl{1,3:end};
+%im_re = abs(reshape(im_s,[128,128]));
+
+%Fpoints = detectSURFFeatures(im_re);
+%[features, validPoints] = extractFeatures(im_re,Fpoints);
+
+
+featureMatrix = [];
+for n = 1:200
+    disp(n)
+    im_s = target_tbl{n,3:end};
+    im_re = abs(reshape(im_s,[128,128]));
+
+    Fpoints = detectSURFFeatures(im_re);
+    [features, validPoints] = extractFeatures(im_re,Fpoints);
+    
+    featurematrix{n} = [featureMatrix; features];
+end

### 2019-12-24 191204_DIP_Fin/svm.m

@@ -1,0 +1,34 @@
+clear all
+clc
+
+% read data from csv file
+data_tbl = readtable('C:\Data\PalmVein\PolyU-M\Multi Spectral\imgs.csv');
+
+target = 'Red';
+target_id = 100;
+
+target_tbl = data_tbl(strcmp(data_tbl.Var1,target),:);
+target_tbl = target_tbl(target_tbl.Var2 <= target_id,:);
+
+imgs = target_tbl{:,4:end};
+labels = target_tbl{:,2};
+
+cols_pca = 2;
+
+indices = crossvalind('Kfold',labels,2);
+cp = classperf(labels);
+
+for i = 1:2
+    test = (indices == i); 
+    train = ~test;
+    train_pca = pca(imgs(train,:)','NumComponents',cols_pca);
+    train_lab = labels(train,:);
+    test_pca = pca(imgs(test,:)','NumComponents',cols_pca);
+    test_lab = labels(test,:);
+    
+    SVMModel = fitcecoc(train_pca,train_lab);
+    [pred_lab,score] = predict(SVMModel,test_pca);
+    acc = sum(test_lab==pred_lab) / length(test_lab);
+    
+    disp([i,acc])
+end

### 2019-12-24 191204_DIP_Fin/tab_svm.m

@@ -1,0 +1,45 @@
+clear all
+clc
+
+% read data from csv file
+data_tbl = readtable('C:\Data\PalmVein\PolyU-M\Multi Spectral\diff_OBNLMcanny1re_image200.csv');
+disp('Read Done');
+
+%target = 'Red';
+target_id = 200;
+
+%target_tbl = data_tbl(strcmp(data_tbl.Var1,target),:);
+target_tbl = data_tbl(data_tbl.Var1 <= target_id,:);
+
+imgs = target_tbl{:,3:end};
+lab1 = target_tbl{:,1};
+lab2 = cellfun(@(x) x(:,1), target_tbl{:,2});
+labels = strcat(string(lab1),'_',lab2);
+
+cols_pca = 20;
+
+indices = crossvalind('Kfold',labels,2);
+cp = classperf(labels);
+
+% show sample image
+im_s = target_tbl{1,3:end};
+im_sre = reshape(im_s,[128,128]);
+imshow(im_sre)
+
+for i = 1:2
+    test = (indices == i); 
+    train = ~test;
+    train_pca = pca(imgs(train,:)','NumComponents',cols_pca);
+    train_lab = labels(train,:);
+    test_pca = pca(imgs(test,:)','NumComponents',cols_pca);
+    test_lab = labels(test,:);
+    
+    SVMModel = fitcecoc(train_pca,train_lab);
+    [pred_lab,score] = predict(SVMModel,test_pca);
+    acc = sum(test_lab==pred_lab) / length(test_lab);
+    
+    disp([i,acc])
+end
+
+
+

### 2019-12-24 191204_DIP_Fin/work_jk/f_Quanta_Gabor.m

@@ -1,0 +1,60 @@
+function QGF = f_Quanta_Gabor(Gabor,np,nm)
+
+A_p = max(max(Gabor));
+A_m = min(min(Gabor));
+
+
+
+for k=1:np+1
+    g_p(k) = A_p/(2*np+1)*(2*(k-1));
+end
+
+for k=1:nm+1
+    g_m(k) = A_m/(2*nm+1)*(2*(k-1));
+end
+
+step_p = g_p(2)-g_p(1);         % step size Plus
+step_m = g_m(2)-g_m(1);         % step size Minus
+
+level_p(1) = 0;
+level_m(1) = 0;
+
+level_p(2) = step_p * (1/2);
+level_m(2) = step_m * (1/2);
+
+if np>=2
+    for k=3:np+1
+        level_p(k) = level_p(k-1)+step_p*(k-2);
+    end
+end
+
+if nm>=2
+    for k=3:nm+1
+        level_m(k) = level_m(k-1)+step_m*(k-2);        
+    end
+end
+
+for y=1:size(Gabor,1)
+    for x=1:size(Gabor,2)
+        val = Gabor(y,x);
+        if(val>=0)
+            for k=1:np
+                if( (val>=level_p(k)) && (val<level_p(k+1)) )
+                    QGF(y,x) = g_p(k);
+                elseif( val>=level_p(k+1) )
+                    QGF(y,x) = g_p(k+1);
+                end
+            end
+        elseif(val<0)
+            for k=1:nm
+                if( (val<=level_m(k)) && (val>level_m(k+1)) )
+                    QGF(y,x) = g_m(k);
+                elseif(val <= level_m(k+1))
+                   QGF(y,x) = g_m(k+1);                     
+                end
+            end
+        end   
+    end
+end
+
+

### 2019-12-24 191204_DIP_Fin/work_jk/origin_gabor.m

@@ -1,0 +1,30 @@
+function gb = origin_gabor(X, Y, sigma, theta, omega)
+		%sigma = scale (in paper root45)
+		%theta = orientation (in paper 6)
+		%omega = frequency (in paper 1/12)
+        %x,y = window size(in paper 33,33)
+   
+       filter_radius = floor(X/2);
+       [x, y] = meshgrid(-filter_radius:filter_radius, -filter_radius:filter_radius);
+        
+        
+        
+		
+        e = exp(1); 
+            
+        r = 1; %constant (values ~=1 -> eliptical filter)
+
+        R1 = x.*cos(theta) + y.*sin(theta);
+        R2 =-x.*sin(theta) + y.*cos(theta);
+
+        expFactor = -1/2 * ( (R1/sigma).^2 + (R2/(r*sigma)).^2  );
+
+        gauss = 1 / ( sqrt(r*pi)*sigma) ;
+        gauss =  gauss .* e.^expFactor;
+
+        gaborReal = gauss .* cos(omega*R1);
+        gaborImag = gauss .* sin(omega*R1);
+
+        kernel = gaborReal + gaborImag*1i;
+        gb = kernel'; 
+end

### 2019-12-24 191204_DIP_Fin/work_jk/run.m

@@ -1,0 +1,31 @@
+clear;
+
+img1_red = imread('tr1.jpg');
+img2_blue = imread('tb1.jpg');
+
+diffimage = diffimage(img1_red,img2_blue,0.5);
+%classifier
+gaborcanny = simplegabor_and_canny(diffimage);
+
+figure(1);
+subplot(1,6,1);
+imshow(gaborcanny(:,:,1));
+subplot(1,6,2);
+imshow(gaborcanny(:,:,2));
+subplot(1,6,3);
+imshow(gaborcanny(:,:,3));
+subplot(1,6,4);
+imshow(gaborcanny(:,:,4));
+subplot(1,6,5);
+imshow(gaborcanny(:,:,5));
+subplot(1,6,6);
+imshow(gaborcanny(:,:,6));
+
+figure(3);
+Ma = max(gaborcanny,[],3);
+imshow(Ma);
+se1 = strel('line',3,0); %change(canny parameter)
+T = edge(real(Ma),'Canny',0.5);
+BW2 = imdilate(T,se1);
+figure(4);
+imshow(BW2);

### 2019-12-24 191204_DIP_Fin/work_jk/simplegabor_and_canny.m

@@ -1,0 +1,38 @@
+function simplegabor_and_canny = simplegabor_and_canny(image)
+
+x = 31; %change
+y = 31; %change
+sigma = 2; %change
+omega = x/(128/31); %change
+
+theta   = 0; %fix
+N = 6; %fix
+
+
+se1 = strel('line',3,0); %change(canny parameter)
+
+img_out = zeros(size(image,1),size(image,2), N);
+BW2 = zeros(size(image,1),size(image,2), N);
+GB = zeros(31,31, N);
+for n=1:N
+    %gabor filter
+    gb = origin_gabor(x, y, sigma, theta, omega);
+    GB(:,:,n) = gb;
+    QCF = f_Quanta_Gabor(gb,1,2); 
+    
+    
+    img_out(:,:,n) = imfilter(image, QCF, 'symmetric');
+     
+    %canny edge detection 
+    T = edge(real(img_out(:,:,n)),'Canny',0.5);
+    BW2(:,:,n) = imdilate(T,se1);
+   
+    
+    theta = theta + 30;
+end
+
+%simplegabor_and_canny = BW2;
+%simplegabor_and_canny = GB;
+simplegabor_and_canny = img_out;
+
+
